### 2012-10-15 doc/ops/report.tex
Added git ignore for latex and initial commit of OPS

% IY Report

%
% WORD COUNT COMMAND
% 
%  untex -m -e -o report.tex | wc -w
%

%The document is a report
\documentclass[12pt,a4paper]{article}

%define horizontal rule
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}

\usepackage{fullpage}

%use the listings package
\usepackage{listings}
%use the English language
\usepackage[english]{babel}
%use graphics
\usepackage{graphicx}
%use wrap figures
\usepackage{wrapfig}
%geometry stuffs
\usepackage{lscape}
%use natbib bibliography package
\usepackage{natbib}
%use harvard bibliography package
%\usepackage{harvard}	
%use captions
\usepackage{caption}
%use multi-row tables
\usepackage{multirow}
\usepackage{url}

\begin{document}

%use harvard citations
%\citationstyle{agsm}

%include the title page
\input{title}

%some definitions for paragraph layout stuff
\setlength{\parindent}{0pt}
\setlength{\parskip}{1.5ex plus 0.5ex minus 0.2ex}

\tableofcontents

\pagebreak

\section{Introduction to IBM and its Organisational Structure}

\subsection{100 Years of Innovation}
2011 marked the centennial anniversary for IBM as a business.  The company was
founded in 1911 as the result of a merger between three $19^{th}$-Century
companies: the Tabulating Machine Company, the International Time Recording
Company and the Computing Scale Company of America. In 1914, Thomas J. Watson
Sr. joined the company shifting the direction of the company to multinational
technology consultation.

\subsection{IBM Today}

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{./company.png}
\caption{A diagram of IBM's internal corporate structure}
\end{figure}
Today, IBM remains one of the largest technology corporations on the
international market, employing over 400,000 people across more than 170
countries. The current CEO, Ginni Rometty, replaced Sam Palmisano, former CEO of
nine years, in January 2012. Rometty has been with IBM since 1981, joining the
firm as a systems engineer. She held the role of senior vice president and group
executive for sales, marketing and strategy for three years previous to her
promotion to CEO. Rometty was also the first female CEO of the firm.

IBM is mainly based in the United States and remains a US-registered company.
However, the company operates on a global scale with three separate business
units servicing the Americas, Europe with the Middle East and Asia (EMEA),   
Asia and the Pacific. Each regional unit is divided up into operational units
based on function: Global Business Services (GBS) provide consulting and
procurement services; the Software Group (SWG) maintains and services IBM’s
software portfolio. There are also separate divisions for research, sales and
distribution and for corporate strategy and management.

SWG is divided up into teams, each one servicing one of IBM’s software products
from the portfolio. Each of these teams can be further subdivided into teams of
developers, testers and customer service engineers. During my placement, I
worked as part of the CICS Testing infrastructure team on the IBM Hursley campus
(for further details, see Section \ref{sec:myteam}).

\subsection{Hursley}
Hursley House is a mansion constructed in the $18^{th}$ Century in rural
Hampshire by William Heathcode, during the reign of King George I. The house was
used in World Wars I and II as a military hospital and as a base of operations
for Vickers Aviation who produced the world famous Spitfire, during their time
at at the site.

In 1958, IBM purchased the site and started using Hursley House for research and
development purposes and as a temporary home. In 1963, the company purchased the
100 acres of land surrounding the house and began to establish a more permanent
base, erecting a modern office complex in the house gardens. The main house no
longer contains any development teams, remaining home only to the senior staff
members and Hursley Lab Director, John McLean.

The rest of the site is made up of office blocks connected internally by glass
walkways. Each block is mainly devoted to a specific software product or a
family of products. Hursley currently houses development and service teams for
many of IBM’s middleware software packages including WebSphere products such as
the MQSeries message propagation server and the WebSphere Application Server
(WAS), CICS and CICS Explorer, and IBM Java Runtime.

Hursley also houses Emerging Technology Services where experimental technology
is tested by IBM and used to develop prototype solutions for clients. ETS is the
only Research and Development department on site. All of the other departments
at Hursley are specifically for development and service of existing software and
fall under the management of IBM’s Software Group business unit.

\section{IBM's Technical and Application Environment}

\subsection{Office and Development Environment}
Upon starting my job at IBM I was given an IBM Thinkpad T60p for my every-day
work and business. Thinkpad laptops and docks are standard issue within the
company as they allow employees to work using external peripherals such as
full mouse and keyboard and external monitor in their office, to take their
laptops with them to meetings and work from home out of hours.

All interns were given identical laptop hardware which came with a pre-installed
Windows XP image customised with IBM utilities . Locks and bags were also
distributed to all interns and we were encouraged to lock our laptops to our
desks at all times, since many of us were based in open-plan offices.

As part of the standard IBM desktop environment, all employees were given a copy
of Lotus Notes for internal communication and organisation. Notes was also used
for organisation of meetings and propagation of meeting invitations across the
site. All employees are also given a copy of Lotus Sametime, an instant
messaging client for communication within large businesses. This made contacting
colleagues for help and assistance a lot easier since you could instantly talk
to anyone currently logged on to a computer terminal connected to the IBM
network.

For editing documents and presentations, all interns were given a copy of IBM 
Lotus Symphony. Symphony is a fork from the OpenOffice.org office suite, an open
source office suite originally started by Sun Microsystems before being bought
out by Oracle. I found Symphony to be quite unstable and was advised to use 
LibreOffice instead, since the document file formats are compatible. In January,
it was announced that IBM will stop developing Symphony, instead contributing to
the OpenOffice project \cite{SunsetSymphony}.

For programming and version control purposes, IBM supplied me with a copy of
Rational Team Concert for System Z. This is a suite of software that sits on top
of the Open Source Eclipse IDE providing version control capability and a
graphical interface for editing data remotely on IBM mainframe systems running
zOS. The package also provides extensions to eclipse for the syntax highlighting
and auto-completion for the programming languages REXX and PL/1.

To complement the Eclipse development suite, my team also use a set of
commandline utilities for development and administration of the test machines.
The x3270 \cite{x3270Site} terminal emulator was used for remote administration
of the team's z/OS test machines whilst SSH and FTP could be used for remote
interaction with the mainframe's Unix System Services interface.

Despite being given a Windows XP installation to start with, I was advised by my
team to install IBM's Ubuntu-based Linux distribution, OCDC, instead. Most of my
team used Linux themselves and I found that many of IBM's software packages ran
a lot more smoothly on a Linux installation than in Windows.

\subsection{Development Server Environment}
%---------------------------------
%YOU NEED A CITATION HERE.
%
%-------------------------------
Much of IBM's software is still designed for z/OS-based mainframe machines, the 
current generation of which, are some of the most powerful enterprise hardware
solutions available in the global marketplace. CICS, the product that I helped
to develop, is one such software package.

\subsubsection{CICS}
During my placement, I was tasked with working on IBM's CICS Transaction Server.
CICS is a commercial middleware package that runs on mainframes and provides
secure and stable transaction handling. CICS was originally released in 1969 and
developed and maintained by a team at the IBM Development Centre in Des Plaines,
Illinois. In earlier versions, CICS was bundled for free with IBM mainframe
hardware at no extra cost. IBM customers were quick to understand the value of
CICS which quickly became one of IBM's most important software packages, helping
to raise over \$60 Billion in hardware revenue. However, IBM Executives did not
see the value of the software package and CICS was sent to Hursley to be
developed and maintained to allow other software packages to be developed in the
US. Despite this, continued development at Hursley park has enabled CICS to
continue to be one of IBM's flagship software packages.  In 2004, IBM reported
that CICS is now used by over ninety per cent of the Fortune 500 companies and many
Government entities now also use the product.

CICS is provided as a Software Development Middleware and users write their own
applications to make use of its features and API. IBM provide bindings and
compilers to enable applications to interact with CICS through languages such as
C, COBOL and PL/1. More recently, Java support has been integrated into CICS,
allowing the use of OSGi bundles within the application environment using IBM's
JRE.

\subsubsection{z/OS}
The IBM Mainframes mainly run the proprietary operating system z/OS. z/OS is the
spiritual successor to IBM's OS/390 and provides many of the same features 
and functions as its predecessor. The operating system is designed to provide
enterprise security and performance on mainframe systems.

For developers only familiar with UNIX and Windows-style operating systems, z/OS 
requires a very steep learning curve. The operating system is unique in its
approach to storage, memory management and security. Programs cannot be 
directly executed on z/OS and instead must be bootstrapped through the use
of Job Control Language (JCL).

\subsubsection{DB2 and MQ}
IBM's policy of reusing much of their own software within new products under
development meant that despite my position in the CICS team, I was also exposed
to many other products in their software portfolio, particularly during my work
on JAT+ (see Section \ref{sec:jatp}).

\section{Job Role}
\label{sec:myteam}
My job role was to serve as part of the CICS Test Infrastructure Team who wrote
and maintained software test infrastructure systems and tools. Our team worked
alongside the CICS Functional Verification (FV) team who were responsible for
testing new CICS code to make sure that it worked as documented before it was
released to the public.

\subsection{RTS}
The FV team used an internal product called Regression Testing Suite (RTS) to
run automated suites of test scripts against the product and check for
regressions as well as any new defects in the code. The infrastructure team and
I were responsible for servicing the mainframes that RTS ran on as well as
writing new features and fixing defects for the RTS framework itself.

Upon my initial placement within the team, my main job role was to help service
and support RTS and related test systems. My day to day role involved
programming in Perl and the IBM scripting language REXX. REXX is an interpreted
language which is not widely used in the larger computing world. However, REXX
is a very popular language in mainframe environments and is the primary
development language for RTS.

RTS can be accessed through a web interface or from a mainframe terminal.
Testers provide a script which specifies the nature of the CICS instances to be
set up, a set of operations to be carried out by the software, and then any
steps required at shutdown. Scripts can be triggered through either of the above
interfaces or scheduled to run on an automated basis.

My duties were often to resolve defects raised against specific parts of the RTS
code-base and occasionally to implement new functionality as required by testing
team members. Unstable code had to be thoroughly tested on the RTS development
servers before being deployed to the primary FV test servers to prevent CICS
tests from failing due to faulty RTS code. The team was also prohibited from
making any changes to RTS on a Friday afternoon to prevent automated test runs
scheduled over the weekend from failing due to unstable infrastructure code.
Stable RTS code that functioned correctly under test for a week was placed in
version control.

The team used a legacy IBM version control system for RTS code. Although the
preferred version control system for IBM systems is Rational Team Concert, 
RTS shared several components with one of the MQ testing utilities. The code
was eventually moved over to RTC towards the end of my placement when the MQ
team also migrated to the new version control tool.

\subsection{COMP4}
After a few months, I was assigned to a new Java project under joint management
of the CICS Infrastructure and the Functional Verification teams. The project was
started by a fellow intern and provided a graphical front end for the compilation
of CICS supported languages on the testing mainframes.

Our system was named COMP4 as it replaced an existing interface named COMP3. It was
designed as an Eclipse plugin. It added a context menu option to "Compile with
COMP4" when inspecting any CICS compatible source file. The system then filled
out a JCL template for execution on the mainframe and sent the job to the 
remote system to be run. Once a specified period of time had passed, the job 
result was collected from the mainframe and displayed to the user in the UI.
The system was also designed in a multi-threaded way which meant that concurrent
compilation of several source files was supported natively by our plugin.

Not only was COMP4 a real test of my Java and OSGi programming knowledge, but it
provided me with an opportunity to hone my management and communication skills.
I was brought in to supervise Daniel, my colleague on the project, and help to
organise the architecture of the application. Daniel was not confident at
programming or application design. Although it was quite tempting to simply do
the programming myself and complete the job on my own, I wanted to facilitate 
Daniel in his learning. I was able to tutor him and I
helped him to improve his programming skills. This in turn, allowed me to put into
practice my mentoring skills which I'd previously acquired from my work as a
demonstrator at Aberystwyth University.

Daniel and I were able to make several critical changes to the way that COMP4
had been designed to speed up development. Our managers had suggested that we
use ANTz, an IBM extension to the Java ANT build engine, for the COMP4 backend.
ANTz is very complicated and would have required a steep learning curve for both
of us. The product was also very heavyweight and would have been over-complicated
for COMP4's needs. Therefore, Daniel and I decided to engineer our own back end
using Apache Velocity as a templating engine and submitting pre-generated JCL
jobs to the mainframe. This solution proved to be much more apt than ANTz and we
received much acclaim for our work. The change also allowed us to release our
tooling a month ahead of the specified deadline, again helping both of our
reputations within the department.

\subsection{JAT+}
\label{sec:jatp}
When I arrived at IBM in July, RTS was already an aging system and had been used
for testing CICS and Functional Verification for several years. RTS was also
very unstable and the complicated nature of the shared source repository meant
that there were often many problems with the system. After my success on the
COMP4 project, I was asked to help design and implement a replacement test
system for CICS that would be more stable, efficient and easier to use.

It was decided that the project should be written in Java and would make use of
existing technology such as Eclipse and J-Unit, the widely used Java unit
testing framework. Like COMP4, the product was designed as an Eclipse plugin
since most of the CICS developers use Eclipse for their day to day work and are
familiar with the IDE's interface. It was also designed to interface with
Eclipse's existing JUnit interface since many of the CICS developers use JUnit
already and are familiar with the framework. Reuse of JUnit also allowed us to
speed up development and avoid rewriting complicated test framework
functionality. It was decided that our product would be called Java Test Plus
(JAT+).

JAT+ facilitates the execution of CICS tests on a local instance of Eclipse by
running sets of remote commands over the network. Tests are provided in a JUnit
test class style with some special annotations and fields that specify which
CICS instances on the network to test etc. The plugin can automatically
provision a testing environment from a pool of available server resources.
Alternatively, the tester can manually set up their testing environment on the
mainframe to save time or test custom CICS functionality.

JAT+ also runs remotely on an automation server and CICS tests can be sent to
the server in OSGi bundles and tested as part of a regular schedule. The results
of remote tests can still be viewed in the eclipse JUnit results view as if they
had been locally executed.

My role on the project varied throughout my placement. I started off as a lead
developer on the back end of the project, building classes that facilitated the
initial setup and provisioning stages of test execution. This required me to
work closely with mainframes and networking libraries in order to execute the
necessary remote jobs and build CICS regions. Luckily, my work with COMP4
prepared me for this task. Once the initial framework was in place, I was asked
to develop several Eclipse User Interface components for the project to make it
more usable by testers. I implemented several new views and context menu options
to make using the plugin more convenient and usable.

Towards the end of my placement, it was decided that JAT+ would be adopted as 
the primary CICS testing framework. Therefore, all of the existing automated
tests for CICS would need to be translated from the RTS format to the JAT+ 
format. There was a very large quantity of automated test suites that had 
already been written for RTS; it was decided that the conversion process should
be automated to minimise the amount of time spent converting the tests. My last
role before leaving IBM in August was to design and implement the conversion 
engine that would translate each of the tests.

\subsection{Extra Roles \& Giveback}
As well as their main job role, IBM employees are expected to contribute up to 
50\% of their working day to side-projects. This practice is known internally
as "Giveback." During my placement I was involved in several Giveback projects
from the very beginning of my placement.

\subsubsection{PHP \& Java classes}
Towards the beginning of my placement, a notice was sent out requesting
volunteers to teach other IBM employees on a range of technical topics including
basic introductions to Java and PHP. I had previous experience of teaching Java
from my work as a Demonstrator at Aberystwyth University, and I had a background
in writing PHP applications from when I first started building websites as a
teenager. I volunteered and was accepted as a teacher/lecturer on both topics.

The PHP course I taught ran over a period of 4 weeks. I prepared and delivered
each presentation without any guidance aside from a briefing on the target
audience and their skill level. The first lecture was a brief introduction to
PHP and its main applications. The second lecture was a brief summary on how to
set up PHP in an Apache environment on your computer and to create a hello world
web page. The final two sessions summarised some standard PHP programming
practices and I provided worksheets and solutions to the audience to help them
to get to grips with the language more effectively. There were also Q\&A
sessions at the end of each lecture and I was able to help many of the audience
members in person.

The Java course ran in a slightly different way. Since more people seemed to be
familiar with the language, there were as many volunteer tutors as there were 
students. It was decided that the group would split into two: Those with no 
technical background at all who wanted to learn to program, and those with 
a technical background in other languages who wanted to learn the language Java.
I was asked to help teach the more technical group. Weekly sessions were run for
approximately 12 weeks at the start of our placement. We also set a programming
challenge for the students to help them to get used to the language and to 
prompt them to ask any questions about topics that confused them.

To begin with, each tutor took it in turns to present a Java concept to the
group. All tutors attended the sessions and were able to add their comments to
the material if they felt that the presenter had forgotten anything or hadn't
explained something in detail. After a period of several weeks, the students 
got used to the core language concepts and the group evolved more into a 
reading/common interest group. We would meet up weekly for a Q\&A session and 
to offer each other tips and advice for Java programming in our day jobs.

After a few weeks of Q\&A, the students decided that they had learned enough 
about Java to be confident using it in their day jobs and the sessions came 
to an end.

\subsubsection{Activity Centre Day}
As well as technical activities, IBM Giveback also offers employees the 
opportunity to go out into the community and do something completely different.
In August 2011, I was asked to go with a team of approximately 50 other IBM
employees to visit a charity-run activity centre in the New Forest, Hampshire.
We spent the day carrying out maintenance tasks at the center including 
cutting grass, trimming back bushes and weeding. Once we'd finished our duties
we were allowed to do some of the activities including rock climbing and raft
building.

\subsubsection{Web Design Skills Workshop}
In March, I was contacted by one of my colleagues to ask for my assistance in
the organisation and delivery of a web design workshop for a small group of
secondary school children because of my knowledge of the PHP language and HTML. 
Three interns, including myself, went out to Romsey School, near Hursley,for 
half a day to deliver the workshop to the children and provide an hour of 1:1
tuition. This experience allowed me to build upon my presentation and teaching
skills which I had already developed from my PHP Lectures and to learn on how
to present to a younger audience more effectively.

\subsubsection{Map Tool Project}
IBM Hursley is a large site with many offices and an inconsistent coordinate
system for navigating around the campus. There is currently a web tool which
provides a map of the site and can be queried to pinpoint the location of a
specific person or room at Hursley. Unfortunately, this tool is not very 
intuitive to use and the map output is difficult to understand. Some colleagues
and I decided that there was a room for improvement and set up a Giveback 
scheme in order to rewrite and improve the Hursley Map tool.

The team, lead by myself, consisted of 7 interns at the Hursley site. We met
weekly and spent half a day discussing and working on the new tool. The 
project was a great opportunity for me to meet many IBM employees as full 
analysis of the project required us to consult the on-site architect, the
previous owner of the map tool and the current web admin for the Hursley 
intranet.

We were told that site plans were available in a common format for all IBM
offices in the UK and that the new map tool could potentially be used by IBM on
a national or even global scale if it was successful. It was decided that the
new project would be written in PHP since most of the team were familiar with
the language and that we would use some mapping frameworks that are already
available to accelerate development.

Unfortunately, the 12 month time limit on our placements at IBM meant that we
were unable to complete the map tool before we left the company. Instead, we
found a group of interns from the 2012 intake to take over the project and I
ran a couple of short handover sessions to help familiarise them with the 
project codebase.

\section{Critical Evaluation}

During my year at IBM I learnt a lot about programming, working in large 
development communities and myself. Although I found the work challenging
to begin with, I quickly adapted to my new environment and was able to  
become a valued member of my team very quickly.

My first few weeks at work were incredibly difficult; the initial learning
curve at the time of joining my team was near vertical. My first few tasks
after joining the CICS Infrastructure Team were to make minor changes to 
some of the RTS software components. Having never seen a mainframe terminal
or worked with CICS, REXX, MVS or z/OS before, I found this task brutally 
challenging. This feeling was exaggerated by reports from some of my friends
that they were working on Java projects on Linux and Windows - environments
that I was a lot more familiar with at the beginning of my placement. I was
informed at the beginning of my placement that if I was not happy with my 
job, I could be found a new role elsewhere in the company. Although I was
tempted at this stage, I persevered and rose to the challenges that I faced.
After a few weeks of struggling and counsel from my team, I started to 
become proficient at my role and enjoyed my job a lot more. The knowledge I
acquired during my first few weeks at IBM  has definitely given me a much
stronger background in IBM software and hardware and has provided me with 
some hugely desirable skills for any employers that use IBM products. After
my experience I think that IBM should certainly consider more avenues of 
support and initial new-starter education so that joining a new team is not
so much of a challenge and does not discourage new employees too much.

IBM's software product portfolio now consists largely of Eclipse-based 
graphical applications are written in Java. Although Java is a powerful
and flexible language, it was surprising to see how much faith the company
are putting into the language. Even mission critical systems like CICS 
that should be programmed in the lowest level languages possible to 
maximise speed and efficiency are being infiltrated by VM-based memory-
hungry Java \cite{cicsJava}. Personally, I feel that this is a
mistake and that development of such applications should continue in 
low level or Ahead-of-time compiled languages like C and COBOL. Unfortunately,
as long as universities continue to train students to be Java programmers, it
would be difficult to obtain a set of graduate employees with the necessary 
skills to maintain a COBOL or even a C-based system. However, as companies like
IBM move more towards apprenticeships, they are able to train new recruits as
they wish.

IBM have a dual management system for interns and graduates who join the 
company. I was assigned a line manager who oversaw my day to day work and
dealt with any problems I might have in my day job, and a Personal 
Development Manager who was assigned to help me make the most of my years
and nurture and develop my skill set. I feel that this system worked very 
well as it meant that there were always multiple avenues for dealing with
any problems that may have arisen from conflicts during my day job, and 
provided me with two equally useful but very different sets of advice. 
There were a few occasions when the dual management system added extra
complication to my role and caused confusion. For example, when I went
out on Giveback schemes, I had to seek approval from both managers. 
Nevertheless, I feel that the benefits of the system certainly outweighed 
the extra work in these cases.

I definitely noticed my changing identity as I progressed though the IBM
‘community of practice’ \cite{Communities}. Communities of practice are
groups of people who share a concern or a passion for something they do and
learn how to do it better as they interact regularly. At the beginning, I was
definitely a 'newcomer,' situated on the periphery and, although I was not
exactly an 'old timer' by the end of my thirteen months, I was certainly an
experienced 'practitioner' compared to those who had just begun their year with
IBM. During my year, learning was not simply a process of assimilation nor of
learning transfer but changed my very identity as mentors became colleagues and
then came to me to ask how to approach certain objectives. For instance, at the
beginning of the year as a 'newcomer' I struggled to understand how to use the 
mainframe terminal system and 
frequently sought advice from my team leader. Towards
the end of my time at IBM my advice regarding Java programming, specifically the
Eclipse Plug-in development, was highly-sought by my colleagues.

As I built up my bank of the 'tacit knowledge' \cite{SocialKnowing} of the IBM, 
community, I found that I
not only defined myself through what I could do with that knowledge, but I also
defined myself through what I no longer needed to do to acquire the necessary
knowledge. That is, I recognised the transition from someone who needed help   
to someone who provided help.

In summary, I am a very different person from when I left Aberystwyth University
in the second year of my studies. The value of my year in industry has not been
what it will add to my CV, nor in a healthy bank balance. The value has been in
the skills I have developed and connections I have made. I feel that these new
skills will help me both with my final year of studies and as an Information 
Technology professional moving forward as a new graduate.

\pagebreak

\bibliography{report}
%set style to plain
\bibliographystyle{plain}

\end{document}

### 2012-10-15 doc/ops/report.tex
Trimmed the IY stuff from ops report

@@
-% IY Report
-
-%
-% WORD COUNT COMMAND
-% 
-%  untex -m -e -o report.tex | wc -w
-%
+% Outline Project Specification Report
 
@@
 
-\subsection{100 Years of Innovation}
-2011 marked the centennial anniversary for IBM as a business.  The company was
-founded in 1911 as the result of a merger between three $19^{th}$-Century
-companies: the Tabulating Machine Company, the International Time Recording
-Company and the Computing Scale Company of America. In 1914, Thomas J. Watson
-Sr. joined the company shifting the direction of the company to multinational
-technology consultation.
-
-\subsection{IBM Today}
-
-\begin{figure}[!ht]
-\includegraphics[width=\textwidth]{./company.png}
-\caption{A diagram of IBM's internal corporate structure}
-\end{figure}
-Today, IBM remains one of the largest technology corporations on the
-international market, employing over 400,000 people across more than 170
-countries. The current CEO, Ginni Rometty, replaced Sam Palmisano, former CEO of
-nine years, in January 2012. Rometty has been with IBM since 1981, joining the
-firm as a systems engineer. She held the role of senior vice president and group
-executive for sales, marketing and strategy for three years previous to her
-promotion to CEO. Rometty was also the first female CEO of the firm.
-
-IBM is mainly based in the United States and remains a US-registered company.
-However, the company operates on a global scale with three separate business
-units servicing the Americas, Europe with the Middle East and Asia (EMEA),   
-Asia and the Pacific. Each regional unit is divided up into operational units
-based on function: Global Business Services (GBS) provide consulting and
-procurement services; the Software Group (SWG) maintains and services IBM’s
-software portfolio. There are also separate divisions for research, sales and
-distribution and for corporate strategy and management.
-
-SWG is divided up into teams, each one servicing one of IBM’s software products
-from the portfolio. Each of these teams can be further subdivided into teams of
-developers, testers and customer service engineers. During my placement, I
-worked as part of the CICS Testing infrastructure team on the IBM Hursley campus
-(for further details, see Section \ref{sec:myteam}).
-
-\subsection{Hursley}
-Hursley House is a mansion constructed in the $18^{th}$ Century in rural
-Hampshire by William Heathcode, during the reign of King George I. The house was
-used in World Wars I and II as a military hospital and as a base of operations
-for Vickers Aviation who produced the world famous Spitfire, during their time
-at at the site.
-
-In 1958, IBM purchased the site and started using Hursley House for research and
-development purposes and as a temporary home. In 1963, the company purchased the
-100 acres of land surrounding the house and began to establish a more permanent
-base, erecting a modern office complex in the house gardens. The main house no
-longer contains any development teams, remaining home only to the senior staff
-members and Hursley Lab Director, John McLean.
-
-The rest of the site is made up of office blocks connected internally by glass
-walkways. Each block is mainly devoted to a specific software product or a
-family of products. Hursley currently houses development and service teams for
-many of IBM’s middleware software packages including WebSphere products such as
-the MQSeries message propagation server and the WebSphere Application Server
-(WAS), CICS and CICS Explorer, and IBM Java Runtime.
-
-Hursley also houses Emerging Technology Services where experimental technology
-is tested by IBM and used to develop prototype solutions for clients. ETS is the
-only Research and Development department on site. All of the other departments
-at Hursley are specifically for development and service of existing software and
-fall under the management of IBM’s Software Group business unit.
-
-\section{IBM's Technical and Application Environment}
-
-\subsection{Office and Development Environment}
-Upon starting my job at IBM I was given an IBM Thinkpad T60p for my every-day
-work and business. Thinkpad laptops and docks are standard issue within the
-company as they allow employees to work using external peripherals such as
-full mouse and keyboard and external monitor in their office, to take their
-laptops with them to meetings and work from home out of hours.
-
-All interns were given identical laptop hardware which came with a pre-installed
-Windows XP image customised with IBM utilities . Locks and bags were also
-distributed to all interns and we were encouraged to lock our laptops to our
-desks at all times, since many of us were based in open-plan offices.
-
-As part of the standard IBM desktop environment, all employees were given a copy
-of Lotus Notes for internal communication and organisation. Notes was also used
-for organisation of meetings and propagation of meeting invitations across the
-site. All employees are also given a copy of Lotus Sametime, an instant
-messaging client for communication within large businesses. This made contacting
-colleagues for help and assistance a lot easier since you could instantly talk
-to anyone currently logged on to a computer terminal connected to the IBM
-network.
-
-For editing documents and presentations, all interns were given a copy of IBM 
-Lotus Symphony. Symphony is a fork from the OpenOffice.org office suite, an open
-source office suite originally started by Sun Microsystems before being bought
-out by Oracle. I found Symphony to be quite unstable and was advised to use 
-LibreOffice instead, since the document file formats are compatible. In January,
-it was announced that IBM will stop developing Symphony, instead contributing to
-the OpenOffice project \cite{SunsetSymphony}.
-
-For programming and version control purposes, IBM supplied me with a copy of
-Rational Team Concert for System Z. This is a suite of software that sits on top
-of the Open Source Eclipse IDE providing version control capability and a
-graphical interface for editing data remotely on IBM mainframe systems running
-zOS. The package also provides extensions to eclipse for the syntax highlighting
-and auto-completion for the programming languages REXX and PL/1.
-
-To complement the Eclipse development suite, my team also use a set of
-commandline utilities for development and administration of the test machines.
-The x3270 \cite{x3270Site} terminal emulator was used for remote administration
-of the team's z/OS test machines whilst SSH and FTP could be used for remote
-interaction with the mainframe's Unix System Services interface.
-
-Despite being given a Windows XP installation to start with, I was advised by my
-team to install IBM's Ubuntu-based Linux distribution, OCDC, instead. Most of my
-team used Linux themselves and I found that many of IBM's software packages ran
-a lot more smoothly on a Linux installation than in Windows.
-
-\subsection{Development Server Environment}
-%---------------------------------
-%YOU NEED A CITATION HERE.
-%
-%-------------------------------
-Much of IBM's software is still designed for z/OS-based mainframe machines, the 
-current generation of which, are some of the most powerful enterprise hardware
-solutions available in the global marketplace. CICS, the product that I helped
-to develop, is one such software package.
-
-\subsubsection{CICS}
-During my placement, I was tasked with working on IBM's CICS Transaction Server.
-CICS is a commercial middleware package that runs on mainframes and provides
-secure and stable transaction handling. CICS was originally released in 1969 and
-developed and maintained by a team at the IBM Development Centre in Des Plaines,
-Illinois. In earlier versions, CICS was bundled for free with IBM mainframe
-hardware at no extra cost. IBM customers were quick to understand the value of
-CICS which quickly became one of IBM's most important software packages, helping
-to raise over \$60 Billion in hardware revenue. However, IBM Executives did not
-see the value of the software package and CICS was sent to Hursley to be
-developed and maintained to allow other software packages to be developed in the
-US. Despite this, continued development at Hursley park has enabled CICS to
-continue to be one of IBM's flagship software packages.  In 2004, IBM reported
-that CICS is now used by over ninety per cent of the Fortune 500 companies and many
-Government entities now also use the product.
-
-CICS is provided as a Software Development Middleware and users write their own
-applications to make use of its features and API. IBM provide bindings and
-compilers to enable applications to interact with CICS through languages such as
-C, COBOL and PL/1. More recently, Java support has been integrated into CICS,
-allowing the use of OSGi bundles within the application environment using IBM's
-JRE.
-
-\subsubsection{z/OS}
-The IBM Mainframes mainly run the proprietary operating system z/OS. z/OS is the
-spiritual successor to IBM's OS/390 and provides many of the same features 
-and functions as its predecessor. The operating system is designed to provide
-enterprise security and performance on mainframe systems.
-
-For developers only familiar with UNIX and Windows-style operating systems, z/OS 
-requires a very steep learning curve. The operating system is unique in its
-approach to storage, memory management and security. Programs cannot be 
-directly executed on z/OS and instead must be bootstrapped through the use
-of Job Control Language (JCL).
-
-\subsubsection{DB2 and MQ}
-IBM's policy of reusing much of their own software within new products under
-development meant that despite my position in the CICS team, I was also exposed
-to many other products in their software portfolio, particularly during my work
-on JAT+ (see Section \ref{sec:jatp}).
-
-\section{Job Role}
-\label{sec:myteam}
-My job role was to serve as part of the CICS Test Infrastructure Team who wrote
-and maintained software test infrastructure systems and tools. Our team worked
-alongside the CICS Functional Verification (FV) team who were responsible for
-testing new CICS code to make sure that it worked as documented before it was
-released to the public.
-
-\subsection{RTS}
-The FV team used an internal product called Regression Testing Suite (RTS) to
-run automated suites of test scripts against the product and check for
-regressions as well as any new defects in the code. The infrastructure team and
-I were responsible for servicing the mainframes that RTS ran on as well as
-writing new features and fixing defects for the RTS framework itself.
-
-Upon my initial placement within the team, my main job role was to help service
-and support RTS and related test systems. My day to day role involved
-programming in Perl and the IBM scripting language REXX. REXX is an interpreted
-language which is not widely used in the larger computing world. However, REXX
-is a very popular language in mainframe environments and is the primary
-development language for RTS.
-
-RTS can be accessed through a web interface or from a mainframe terminal.
-Testers provide a script which specifies the nature of the CICS instances to be
-set up, a set of operations to be carried out by the software, and then any
-steps required at shutdown. Scripts can be triggered through either of the above
-interfaces or scheduled to run on an automated basis.
-
-My duties were often to resolve defects raised against specific parts of the RTS
-code-base and occasionally to implement new functionality as required by testing
-team members. Unstable code had to be thoroughly tested on the RTS development
-servers before being deployed to the primary FV test servers to prevent CICS
-tests from failing due to faulty RTS code. The team was also prohibited from
-making any changes to RTS on a Friday afternoon to prevent automated test runs
-scheduled over the weekend from failing due to unstable infrastructure code.
-Stable RTS code that functioned correctly under test for a week was placed in
-version control.
-
-The team used a legacy IBM version control system for RTS code. Although the
-preferred version control system for IBM systems is Rational Team Concert, 
-RTS shared several components with one of the MQ testing utilities. The code
-was eventually moved over to RTC towards the end of my placement when the MQ
-team also migrated to the new version control tool.
-
-\subsection{COMP4}
-After a few months, I was assigned to a new Java project under joint management
-of the CICS Infrastructure and the Functional Verification teams. The project was
-started by a fellow intern and provided a graphical front end for the compilation
-of CICS supported languages on the testing mainframes.
-
-Our system was named COMP4 as it replaced an existing interface named COMP3. It was
-designed as an Eclipse plugin. It added a context menu option to "Compile with
-COMP4" when inspecting any CICS compatible source file. The system then filled
-out a JCL template for execution on the mainframe and sent the job to the 
-remote system to be run. Once a specified period of time had passed, the job 
-result was collected from the mainframe and displayed to the user in the UI.
-The system was also designed in a multi-threaded way which meant that concurrent
-compilation of several source files was supported natively by our plugin.
-
-Not only was COMP4 a real test of my Java and OSGi programming knowledge, but it
-provided me with an opportunity to hone my management and communication skills.
-I was brought in to supervise Daniel, my colleague on the project, and help to
-organise the architecture of the application. Daniel was not confident at
-programming or application design. Although it was quite tempting to simply do
-the programming myself and complete the job on my own, I wanted to facilitate 
-Daniel in his learning. I was able to tutor him and I
-helped him to improve his programming skills. This in turn, allowed me to put into
-practice my mentoring skills which I'd previously acquired from my work as a
-demonstrator at Aberystwyth University.
-
-Daniel and I were able to make several critical changes to the way that COMP4
-had been designed to speed up development. Our managers had suggested that we
-use ANTz, an IBM extension to the Java ANT build engine, for the COMP4 backend.
-ANTz is very complicated and would have required a steep learning curve for both
-of us. The product was also very heavyweight and would have been over-complicated
-for COMP4's needs. Therefore, Daniel and I decided to engineer our own back end
-using Apache Velocity as a templating engine and submitting pre-generated JCL
-jobs to the mainframe. This solution proved to be much more apt than ANTz and we
-received much acclaim for our work. The change also allowed us to release our
-tooling a month ahead of the specified deadline, again helping both of our
-reputations within the department.
-
-\subsection{JAT+}
-\label{sec:jatp}
-When I arrived at IBM in July, RTS was already an aging system and had been used
-for testing CICS and Functional Verification for several years. RTS was also
-very unstable and the complicated nature of the shared source repository meant
-that there were often many problems with the system. After my success on the
-COMP4 project, I was asked to help design and implement a replacement test
-system for CICS that would be more stable, efficient and easier to use.
-
-It was decided that the project should be written in Java and would make use of
-existing technology such as Eclipse and J-Unit, the widely used Java unit
-testing framework. Like COMP4, the product was designed as an Eclipse plugin
-since most of the CICS developers use Eclipse for their day to day work and are
-familiar with the IDE's interface. It was also designed to interface with
-Eclipse's existing JUnit interface since many of the CICS developers use JUnit
-already and are familiar with the framework. Reuse of JUnit also allowed us to
-speed up development and avoid rewriting complicated test framework
-functionality. It was decided that our product would be called Java Test Plus
-(JAT+).
-
-JAT+ facilitates the execution of CICS tests on a local instance of Eclipse by
-running sets of remote commands over the network. Tests are provided in a JUnit
-test class style with some special annotations and fields that specify which
-CICS instances on the network to test etc. The plugin can automatically
-provision a testing environment from a pool of available server resources.
-Alternatively, the tester can manually set up their testing environment on the
-mainframe to save time or test custom CICS functionality.
-
-JAT+ also runs remotely on an automation server and CICS tests can be sent to
-the server in OSGi bundles and tested as part of a regular schedule. The results
-of remote tests can still be viewed in the eclipse JUnit results view as if they
-had been locally executed.
-
-My role on the project varied throughout my placement. I started off as a lead
-developer on the back end of the project, building classes that facilitated the
-initial setup and provisioning stages of test execution. This required me to
-work closely with mainframes and networking libraries in order to execute the
-necessary remote jobs and build CICS regions. Luckily, my work with COMP4
-prepared me for this task. Once the initial framework was in place, I was asked
-to develop several Eclipse User Interface components for the project to make it
-more usable by testers. I implemented several new views and context menu options
-to make using the plugin more convenient and usable.
-
-Towards the end of my placement, it was decided that JAT+ would be adopted as 
-the primary CICS testing framework. Therefore, all of the existing automated
-tests for CICS would need to be translated from the RTS format to the JAT+ 
-format. There was a very large quantity of automated test suites that had 
-already been written for RTS; it was decided that the conversion process should
-be automated to minimise the amount of time spent converting the tests. My last
-role before leaving IBM in August was to design and implement the conversion 
-engine that would translate each of the tests.
-
-\subsection{Extra Roles \& Giveback}
-As well as their main job role, IBM employees are expected to contribute up to 
-50\% of their working day to side-projects. This practice is known internally
-as "Giveback." During my placement I was involved in several Giveback projects
-from the very beginning of my placement.
-
-\subsubsection{PHP \& Java classes}
-Towards the beginning of my placement, a notice was sent out requesting
-volunteers to teach other IBM employees on a range of technical topics including
-basic introductions to Java and PHP. I had previous experience of teaching Java
-from my work as a Demonstrator at Aberystwyth University, and I had a background
-in writing PHP applications from when I first started building websites as a
-teenager. I volunteered and was accepted as a teacher/lecturer on both topics.
-
-The PHP course I taught ran over a period of 4 weeks. I prepared and delivered
-each presentation without any guidance aside from a briefing on the target
-audience and their skill level. The first lecture was a brief introduction to
-PHP and its main applications. The second lecture was a brief summary on how to
-set up PHP in an Apache environment on your computer and to create a hello world
-web page. The final two sessions summarised some standard PHP programming
-practices and I provided worksheets and solutions to the audience to help them
-to get to grips with the language more effectively. There were also Q\&A
-sessions at the end of each lecture and I was able to help many of the audience
-members in person.
-
-The Java course ran in a slightly different way. Since more people seemed to be
-familiar with the language, there were as many volunteer tutors as there were 
-students. It was decided that the group would split into two: Those with no 
-technical background at all who wanted to learn to program, and those with 
-a technical background in other languages who wanted to learn the language Java.
-I was asked to help teach the more technical group. Weekly sessions were run for
-approximately 12 weeks at the start of our placement. We also set a programming
-challenge for the students to help them to get used to the language and to 
-prompt them to ask any questions about topics that confused them.
-
-To begin with, each tutor took it in turns to present a Java concept to the
-group. All tutors attended the sessions and were able to add their comments to
-the material if they felt that the presenter had forgotten anything or hadn't
-explained something in detail. After a period of several weeks, the students 
-got used to the core language concepts and the group evolved more into a 
-reading/common interest group. We would meet up weekly for a Q\&A session and 
-to offer each other tips and advice for Java programming in our day jobs.
-
-After a few weeks of Q\&A, the students decided that they had learned enough 
-about Java to be confident using it in their day jobs and the sessions came 
-to an end.
-
-\subsubsection{Activity Centre Day}
-As well as technical activities, IBM Giveback also offers employees the 
-opportunity to go out into the community and do something completely different.
-In August 2011, I was asked to go with a team of approximately 50 other IBM
-employees to visit a charity-run activity centre in the New Forest, Hampshire.
-We spent the day carrying out maintenance tasks at the center including 
-cutting grass, trimming back bushes and weeding. Once we'd finished our duties
-we were allowed to do some of the activities including rock climbing and raft
-building.
-
-\subsubsection{Web Design Skills Workshop}
-In March, I was contacted by one of my colleagues to ask for my assistance in
-the organisation and delivery of a web design workshop for a small group of
-secondary school children because of my knowledge of the PHP language and HTML. 
-Three interns, including myself, went out to Romsey School, near Hursley,for 
-half a day to deliver the workshop to the children and provide an hour of 1:1
-tuition. This experience allowed me to build upon my presentation and teaching
-skills which I had already developed from my PHP Lectures and to learn on how
-to present to a younger audience more effectively.
-
-\subsubsection{Map Tool Project}
-IBM Hursley is a large site with many offices and an inconsistent coordinate
-system for navigating around the campus. There is currently a web tool which
-provides a map of the site and can be queried to pinpoint the location of a
-specific person or room at Hursley. Unfortunately, this tool is not very 
-intuitive to use and the map output is difficult to understand. Some colleagues
-and I decided that there was a room for improvement and set up a Giveback 
-scheme in order to rewrite and improve the Hursley Map tool.
-
-The team, lead by myself, consisted of 7 interns at the Hursley site. We met
-weekly and spent half a day discussing and working on the new tool. The 
-project was a great opportunity for me to meet many IBM employees as full 
-analysis of the project required us to consult the on-site architect, the
-previous owner of the map tool and the current web admin for the Hursley 
-intranet.
-
-We were told that site plans were available in a common format for all IBM
-offices in the UK and that the new map tool could potentially be used by IBM on
-a national or even global scale if it was successful. It was decided that the
-new project would be written in PHP since most of the team were familiar with
-the language and that we would use some mapping frameworks that are already
-available to accelerate development.
-
-Unfortunately, the 12 month time limit on our placements at IBM meant that we
-were unable to complete the map tool before we left the company. Instead, we
-found a group of interns from the 2012 intake to take over the project and I
-ran a couple of short handover sessions to help familiarise them with the 
-project codebase.
-
-\section{Critical Evaluation}
-
-During my year at IBM I learnt a lot about programming, working in large 
-development communities and myself. Although I found the work challenging
-to begin with, I quickly adapted to my new environment and was able to  
-become a valued member of my team very quickly.
-
-My first few weeks at work were incredibly difficult; the initial learning
-curve at the time of joining my team was near vertical. My first few tasks
-after joining the CICS Infrastructure Team were to make minor changes to 
-some of the RTS software components. Having never seen a mainframe terminal
-or worked with CICS, REXX, MVS or z/OS before, I found this task brutally 
-challenging. This feeling was exaggerated by reports from some of my friends
-that they were working on Java projects on Linux and Windows - environments
-that I was a lot more familiar with at the beginning of my placement. I was
-informed at the beginning of my placement that if I was not happy with my 
-job, I could be found a new role elsewhere in the company. Although I was
-tempted at this stage, I persevered and rose to the challenges that I faced.
-After a few weeks of struggling and counsel from my team, I started to 
-become proficient at my role and enjoyed my job a lot more. The knowledge I
-acquired during my first few weeks at IBM  has definitely given me a much
-stronger background in IBM software and hardware and has provided me with 
-some hugely desirable skills for any employers that use IBM products. After
-my experience I think that IBM should certainly consider more avenues of 
-support and initial new-starter education so that joining a new team is not
-so much of a challenge and does not discourage new employees too much.
-
-IBM's software product portfolio now consists largely of Eclipse-based 
-graphical applications are written in Java. Although Java is a powerful
-and flexible language, it was surprising to see how much faith the company
-are putting into the language. Even mission critical systems like CICS 
-that should be programmed in the lowest level languages possible to 
-maximise speed and efficiency are being infiltrated by VM-based memory-
-hungry Java \cite{cicsJava}. Personally, I feel that this is a
-mistake and that development of such applications should continue in 
-low level or Ahead-of-time compiled languages like C and COBOL. Unfortunately,
-as long as universities continue to train students to be Java programmers, it
-would be difficult to obtain a set of graduate employees with the necessary 
-skills to maintain a COBOL or even a C-based system. However, as companies like
-IBM move more towards apprenticeships, they are able to train new recruits as
-they wish.
-
-IBM have a dual management system for interns and graduates who join the 
-company. I was assigned a line manager who oversaw my day to day work and
-dealt with any problems I might have in my day job, and a Personal 
-Development Manager who was assigned to help me make the most of my years
-and nurture and develop my skill set. I feel that this system worked very 
-well as it meant that there were always multiple avenues for dealing with
-any problems that may have arisen from conflicts during my day job, and 
-provided me with two equally useful but very different sets of advice. 
-There were a few occasions when the dual management system added extra
-complication to my role and caused confusion. For example, when I went
-out on Giveback schemes, I had to seek approval from both managers. 
-Nevertheless, I feel that the benefits of the system certainly outweighed 
-the extra work in these cases.
-
-I definitely noticed my changing identity as I progressed though the IBM
-‘community of practice’ \cite{Communities}. Communities of practice are
-groups of people who share a concern or a passion for something they do and
-learn how to do it better as they interact regularly. At the beginning, I was
-definitely a 'newcomer,' situated on the periphery and, although I was not
-exactly an 'old timer' by the end of my thirteen months, I was certainly an
-experienced 'practitioner' compared to those who had just begun their year with
-IBM. During my year, learning was not simply a process of assimilation nor of
-learning transfer but changed my very identity as mentors became colleagues and
-then came to me to ask how to approach certain objectives. For instance, at the
-beginning of the year as a 'newcomer' I struggled to understand how to use the 
-mainframe terminal system and 
-frequently sought advice from my team leader. Towards
-the end of my time at IBM my advice regarding Java programming, specifically the
-Eclipse Plug-in development, was highly-sought by my colleagues.
-
-As I built up my bank of the 'tacit knowledge' \cite{SocialKnowing} of the IBM, 
-community, I found that I
-not only defined myself through what I could do with that knowledge, but I also
-defined myself through what I no longer needed to do to acquire the necessary
-knowledge. That is, I recognised the transition from someone who needed help   
-to someone who provided help.
-
-In summary, I am a very different person from when I left Aberystwyth University
-in the second year of my studies. The value of my year in industry has not been
-what it will add to my CV, nor in a healthy bank balance. The value has been in
-the skills I have developed and connections I have made. I feel that these new
-skills will help me both with my final year of studies and as an Information 
-Technology professional moving forward as a new graduate.
-
 \pagebreak

### 2012-10-17 doc/ops/report.tex
Added cover logo to report
Added some of Maria's papers to initial bibliography
made title page relevant/added required information, set up annotated bibliography
first paragraph of OPS is done, started annotating my bibliography

@@
 %use natbib bibliography package
-\usepackage{natbib}
+%\usepackage[numbers]{natbib}
 %use harvard bibliography package
@@
 
-\tableofcontents
+%\tableofcontents
 
@@
 
-\section{Introduction to IBM and its Organisational Structure}
+\section{Project Description}
+
+In academic research, there are a huge abundance of scientific papers available for
+consumption for any given scientific pursuit. In 2010, the famous journal,
+PLOS One (\url{http://plosone.org}), reached the 10,000 papers published milestone \cite{PlosOne2010}. If you 
+are doing background reading for a paper you are authoring, or looking for 
+research on a specific topic that interests you, the vast quantity of data available can often be
+quite daunting and choosing which papers to read very difficult. This problem
+is further exacerbated when there is a time limit on the research to be carried
+out. Partridge aims to aid the reader in finding documents relative to their
+interests through the use of Artificial Intelligence techniques.
+
+\section{Work to be tackled}
+
+The main body of work to be tackled during the project is the Natural Language
+Parsing (NLP) element of the application.
+
+\section{Project Deliverables}
 
@@
 
+\bibliographystyle{IEEEannot}
+\nocite{*}
 \bibliography{report}
-%set style to plain
-\bibliographystyle{plain}
 

### 2012-10-17 doc/ops/report.tex
first draft of project description

@@
 In academic research, there are a huge abundance of scientific papers available for
-consumption for any given scientific pursuit. In 2010, the famous journal,
-PLOS One (\url{http://plosone.org}), reached the 10,000 papers published milestone \cite{PlosOne2010}. If you 
-are doing background reading for a paper you are authoring, or looking for 
-research on a specific topic that interests you, the vast quantity of data available can often be
+consumption for any given scientific pursuit. There are hundreds of journals,
+each with thousands of articles published on a yearly basis. In 2010, the famous journal,
+PLOS One (\url{http://plosone.org}), reached the 10,000 papers published
+milestone \cite{PlosOne2010}. With the advent of internet publishing,
+researchers have access to an immense volume of information at their disposal.
+
+For researchers doing background reading for a paper they are authoring, or looking for 
+research on a specific topic that interests them, the vast quantity of data available can often be
 quite daunting and choosing which papers to read very difficult. This problem
@@
 interests through the use of Artificial Intelligence techniques.
+
+The project will use a web interface to allow a user to indicate which
+specific scientific fields they are interested in - either through manual entry
+of interests and types of report or by allowing the application to collect a
+list of papers that the user has already read and to learn their user profile.
+The program will then suggest sets of papers from the corpus depending on their
+contents and relevance to the user.
 

### 2012-10-17 doc/ops/report.tex
Editing the initial description trying to make it good

--- 2012-10-15 doc/ops/report.tex
@@
 
-\section{Introduction to IBM and its Organisational Structure}
+\section{Project Description}
 
-\pagebreak
+For scientists carrying out background research for a paper they are authoring, or looking for 
+information on a specific topic that interests them, the vast quantity of
+research papers available online can often be quite daunting, making 
+choosing which papers to read very difficult. This problem
+is exacerbated when there is a time limit on the research to be carried
+out. Partridge aims to aid the reader in finding documents relative to their
+interests through the use of Artificial Intelligence techniques. This should
+make the research process more efficient and save the reader time. The program
+may also help them find papers they may otherwise not have read.
 
+Partridge will use a web interface to allow a user to indicate which
+specific scientific fields they are interested in - either through manual entry
+of interests and types of report or by allowing the application to collect a
+list of papers that the user has already read and to learn their user profile.
+The program will then suggest sets of papers from the corpus depending on their
+contents and relevance to the user. The program will make these recommendations
+based upon a machine learning approach to classifying the text corpus and
+learning the user's preferences.
+
+\section{Work to be tackled}
+Whilst a web interface for the program will need to be implemented, the main
+body of the work in this project comes from the backend of the system and the
+Artificial Intelligence that drives it.
+
+Firstly, there will need to be some significant research into Natural Language
+Parsing techniques and how different features of the text can be used to
+classify papers and help the system to understand the differences between them.
+
+Once these features are understood, it will be possible to set up a learning
+algorithm to analyse some collections of scientific papers and store
+information about the differences between them. The system will make use of
+some third party software to help with this process, however I will be using
+knowledge from CS36110 Machine Learning as well as any relevant research papers
+and text books to build a paper classifier myself.
+
+\section{Project Deliverables}
+
+\bibliographystyle{plain}
+\nocite{*}
 \bibliography{report}
-%set style to plain
-\bibliographystyle{plain}
 

### 2012-10-17 tools/pdf2scixml.py
started playing with pythonic tools for processing SciXML

@@ -1,0 +1,16 @@
+#!/usr/bin/python2 
+
+'''
+ Python tooling for working with annotated XML papers
+
+ @author James Ravenscroft
+ @date 17/12/2012
+'''
+
+from pyPdf import PdfFileReader
+
+f = open("test.pdf","rb")
+
+p = PdfFileReader(f)
+
+print p.getPage(0).extractText()

### 2012-10-17 tools/scixml.py

@@ -1,0 +1,19 @@
+from xml.dom import minidom
+
+
+d = minidom.parse(open("mode2.xml","rb"))
+
+doctext = ""
+
+for e in d.getElementsByTagName("s"):
+
+    for child in e.childNodes:
+        
+        if(child.nodeType == d.ELEMENT_NODE):
+            if(child.localName == "annotationART"):
+                
+                for textPart in child.childNodes:
+                    
+                    if( textPart.nodeType == d.TEXT_NODE):
+                        doctext += textPart.wholeText
+print doctext

### 2012-10-21 doc/ops/report.tex
Made lots of changes and fixed some silly language

--- 2012-10-17 doc/ops/report.tex
@@
 
-In academic research, there are a huge abundance of scientific papers available for
-consumption for any given scientific pursuit. In 2010, the famous journal,
-PLOS One (\url{http://plosone.org}), reached the 10,000 papers published milestone \cite{PlosOne2010}. If you 
-are doing background reading for a paper you are authoring, or looking for 
-research on a specific topic that interests you, the vast quantity of data available can often be
-quite daunting and choosing which papers to read very difficult. This problem
-is further exacerbated when there is a time limit on the research to be carried
-out. Partridge aims to aid the reader in finding documents relative to their
-interests through the use of Artificial Intelligence techniques.
+For scholars carrying out a literature review or researching a specific topic
+the vast quantity of research papers available on the internet can often be quite daunting;  
+with the advent of the `Information Age', choosing which papers to read 
+has become very difficult. This problem is exacerbated when there is a 
+time limit to the research. Partridge aims to aid the 
+reader in finding documents aposite to their interests through the use of 
+Artificial Intelligence techniques. As well as making research processes 
+more efficient and saving time, the program may also help the scholar to find
+papers that they may otherwise not have read.
 
-\section{Work to be tackled}
+Partridge will use a web interface to allow users to specify particular
+research topics. This can be done through manual entry of interests and types of 
+report or by allowing the application to collate the papers that the user 
+has read and to learn what is relevant to them. By appropriating this information,
+Partridge will use learning algorithms to examine and classify the available
+corpus of literature and make recommendations as to which articles the
+scholar would find most helpful.
 
-The main body of work to be tackled during the project is the Natural Language
-Parsing (NLP) element of the application.
+\section{Work to be `tackled':}
+Despite the need for a web interface, the main body of the work in this project 
+comes from the backend of the system and the Artificial Intelligence that drives it.
 
-\section{Project Deliverables}
+Initial research must be undertaken  into Natural Language
+Parsing techniques and how different features of a text can be used to
+classify papers. Furthermore, clear identification of the attributes which
+allow the system to understand the differences between texts is vital.
 
-\pagebreak
+Once these features are understood, a learning algorithm will be developed to
+analyse scientific papers and to store information about the differences between 
+them. The system will make use of some third party software (SAPIENTA) to help
+with this process. Additionally, knowledge from CS36110 Machine will be used in
+this project.
 
-\bibliographystyle{IEEEannot}
+The first iteration of the system should the search for  that match specific criteria,
+corresponding directly to `features' identified using the aforementioned AI
+algorithms. Further iterations could be used  to build a profile based upon the user's 
+reading history and used to make suggestions for further.
+
+\section{`Project Deliverables'}
+
+Although a formal 'XP' methodology will not be adopted since this is an
+individual project, the project will be developed using an agile approach. It will be built in an
+iterative manner. An initial release of the product will be made as soon as
+possible. Subsequent releases will be made in iterations of two months.
+
+Deliverables include:
+\begin{itemize}
+    \item Initial version of the system with restricted functionality; This
+    would  use simple search and filtering techniques to find relevant research
+    papers;
+    \item Progress report evaluating the initial product and outlining ongoing
+    development of the Artificial Intellegince underlying the results
+    classifier module;
+    \item Release two of the product, including result classifying behaviour;
+    \item Demonstration of the artificial intelligence in the product;
+    \item Following iteration three, the next release of the product will show
+    evolved classification behaviour.
+    \item Final report and release of software.
+\end{itemize}
+
+\renewcommand{\refname}{Initial Bibliography} 
+\bibliographystyle{plain}
 \nocite{*}

### 2012-11-10 doc/progress_plan/report.tex
Copied ops to progress_plan to start that document

--- 2012-10-21 doc/ops/report.tex
@@
 
-For scholars carrying out a literature review or researching a specific topic
+For scholars carrying out a literature review or researching a specific topic,
 the vast quantity of research papers available on the internet can often be quite daunting;  
@@
 reader in finding documents aposite to their interests through the use of 
-Artificial Intelligence techniques. As well as making research processes 
+Artificial Intelligence. As well as making the research processes 
 more efficient and saving time, the program may also help the scholar to find
@@
 report or by allowing the application to collate the papers that the user 
-has read and to learn what is relevant to them. By appropriating this information,
+has read and to learn what is relevant to them. After appropriating this information,
 Partridge will use learning algorithms to examine and classify the available
-corpus of literature and make recommendations as to which articles the
+corpus of literature and to make recommendations as to which articles the
 scholar would find most helpful.
@@
 them. The system will make use of some third party software (SAPIENTA) to help
-with this process. Additionally, knowledge from CS36110 Machine will be used in
+with this process. Additionally, knowledge from CS36110 Machine Learning will be used in
 this project.
 
-The first iteration of the system should the search for  that match specific criteria,
-corresponding directly to `features' identified using the aforementioned AI
+The first iteration of the system should search for specific criteria corresponding directly to `features' identified using the aforementioned AI
 algorithms. Further iterations could be used  to build a profile based upon the user's 
-reading history and used to make suggestions for further.
+reading history and to make suggestions for further reading.
 
@@
 
-Although a formal 'XP' methodology will not be adopted since this is an
-individual project, the project will be developed using an agile approach. It will be built in an
+Although a formal `XP' methodology will not be adopted since this is an
+individual project, it will be developed using an agile approach and will be built in an
 iterative manner. An initial release of the product will be made as soon as
@@
 \begin{itemize}
-    \item Initial version of the system with restricted functionality; This
+    \item Initial version of the system with restricted functionality; this
     would  use simple search and filtering techniques to find relevant research
@@
     \item Progress report evaluating the initial product and outlining ongoing
-    development of the Artificial Intellegince underlying the results
+    development of the Artificial Intelligence underlying the results
     classifier module;
     \item Release two of the product, including result classifying behaviour;
-    \item Demonstration of the artificial intelligence in the product;
+    \item Demonstration of the Artificial Intelligence in the product;
     \item Following iteration three, the next release of the product will show
-    evolved classification behaviour.
+    evolved classification behaviour;
     \item Final report and release of software.

### 2012-11-10 doc/progress_plan/report.tex
set up empty report doc

--- 2012-10-17 doc/ops/report.tex
@@
 
-%\tableofcontents
+\tableofcontents
 
@@
 
-\section{Project Description}
+\section{Project Summary}
 
-For scientists carrying out background research for a paper they are authoring, or looking for 
-information on a specific topic that interests them, the vast quantity of
-research papers available online can often be quite daunting, making 
-choosing which papers to read very difficult. This problem
-is exacerbated when there is a time limit on the research to be carried
-out. Partridge aims to aid the reader in finding documents relative to their
-interests through the use of Artificial Intelligence techniques. This should
-make the research process more efficient and save the reader time. The program
-may also help them find papers they may otherwise not have read.
+\section{Current Progress}
 
-Partridge will use a web interface to allow a user to indicate which
-specific scientific fields they are interested in - either through manual entry
-of interests and types of report or by allowing the application to collect a
-list of papers that the user has already read and to learn their user profile.
-The program will then suggest sets of papers from the corpus depending on their
-contents and relevance to the user. The program will make these recommendations
-based upon a machine learning approach to classifying the text corpus and
-learning the user's preferences.
+\section{Planning}
 
-\section{Work to be tackled}
-Whilst a web interface for the program will need to be implemented, the main
-body of the work in this project comes from the backend of the system and the
-Artificial Intelligence that drives it.
-
-Firstly, there will need to be some significant research into Natural Language
-Parsing techniques and how different features of the text can be used to
-classify papers and help the system to understand the differences between them.
-
-Once these features are understood, it will be possible to set up a learning
-algorithm to analyse some collections of scientific papers and store
-information about the differences between them. The system will make use of
-some third party software to help with this process, however I will be using
-knowledge from CS36110 Machine Learning as well as any relevant research papers
-and text books to build a paper classifier myself.
-
-\section{Project Deliverables}
-
+\renewcommand{\refname}{Initial Bibliography} 
 \bibliographystyle{plain}

### 2012-11-10 doc/progress_plan/report.tex
Created opening paragraphs with citations

@@
 \section{Project Summary}
+Partridge is a web-based tool designed to assist research and knowledge
+acquisition in the domain of scientific papers.
+
+With the advent of the 'Digital Age' and the ability of computers to copy and
+reproduce information for a negligible cost, the amount of information
+available to researchers is increasing drastically.  Bj\"{o}rk's 2009 study
+suggests that approximately 1.4 Million papers were published in the year 2006
+alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
+publishing (making papers available for free online\cite{Suber2012}) across
+most scientific disciplines is providing researchers with an even larger volume
+of information to be processed. It logically follows that as the amount of
+general information grows, the proportion of relevant material becomes harder
+to find without the assistance of complicated information filtering and retrieval
+systems.
+
+Partridge aims to autonomously process as many scientific papers as
+possible to facilitate intelligent filtering and recommendations to
+researchers, who would otherwise be required to manually browse thousands of
+online documents. This should reduce the amount of information that the user is
+required to process themselves, thereby speeding up the research process.
 
@@
 \bibliographystyle{plain}
-\nocite{*}
 \bibliography{report}

### 2012-11-10 doc/progress_plan/report.tex
Finished provisional introduction to partridge and added IEEEAnnot style bib

--- 2012-11-10 doc/progress_plan/report.tex
@@
 
+\subsection{Introduction}
+Partridge is a web-based tool designed to assist information processing and knowledge
+acquisition in the domain of scientific research.
+
+Since the advent of the 'Digital Age' and the ability of computers to copy and
+reproduce information for a negligible cost, the amount of information
+available to researchers has been increasing drastically.  A 2009 study by B-C
+Bj\"{o}rk suggests that approximately 1.4 Million papers were published in the
+year 2006 alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
+publishing (making papers available for free online\cite{Suber2012}) across
+most scientific disciplines is providing researchers with an even larger volume
+of information to be processed. It logically follows that as the amount of
+general information grows, the proportion of relevant material becomes harder
+to find without the assistance of complicated information filtering and retrieval
+systems.
+
+Partridge aims to autonomously process as many scientific papers as possible to
+facilitate researchers who would otherwise be required to manually read each
+paper themselves. This should reduce the amount of information that the user is
+required to process themselves, thereby speeding up the research process.
+Partridge will achieve this through the use of several existing techniques in
+the field of Natural Language Processing which are discussed below.
+
+From the point of view of it's users, Partridge will assist researchers in two
+ways. The system will provide filtering of papers based upon their
+specific domain (i.e. is the paper primarily concerned with methodology within
+an experiment in chemistry or is it about Ethics in Psychological studies?) and
+their result, whether the paper yielded positive, negative or inconclusive
+evidence for a hypothesis. Depending upon the time constraints of the
+project, it is hoped that Partridge will also offer a user 'profiling' system
+that provides recommendations for researchers based on their reading history.
+This may help Partridge users find relevant papers more quickly or find
+research that they may have otherwise overlooked.
+
+Despite the existence of several complex information retrieval systems
+already in this domain, it is hoped that Partridge will offer a service that
+proves to be more effective and useful for locating relevant scientific papers
+than any counterparts.
+
+\subsection{Prior Art}
+
 \section{Current Progress}
@@
 \renewcommand{\refname}{Initial Bibliography} 
-\bibliographystyle{plain}
-\nocite{*}
+\bibliographystyle{IEEEannot}
 \bibliography{report}

### 2012-11-10 doc/progress_plan/report.tex
Added pagebreak to bibliography and annotation for open access article
Refactored the first couple of paragraphs and started intro to NLP. Need to say why its interesting

@@
 \subsection{Introduction}
-Partridge is a web-based tool designed to assist information processing and knowledge
+Partridge is a web-based tool designed to assist in information processing and knowledge
 acquisition in the domain of scientific research.
@@
 most scientific disciplines is providing researchers with an even larger volume
-of information to be processed. It logically follows that as the amount of
-general information grows, the proportion of relevant material becomes harder
-to find without the assistance of complicated information filtering and retrieval
-systems.
+of information to be processed. As the amount of available information grows,
+relevant material becomes increasingly difficult to find and the need for an
+automated information retrieval tool is ever more apparent.
 
@@
 that provides recommendations for researchers based on their reading history.
-This may help Partridge users find relevant papers more quickly or find
-research that they may have otherwise overlooked.
+This feature should help users find relevant papers more quickly or find research that
+they may have otherwise overlooked.
 
-Despite the existence of several complex information retrieval systems
-already in this domain, it is hoped that Partridge will offer a service that
-proves to be more effective and useful for locating relevant scientific papers
-than any counterparts.
+To facilitate the above behaviour, Partridge will make use of Natural
+Language Processing (NLP) techniques. NLP enables the automated extraction of
+meaningful information from texts written in human languages such as English or
+French.
+
+\section{Current Progress}
 
@@
 
-\section{Current Progress}
+Within the field of scientific research and on the internet in general, there
+are already several systems for assisting users in retrieving useful and
+relevant information.
+
+There are many existing search engines for finding information on the internet
+in general. Most people have heard of Google (\url{http://wwww.google.com}),
+and Yahoo (\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
+(\url{http://www.ask.com}). There are many more similar systems available for free
+general use across the internet. They all present very similar user interfaces in
+which users are asked to supply keywords that might be linked to relevant documents 
+and the search engine returns a list of Uniform Resource Locators (URLs) that they 
+consider to match the user's query.
+
+These search engines are often helpful in locating other pages within the World Wide
+Web. Unfortunately, the results they provide are usually too general to find
+scientific papers and journals. Search engines also index a huge proportion of
+irrelevant information compared to useful information\cite{Berghel1997}, and as
+a result, even relatively specific queries such as effects of gravity on rockets" yield
+millions of results (as shown in Figure \ref{fig:rocket_results}).
+
+\begin{figure}[!ht]
+\includegraphics[width=0.80\textwidth]{images/space_rocket_query.png}
+\caption{{Google showing over 7M results for ``effects of gravity on rockets"}}
+\label{fig:rocket_results}
+\end{figure}
+
+There are also a number of search and indexing systems available for locating
+scientific papers by keyword or through the use of metadata to make
+recommendations. One of the most publicised paper search system is Google
+Scholar. This is an adaptation of Google's general search algorithm to
+specifically handle scientific papers.
 
@@
 
-\renewcommand{\refname}{Initial Bibliography} 
+\pagebreak
 \bibliographystyle{IEEEannot}

### 2012-11-12 doc/progress_plan/report.tex
Added some diagrams to progress plan repository and updated gitignore to ignore swp files

@@
 Partridge is a web-based tool designed to assist in information processing and knowledge
-acquisition in the domain of scientific research.
+acquisition within the domain of scientific research.
 
@@
 publishing (making papers available for free online\cite{Suber2012}) across
-most scientific disciplines is providing researchers with an even larger volume
-of information to be processed. As the amount of available information grows,
-relevant material becomes increasingly difficult to find and the need for an
-automated information retrieval tool is ever more apparent.
+most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
+providing researchers with an even larger volume of information to be
+processed. As available information increases, relevant material becomes
+progressively more difficult to find and the need for an automated information
+retrieval tool more apparent.
 

### 2012-11-12 doc/progress_plan/report.tex
actually added git ignore this time
Added evaluation of search engines and google scholar

@@
 \usepackage{url}
+\usepackage{subcaption}
 
@@
 %include the title page
+\input{revision}
 \input{title}
@@
 
-\subsection{Introduction}
 Partridge is a web-based tool designed to assist in information processing and knowledge
@@
 facilitate researchers who would otherwise be required to manually read each
-paper themselves. This should reduce the amount of information that the user is
-required to process themselves, thereby speeding up the research process.
+paper themselves. This should reduce the amount of information that the reader
+is required to process themselves, thereby speeding up the research process.
 Partridge will achieve this through the use of several existing techniques in
@@
 that provides recommendations for researchers based on their reading history.
-This feature should help users find relevant papers more quickly or find research that
-they may have otherwise overlooked.
+This feature should help users find relevant papers more quickly or find
+research that they may have otherwise overlooked.
 
-To facilitate the above behaviour, Partridge will make use of Natural
-Language Processing (NLP) techniques. NLP enables the automated extraction of
-meaningful information from texts written in human languages such as English or
-French.
+There are already several tools that help researchers manage the vast library
+of internet journals available on the internet. Search engines such as Google
+({\url{http://www.google.com/}}), and social citation management tools such as
+CiteULike ({\url{http://www.citeulike.org}}), do offer some assistance in
+tracking down relevant information. However, these tools are often too general
+or rely upon the user knowing exactly what keywords to search for before
+carrying out the search. These drawbacks are further discussed in Section
+\ref{sec:prior_art} below.
+
+To overcome the drawbacks of these existing systems, Partridge will make use of
+several modern Natural Language Processing (NLP) techniques.  NLP enables the
+automated extraction of meaningful information from texts written in human
+languages such as English or French. There have already been several papers on
+using NLP for detecting emotions in suicide notes\cite{citeulike:11077287}, the
+genre of a web page on the World Wide Web\cite{citeulike:11288938} and
+emotional polarity of a phrase or sentence\cite{Wilson05Polarity}. Liakata et
+al. have also used NLP techniques to classify sentences within scientific
+papers to determine what scientific concept they relate to (i.e. does this
+sentence cover background information or is it a part of the
+hypothesis?)\cite{citeulike:10444769}. Partridge will build upon and make use
+of these existing applications of NLP to filter and retrieve data from
+scientific papers in a novel way.
 
@@
 
-\subsection{Prior Art}
+The Partridge project has been underway since the beginning of October. The
+following section looks at related works and how Partridge compares to them,
+some prior investigation and prototyping work that has already been carried
+out.
 
-Within the field of scientific research and on the internet in general, there
-are already several systems for assisting users in retrieving useful and
-relevant information.
+\subsection{Related Works}
+\label{sec:prior_art}
 
-There are many existing search engines for finding information on the internet
-in general. Most people have heard of Google (\url{http://wwww.google.com}),
-and Yahoo (\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
+There are already many existing systems for finding and filtering information
+on the World Wide Web. Search engines are very useful for information retrieval
+in this very large and generalised search domain. Most people have heard of Google (\url{http://wwww.google.com}),
+Yahoo (\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
 (\url{http://www.ask.com}). There are many more similar systems available for free
-general use across the internet. They all present very similar user interfaces in
-which users are asked to supply keywords that might be linked to relevant documents 
+general use across the internet. They all present very similar user interfaces
+(as shown in Figure \ref{fig:search_interfaces})
+in which users are asked to supply keywords that might be linked to relevant documents 
 and the search engine returns a list of Uniform Resource Locators (URLs) that they 
@@
 
-These search engines are often helpful in locating other pages within the World Wide
-Web. Unfortunately, the results they provide are usually too general to find
-scientific papers and journals. Search engines also index a huge proportion of
-irrelevant information compared to useful information\cite{Berghel1997}, and as
-a result, even relatively specific queries such as effects of gravity on rockets" yield
-millions of results (as shown in Figure \ref{fig:rocket_results}).
+\begin{figure}[!ht]
+        \centering
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/ask_front.png}
+                \caption{Ask.com}
+                \label{fig:ask_interface}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/bing_front.png}
+                \caption{Bing.com}
+                \label{fig:bing_interface}
+        \end{subfigure}\\
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/google_front.png}
+                \caption{Google.com}
+                \label{fig:google_interface}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/yahoo_front.png}
+                \caption{Yahoo.com}
+                \label{fig:yahoo_interface}
+        \end{subfigure}%
+        \caption{4 popular search engine interfaces}\label{fig:animals}
+        \label{fig:search_interfaces}
+\end{figure}
+
+Search engines are helpful in locating pages and websites within the World Wide
+Web. Unfortunately, the problem space they deal with is usually too big for
+them to find scientific papers and journals given a set of keywords. Internet
+search engines index a huge proportion of irrelevant information compared to
+useful information\cite{Berghel1997}, and as a result, even relatively specific
+queries such as effects of gravity on rockets" yield millions of results (as
+shown in Figure \ref{fig:rocket_results}).
 
@@
 
-There are also a number of search and indexing systems available for locating
-scientific papers by keyword or through the use of metadata to make
-recommendations. One of the most publicised paper search system is Google
-Scholar. This is an adaptation of Google's general search algorithm to
-specifically handle scientific papers.
+Partridge offers an advantage over these mechanisms as it will specifically
+index research papers rather than attempting to index the whole Internet.
+This means that there should be a higher proportion of useful information as
+output compared to the output of an Internet Search Engine.
+
+There are also a number of search and indexing systems that specifically look
+for scientific papers as opposed to web pages. One of the most publicised and
+well known paper search system is Google Scholar
+(\url{http://scholar.google.com}).  As can be seen in Figure
+\ref{fig:scholar_basic}, This is an adaptation of Google's general search
+engine (discussed above) to specifically index and search scientific papers.
+Google also offers advanced query options specific to Scholar that allow
+searching by author, year and for words that occur only in the document title
+as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
+problem of `information overload' and provides even more fine control over the
+information returned from searches,  the user is still required to have a very
+good idea of what they are looking for in terms of keywords and/or specific
+authors. It is possible that a user would not know what they are looking for
+until they've seen it.
+
+\begin{figure}[!hbt]
+        \centering
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/googlescholar_front.png}
+                \caption{Google Scholar's General front page}
+                \label{fig:scholar_basic}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/googlescholar_advanced.png}
+                \caption{Advanced search features}
+                \label{fig:scholar_advanced}
+        \end{subfigure}
+
+        \caption{Google Scholar's user interface}
+        \label{fig:scholar_interface}
+\end{figure}
+
+Partridge will provide the option to filter papers by subject and it is hoped
+that the system will also provide user-specific recommendations by profiling
+them through their reading history. This will make it easier for users to find
+relevant papers without knowing exactly what keywords they want to search for.
 

### 2012-11-12 doc/progress_plan/report.tex
pretty much done intro and started lit review

@@
 The Partridge project has been underway since the beginning of October. The
-following section looks at related works and how Partridge compares to them,
-some prior investigation and prototyping work that has already been carried
-out.
+following section looks at some literature on the subjects of Natural Language
+Processing and information retrieval within the domain of scientific papers.
+Some related works are investigated and compared to Partridge and details of
+prototyping work that has been carried out are given.
+
+\subsection{Literature Review}
+Natural Language Processing is still a relatively unexplored discipline and as
+such is still a very active area of research and development within the
+Artificial Intelligence community. E. Liddy defines Natural Language Processing as:
+
+\begin{quotation} 
+A theoretically motivated range of computational techniques for analyzing and
+representing naturally occurring texts at one or more levels of linguistic
+analysis for the purpose of achieving human-like language processing for a
+range of tasks or applications. \cite{liddy2001natural} 
+\end{quotation}
+
+In the case of Partridge, scientific papers, constituting the naturally occuring
+texts, are processed at sentence-by-sentence and word-by-word levels of
+linguistics and represented in the form of Extended Markup Language (XML)
+documents, a format that is both human and machine readable. This information
+is then used for the purpose of classifying and searching papers in a
+human-like way.
+
+It is therefore necessary to define what a 'human-like way' of processing
+scientific papers on the internet consists of. Steven Krug is an expert in the field of
+human-computer interaction on the internet. In `Don't Make Me Think', Krug
+suggests that when browsing the internet, humans find it much easier to locate
+specific information within a labelled and logically structured document than
+one that is provided as a single text entity.\cite{Krug:2005:DMM:1051204}. In
+order to help humans to find relevant research papers, Partridge will represent
+all research papers in its repository in a logical hierarchy that can be
+queried directly by the human users and also processed using other NLP
+techniques to extract further information.
+
+Partridge's document storage format should therefore be formalised to provide a
+standard way of processing each document. In their 2007 paper, Soldatova and
+Liakata propose a methodology for storing the Core Information about Scientific
+Papers (CISP) as a way to formally represent scientific concepts that should be
+present in the papers in a logical ontology\cite{soldatova2007ontology}. They
+then proceed to define a schema for their CISP ontology that defines the
+Core Scientific Concepts (CoreSC) as part of the XML document
+itself\cite{liakata2008guidelines}. Using this format for Partridge would allow
+the system to read and process the ART corpus produced using CoreSC markup
 
@@
 on the World Wide Web. Search engines are very useful for information retrieval
-in this very large and generalised search domain. Most people have heard of Google (\url{http://wwww.google.com}),
-Yahoo (\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
-(\url{http://www.ask.com}). There are many more similar systems available for free
-general use across the internet. They all present very similar user interfaces
-(as shown in Figure \ref{fig:search_interfaces})
-in which users are asked to supply keywords that might be linked to relevant documents 
-and the search engine returns a list of Uniform Resource Locators (URLs) that they 
-consider to match the user's query.
+in this very large and generalised search domain. Most people have heard of
+Google (\url{http://wwww.google.com}), Yahoo (\url{http://www.yahoo.co.uk}),
+Bing (\url{http://www.bing.com}) and Ask (\url{http://www.ask.com}). There are
+many more similar systems available for free general use across the internet.
+They all present very similar user interfaces (as shown in Figure
+\ref{fig:search_interfaces}) in which users are asked to supply keywords that
+might be linked to relevant documents and the search engine returns a list of
+Uniform Resource Locators (URLs) that they consider to match the user's query.
 
@@
 authors. It is possible that a user would not know what they are looking for
-until they've seen it.
+until they've seen it. Even if the user has a set of keywords to search for,
+they can only search the title of the paper or the content as a whole. This
+means that users who want to find a particular phrase within a CoreSC part of
+the paper (e.g. only look for this phrase in the `Result' section of the
+paper) are unable to get results at their desired level of detail.
 
@@
 them through their reading history. This will make it easier for users to find
-relevant papers without knowing exactly what keywords they want to search for.
+relevant papers without knowing exactly which keywords they need to search for.
+Partridge will also offer facilitate searching for keywords within a specific
+CoreSC section by making use of Liaketa et al's SAPIENTA project for
+classifying each sentence of paper.
 

### 2012-11-13 doc/progress_plan/report.tex
Started adding other sections to document

@@
 reproduce information for a negligible cost, the amount of information
-available to researchers has been increasing drastically.  A 2009 study by B-C
-Bj\"{o}rk suggests that approximately 1.4 Million papers were published in the
-year 2006 alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
+available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
+estimates that approximately 1.4 Million papers were published in the year 2006
+alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
 publishing (making papers available for free online\cite{Suber2012}) across
@@
 progressively more difficult to find and the need for an automated information
-retrieval tool more apparent.
+retrieval tool more apparent. The problem is even more vital for General
+Practitioners. Goldacre (2008:97) points out that ``there have been an
+estimated 15 million medical academic articles published so far, and 5000
+journals published every month... picking out what's relevant is a garganutan
+task."\cite{goldacre2009bad}
 
@@
 Partridge will achieve this through the use of several existing techniques in
-the field of Natural Language Processing which are discussed below.
+Natural Language Processing which are discussed below.
 
@@
 There are already several tools that help researchers manage the vast library
-of internet journals available on the internet. Search engines such as Google
+of journals available on the internet. Search engines such as Google
 ({\url{http://www.google.com/}}), and social citation management tools such as
@@
 tracking down relevant information. However, these tools are often too general
-or rely upon the user knowing exactly what keywords to search for before
-carrying out the search. These drawbacks are further discussed in Section
+or rely upon the user knowing exactly what keywords to use before carrying out
+the search. These drawbacks are further discussed in Section
 \ref{sec:prior_art} below.
@@
 To overcome the drawbacks of these existing systems, Partridge will make use of
-several modern Natural Language Processing (NLP) techniques.  NLP enables the
-automated extraction of meaningful information from texts written in human
-languages such as English or French. There have already been several papers on
-using NLP for detecting emotions in suicide notes\cite{citeulike:11077287}, the
-genre of a web page on the World Wide Web\cite{citeulike:11288938} and
-emotional polarity of a phrase or sentence\cite{Wilson05Polarity}. Liakata et
-al. have also used NLP techniques to classify sentences within scientific
-papers to determine what scientific concept they relate to (i.e. does this
-sentence cover background information or is it a part of the
-hypothesis?)\cite{citeulike:10444769}. Partridge will build upon and make use
-of these existing applications of NLP to filter and retrieve data from
-scientific papers in a novel way.
+several cutting edge Artificial Intelligence (AI) techniques in order to analyse and
+process the papers in a more in depth way. AI is a very complex and field and
+implementing the above features will be incredibly challenging. To help with
+this, Partridge will build upon the system implemented by Liakata et al. for
+classifying papers on a sentence-by-sentence basis\cite{citeulike:10444769} and
+make use of Natural Language Toolkit for Python
+\cite{Bird:2006:NNL:1225403.1225421}
 
@@
 \subsection{Literature Review}
-Natural Language Processing is still a relatively unexplored discipline and as
-such is still a very active area of research and development within the
-Artificial Intelligence community. E. Liddy defines Natural Language Processing as:
+
+\subsubsection{Natural Language Processing}
+
+Start with history of NLP.
+
+Natural Language Processing is
+still a relatively unexplored discipline and as such is still a very active
+area of research and development within the Artificial Intelligence
+community\cite{liddy2001natural}. Liddy goes on to define Natural Language
+Processing as:
 
@@
 analysis for the purpose of achieving human-like language processing for a
-range of tasks or applications. \cite{liddy2001natural} 
+range of tasks or applications \it{(Ibid)}.  
 \end{quotation}
@@
 It is therefore necessary to define what a 'human-like way' of processing
-scientific papers on the internet consists of. Steven Krug is an expert in the field of
-human-computer interaction on the internet. In `Don't Make Me Think', Krug
-suggests that when browsing the internet, humans find it much easier to locate
-specific information within a labelled and logically structured document than
-one that is provided as a single text entity.\cite{Krug:2005:DMM:1051204}. In
-order to help humans to find relevant research papers, Partridge will represent
-all research papers in its repository in a logical hierarchy that can be
-queried directly by the human users and also processed using other NLP
-techniques to extract further information.
+scientific papers.  Krug (2005), suggests that when browsing the internet,
+humans find it much easier to locate specific information within a labelled and
+logically structured document than one that is provided as a single text
+entity\cite{Krug:2005:DMM:1051204}. In order to help humans to find relevant
+research papers, Partridge will represent all research papers in its repository
+in a logical hierarchy that can be queried directly by the human users and also
+processed using other NLP techniques to extract further information.
+Partridge's document storage format should therefore be standardised to provide
+a uniform way of processing each document.
 
-Partridge's document storage format should therefore be formalised to provide a
-standard way of processing each document. In their 2007 paper, Soldatova and
-Liakata propose a methodology for storing the Core Information about Scientific
-Papers (CISP) as a way to formally represent scientific concepts that should be
-present in the papers in a logical ontology\cite{soldatova2007ontology}. They
-then proceed to define a schema for their CISP ontology that defines the
-Core Scientific Concepts (CoreSC) as part of the XML document
-itself\cite{liakata2008guidelines}. Using this format for Partridge would allow
-the system to read and process the ART corpus produced using CoreSC markup
+\subsubsection{CISP, CoreSC and SAPIENTA}
+
+Soldatova and Liakata(2007) proposed a methodology for storing the Core
+Information about Scientific Papers (CISP) as a way to formally represent
+scientific concepts that should be present in the articles in a logical
+ontology\cite{soldatova2007ontology}. They then proceed to define a schema for
+their CISP ontology that defines the Core Scientific Concepts (CoreSC) as part
+of the XML document itself\cite{liakata2008guidelines}.
+
+Partridge will make use of
+several modern Natural Language Processing (NLP) techniques.  NLP enables the
+automated extraction of meaningful information from texts written in human
+languages such as English or French. There have already been several papers on
+using NLP for detecting emotions in suicide notes\cite{citeulike:11077287}, the
+genre of a web page on the World Wide Web\cite{citeulike:11288938} and
+emotional polarity of a phrase or sentence\cite{Wilson05Polarity}. Liakata et
+al. have also used NLP techniques to classify sentences within scientific
+papers to determine what scientific concept they relate to (i.e. does this
+sentence cover background information or is it a part of the
+hypothesis?). Partridge will build upon and make use
+of these existing applications of NLP to filter and retrieve data from
+scientific papers in a novel way.
 
@@
 useful information\cite{Berghel1997}, and as a result, even relatively specific
-queries such as effects of gravity on rockets" yield millions of results (as
+queries such as ``effects of gravity on rockets" yield millions of results (as
 shown in Figure \ref{fig:rocket_results}).
@@
 
+\subsection{Methodology}
+
+\subsection{Prototyping/Pilot Studies}
+
+\subsection{Subsequent Changes to Methodology}
+
 \section{Planning}

### 2012-11-13 doc/progress_plan/report.tex
added several references and some intro about AI and NLP

@@
 
+In science fiction literature and films, Artificial Intelligence (AI) and the
+ability of machines to automatically process and understand human language is
+almost always present. The current state of AI is a long way behind these
+fantastic visions. Dale(2000) comments that ``Even the most ardent exponent of
+artificial intelligence research would have to admit that the likes of HAL in
+Kubrick's 2001: A Space Odyssey remain firmly in the realms of science
+fiction\cite{dale2000handbook}".
+
+Despite lacking behind the imagination of authors and script writers, over the last 60 years there
+has been a huge amount of progress in AI techniques. The phrase `Artificial
+Intelligence' was coined in 1956\cite{russell2010artificial} and can be used as
+an umbrella term, describing many subfields from ``learning and perception
+to... diagnosing diseases\it{(Ibid)}."
+
+Turing(1950) proposed a test for determining whether a machine could be
+considered intelligent or not\cite{turing1950computing}. Turing's test is based
+upon whether a computer can communicate in a natural language proficiently
+enough to deceive a human into thinking that the machine is also human. A
+machine able to pass such a test would need to possess the ability to represent
+and learn from knowledge, to be able to reason about what it knows and to be
+able to process natural language\cite{russell2010artificial}. Partridge will
+also need to be able to process natural language and learn from any
+observations it makes. It is reasonable to consider Partridge's backend system
+to be an Artificial Intelligence problem.
+
 \subsubsection{Natural Language Processing}
 
-Start with history of NLP.
-
-Natural Language Processing is
-still a relatively unexplored discipline and as such is still a very active
-area of research and development within the Artificial Intelligence
-community\cite{liddy2001natural}. Liddy goes on to define Natural Language
-Processing as:
+Natural Language Processing (NLP) is still a relatively unexplored discipline
+and as such is a very active area of research and development within the
+Artificial Intelligence community\cite{liddy2001natural}. NLP enables the
+automated extraction of meaningful information from texts written in human
+languages such as English or French. NLP has already been applied to many text
+classification and data extraction problems. Studies have been carried out in
+the detection of emotions in suicide notes\cite{citeulike:11077287}, the
+classification of a web page's genre on the World Wide
+Web\cite{citeulike:11288938} and emotional polarity (is the sentence positive
+or negative) of a phrase or sentence\cite{Wilson05Polarity}. Liddy(2001)
+defines Natural Language Processing as:
 
@@
 entity\cite{Krug:2005:DMM:1051204}. In order to help humans to find relevant
-research papers, Partridge will represent all research papers in its repository
-in a logical hierarchy that can be queried directly by the human users and also
-processed using other NLP techniques to extract further information.
+research papers, Partridge will represent all papers in its repository in a
+logical hierarchical structure. This will facilitate better information
+retrieval for keyword searches and enable more advanced NLP techniques.
 Partridge's document storage format should therefore be standardised to provide
@@
 
-Partridge will make use of
-several modern Natural Language Processing (NLP) techniques.  NLP enables the
-automated extraction of meaningful information from texts written in human
-languages such as English or French. There have already been several papers on
-using NLP for detecting emotions in suicide notes\cite{citeulike:11077287}, the
-genre of a web page on the World Wide Web\cite{citeulike:11288938} and
-emotional polarity of a phrase or sentence\cite{Wilson05Polarity}. Liakata et
-al. have also used NLP techniques to classify sentences within scientific
-papers to determine what scientific concept they relate to (i.e. does this
-sentence cover background information or is it a part of the
-hypothesis?). Partridge will build upon and make use
-of these existing applications of NLP to filter and retrieve data from
-scientific papers in a novel way.
+It is proposed that Partridge should use the CoreSC schema for document storage
+in order to provide a standard way to access and process the papers and thus
+eliminate the task of dealing with multiple documents during its learning
+phase. Using CoreSC also offers the advantage of making Partridge compatible
+with the ART corpus. This is a set of physical chemistry and biochemistry
+research papers that have been pre-processed and already annotated using CISP
+concepts\cite{liakataART}. This would provide Partridge with a set of papers
+that could be used as a training set for classification tasks and could be used
+for information retrieval tests from early on in the project.
+
+Liakata et al. (2012) describe a system for automatically processing and
+categorising sentences in a research paper according to their respective
+CoreSC.
+
+\subsubsection{NLTK}
 
@@
 Partridge will also offer facilitate searching for keywords within a specific
-CoreSC section by making use of Liaketa et al's SAPIENTA project for
+CoreSC section by making use of Liakata et al's SAPIENTA project for
 classifying each sentence of paper.

### 2012-11-13 doc/progress_plan/report.tex
Added SAPIENTA paragraph

@@
 categorising sentences in a research paper according to their respective
-CoreSC.
+CoreSC element\cite{citeulike:10444769}. SAPIENTA
+(\url({http://www.sapientaproject.com}) was trained using the ART corpus and
+can achieve promising accuracies when categorising sentences \it{(Ibid)}. With
+the authors' permissions, Partridge will make use of SAPIENTA when introducing
+new papers into its repository. It is hoped that preclassifying papers will
+make the development of Partridge more manageable within the timeframe
+available and will also allow more effort to be put into other classification
+problems rather than re-implementing a SAPIENTA clone. Any modifications that
+have to be made to SAPIENTA to integrate it into Partridge will be submitted
+back to the original authors to help them improve their works.
 

### 2012-11-13 doc/progress_plan/report.tex
Added some more references and basically finished lit review

@@
 
-It is proposed that Partridge should use the CoreSC schema for document storage
-in order to provide a standard way to access and process the papers and thus
-eliminate the task of dealing with multiple documents during its learning
-phase. Using CoreSC also offers the advantage of making Partridge compatible
+It is proposed that Partridge uses the CoreSC schema for document storage
+to provide a standard way to access and process the papers and thus
+eliminate dealing with multiple documents during its learning phase. 
+Using CoreSC also offers the advantage of making Partridge compatible
 with the ART corpus. This is a set of physical chemistry and biochemistry
@@
 
+After pre-processing by SAPIENTA is complete, Partridge will need to do some
+classification work of its own to determine the area of study (i.e. Physics,
+Chemistry, Biology), type of paper (Literature review, Case Study, Experiment)
+and the polarity of the result (positive, negative, inconclusive). These tasks
+involve implementing existing AI techniques and applying them specifically to
+the task of text classification. To avoid the time consuming task of re-implementing these
+methods, it was decided that a library should be used instead.
+
 \subsubsection{NLTK}
+
+There are several existing libraries to facilitate Natural Language Processing.
+Many are written for Java \cite{mallet2002}\cite{cunningham2011text} and are
+very complex or not well documented. The Natural Language Toolkit (NLTK) is a
+simple and intuitive library written for Python. Bird(2009) states that NLTK
+was designed ``to provide an intuitive framework along with substantial
+building blocks, giving users a practical knowledge of NLP". The project is
+relatively mature in comparison to the above named Java libraries. There is
+also a free book that accompanies the project available at
+\url{http://nltk.org/book/} which provides a huge amount of information on how
+to implement many popular NLP techniques using the library. For this reason
+NLTK was chosen as the primary accompanying library for the project.
 
@@
 for scientific papers as opposed to web pages. One of the most publicised and
-well known paper search system is Google Scholar
+well known paper search systems is Google Scholar
 (\url{http://scholar.google.com}).  As can be seen in Figure
@@
 CoreSC section by making use of Liakata et al's SAPIENTA project for
-classifying each sentence of paper.
+classifying each sentence of paper as it is added to the repository.
 

### 2012-11-13 doc/progress_plan/report.tex
Added social citation engines with screenshots and some new subsections

@@
 
+\subsubsection{Search Engines}
 There are already many existing systems for finding and filtering information
@@
 
+\subsubsection{Scientific Paper Search Engines}
 There are also a number of search and indexing systems that specifically look
@@
 
+\subsubsection{Social Citation and Recommendation Engines}
+Social citation and recommendation engines also provide a partial solution to
+the `information overload' problem.  Services like Goodreads
+(\url{http://www.goodreads.com/}) and CiteUlike
+(\url{http://www.citeulike.org/}) allow you to register your interest in
+specific authors and subjects. This allows the sites to build up a profile of
+the sorts of materials that you might be interested in and provide lists of
+recommendations as in Figure \cite{social_indexes}.
+
+\begin{figure}[!hbt]
+        \centering
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/goodreads_index.png}
+                \caption{Goodreads user profile page}
+                \label{fig:goodreads_index}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/citeulike_index.png}
+                \caption{a CiteULike user profile page}
+                \label{fig:citeulike_index}
+        \end{subfigure}
+
+        \caption{Goodreads and citeulike social recommendation systems}
+        \label{fig:social_indexes}
+\end{figure}
+
 \subsection{Methodology}

### 2012-11-13 doc/progress_plan/report.tex
Added talk about why goodreads and citeulike aren't great for content indexing

@@
 
+These systems have the ability to make recommendations to the user without
+requiring specific keywords or search terms. They are able to do this by
+learning the user's profile and taking into account the preferences of their
+'friends' and their browsing history. However, the above-named systems do not
+take into account the content of the paper or book. They only deal with
+metadata as can be seen in Figure \ref{fig:social_searches}. This means that
+important discriminatory information that could be contained within the actual
+document content is overlooked completely. Partridge will analyse documents on
+a sentence-by-sentence and possibly word-by-word basis, thereby taking account
+of any embedded information that could be missed by these social metadata
+systems.
+
+\begin{figure}[!hbt]
+        \centering
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/goodreads_search.png}
+                \caption{Goodreads advanced search page}
+                \label{fig:goodreads_search}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/citeulike_search.png}
+                \caption{CiteULike advanced search options}
+                \label{fig:citeulike_search}
+        \end{subfigure}
+
+        \caption{Goodreads and citeulike search only deal with metadata.}
+        \label{fig:social_searches}
+\end{figure}
+
 \subsection{Methodology}

### 2012-11-13 doc/progress_plan/report.tex
Added section on programming language selection

@@
 an umbrella term, describing many subfields from ``learning and perception
-to... diagnosing diseases\it{(Ibid)}."
+to... diagnosing diseases\emph{(Ibid)}."
 
@@
 CoreSC element\cite{citeulike:10444769}. SAPIENTA
-(\url({http://www.sapientaproject.com}) was trained using the ART corpus and
-can achieve promising accuracies when categorising sentences \it{(Ibid)}. With
+(\url{http://www.sapientaproject.com}) was trained using the ART corpus and
+can achieve promising accuracies when categorising sentences (\emph{Ibid}). With
 the authors' permissions, Partridge will make use of SAPIENTA when introducing
@@
 the task of text classification. To avoid the time consuming task of re-implementing these
-methods, it was decided that a library should be used instead.
-
-\subsubsection{NLTK}
-
-There are several existing libraries to facilitate Natural Language Processing.
-Many are written for Java \cite{mallet2002}\cite{cunningham2011text} and are
-very complex or not well documented. The Natural Language Toolkit (NLTK) is a
-simple and intuitive library written for Python. Bird(2009) states that NLTK
-was designed ``to provide an intuitive framework along with substantial
-building blocks, giving users a practical knowledge of NLP". The project is
-relatively mature in comparison to the above named Java libraries. There is
-also a free book that accompanies the project available at
-\url{http://nltk.org/book/} which provides a huge amount of information on how
-to implement many popular NLP techniques using the library. For this reason
-NLTK was chosen as the primary accompanying library for the project.
+methods, it was decided that a library should be used instead. Different NLP
+libraries and their properies are discussed below in Section
+\ref{sec:libschoice}.
 
@@
 the sorts of materials that you might be interested in and provide lists of
-recommendations as in Figure \cite{social_indexes}.
+recommendations as in Figure \ref{social_indexes}.
 
@@
 These systems have the ability to make recommendations to the user without
-requiring specific keywords or search terms. They are able to do this by
-learning the user's profile and taking into account the preferences of their
-'friends' and their browsing history. However, the above-named systems do not
-take into account the content of the paper or book. They only deal with
-metadata as can be seen in Figure \ref{fig:social_searches}. This means that
-important discriminatory information that could be contained within the actual
-document content is overlooked completely. Partridge will analyse documents on
-a sentence-by-sentence and possibly word-by-word basis, thereby taking account
-of any embedded information that could be missed by these social metadata
-systems.
+requiring specific keywords or search terms. They do this by learning the
+user's profile and taking into account the preferences of their 'friends' and
+their browsing history. However, the above-named systems do not take into
+account the content of the paper or book. They only deal with metadata as can
+be seen in Figure \ref{fig:social_searches}. This means that important
+discriminatory information that could be contained within the actual document
+content is overlooked completely. Partridge will analyse documents on a
+sentence-by-sentence and possibly word-by-word basis, thereby taking account of
+any embedded information that could be missed by these social metadata systems.
 
@@
 
+Partridge is based upon several fairly complex and new ideas in AI and NLP.
+For the project to be a success it is imperative that the right language,
+environment and toolkits are used to avoid unnecessary work on existing
+technologies and allow priority to be given to the novel aspects of the
+project.
+
+The language that Partridge will be written in is one of the most fundamental
+and important choices to be made. The language choice effects not only the end
+performance of the application, but the speed at which the project is developed
+and the portability of the end code \cite{britton2008}. To avoid a learning
+overhead, it was decided that the programming language should be one that the
+author is familiar with. This reduced the choice of language down to C, Java
+and Python.
+
+The C programming language was invented by Kernighan and Ritchie and
+published in 1978\cite{ritchie1978c}. The language is small and
+optimised\cite{prinz2002c} and therefore compiled C programs tend to run
+extremely fast. Unfortunately, C is designed to be general and lack restriction
+\cite{ricthie1978c} which is often an advantage for programmers who favour
+optimised code over excessive error checking. However, this means that
+debugging C programms can be quite long winded and challenging. Since the NLP
+aspects of Partridge present an amibitious challenge in themselves, having to
+debug applications without help from a managed programming environment is not
+desirable.
+
+The Java programming language on the other hand, does provide memory management
+and error checking\cite{Coffey2008} at the cost of program performance. Java is
+a pseudo-compiled language that is translated into an intermediate bytecode
+which is then interpreted at runtime by an interpreter on the client computer
+called a Virtuam Machine(VM). Gosling (2000) describes java as as a
+``general-purpose...  programming language [that allows] developers to write a
+program once and then be able to run it everywhere on the
+internet\cite{gosling2000java}." Java provides a solid and stable programming
+environment and stringent error checking, both of which would be advantageous
+in the development of Partridge.  The language syntax is very verbose and a lot
+of `boiler-plate' code must be written before a program can be executed.
+Therefore Java is not suitable as a rapid prototyping language. Since
+Partridge's development requires a steep learning curve for the author, a
+language that allows quick prototyping with minimal programming.
+
+Python is a programming language with a famously shallow learning curve,
+readable syntax and dynamic inspection that facilitates rapid prototyping
+\cite{bird2009natural}. The language was invented by Guido Van Rossum as a
+multi-use, flexible, interpreted scripting language, extensible via compiled C
+modules\cite{An93pythonfor}. Developing Partridge in python
+would provide a flexible prototyping environment and readable syntax allowing
+for investigative work to be carried out quickly and efficiently with minimal
+overheads for writing boiler-plate code and debugging. The ability to extend
+the language using native code would give Partridge an even greater advantage.
+Since NLP techniques can be quite processor intensive and Python is an
+interpreted language, and in its very nature, slower than a compiled language,
+inefficient sections of Python code could be re-written as C extensions and
+compiled into the application. For these reasons, Python was selected as the
+preferred programming language for Partridge development.
+
+\subsubsection{User Interface Style}
+
+\subsubsection{Web Presentation Frameworks}
+
+\subsubsection{Natural Language Libraries}
+\label{sec:libschoice}.
+There are several existing libraries to facilitate Natural Language Processing.
+Many are written for Java \cite{mallet2002}\cite{cunningham2011text} and are
+very complex or not well documented. The Natural Language Toolkit (NLTK) is a
+simple and intuitive library written for Python. Bird(2009) states that NLTK
+was designed ``to provide an intuitive framework along with substantial
+building blocks, giving users a practical knowledge of
+NLP\cite{bird2009natural}". The project is
+relatively mature in comparison to the above named Java libraries. There is
+also a free book that accompanies the project available at
+\url{http://nltk.org/book/} which provides a huge amount of information on how
+to implement many popular NLP techniques using the library. For this reason
+NLTK was chosen as the primary accompanying library for the project.
+
 \subsection{Prototyping/Pilot Studies}
@@
 
+\subsection{Development Methodology}
+
+\subsubsection{Agile}
+\subsubsection{Waterfall Development}
+
+\subsubsection{ Partridge's methodology}
+
+\subsection{ Work Timeline }
+
 \pagebreak

### 2012-11-13 doc/progress_plan/report.tex
Finished web framework comparisons

@@
 
-Partridge is based upon several fairly complex and new ideas in AI and NLP.
-For the project to be a success it is imperative that the right language,
-environment and toolkits are used to avoid unnecessary work on existing
-technologies and allow priority to be given to the novel aspects of the
-project.
-
 The language that Partridge will be written in is one of the most fundamental
@@
 
-\subsubsection{User Interface Style}
+\subsubsection{Web Presentation Frameworks}
 
-\subsubsection{Web Presentation Frameworks}
+Partridge's web frontend will be used by researchers to wish to query the
+system for information on scientific papers. As it is a web tool, Partridge
+will be presented as a set of HTML web pages.
+
+It is possible to use a separate software stack Such as Apache web server
+(\url{http://httpd.apache.org/}) and PHP (\url{http://www.php.net}) as a web
+presentation layer. However, this would involve adding more software to the
+project and building an interface between the PHP scripts and Partridge's
+python backend. To prevent unnecessary complication, this approach will be
+avoided and instead, a Python web toolkit will be used and integrated directly
+with the backend.
+
+Django (\url{http://www.djangoproject.com/}) is a Python web framework with
+integrated database management and templating capabilities \cite{django2012}.
+The framework provides automatic management of all aspects of your
+application's data storage systems unless explicitely disabled. The framework
+also uses a fairly stricty Model-View-Controller pattern and this is enforced
+in the structure of the application code. These features may be useful in a
+general web application such as a news site. Partridge requires a much more
+complex internal structure to take into account the machine learning and NLP
+aspects of the system. Having to `shoehorn' Partridge into a specific structure
+to make it compatible with Django adds extra overhead to the project and is not
+desirable.
+
+Flask (\url{http://flask.pocoo.org}) is a python `microframework' for web
+development. Ronacher (2012) writes that ``Flask aims to keep the core simple
+but extensible...[and] won't make any decisions for you\cite{flask2012}." It
+uses a simple templating system that can optionally be swapped out for an
+equivalent system and does not impose any limitations or requirements on the
+layout of the program or the type of database that is used. Flask integrates
+very simply into existing software using Python annotations\emph{(Ibid)}. This approach
+means that the framework could be adapted to Partridge very quickly, rather
+than requiring Partridge to be adapted to the framework. Therefore, Flask has
+been chosen as the preferred web framework for use in the project.
 

### 2012-11-13 doc/progress_plan/report.tex
Finished planning section

@@
 and error checking\cite{Coffey2008} at the cost of program performance. Java is
-a pseudo-compiled language that is translated into an intermediate bytecode
-which is then interpreted at runtime by an interpreter on the client computer
-called a Virtuam Machine(VM). Gosling (2000) describes java as as a
-``general-purpose...  programming language [that allows] developers to write a
-program once and then be able to run it everywhere on the
-internet\cite{gosling2000java}." Java provides a solid and stable programming
-environment and stringent error checking, both of which would be advantageous
-in the development of Partridge.  The language syntax is very verbose and a lot
-of `boiler-plate' code must be written before a program can be executed.
-Therefore Java is not suitable as a rapid prototyping language. Since
-Partridge's development requires a steep learning curve for the author, a
-language that allows quick prototyping with minimal programming.
+a pseudo-compiled language that is translated into bytecode then interpreted at
+runtime by a Virtual Machine(VM) on the client computer. Gosling (2000)
+describes java as a ``general-purpose...  programming language [that allows]
+developers to write a program once and then be able to run it everywhere on the
+internet\cite{gosling2000java}." Java provides a stable programming environment
+and error checking, both of which would be advantageous in the development of
+Partridge. Java's syntax is very verbose and a lot of `boiler-plate' code must
+be written before a program can be executed.  Therefore Java is not suitable as
+a rapid prototyping language. Since Partridge's development requires a steep
+learning curve for the author, a language that allows quick prototyping with
+minimal programming.
 
@@
 
-\subsubsection{Natural Language Libraries}
-\label{sec:libschoice}.
-There are several existing libraries to facilitate Natural Language Processing.
-Many are written for Java \cite{mallet2002}\cite{cunningham2011text} and are
-very complex or not well documented. The Natural Language Toolkit (NLTK) is a
-simple and intuitive library written for Python. Bird(2009) states that NLTK
-was designed ``to provide an intuitive framework along with substantial
-building blocks, giving users a practical knowledge of
-NLP\cite{bird2009natural}". The project is
-relatively mature in comparison to the above named Java libraries. There is
-also a free book that accompanies the project available at
+\subsubsection{Natural Language Libraries} \label{sec:libschoice}.  There are
+several existing libraries to facilitate Natural Language Processing.  Many are
+written for Java \cite{mallet2002}\cite{cunningham2011text} and are very
+complex or not well documented. The Natural Language Toolkit (NLTK) is a simple
+and intuitive library written for Python. Bird(2009) states that NLTK was
+designed ``to provide an intuitive framework along with substantial building
+blocks, giving users a practical knowledge of NLP\cite{bird2009natural}". The
+project is relatively mature in comparison to the above named Java libraries.
+There is also a free book that accompanies the project available at
 \url{http://nltk.org/book/} which provides a huge amount of information on how
@@
 
-\subsubsection{Agile}
-\subsubsection{Waterfall Development}
+\subsubsection{Existing Methodologies}
+Selecting a suitable development methodology for building Partridge is another
+very important choice for the project.
 
-\subsubsection{ Partridge's methodology}
+Under the traditional `Waterfall' Software Development model, Requirements
+Gathering, Analysis, Program Design, Coding, Testing and Operations were all
+defined as formal phases in the development cycle. There is little flexibility
+other than moving back up the waterfall to rectify mistakes after
+testing.\cite{Royce:1987:MDL:41765.41801}. This model was very focused on
+paperwork and bureaucracy, trying to maintain a paper trail and manage risk
+through accountability \emph{(Ibed)}. This approach to software development is
+very heavyweight and slow and often produced software that did not match the
+users' needs as a result \cite{Boehm1988}.
 
-\subsection{ Work Timeline }
+As an alternative to the heavyweight Waterfall approach, Beck et al came up
+with the principle of the Agile Manifesto, favouring a lightweight, responsive
+development model over the heavyweight slow waterfall
+system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
+of developers and prioriting communication between team members. This is most
+prominent in the Extreme Programming (XP) method of software development. Since
+Partridge is an individual project, XP is not really applicable. However, some
+concepts like rapid prototyping/spike work and iterative release cycles will be
+used as part of the Partridge development methodology.
+
+\subsubsection{ Partridge's Development Methodology}
+
+Since Partridge is an individual project but does involve discussions with
+supervisors, a customised methodology has been adopted. Firstly, all design
+and planning documentation have been written up and placed on a wiki which is
+accessible and modifiable by the author and both supervisors. This creates a
+paper trail for all tasks and also allows collaboration between involved
+parties through the Internet. A full printout of the wiki is available in
+Appendix \ref{sec:wiki}.
+
+Weekly meetings are held with both supervisors. The notes from the preceeding
+week are analysed and each task discussed in depth. New tasks are then noted
+down along with any observations that should be documented. These new notes are
+uploaded to the wiki the following day or earlier. Each party present at the
+meeting adds their own observations to the notes page. This page is then
+reviewed at the next meeting. As seen in Appendix \ref{sec:wiki}, this practice
+has already been running for several weeks and has so far proven to be highly
+effective.
+
+Partridge will adopt an Agile approach to release cycles, producing a working
+software package at iterations of one month.  Each iteration, the software will
+include more of the desired functionality discussed above and in the wiki.
+GitHub's issue manager program will be used to track tasks and bugfixes and
+plan which tasks will be carried out in which iteration. Tasks that are created
+in a full iteration (where no development time is left) will be added to a
+backlog and integrated in the next iteration with enough development time to
+contain it.
+
+Partridge's testing strategy consists of multiple unit tests that are run at
+integration of new code into the codebase. As soon as the first release is
+built, Partridge will be made available for use by the public and users
+encouraged to test the system and submit any bugs via the GitHub issue manager.
+It is hoped that colleagues at Aberystwyth University and Dr. Liakata's
+colleages at the EBI will try to use the system one it becomes available.
+
+\subsubsection{ Work Timeline }
+
+The tasks involved in Partridge have been carefully calculated and prioritised.
+They were then added to the GitHub issue management system and a report
+generated listing them in the order that they are expected to be
+accomplished. This report can be seen in Appendix \ref{sec:timeline}.
+
+\subsubsection{ Mid-Project Demonstration Plan}
+
+The mid-project demonstration is scheduled for after iteration two of the
+Partridge project. If everything runs to schedule, then at this point it will
+be possible to demonstrate keyword search within the project's database and
+filter based upon the polarity of the paper's results. For redundancy purposes,
+Partridge will be configured to run as a server on multiple computers. Both
+this and the final project demonstration will require a room with Internet
+access. However, should this be unavailable, then Partridge could be run
+locally on the author's laptop.
+
+\subsubsection{ Final Project Demonstration Plan}
+
+The final demonstration of Partridge will be fairly similar to the Mid-Project
+demonstration. However, it should include all of the planned classifiers and if
+there is extra time on the project, the profiling/recommendation engine will
+also be demonstrated. This demonstration will use the same redundancy
+precautions as the Mid-project demonstration above, and will also need a room
+with the internet if available.
+
+\appendix
+\section{Project Timeline}
+\label{sec:timeline}
+
+\appendix
+\section{Project Wiki}
+\label{sec:wiki}
 

### 2012-11-13 doc/progress_plan/report.tex
Added PDF conversion bit

@@
 
-\subsection{Prototyping/Pilot Studies}
+\subsection{Prototyping/Current Work}
 
-\subsection{Subsequent Changes to Methodology}
+\subsubsection{PDF Conversion}
+Most scientific papers available on the internet are formatted as PDF
+documents. However, Partridge uses and stores documents that use the CoreSC
+schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
+spike work was carried out to determine the feasibility of converting papers
+published as PDF documents into XML documents. Townsendi et al(2009) liken converting
+PDF to XML to ``converting hamburgers into cows," they go on to explain that
+PDF documents do not contain any semantic data and documents lose much of their
+explicit structure when they are formatted in this way \cite{Townsend2009}.
+Therefore, to convert PDF documents into an NLP-friendly format, some
+heuristics must be used to detect the document's structure.
+
+A prototype script was written using a Python PDF extraction library called
+PDFMiner (\url{http://www.unixuser.org/~euske/python/pdfminer/index.html}).
+This toolkit already contains some heuristics about how to extract text from
+PDF documents in a sane way\cite{pdfminer}. The script then used the NLTK
+library to split the text into sentences and save the document in a CoreSC
+compatible format for processing by SAPIENTA.
+
+The script had limited success due to the high variation of formatting within
+scientific papers. It was suggested that PDFX (\url{http://pdfx.cs.man.ac.uk/})
+a free service hosted by the university of manchester, could be used instead of
+PDFMiner. PDFX's main advantage is that it uses a machine learning system to
+guess PDF document structures more accurately than through the use of simple
+Heuristics. With an adapted backend that sends PDFs for analysis using PDFX and
+then splits the results using NLTK, the conversion script now has a much higher
+success rate and will be used as a preprocessor for adding PDF  documents to
+Partridge.
+
+\subsubsection{Interface Design}
+
+\subsubsection{System Processes}
 

### 2012-11-14 doc/progress_plan/report.tex
Made some minor changes and rephrased a few things

@@
 \usepackage{subcaption}
+
+\usepackage[nottoc,numbib]{tocbibind}
 
@@
 journals published every month... picking out what's relevant is a garganutan
-task."\cite{goldacre2009bad}
+task."\cite{goldacre2008bad}
 
@@
 specific domain (i.e. is the paper primarily concerned with methodology within
-an experiment in chemistry or is it about Ethics in Psychological studies?) and
+an experiment in chemistry or is it about ethics in psychological studies?) and
 their result, whether the paper yielded positive, negative or inconclusive
@@
 make use of Natural Language Toolkit for Python
-\cite{Bird:2006:NNL:1225403.1225421}
+\cite{bird2009natural}
 
 \section{Current Progress}
-
-The Partridge project has been underway since the beginning of October. The
-following section looks at some literature on the subjects of Natural Language
-Processing and information retrieval within the domain of scientific papers.
-Some related works are investigated and compared to Partridge and details of
-prototyping work that has been carried out are given.
 
@@
 ability of machines to automatically process and understand human language is
-almost always present. The current state of AI is a long way behind these
+almost always taken for granted. The current state of AI is a long way behind these
 fantastic visions. Dale(2000) comments that ``Even the most ardent exponent of
@@
 observations it makes. It is reasonable to consider Partridge's backend system
-to be an Artificial Intelligence problem.
+to be an Artificial Intelligence problem. Primarily, Patridge can be considered
+a Natural Language Processing problem.
 
@@
 Natural Language Processing (NLP) is still a relatively unexplored discipline
-and as such is a very active area of research and development within the
-Artificial Intelligence community\cite{liddy2001natural}. NLP enables the
-automated extraction of meaningful information from texts written in human
-languages such as English or French. NLP has already been applied to many text
-classification and data extraction problems. Studies have been carried out in
-the detection of emotions in suicide notes\cite{citeulike:11077287}, the
-classification of a web page's genre on the World Wide
-Web\cite{citeulike:11288938} and emotional polarity (is the sentence positive
-or negative) of a phrase or sentence\cite{Wilson05Polarity}. Liddy(2001)
-defines Natural Language Processing as:
+and as such is a very active area of research and development within the AI
+community\cite{liddy2001natural}. NLP enables the automated extraction of
+meaningful information from texts written in human languages such as English or
+French. NLP has already been applied to many text classification and data
+extraction problems. Studies have been carried out in the detection of emotions
+in suicide notes\cite{citeulike:11077287}, the classification of a web page's
+genre on the World Wide Web\cite{citeulike:11288938} and emotional polarity
+(determining the positive or negative implications of) of a phrase or
+sentence\cite{Wilson05Polarity}. Liddy(2001) defines Natural Language
+Processing as:
 
@@
 Liakata et al. (2012) describe a system for automatically processing and
-categorising sentences in a research paper according to their respective
-CoreSC element\cite{citeulike:10444769}. SAPIENTA
-(\url{http://www.sapientaproject.com}) was trained using the ART corpus and
-can achieve promising accuracies when categorising sentences (\emph{Ibid}). With
+categorising sentences in a research paper according to their respective CoreSC
+element\cite{citeulike:10444769}. SAPIENTA
+(\url{http://www.sapientaproject.com}) was trained using the ART corpus and can
+achieve promising accuracies when categorising sentences (\emph{Ibid}). With
 the authors' permissions, Partridge will make use of SAPIENTA when introducing
-new papers into its repository. It is hoped that preclassifying papers will
-make the development of Partridge more manageable within the timeframe
-available and will also allow more effort to be put into other classification
-problems rather than re-implementing a SAPIENTA clone. Any modifications that
-have to be made to SAPIENTA to integrate it into Partridge will be submitted
-back to the original authors to help them improve their works.
+new papers into its repository. It is hoped that preclassifying papers with
+SAPIENTA will make the development of Partridge more manageable within the
+timeframe available and will also allow more effort to be put into other
+classification problems rather than re-implementing a SAPIENTA clone. Any
+modifications that have to be made to SAPIENTA to integrate it into Partridge
+will be submitted back to the original authors to assist them in their research.
 
@@
 involve implementing existing AI techniques and applying them specifically to
-the task of text classification. To avoid the time consuming task of re-implementing these
-methods, it was decided that a library should be used instead. Different NLP
-libraries and their properies are discussed below in Section
-\ref{sec:libschoice}.
+the task of text classification. To avoid the time consuming task of
+re-implementing these methods, it was decided that a library should be used
+instead. Different NLP libraries and their properies are discussed below in
+Section \ref{sec:libschoice}.
 
@@
 \subsubsection{Search Engines}
+
 There are already many existing systems for finding and filtering information
 on the World Wide Web. Search engines are very useful for information retrieval
-in this very large and generalised search domain. Most people have heard of
-Google (\url{http://wwww.google.com}), Yahoo (\url{http://www.yahoo.co.uk}),
-Bing (\url{http://www.bing.com}) and Ask (\url{http://www.ask.com}). There are
-many more similar systems available for free general use across the internet.
-They all present very similar user interfaces (as shown in Figure
-\ref{fig:search_interfaces}) in which users are asked to supply keywords that
-might be linked to relevant documents and the search engine returns a list of
-Uniform Resource Locators (URLs) that they consider to match the user's query.
+in the very large and generalised search domain of the Internet. Most people
+have heard of Google (\url{http://wwww.google.com}), Yahoo
+(\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
+(\url{http://www.ask.com}). There are many more similar systems available for
+free general use across the internet.  They all present very similar user
+interfaces (as shown in Figure \ref{fig:search_interfaces}) in which users are
+asked to supply keywords that might be linked to relevant documents and the
+search engine returns a list of Uniform Resource Locators (URLs) that they
+consider to match the user's query.
 
@@
 Therefore, to convert PDF documents into an NLP-friendly format, some
-heuristics must be used to detect the document's structure.
+heuristics must be used to detect the document's structure\cite{pdfminer}.
 
@@
 
+To help in visualising how the final web frontend will appear, some diagrams of
+the user interface have been drawn. You can see these diagrams in Appendix
+\ref{sec:ui_designs}.
+
 \subsubsection{System Processes}
+
+To visualise how some of the system processes will work and how they should be
+programmed, some flow diagrams have been produced and attached in Appendix
+\ref{sec:system_diagrams}
 
@@
 other than moving back up the waterfall to rectify mistakes after
-testing.\cite{Royce:1987:MDL:41765.41801}. This model was very focused on
+testing\cite{Royce:1987:MDL:41765.41801}. This model was very focused on
 paperwork and bureaucracy, trying to maintain a paper trail and manage risk
@@
 system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
-of developers and prioriting communication between team members. This is most
-prominent in the Extreme Programming (XP) method of software development. Since
-Partridge is an individual project, XP is not really applicable. However, some
-concepts like rapid prototyping/spike work and iterative release cycles will be
-used as part of the Partridge development methodology.
+of developers and prioriting communication between team members \emph{(Ibid)}.
+This is most prominent in the Extreme Programming (XP) method of software
+development. Since Partridge is an individual project, XP is not really
+applicable. However, some concepts like rapid prototyping/spike work and
+iterative release cycles will be used as part of the Partridge development
+methodology.
 
@@
 
-Since Partridge is an individual project but does involve discussions with
-supervisors, a customised methodology has been adopted. Firstly, all design
-and planning documentation have been written up and placed on a wiki which is
+Partridge is an individual project but does involve discussions with
+supervisors. The customers have been identified as the end-users of the system.
+Therefore, a customised methodology has been adopted. Firstly, all design and
+planning documentation have been written up and placed on a wiki which is
 accessible and modifiable by the author and both supervisors. This creates a
@@
 include more of the desired functionality discussed above and in the wiki.
-GitHub's issue manager program will be used to track tasks and bugfixes and
+GitHub's issue manager program is being used to track tasks and bugfixes and
 plan which tasks will be carried out in which iteration. Tasks that are created
@@
 backlog and integrated in the next iteration with enough development time to
-contain it.
+contain it. Tasks are also assigned a priority, higher priority issues being
+tackled before low priority ones.
 
@@
 \appendix
+\section{User Interface Designs}
+\label{sec:ui_designs}
+
+\appendix
+\section{System Process Diagrams}
+\label{sec:system_diagrams}
+
+\appendix
 \section{Project Timeline}
@@
 
-\pagebreak
 \bibliographystyle{IEEEannot}

### 2012-11-15 doc/progress_plan/report.tex
Fixed a couple of small errors
Rephrased section 1 and made things a bit less ambigious

@@
 
-Partridge is a web-based tool designed to assist in information processing and knowledge
-acquisition within the domain of scientific research.
+This document describes the creation of Partridge, a new web-based tool
+designed to assist in information processing and knowledge acquisition within
+the domain of scientific research.
 
@@
 alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
-publishing (making papers available for free online\cite{Suber2012}) across
+publishing (making papers available to readers for free online\cite{Suber2012}) across
 most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
-providing researchers with an even larger volume of information to be
+providing scientists and researchers with an even larger volume of information to be
 processed. As available information increases, relevant material becomes
@@
 estimated 15 million medical academic articles published so far, and 5000
-journals published every month... picking out what's relevant is a garganutan
+journals published every month... picking out what's relevant is a gargantuan
 task."\cite{goldacre2008bad}
 
-Partridge aims to autonomously process as many scientific papers as possible to
-facilitate researchers who would otherwise be required to manually read each
-paper themselves. This should reduce the amount of information that the reader
-is required to process themselves, thereby speeding up the research process.
+Partridge's main objective is to provide reading recommendations and
+information retrieval for scientists and researchers. This should reduce the
+amount of extraneous information that users have to read for themselves by
+helping them find information specific to their interests more quickly.
 Partridge will achieve this through the use of several existing techniques in
@@
 
-There are already several tools that help researchers manage the vast library
-of journals available on the internet. Search engines such as Google
-({\url{http://www.google.com/}}), and social citation management tools such as
-CiteULike ({\url{http://www.citeulike.org}}), do offer some assistance in
-tracking down relevant information. However, these tools are often too general
-or rely upon the user knowing exactly what keywords to use before carrying out
-the search. These drawbacks are further discussed in Section
-\ref{sec:prior_art} below.
+Search engines such as Google ({\url{http://www.google.com/}}), and social
+citation management tools such as CiteULike ({\url{http://www.citeulike.org}}),
+do offer some assistance in tracking down relevant information. However, these
+tools are often too general or rely upon the user knowing exactly what keywords
+to use before carrying out the search. These drawbacks are further discussed in 
+Section \ref{sec:prior_art} below.
 
@@
 this, Partridge will build upon the system implemented by Liakata et al. for
-classifying papers on a sentence-by-sentence basis\cite{citeulike:10444769} and
-make use of Natural Language Toolkit for Python
-\cite{bird2009natural}
+recognising hypotheses, methods, results, conclusions and a number of other
+scientific concepts in scientific articles \cite{citeulike:10444769}. The
+Natural Language Toolkit for Python will also be used to build models for
+recognising different fields and topics, classifying results as positive or
+negative and recognising different types of papers, from case studies to
+methodology papers\cite{bird2009natural}.
 
@@
 
-\appendix
 \section{System Process Diagrams}
@@
 
-\appendix
 \section{Project Timeline}
@@
 
-\appendix
 \section{Project Wiki}

### 2012-11-15 doc/progress_plan/report.tex
Finished rewriting background and started rewriting similar systems, also working on 'what I've done' but

@@
 
-\subsection{Literature Review}
+\subsection{Background}
 
+\subsubsection{Artificial Intelligence}
 In science fiction literature and films, Artificial Intelligence (AI) and the
@@
 and learn from knowledge, to be able to reason about what it knows and to be
-able to process natural language\cite{russell2010artificial}. Partridge will
-also need to be able to process natural language and learn from any
-observations it makes. It is reasonable to consider Partridge's backend system
-to be an Artificial Intelligence problem. Primarily, Patridge can be considered
-a Natural Language Processing problem.
+able to process natural language\cite{russell2010artificial}.
 
@@
 
-Natural Language Processing (NLP) is still a relatively unexplored discipline
-and as such is a very active area of research and development within the AI
-community\cite{liddy2001natural}. NLP enables the automated extraction of
-meaningful information from texts written in human languages such as English or
-French. NLP has already been applied to many text classification and data
-extraction problems. Studies have been carried out in the detection of emotions
-in suicide notes\cite{citeulike:11077287}, the classification of a web page's
-genre on the World Wide Web\cite{citeulike:11288938} and emotional polarity
-(determining the positive or negative implications of) of a phrase or
-sentence\cite{Wilson05Polarity}. Liddy(2001) defines Natural Language
-Processing as:
+Natural Language Processing (NLP)  enables the automated extraction of
+meaningful information from texts written in human languages such as French or
+English. Liddy(2001) defines Natural Language Processing as:
 
@@
 analysis for the purpose of achieving human-like language processing for a
-range of tasks or applications \it{(Ibid)}.  
+range of tasks or applications \cite{liddy2001natural}.  
 \end{quotation}
 
-In the case of Partridge, scientific papers, constituting the naturally occuring
-texts, are processed at sentence-by-sentence and word-by-word levels of
-linguistics and represented in the form of Extended Markup Language (XML)
-documents, a format that is both human and machine readable. This information
-is then used for the purpose of classifying and searching papers in a
-human-like way.
-
-It is therefore necessary to define what a 'human-like way' of processing
-scientific papers.  Krug (2005), suggests that when browsing the internet,
-humans find it much easier to locate specific information within a labelled and
-logically structured document than one that is provided as a single text
-entity\cite{Krug:2005:DMM:1051204}. In order to help humans to find relevant
-research papers, Partridge will represent all papers in its repository in a
-logical hierarchical structure. This will facilitate better information
-retrieval for keyword searches and enable more advanced NLP techniques.
-Partridge's document storage format should therefore be standardised to provide
-a uniform way of processing each document.
+Over the last 60 years, NLP has been used in a wide variety of applications
+such as automated translation between languages\cite{hutchins2004first}, the
+engineering of systems for querying databases using natural languages
+\cite{rao2010natural} and for building `chatterbot' systems designed to
+communicate with their users in a human-like way\cite{Alfonsi2006}.
+More recently, NLP has been used for text classification purposes such as
+classifying emotions within phrases and sentences \cite{Wilson05Polarity} and
+even within suicide notes \cite{citeulike:11077287}.
 
@@
 
-Soldatova and Liakata(2007) proposed a methodology for storing the Core
-Information about Scientific Papers (CISP) as a way to formally represent
-scientific concepts that should be present in the articles in a logical
-ontology\cite{soldatova2007ontology}. They then proceed to define a schema for
-their CISP ontology that defines the Core Scientific Concepts (CoreSC) as part
-of the XML document itself\cite{liakata2008guidelines}.
+Liakata et al. (2012) describe a system for automatically processing and
+classifying sentences in a research paper according to the scientific concept
+they describe (e.g. a sentence can be categorised as a hypothesis, background
+information, a method or similar)\cite{citeulike:10444769}. SAPIENTA
+(\url{http://www.sapientaproject.com}) is a machine learning application,
+trained using a corpus of physical chemistry and biochemistry research papers
+that were pre-processed and annotated using Core Information about Scientific
+Papers (CISP)\cite{LIAKATA10.644}.
 
-It is proposed that Partridge uses the CoreSC schema for document storage
-to provide a standard way to access and process the papers and thus
-eliminate dealing with multiple documents during its learning phase. 
-Using CoreSC also offers the advantage of making Partridge compatible
-with the ART corpus. This is a set of physical chemistry and biochemistry
-research papers that have been pre-processed and already annotated using CISP
-concepts\cite{liakataART}. This would provide Partridge with a set of papers
-that could be used as a training set for classification tasks and could be used
-for information retrieval tests from early on in the project.
-
-Liakata et al. (2012) describe a system for automatically processing and
-categorising sentences in a research paper according to their respective CoreSC
-element\cite{citeulike:10444769}. SAPIENTA
-(\url{http://www.sapientaproject.com}) was trained using the ART corpus and can
-achieve promising accuracies when categorising sentences (\emph{Ibid}). With
-the authors' permissions, Partridge will make use of SAPIENTA when introducing
-new papers into its repository. It is hoped that preclassifying papers with
-SAPIENTA will make the development of Partridge more manageable within the
-timeframe available and will also allow more effort to be put into other
-classification problems rather than re-implementing a SAPIENTA clone. Any
-modifications that have to be made to SAPIENTA to integrate it into Partridge
-will be submitted back to the original authors to assist them in their research.
-
-After pre-processing by SAPIENTA is complete, Partridge will need to do some
-classification work of its own to determine the area of study (i.e. Physics,
-Chemistry, Biology), type of paper (Literature review, Case Study, Experiment)
-and the polarity of the result (positive, negative, inconclusive). These tasks
-involve implementing existing AI techniques and applying them specifically to
-the task of text classification. To avoid the time consuming task of
-re-implementing these methods, it was decided that a library should be used
-instead. Different NLP libraries and their properies are discussed below in
-Section \ref{sec:libschoice}.
+CISP, Soldatova and Liakata(2007), is a way to formally represent core
+scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
+should be present in the articles in a logical
+ontology\cite{soldatova2007ontology}. Subsequent work implements this set of
+concepts as a three layered sentence based annotation scheme (CoreSC scheme)
+where annotations are encoded in Extended Markup Language
+(XML)\cite{LIAKATA10.644}.
 
@@
 (\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
-(\url{http://www.ask.com}). There are many more similar systems available for
-free general use across the internet.  They all present very similar user
-interfaces (as shown in Figure \ref{fig:search_interfaces}) in which users are
-asked to supply keywords that might be linked to relevant documents and the
-search engine returns a list of Uniform Resource Locators (URLs) that they
-consider to match the user's query.
-
-\begin{figure}[!ht]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/ask_front.png}
-                \caption{Ask.com}
-                \label{fig:ask_interface}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/bing_front.png}
-                \caption{Bing.com}
-                \label{fig:bing_interface}
-        \end{subfigure}\\
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/google_front.png}
-                \caption{Google.com}
-                \label{fig:google_interface}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/yahoo_front.png}
-                \caption{Yahoo.com}
-                \label{fig:yahoo_interface}
-        \end{subfigure}%
-        \caption{4 popular search engine interfaces}\label{fig:animals}
-        \label{fig:search_interfaces}
-\end{figure}
-
-Search engines are helpful in locating pages and websites within the World Wide
-Web. Unfortunately, the problem space they deal with is usually too big for
-them to find scientific papers and journals given a set of keywords. Internet
-search engines index a huge proportion of irrelevant information compared to
-useful information\cite{Berghel1997}, and as a result, even relatively specific
-queries such as ``effects of gravity on rockets" yield millions of results (as
-shown in Figure \ref{fig:rocket_results}).
+(\url{http://www.ask.com}).
 
@@
 
-Partridge offers an advantage over these mechanisms as it will specifically
-index research papers rather than attempting to index the whole Internet.
-This means that there should be a higher proportion of useful information as
-output compared to the output of an Internet Search Engine.
+Despite their use as general search tools on the World Wide Web, the problem
+space that search engines deal with is usually too big for them to find
+scientific papers and journals given a set of keywords. Internet search engines
+index a huge proportion of irrelevant information compared to useful
+information\cite{Berghel1997}, and as a result, even relatively specific
+queries such as ``effects of gravity on rockets" yield millions of results (as
+shown in Figure \ref{fig:rocket_results}). This shortcoming has already led to
+the development of search engines designed specifically to find scientific
+papers.
 
 \subsubsection{Scientific Paper Search Engines}
+
 There are also a number of search and indexing systems that specifically look
@@
 
-Partridge will provide the option to filter papers by subject and it is hoped
-that the system will also provide user-specific recommendations by profiling
-them through their reading history. This will make it easier for users to find
-relevant papers without knowing exactly which keywords they need to search for.
-Partridge will also offer facilitate searching for keywords within a specific
-CoreSC section by making use of Liakata et al's SAPIENTA project for
-classifying each sentence of paper as it is added to the repository.
-
 \subsubsection{Social Citation and Recommendation Engines}
@@
 discriminatory information that could be contained within the actual document
-content is overlooked completely. Partridge will analyse documents on a
-sentence-by-sentence and possibly word-by-word basis, thereby taking account of
-any embedded information that could be missed by these social metadata systems.
+content is overlooked completely.
 
@@
 
-A prototype script was written using a Python PDF extraction library called
-PDFMiner (\url{http://www.unixuser.org/~euske/python/pdfminer/index.html}).
-This toolkit already contains some heuristics about how to extract text from
-PDF documents in a sane way\cite{pdfminer}. The script then used the NLTK
-library to split the text into sentences and save the document in a CoreSC
-compatible format for processing by SAPIENTA.
+This was the first big challenge in the project. A prototype script was written
+using a Python PDF extraction library called PDFMiner
+(\url{http://www.unixuser.org/~euske/python/pdfminer/index.html}).  This
+toolkit already contains some heuristics about how to extract text from PDF
+documents, grouping together characters that appear very close to each other,
+and separating paragraphs and headings when a larger area of whitespace is
+detected\cite{pdfminer}. Despite these rules, the library still produced some
+extraneous whitespace and newline characters as part of the output. A
+subroutine to trim whitespace and newlines was added to the script to resolve
+this problem.
 
-The script had limited success due to the high variation of formatting within
-scientific papers. It was suggested that PDFX (\url{http://pdfx.cs.man.ac.uk/})
-a free service hosted by the university of manchester, could be used instead of
-PDFMiner. PDFX's main advantage is that it uses a machine learning system to
+The next stage was to split the text into sentences in preparation for
+processing with SAPIENTA. With the assistance of the NLTK library, a sentence
+splitting subroutine was implemented. This used a machine learning algorithm
+that had been trained to recognise sentence boundaries to split the text. Each
+sentence was then added to a CoreSC compatible XML document for processing by
+SAPIENTA.
+
+Initially, the PDF conversion subroutine had a very high error rate due to high
+variation in the formatting of scientific papers. It was suggested that PDFX (\url{http://pdfx.cs.man.ac.uk/})
+a free service hosted by the University of Manchester could be used instead of
+PDFMiner for the initial PDF data extraction. The main advantage of PDFX over
+the PDFMiner library is that is a trained machine learning system that has been
+trained using a large full-text selection of articles; PDFX's classifier is
+more suited to paper conversion than PDFMiner's more general heuristic
+approach.
+
+PDFX's main advantage is that it uses a machine learning system to
 guess PDF document structures more accurately than through the use of simple

### 2012-11-15 doc/progress_plan/report.tex
Finished talking about pdf extraction stuff

@@
 
+\subsubsection{ Sourcing Scientific Papers}
+For Partridge to be a success, it is important to include a large variety of
+different scientific papers in its corpus. Therefore, several sources of
+scientific papers were explored and considered.
+
 \subsubsection{PDF Conversion}
@@
 
-Initially, the PDF conversion subroutine had a very high error rate due to high
-variation in the formatting of scientific papers. It was suggested that PDFX (\url{http://pdfx.cs.man.ac.uk/})
-a free service hosted by the University of Manchester could be used instead of
-PDFMiner for the initial PDF data extraction. The main advantage of PDFX over
-the PDFMiner library is that is a trained machine learning system that has been
-trained using a large full-text selection of articles; PDFX's classifier is
-more suited to paper conversion than PDFMiner's more general heuristic
-approach.
+Initially, the PDF conversion subroutine had a very high error rate due to the
+variation in the formatting of scientific papers. It was suggested that PDFX
+(\url{http://pdfx.cs.man.ac.uk/}) a free service hosted by the University of
+Manchester could be used instead of PDFMiner for the initial PDF data
+extraction. The main advantage of PDFX over the PDFMiner library is that is a
+trained machine learning system that has been trained using a large full-text
+selection of articles; PDFX's classifier is more suited to paper conversion
+than PDFMiner's more general heuristic approach.
 
-PDFX's main advantage is that it uses a machine learning system to
-guess PDF document structures more accurately than through the use of simple
-Heuristics. With an adapted backend that sends PDFs for analysis using PDFX and
-then splits the results using NLTK, the conversion script now has a much higher
-success rate and will be used as a preprocessor for adding PDF  documents to
-Partridge.
+PDFX also provides output that already has some metadata, such as title,
+author, and abstract, associated with it. PDFMiner did not provide any
+metadata, and it was necessary for the script to guess which passage of text
+was the abstract after the initial text extraction stage.
+
+With the new PDF extraction method in place, the script ran without the need
+to modify either of the whitespace sanitiser or sentence splitter routines. The
+process was much more successful and able to produce SAPIENTA-compatible
+documents from most of the PDF input files that were provided.
 

### 2012-11-15 doc/progress_plan/report.tex
Talking about research papers and sources

@@
 
+The most convenient and accessible source is the ART corpus that SAPIENTA was
+trained with\cite{citeulike:11077287}. This corpus is already stored using the
+CoreSC schema and has been pre-annotated. This means that Partridge would not
+need to do any conversion or pre-processing on the papers. These scientific
+papers are all chemistry papers. Therefore, more papers from other scientific
+domains are needed to get a wider variety of topics and make Partridge useful
+to as wide an audience as possible.
+
 \subsubsection{PDF Conversion}

### 2012-11-15 doc/progress_plan/report.tex
Currently talking about sapienta python edition and problems with crfsuite

@@
 variation in the formatting of scientific papers. It was suggested that PDFX
-(\url{http://pdfx.cs.man.ac.uk/}) a free service hosted by the University of
+(\url{http://pdfx.cs.man.ac.uk/}), a free service hosted by the University of
 Manchester could be used instead of PDFMiner for the initial PDF data
-extraction. The main advantage of PDFX over the PDFMiner library is that is a
+extraction. The main advantage of PDFX over the PDFMiner library is that it is a
 trained machine learning system that has been trained using a large full-text
-selection of articles; PDFX's classifier is more suited to paper conversion
-than PDFMiner's more general heuristic approach.
+selection of scientific articles; PDFMiner uses more general heuristics
+designed to process a large selection of different types of PDF document.
 
@@
 documents from most of the PDF input files that were provided.
+
+\subsubsection{Pre-processing with SAPIENTA}
+
+With a successful PDF conversion script, the next step was to try and run
+SAPIENTA over the converted papers and annotate them, ready for inclusion in
+the Partridge corpus.
+
+By default, SAPIENTA is packaged as a web-based tool, written in Java, that
+can be downloaded (from \url{http://www.sapientaproject.com/software}) and used
+to annotate one paper at a time. Dr Liakata was able to provide information on
+two alternative ways of using the system. One method was to submit a remote
+procedure call (RPC) to a server running SAPIENTA with a batch of papers and
+retrieve the output. The other method was to use an alternative version of the
+code that runs locally in a Python environment and could be modified to process
+papers as a batch.
+
+A script was written to send un-annotated XML documents to the remote SAPIENTA
+server and retrieve a list of annotations. This worked well until the server
+stopped replying to requests. This meant that no further conversions could be
+carried out until the server was repaired and raised concerns about how the
+remote servers might cope with a large number of automated requests from a
+full version of Partridge.
+
+The Python version of SAPIENTA was then installed
 

### 2012-11-16 doc/progress_plan/report.tex
Added crf mailing list problem appendix

@@
 performance of the application, but the speed at which the project is developed
-and the portability of the end code \cite{britton2008}. To avoid a learning
-overhead, it was decided that the programming language should be one that the
-author is familiar with. This reduced the choice of language down to C, Java
-and Python.
-
-The C programming language was invented by Kernighan and Ritchie and
-published in 1978\cite{ritchie1978c}. The language is small and
-optimised\cite{prinz2002c} and therefore compiled C programs tend to run
-extremely fast. Unfortunately, C is designed to be general and lack restriction
-\cite{ricthie1978c} which is often an advantage for programmers who favour
-optimised code over excessive error checking. However, this means that
-debugging C programms can be quite long winded and challenging. Since the NLP
-aspects of Partridge present an amibitious challenge in themselves, having to
-debug applications without help from a managed programming environment is not
-desirable.
-
-The Java programming language on the other hand, does provide memory management
-and error checking\cite{Coffey2008} at the cost of program performance. Java is
-a pseudo-compiled language that is translated into bytecode then interpreted at
-runtime by a Virtual Machine(VM) on the client computer. Gosling (2000)
-describes java as a ``general-purpose...  programming language [that allows]
-developers to write a program once and then be able to run it everywhere on the
-internet\cite{gosling2000java}." Java provides a stable programming environment
-and error checking, both of which would be advantageous in the development of
-Partridge. Java's syntax is very verbose and a lot of `boiler-plate' code must
-be written before a program can be executed.  Therefore Java is not suitable as
-a rapid prototyping language. Since Partridge's development requires a steep
-learning curve for the author, a language that allows quick prototyping with
-minimal programming.
+and the portability of the end code \cite{britton2008}. It was decided that
+Python would be the best language for developing Partridge.
 
@@
 inefficient sections of Python code could be re-written as C extensions and
-compiled into the application. For these reasons, Python was selected as the
-preferred programming language for Partridge development.
+compiled into the application.
+
+Other languages that were considered were Java and C. However, it was decided
+that Python's clean syntax and ease of use for prototyping were preferable to
+the C and Java style syntax. As stated above, C may still be used in part for
+developing Python extensions to improve the overall performance of the
+application.
 
@@
 
-It is possible to use a separate software stack Such as Apache web server
-(\url{http://httpd.apache.org/}) and PHP (\url{http://www.php.net}) as a web
-presentation layer. However, this would involve adding more software to the
+For this purpose, the Flask (\url{http://flask.pocoo.org}) library was chosen.
+Flask is a python `microframework' for web development. Ronacher (2012) writes
+that ``Flask aims to keep the core simple but extensible...[and] won't make any
+decisions for you\cite{flask2012}." It uses a simple templating system that can
+optionally be swapped out for an equivalent system and does not impose any
+limitations or requirements on the layout of the program or the type of
+database that is used. Flask also integrates very simply into existing software
+using Python annotations\emph{(Ibid)}.
+
+An alternative approach that was considered was using a separate software
+stack such as the Apache web server (\url{http://httpd.apache.org/}) and PHP 
+(\url{http://www.php.net}). However, this would involve adding more software to the
 project and building an interface between the PHP scripts and Partridge's
-python backend. To prevent unnecessary complication, this approach will be
-avoided and instead, a Python web toolkit will be used and integrated directly
-with the backend.
+python backend. The Django framework (\url{http://www.djangoproject.com/}) for Python was also
+considered but it was determined to be overly complicated in terms of
+Partridge's requirements.
 
-Django (\url{http://www.djangoproject.com/}) is a Python web framework with
-integrated database management and templating capabilities \cite{django2012}.
-The framework provides automatic management of all aspects of your
-application's data storage systems unless explicitely disabled. The framework
-also uses a fairly stricty Model-View-Controller pattern and this is enforced
-in the structure of the application code. These features may be useful in a
-general web application such as a news site. Partridge requires a much more
-complex internal structure to take into account the machine learning and NLP
-aspects of the system. Having to `shoehorn' Partridge into a specific structure
-to make it compatible with Django adds extra overhead to the project and is not
-desirable.
+\subsubsection{Natural Language Libraries} \label{sec:libschoice}.
 
-Flask (\url{http://flask.pocoo.org}) is a python `microframework' for web
-development. Ronacher (2012) writes that ``Flask aims to keep the core simple
-but extensible...[and] won't make any decisions for you\cite{flask2012}." It
-uses a simple templating system that can optionally be swapped out for an
-equivalent system and does not impose any limitations or requirements on the
-layout of the program or the type of database that is used. Flask integrates
-very simply into existing software using Python annotations\emph{(Ibid)}. This approach
-means that the framework could be adapted to Partridge very quickly, rather
-than requiring Partridge to be adapted to the framework. Therefore, Flask has
-been chosen as the preferred web framework for use in the project.
+It was decided that a pre-existing NLP library should be used to provide
+implementations of existing algorithms and techniques for Partridge. For this
+purpose the The Natural Language Toolkit (NLTK) was selected. The NLTK is a
+simple and intuitive library written for Python. Bird(2009) states that NLTK
+was designed ``to provide an intuitive framework along with substantial
+building blocks, giving users a practical knowledge of
+NLP\cite{bird2009natural}". NLTK provides implementations for sentence
+splitting, tagging (the process of analysing sentences and classifying words as
+verbs, nouns etc.), and information retrieval from text \emph{(Ibid)}. NLTK
+also provides implementations of classifiers and a framework for extracting
+features to be used for classification from text. There is also a free book
+that accompanies the project available at \url{http://nltk.org/book/} which
+provides a huge amount of information on how to implement many popular NLP
+techniques using the library.
 
-\subsubsection{Natural Language Libraries} \label{sec:libschoice}.  There are
-several existing libraries to facilitate Natural Language Processing.  Many are
-written for Java \cite{mallet2002}\cite{cunningham2011text} and are very
-complex or not well documented. The Natural Language Toolkit (NLTK) is a simple
-and intuitive library written for Python. Bird(2009) states that NLTK was
-designed ``to provide an intuitive framework along with substantial building
-blocks, giving users a practical knowledge of NLP\cite{bird2009natural}". The
-project is relatively mature in comparison to the above named Java libraries.
-There is also a free book that accompanies the project available at
-\url{http://nltk.org/book/} which provides a huge amount of information on how
-to implement many popular NLP techniques using the library. For this reason
-NLTK was chosen as the primary accompanying library for the project.
+Some other libraries were considered\cite{mallet2002}\cite{cunningham2011text}.
+However, these were written for Java and Partridge is a python project. They
+also require a steeper learning curve than NLTK.
 
@@
 to as wide an audience as possible.
+
+The `mega-journals' PLOS ONE \url{http://www.plosone.org/} and arXiv
+\url{http://www.arxiv.org/} were suggested as sources for more open access
+articles that could be added to Partridge. Both of these sites were found to
+contain large volumes of open access papers. However, most of these papers were
+published as PDF files which meant that some conversion would be required to
+make them compatible with Partridge.
 
@@
 
-The Python version of SAPIENTA was then installed
+The Python version of SAPIENTA was then downloaded and a test executed.
+Unfortunately there were several data files missing from the package that had
+to be acquired from Dr Liakata.
+
+SAPIENTA for Python also relies upon a package called CRFSuite which implements
+Conditional Random Fields, a method for segmenting and labelling sequence
+data\cite{CRFsuite}. This library did not compile properly on the test
+environment and its creator had to be contacted via a mailing list (See
+Appendix \ref{sec:crfletter}.
 
@@
 
+\section{Email for CRFSuite}
+\label{sec:crfemail}
+\input{crfletter}
+
 \section{Project Timeline}

### 2012-11-16 doc/progress_plan/report.tex
Finished talking abotu sapienta

@@
 environment and its creator had to be contacted via a mailing list (See
-Appendix \ref{sec:crfletter}.
+Appendix \ref{sec:crfletter}. After a few days, the owner responded and the
+library was compiled successfully.
+
+Once all the data files and libraries were successfully in place, the Python
+version of SAPIENTA was used to process some of the papers converted from PDF.
+This was a great success and the annotations provided by SAPIENTA seemed to be
+accurate.
 

### 2012-11-16 doc/progress_plan/appendix.tex
Finished compiling appendicies

\appendix
\section{User Interface Designs}
\label{sec:ui_designs}

\subsection{ Partridge Query Interface}

Figure \ref{fig:ui_mockup} shows the user interface that will be utilised to
search and query Partridge's corpus.

The query form shows two main sections: Filters and Keywords.

Filters can be used to show a large set of papers where the user is unsure of
what to search for. Users will be able to look for papers by type and topic as
discussed above. The paper result filter has not been included in this diagram.
However, it is expected that a drop down menu for result type would be included
in the filters section of the form.

Keywords allows the user to look for a set of keywords that is specifically
within a CoreSC concept for a paper. For example, the reader may want to find
experiments that use a server farm to do lots of calculations. Therefore, they
would enter ``Server Farm" as their keywords and chose ``Method" from the paper
section. The user then adds this to the set of keyword queries in the table
below the text field with the add button.

Once a user has configured both filters and keywords to their preferences, they
click the search form to run the search itself.

Other notable features on this mockup include a list of most recent searches.
This helps the user to understand how to use Partridge and gives them some
suggestions for what they might search for. Similar listings are provided for
the most popular papers in the Partridge database and the most recent papers
added to the system.

\begin{figure}[!ht]
\includegraphics[width=\textwidth]{images/mockup_1.png}
\caption{User interface design for querying Partridge}
\label{fig:ui_mockup}
\end{figure}

\section{System Process Diagrams}
\label{sec:system_diagrams}

This section documents the system process diagrams that have been produced. The
first completed diagram shows how a paper will be added to Partridge and the
actions that will be carried out upon it.

\subsection{Adding a Paper to Partridge}

\begin{figure}[!ht]
\includegraphics[width=0.75\textwidth]{images/PaperAddedProcess.png}
\caption{The process of adding a new paper to Partridge}
\end{figure}

The system starts off by converting the document to XML from PDF if necessary
through the use of the PDFX tool provided by Manchester University. A sentence
splitting tool is then used to parse the resulting document and separate the
sentences.

Once the sentences have been split, Maria's SAPIENTA tool is used to annotate
each sentence to determine which of the core scientific concepts it covers.
This information is stored back in the XML file with the document.

After this, feature extraction is carried out upon the document to find useful
features for the following classification tasks:

\begin{enumerate}
\item Paper topic/subject -i.e. is the paper a biology paper or a computer science paper?
\item Type of paper - i.e. is the paper a case study, an experiment or a literature review?
\item Paper result - i.e. did the paper have a positive, negative or inconclusive result?
\end{enumerate}

These classifiers are then run (they could potentially be run in parallel if
processing power is available) to determine the paper's class for each
classifier respectively. The data gathered along with any paper metadata
captured such as title, author, date, institute etc are then stored in the
database.

\section{Email for CRFSuite}
\label{sec:crfemail}
\input{crfletter}

\section{Project Timeline}
\label{sec:timeline}

This table shows the projected timeline for the Partridge project. These
calculations were carried out under the assumption of 2 full days of work per
week on the project and one iteration equating to one month (28 days). There
will be 7 iterations in total and after each, a new version of Partridge will
be made available (except for iteration zero which is a research only
iteration).

\begin{figure}[htp] 
 \vspace{ -1cm }
 \centering{\includegraphics[scale=0.60,page=1]{../timeline.pdf}}

\end{figure}

\begin{figure}[!htp] 
 \centering{\includegraphics[scale=0.60,page=2]{../timeline.pdf}}
 \vspace{-2cm}
\centering{\includegraphics[scale=0.60,page=3]{../timeline.pdf}}
\end{figure}

\pagebreak
\section{Project Wiki}
\label{sec:wiki}

All pages from the Wiki are shown below with the exceptions of those pages
which have already been mostly featured in the document (UI Mockups and
Progress Diagrams and the project timetable are not shown in this section).

\subsection{ Notes 03/10/2012 }
\input{wiki/Notes-03-10-2012}

\subsection{ Notes 10/10/2012 }
\input{wiki/Notes-10-10-2012}

\subsection{ Notes 19/10/2012 }
\input{wiki/Notes-19-10-2012}

\subsection{ Notes 24/10/2012 }
\input{wiki/Notes-24-10-2012}

\subsection{ Notes 31/10/2012 }
\input{wiki/Notes-31-10-2012}

\subsection{ Notes 07/11/2012 }
\input{wiki/Notes-07-11-2012}

\pagebreak
\bibliographystyle{IEEEannot}
\bibliography{report}

### 2012-11-16 doc/progress_plan/report.tex
Finished compiling appendicies

@@
 \usepackage{fullpage}
-
+\usepackage{pdfpages}
 %use the listings package
@@
 the sorts of materials that you might be interested in and provide lists of
-recommendations as in Figure \ref{social_indexes}.
+recommendations as in Figure \ref{fig:social_indexes}.
 
@@
 environment and its creator had to be contacted via a mailing list (See
-Appendix \ref{sec:crfletter}. After a few days, the owner responded and the
+Appendix \ref{sec:crfemail}. After a few days, the owner responded and the
 library was compiled successfully.
@@
 
-\appendix
-\section{User Interface Designs}
-\label{sec:ui_designs}
-
-\section{System Process Diagrams}
-\label{sec:system_diagrams}
-
-\section{Email for CRFSuite}
-\label{sec:crfemail}
-\input{crfletter}
-
-\section{Project Timeline}
-\label{sec:timeline}
-
-\section{Project Wiki}
-\label{sec:wiki}
-
-\bibliographystyle{IEEEannot}
-\bibliography{report}
+%include document appendix
+\input{appendix}
 

### 2012-11-16 doc/progress_plan/wiki/Notes-03-10-2012.tex
Finished compiling appendicies

\subsection{Meeting Notes from 03/10/2012}

\subsubsection{General topics}

\begin{itemize}
\item
  Talked about using research papers instead of books :-
\item
  copyright issues - mainly resolved because of Gutenburg project
\item
  processing issues - too much information to process quickly and
  realistically
\item
  Maria has some software for identifying sections in papers - could be
  used to help locate specific features
\item
  There are quite a few sources for papers that could be used for the
  project:
\item
  http://arxiv.org/
\item
  http://plosone.org/
\item
  Maria's papers are in XML format
\item
  Formatting may or may not be an issue - PDFs are a nightmare to parse
\end{itemize}

\subsubsection{Things to consider}

\begin{itemize}
\item
  What sort of recommendations for different sources might there be and
  how would these recommendations be extracted?
\item
  Feature engineering - what sorts of features might there be to pick
  out in the papers?
\item
  I need to have a read through the sentiment analysis paper that Maria
  has been working on
\item
  I need to have a play with the software for identifying sections in
  papers.
\end{itemize}

\subsubsection{Misc concerns}

\begin{itemize}
\item
  Decided that our weekly meeting should be Wednesdays at 3pm
\item
  Investigate setting up source control and a wiki (that's been done as
  you can tell)
\end{itemize}

### 2012-11-16 doc/progress_plan/wiki/Notes-31-10-2012.tex
Finished compiling appendicies

\subsection{James' Meeting Notes}

\subsubsection{To Think about}

\begin{itemize}
\item
  Discussed imminent deadline for project progress report - 19/11/2012
\item
  Decided that having a report finished by 14/11/2012 would be a good
  report to give Amanda and Maria a chance to check over the report
  before handin.
\item
  Maria explained that it is possible to send a batch of papers to
  Sapienta rather than one at a time. She is going to provide
  information on how this can be achieved at some point during the week.
\item
  I should describe my working processes and why they are helpful.
\end{itemize}

\subsubsection{Todo}

\begin{itemize}
\item
  We discussed the merits of using the pdfx converter instead of my
  script - might have plug-and-play compatibility with Sapienta for a
  start - need to verify this.
\item
  I need to send my error message the CRFSuite compilation to Maria so
  that she can contact the maintainer.
\item
  I need to expand on the system outline providing more specific goals
  and timeframes - this will become my development plan.
\item
  I need to look at textpresso and see if it will help me with my
  comparison/evaluation
\end{itemize}

### 2012-11-18 doc/progress_plan/report.tex
Made a few changes to the report in terms of punctuation and whatnot

@@
 
-From the point of view of it's users, Partridge will assist researchers in two
+From the point of view of its users, Partridge will assist researchers in two
 ways. The system will provide filtering of papers based upon their
@@
 implementing the above features will be incredibly challenging. To help with
-this, Partridge will build upon the system implemented by Liakata et al. for
+this, Partridge will build upon the system implemented by Liakata \emph{et al.} for
 recognising hypotheses, methods, results, conclusions and a number of other
@@
 almost always taken for granted. The current state of AI is a long way behind these
-fantastic visions. Dale(2000) comments that ``Even the most ardent exponent of
+fantastic visions. Dale (2000) comments that ``Even the most ardent exponent of
 artificial intelligence research would have to admit that the likes of HAL in
@@
 an umbrella term, describing many subfields from ``learning and perception
-to... diagnosing diseases\emph{(Ibid)}."
+to... diagnosing diseases\emph{(Ibid.)}."
 
-Turing(1950) proposed a test for determining whether a machine could be
+Turing (1950) proposed a test for determining whether a machine could be
 considered intelligent or not\cite{turing1950computing}. Turing's test is based
@@
 meaningful information from texts written in human languages such as French or
-English. Liddy(2001) defines Natural Language Processing as:
+English. Liddy (2001) defines Natural Language Processing as:
 
@@
 
-Liakata et al. (2012) describe a system for automatically processing and
+Liakata \emph{et al.} (2012) describe a system for automatically processing and
 classifying sentences in a research paper according to the scientific concept
@@
 
-CISP, Soldatova and Liakata(2007), is a way to formally represent core
+CISP, Soldatova and Liakata (2007), is a way to formally represent core
 scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
@@
 database that is used. Flask also integrates very simply into existing software
-using Python annotations\emph{(Ibid)}.
+using Python annotations\emph{(Ibid.)}.
 
@@
 purpose the The Natural Language Toolkit (NLTK) was selected. The NLTK is a
-simple and intuitive library written for Python. Bird(2009) states that NLTK
+simple and intuitive library written for Python. Bird (2009) states that NLTK
 was designed ``to provide an intuitive framework along with substantial
@@
 splitting, tagging (the process of analysing sentences and classifying words as
-verbs, nouns etc.), and information retrieval from text \emph{(Ibid)}. NLTK
+verbs, nouns etc.), and information retrieval from text \emph{(Ibid.)}. NLTK
 also provides implementations of classifiers and a framework for extracting
@@
 spike work was carried out to determine the feasibility of converting papers
-published as PDF documents into XML documents. Townsendi et al(2009) liken converting
+published as PDF documents into XML documents. Townsendi \emph{et al.} (2009) liken converting
 PDF to XML to ``converting hamburgers into cows," they go on to explain that
@@
 
-As an alternative to the heavyweight Waterfall approach, Beck et al came up
+As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.} came up
 with the principle of the Agile Manifesto, favouring a lightweight, responsive
@@
 system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
-of developers and prioriting communication between team members \emph{(Ibid)}.
+of developers and prioriting communication between team members \emph{(Ibid.)}.
 This is most prominent in the Extreme Programming (XP) method of software

### 2012-11-18 doc/progress_plan/wiki/Notes-07-11-2012.tex

\subsection{Notes from 7/11/2012}

\subsubsection{Discussed}

\begin{itemize}
\item
  What I'll need to have for my demo:

  \begin{itemize}
  \item
    Simple web interface
  \item
    Few basic classifiers - probably result of paper positive/negative
    and maybe paper type - proportions of coreSC concepts.
  \item
    Could show off PDF to XML converter script
  \end{itemize}
\end{itemize}

\subsubsection{To Consider}

\begin{itemize}
\item
  Is the disparity between bio paper CoreSC classification and other
  sorts of paper to do with Sapienta's model or does it demonstrate a
  feature - different subjects may have different proportions of each
  concept.
\item
  If I'm using distribution of concepts as an aggregate feature, I need
  to make sure the system does not fall over if a concept is missing.
\item
  Front end interface:
\item
  Need to find a new word for `section' Scientific Concept may be a bit
  too `scary', is there a better term for this?
\item
  If I allow users to upload papers, they must sign a digital disclaimer
  to say that they have the right to do so
\item
  There should be a ``report copyrighted material'' system
\end{itemize}

\subsubsection{To Do}

\begin{itemize}
\item
  Biggest task this week: Progress Report.

  \begin{itemize}
  \item
    Draft due 14/11/2012 for discussion on 15/11/2012
  \item
    Final deadline 19/11/2012
  \item
    Could provide wiki content as an appendix to the report
  \item
    Come up with a project timeline - actually consider dates
  \item
    Start with the web interface and work upwards.
  \end{itemize}
\item
  Send Maria the missing header file from crfsuite
\item
  Link system outline from wiki index
\item
  Maria said she'd look for a topic detection paper for me to peruse
\item
  I need to have another look at relevant features - struggling with
  this
\item
  Make a wiki list of features that could be used for classification
\end{itemize}

### 2012-11-18 doc/progress_plan/wiki/Notes-10-10-2012.tex

\subsection{Meeting Summary 10/10/2012}

\subsubsection{From Maria's notes}

\begin{itemize}
\item
  James has gone through papers and thinks would be more doable to work
  with papers than Books
\item
  James has found the XML format of PlosOne and ART/CoreSC corpus
\item
  Domain needs to be determined
\item
  Maria to send paper on sentiment analysis of citations
\end{itemize}

\subsubsection{Current features and recommendations}

\begin{itemize}
\item
  Analysis of results section - positive or negative result
\item
  Potentially look at writing styles of authors using syntactic analysis
\item
  Isolating terms within sections of papers (i.e.~find me papers where
  methodology x was used)
\item
  finer grain analysis of CoreSC categories
\item
  nltk python toolkit. What other toolkits? Would jerboa be any good?
\item
  common features for sentiment analysis
\end{itemize}

\subsubsection{Basic system design}

I have started a basic system design although it is very basic at the
moment. [Image Omitted]

\subsubsection{Background - Similar Systems and how they work}

\begin{itemize}
\item
  Google Scholar
\item
  Mendeley
\item
  Citeulike
\item
  Tweeting or `liking' on facebook.
\end{itemize}

\subsubsection{Reading}

\begin{itemize}
\item
  TF-IDF
\item
  Take a brief look at journal of negative results
\item
  `Bigrams + trigrams' and syntactic pattern finding
\item
  Common features used in NLP
\item
  Sentiment analysis of citations in papers
\item
  `Bag of words'
\end{itemize}

\subsubsection{Coding/practical research}

\begin{itemize}
\item
  Play some more with SAPIENTA
\item
  Implement a (La)TeX to SciXML or pubmed command-line tool.
\end{itemize}

### 2012-11-18 doc/progress_plan/wiki/Notes-19-10-2012.tex

\subsection{Notes from Meeting 18/10/2012}

\subsubsection{General Comments}

\begin{itemize}
\item
  I need to decide on a domain for the project. It may be that papers on
  a varied selection of topics would be a good start
\item
  Decided on an agile development cycle with a basic program that is
  improved in `iterations'.
\item
  As part of testing the software, it may be possible to get other final
  year students to trial the engine and use it to make recommendations
  for their reading.
\item
  I need to investigate ways of analysing papers for syntactic patterns.
  This may be indicative of:

  \begin{itemize}
  \item
    Different authors' writing styles
  \item
    Different types of paper -i.e.~psychology vs physics
  \end{itemize}
\end{itemize}

\subsubsection{TODO}

\begin{itemize}
\item
  Revisit PDF to XML conversion as conversion from PDF would make life a
  lot easier
\item
  Maria mentioned that she may have access to an HTML to XML program
  which would be good to look at.
\item
  Check out python Jerboa to see if it would be useful for the project.
\end{itemize}

### 2012-11-18 doc/progress_plan/wiki/Notes-24-10-2012.tex

\subsection{Notes from meeting 24/10/2012}

Amanda was not present for this meeting.

\subsection{Discussed}

\begin{itemize}
\item
  We discussed the PDF conversion routine and decided that whilst
  important, it is crucial not to get too caught up in this.
\item
  Maria is going to send me a link to an existing PDF to XML converter
  that might provide the functionality with some tweaking - or at least
  help
\item
  We discussed the Python version of Sapienta which currently supports
  SciXML and simplified versions thereof.
\item
  Maria needs to send me a couple of data files for this to work
  properly.
\item
  Confirmed that Jerboa is a Java library (I was confused because I was
  expecting a python toolkit) and need to look at it properly now.
\item
  Discussed the actual functionality of the system and came up with a
  brief system outline, around which I can plan.
\end{itemize}

\subsection{TODO}

\begin{itemize}
\item
  Now that we know what the system is going to do (See System Outline), I need to look at features that
  will allow us to:
\item
  Pre-classify documents based on their topic, type, result etc
\item
  Determine document similarity based on user preference from their
  tagging etc. (I can make use of the ``Features in sentiment analysis''
  paper for this)
\item
  Run more tests on the PDF parser and potentially look at another
  solution if this takes up too much time.
\item
  Have a go with Python SAPIENTA once the data models are present
\end{itemize}

### 2012-11-18 partridge/tools/pdf2xml.py
Fixed import error for sys in pdfxconv and removed old pdf2xml (can always get it back)

@@ -1,198 +1,0 @@
-#!/usr/bin/python2 
-
-'''
-Python tooling for working with annotated XML papers
-
-@author James Ravenscroft
-@date 17/12/2012
-'''
-
-import sys
-import os
-import codecs
-
-from pdfminer.pdfparser import PDFParser, PDFDocument
-from pdfminer.pdfinterp import PDFResourceManager, PDFPageInterpreter
-from pdfminer.pdfdevice import PDFDevice
-from pdfminer.layout import LAParams, LTTextBox
-from pdfminer.converter import PDFPageAggregator
-from pdfminer.pdftypes import resolve1
-
-from xml.dom import minidom
-from optparse import OptionParser
-
-from nltk.tokenize import word_tokenize, sent_tokenize
-
-class SciXMLConverter(object):
-
-    title = ""
-    nextSID = 1
-
-    def convert(self, pdfinput, pdfoutput, pdfpassword="", splitsentences=False):
-        '''Given a PDF input stream, converts the text to a SciXML document
-        '''
-        #start the xml stuff
-        self.initxml()
-
-        self.splitsentences = splitsentences
-
-        self.abstractFound = False
-
-        # initialization routine adapted from PDFMiner documentation
-        # http://www.unixuser.org/~euske/python/pdfminer/programming.html
-        parser = PDFParser(f)
-        doc    = PDFDocument()
-        parser.set_document(doc)
-        doc.set_parser(parser)
-        doc.initialize(pdfpassword)
-        
-        # Check if the document allows text extraction. If not, abort.
-        if not doc.is_extractable:
-            raise PDFTextExtractionNotAllowed
-
-        # Create a PDF resource manager object that stores shared resources.
-        rsrcmgr = PDFResourceManager()
-        # Set parameters for analysis.
-        laparams = LAParams()
-        # Create a PDF page aggregator object.
-        device = PDFPageAggregator(rsrcmgr, laparams=laparams)
-        interpreter = PDFPageInterpreter(rsrcmgr, device)
-
-        #Here starts my code for detecting and collecting text regions in the PDF
-        for page in doc.get_pages():
-            interpreter.process_page(page)
-            # receive the LTPage object for the page.
-            layout = device.get_result()
-
-            for obj in layout:
-                if( isinstance(obj, LTTextBox) ):
-                    txt = obj.get_text().replace("\n"," ").replace("  "," ").strip()
-                    #process the text in this section
-                    self.process_text(txt)
[…]

### 2012-11-20 partridge/web/__init__.py
Started implementation of web interface * added twitter bootstrap as a submodule * added web interface root module

@@ -1,0 +1,19 @@
+'''
+Partridge's main web interface entrypoint
+
+'''
+
+from flask import Flask
+
+app = Flask(__name__)
+
+@app.route('/')
+def index():
+  '''Index view shows the front page for partridge
+  '''
+  return "Hello there!"
+
+
+def serve(port=5000, debug=False):
+  app.debug = True
+  app.run(port=port)

### 2013-02-26 partridge/tools/plosget.py
Wrote plosget utility for downloading papers from plos journals

@@ -1,0 +1,123 @@
+""" Retrieve papers from plosONE
+
+
+"""
+import sys
+from optparse import OptionParser
+import os
+import json
+from urllib2 import urlopen, quote
+
+searchUrl = 'http://api.plos.org/search?'
+apiKey = "dCFoAOqdkBUcOI2"
+dlURL = "http://%s/article/fetchObjectAttachment.action?uri=info%%3Adoi%%2F%s&representation=XML"
+
+
+
+def downloadPaper( paper_id, folder ):
+    '''Download the paper with given paper_id as XML and store in folder.'''
+
+    outfilename = os.path.join(folder, paper_id.split("/")[1] + ".xml")
+
+    bits = paper_id.split("/")
+
+    if(len(bits) > 2):
+        paper_id = bits[0] + "/" + bits[1]
+
+    journals = {
+        "pone" : "www.plosone.org",
+        "pcbi" : "www.ploscompbiol.org"
+    }
+
+    try:
+        journal = journals[paper_id.split("/")[1].split(".")[1]]
+    except:
+        journal = journals["pone"]
+
+    url = dlURL % (journal, paper_id)
+
+    
+    if(os.path.isfile(outfilename)):
+        print "Skipping %s, already downloaded..." % url
+    else:
+        print "Downloading %s..." % url
+        print "Storing it at %s..." % outfilename
+
+        u = urlopen( url )
+        with open(outfilename, 'wb') as f:
+                f.write(u.read())
+        u.close()
+
+def query( query_params ):
+    '''Find papers using plos api and return as JSON model
+    '''
+
+    query = {
+        "q" : "*:*",
+        "api_key" : apiKey,
+        "wt" : "json",
+        "fq" : quote('doc_type:full AND article_type:Opinion'),
+        }
+
+    query = dict( query.items() + query_params.items() )
+
+
+    url = searchUrl
+
+    for part in query:
+        url += '%s%s=%s' % ('&' if url is not searchUrl else '',part,query[part])
+
+    print "Requesting %s" % url
+
+    response = json.load(urlopen(url))
+
+    return response['response']
+
+
+#--------------------------------------------------------------------------------
+
+if __name__ == "__main__":
+    
+
+    o = OptionParser()
+
+    o.add_option("-q", "--query", dest="query", default="*:*",
+        help="Main query, [default *:*]")
+
+    o.add_option("--field-query", dest="fq", default="",
+        help="Set field specific constraints such as paper type")
+
+    o.add_option("-d", "--directory", dest="directory", 
[…]

### 2013-02-26 partridge/tools/plosget.py
Fixed some small errors in plosget

@@ -96,7 +96,7 @@ if __name__ == "__main__":
     o.add_option("-s", "--start", dest="start", default=0,
         help="First row to return [default: 0]")
 
-    o.add_option("-p", "--print", dest="print" action="store_true",
+    o.add_option("-p", "--print", dest="p", action="store_true",
         help="If set, just print the result of the query and exit")
     
    
@@ -117,7 +117,9 @@ if __name__ == "__main__":
 
 
     for doc in response['docs']:
-        print doc
-        #downloadPaper( doc['id'], opts.directory )
+        if(opts.p):
+            print doc
+        else:
+            downloadPaper( doc['id'], opts.directory )
     
 

### 2013-02-26 doc/final_report/report.tex
started work on final report

--- 2012-11-16 doc/progress_plan/report.tex
@@
-% Outline Project Specification Report
+% Final Dissertation Report
 
 %The document is a report
-\documentclass[12pt,a4paper]{article}
+\documentclass[11pt,a4paper]{article}
 
@@
 
-%use harvard citations
-%\citationstyle{agsm}
-
 %include the title page
@@
 
+%TODO: STATEMENT OF ORIGINALITY
+
+%TODO: ACKNOWLEDGEMENTS
+
+%TODO: ABSTRACT
+
 \tableofcontents
@@
 
-\section{Project Summary}
+\section{Introduction}
 
-This document describes the creation of Partridge, a new web-based tool
-designed to assist in information processing and knowledge acquisition within
-the domain of scientific research.
-
-Since the advent of the 'Digital Age' and the ability of computers to copy and
-reproduce information for a negligible cost, the amount of information
-available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
-estimates that approximately 1.4 Million papers were published in the year 2006
-alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
-publishing (making papers available to readers for free online\cite{Suber2012}) across
-most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
-providing scientists and researchers with an even larger volume of information to be
-processed. As available information increases, relevant material becomes
-progressively more difficult to find and the need for an automated information
-retrieval tool more apparent. The problem is even more vital for General
-Practitioners. Goldacre (2008:97) points out that ``there have been an
-estimated 15 million medical academic articles published so far, and 5000
-journals published every month... picking out what's relevant is a gargantuan
-task."\cite{goldacre2008bad}
-
-Partridge's main objective is to provide reading recommendations and
-information retrieval for scientists and researchers. This should reduce the
-amount of extraneous information that users have to read for themselves by
-helping them find information specific to their interests more quickly.
-Partridge will achieve this through the use of several existing techniques in
-Natural Language Processing which are discussed below.
-
-From the point of view of it's users, Partridge will assist researchers in two
-ways. The system will provide filtering of papers based upon their
-specific domain (i.e. is the paper primarily concerned with methodology within
-an experiment in chemistry or is it about ethics in psychological studies?) and
-their result, whether the paper yielded positive, negative or inconclusive
-evidence for a hypothesis. Depending upon the time constraints of the
-project, it is hoped that Partridge will also offer a user 'profiling' system
-that provides recommendations for researchers based on their reading history.
-This feature should help users find relevant papers more quickly or find
-research that they may have otherwise overlooked.
-
-Search engines such as Google ({\url{http://www.google.com/}}), and social
-citation management tools such as CiteULike ({\url{http://www.citeulike.org}}),
-do offer some assistance in tracking down relevant information. However, these
-tools are often too general or rely upon the user knowing exactly what keywords
-to use before carrying out the search. These drawbacks are further discussed in 
-Section \ref{sec:prior_art} below.
-
-To overcome the drawbacks of these existing systems, Partridge will make use of
-several cutting edge Artificial Intelligence (AI) techniques in order to analyse and
-process the papers in a more in depth way. AI is a very complex and field and
-implementing the above features will be incredibly challenging. To help with
-this, Partridge will build upon the system implemented by Liakata et al. for
-recognising hypotheses, methods, results, conclusions and a number of other
-scientific concepts in scientific articles \cite{citeulike:10444769}. The
-Natural Language Toolkit for Python will also be used to build models for
-recognising different fields and topics, classifying results as positive or
-negative and recognising different types of papers, from case studies to
-methodology papers\cite{bird2009natural}.
-
-\section{Current Progress}
-
-\subsection{Background}
-
-\subsubsection{Artificial Intelligence}
-In science fiction literature and films, Artificial Intelligence (AI) and the
-ability of machines to automatically process and understand human language is
-almost always taken for granted. The current state of AI is a long way behind these
-fantastic visions. Dale(2000) comments that ``Even the most ardent exponent of
-artificial intelligence research would have to admit that the likes of HAL in
-Kubrick's 2001: A Space Odyssey remain firmly in the realms of science
-fiction\cite{dale2000handbook}".
-
-Despite lacking behind the imagination of authors and script writers, over the last 60 years there
-has been a huge amount of progress in AI techniques. The phrase `Artificial
-Intelligence' was coined in 1956\cite{russell2010artificial} and can be used as
-an umbrella term, describing many subfields from ``learning and perception
-to... diagnosing diseases\emph{(Ibid)}."
-
-Turing(1950) proposed a test for determining whether a machine could be
-considered intelligent or not\cite{turing1950computing}. Turing's test is based
-upon whether a computer can communicate in a natural language proficiently
-enough to deceive a human into thinking that the machine is also human. A
-machine able to pass such a test would need to possess the ability to represent
-and learn from knowledge, to be able to reason about what it knows and to be
-able to process natural language\cite{russell2010artificial}.
-
-\subsubsection{Natural Language Processing}
-
-Natural Language Processing (NLP)  enables the automated extraction of
-meaningful information from texts written in human languages such as French or
-English. Liddy(2001) defines Natural Language Processing as:
-
-\begin{quotation} 
-A theoretically motivated range of computational techniques for analyzing and
-representing naturally occurring texts at one or more levels of linguistic
-analysis for the purpose of achieving human-like language processing for a
-range of tasks or applications \cite{liddy2001natural}.  
-\end{quotation}
-
-Over the last 60 years, NLP has been used in a wide variety of applications
-such as automated translation between languages\cite{hutchins2004first}, the
-engineering of systems for querying databases using natural languages
-\cite{rao2010natural} and for building `chatterbot' systems designed to
-communicate with their users in a human-like way\cite{Alfonsi2006}.
-More recently, NLP has been used for text classification purposes such as
-classifying emotions within phrases and sentences \cite{Wilson05Polarity} and
-even within suicide notes \cite{citeulike:11077287}.
-
-\subsubsection{CISP, CoreSC and SAPIENTA}
-
-Liakata et al. (2012) describe a system for automatically processing and
-classifying sentences in a research paper according to the scientific concept
-they describe (e.g. a sentence can be categorised as a hypothesis, background
-information, a method or similar)\cite{citeulike:10444769}. SAPIENTA
-(\url{http://www.sapientaproject.com}) is a machine learning application,
-trained using a corpus of physical chemistry and biochemistry research papers
-that were pre-processed and annotated using Core Information about Scientific
-Papers (CISP)\cite{LIAKATA10.644}.
-
-CISP, Soldatova and Liakata(2007), is a way to formally represent core
-scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
-should be present in the articles in a logical
-ontology\cite{soldatova2007ontology}. Subsequent work implements this set of
-concepts as a three layered sentence based annotation scheme (CoreSC scheme)
-where annotations are encoded in Extended Markup Language
-(XML)\cite{LIAKATA10.644}.
-
-\subsection{Related Works}
-\label{sec:prior_art}
-
-\subsubsection{Search Engines}
-
-There are already many existing systems for finding and filtering information
-on the World Wide Web. Search engines are very useful for information retrieval
-in the very large and generalised search domain of the Internet. Most people
-have heard of Google (\url{http://wwww.google.com}), Yahoo
-(\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
-(\url{http://www.ask.com}).
-
-\begin{figure}[!ht]
-\includegraphics[width=0.80\textwidth]{images/space_rocket_query.png}
-\caption{{Google showing over 7M results for ``effects of gravity on rockets"}}
-\label{fig:rocket_results}
-\end{figure}
-
-Despite their use as general search tools on the World Wide Web, the problem
-space that search engines deal with is usually too big for them to find
-scientific papers and journals given a set of keywords. Internet search engines
-index a huge proportion of irrelevant information compared to useful
-information\cite{Berghel1997}, and as a result, even relatively specific
-queries such as ``effects of gravity on rockets" yield millions of results (as
-shown in Figure \ref{fig:rocket_results}). This shortcoming has already led to
-the development of search engines designed specifically to find scientific
-papers.
-
-\subsubsection{Scientific Paper Search Engines}
-
-There are also a number of search and indexing systems that specifically look
-for scientific papers as opposed to web pages. One of the most publicised and
-well known paper search systems is Google Scholar
-(\url{http://scholar.google.com}).  As can be seen in Figure
-\ref{fig:scholar_basic}, This is an adaptation of Google's general search
-engine (discussed above) to specifically index and search scientific papers.
-Google also offers advanced query options specific to Scholar that allow
-searching by author, year and for words that occur only in the document title
-as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
-problem of `information overload' and provides even more fine control over the
-information returned from searches,  the user is still required to have a very
-good idea of what they are looking for in terms of keywords and/or specific
-authors. It is possible that a user would not know what they are looking for
-until they've seen it. Even if the user has a set of keywords to search for,
-they can only search the title of the paper or the content as a whole. This
-means that users who want to find a particular phrase within a CoreSC part of
-the paper (e.g. only look for this phrase in the `Result' section of the
-paper) are unable to get results at their desired level of detail.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/googlescholar_front.png}
-                \caption{Google Scholar's General front page}
-                \label{fig:scholar_basic}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/googlescholar_advanced.png}
-                \caption{Advanced search features}
-                \label{fig:scholar_advanced}
-        \end{subfigure}
-
-        \caption{Google Scholar's user interface}
-        \label{fig:scholar_interface}
-\end{figure}
-
-\subsubsection{Social Citation and Recommendation Engines}
-Social citation and recommendation engines also provide a partial solution to
-the `information overload' problem.  Services like Goodreads
-(\url{http://www.goodreads.com/}) and CiteUlike
-(\url{http://www.citeulike.org/}) allow you to register your interest in
-specific authors and subjects. This allows the sites to build up a profile of
-the sorts of materials that you might be interested in and provide lists of
-recommendations as in Figure \ref{fig:social_indexes}.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/goodreads_index.png}
-                \caption{Goodreads user profile page}
-                \label{fig:goodreads_index}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/citeulike_index.png}
-                \caption{a CiteULike user profile page}
-                \label{fig:citeulike_index}
-        \end{subfigure}
-
-        \caption{Goodreads and citeulike social recommendation systems}
-        \label{fig:social_indexes}
-\end{figure}
-
-These systems have the ability to make recommendations to the user without
-requiring specific keywords or search terms. They do this by learning the
-user's profile and taking into account the preferences of their 'friends' and
-their browsing history. However, the above-named systems do not take into
-account the content of the paper or book. They only deal with metadata as can
-be seen in Figure \ref{fig:social_searches}. This means that important
-discriminatory information that could be contained within the actual document
-content is overlooked completely.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/goodreads_search.png}
-                \caption{Goodreads advanced search page}
-                \label{fig:goodreads_search}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/citeulike_search.png}
-                \caption{CiteULike advanced search options}
-                \label{fig:citeulike_search}
-        \end{subfigure}
-
-        \caption{Goodreads and citeulike search only deal with metadata.}
-        \label{fig:social_searches}
-\end{figure}
-
-\subsection{Methodology}
-
-The language that Partridge will be written in is one of the most fundamental
-and important choices to be made. The language choice effects not only the end
-performance of the application, but the speed at which the project is developed
-and the portability of the end code \cite{britton2008}. It was decided that
-Python would be the best language for developing Partridge.
-
-Python is a programming language with a famously shallow learning curve,
-readable syntax and dynamic inspection that facilitates rapid prototyping
-\cite{bird2009natural}. The language was invented by Guido Van Rossum as a
-multi-use, flexible, interpreted scripting language, extensible via compiled C
-modules\cite{An93pythonfor}. Developing Partridge in python
-would provide a flexible prototyping environment and readable syntax allowing
-for investigative work to be carried out quickly and efficiently with minimal
-overheads for writing boiler-plate code and debugging. The ability to extend
-the language using native code would give Partridge an even greater advantage.
-Since NLP techniques can be quite processor intensive and Python is an
-interpreted language, and in its very nature, slower than a compiled language,
-inefficient sections of Python code could be re-written as C extensions and
-compiled into the application.
-
-Other languages that were considered were Java and C. However, it was decided
-that Python's clean syntax and ease of use for prototyping were preferable to
-the C and Java style syntax. As stated above, C may still be used in part for
-developing Python extensions to improve the overall performance of the
-application.
-
-\subsubsection{Web Presentation Frameworks}
-
-Partridge's web frontend will be used by researchers to wish to query the
-system for information on scientific papers. As it is a web tool, Partridge
-will be presented as a set of HTML web pages.
-
-For this purpose, the Flask (\url{http://flask.pocoo.org}) library was chosen.
-Flask is a python `microframework' for web development. Ronacher (2012) writes
-that ``Flask aims to keep the core simple but extensible...[and] won't make any
-decisions for you\cite{flask2012}." It uses a simple templating system that can
-optionally be swapped out for an equivalent system and does not impose any
-limitations or requirements on the layout of the program or the type of
-database that is used. Flask also integrates very simply into existing software
-using Python annotations\emph{(Ibid)}.
-
-An alternative approach that was considered was using a separate software
-stack such as the Apache web server (\url{http://httpd.apache.org/}) and PHP 
-(\url{http://www.php.net}). However, this would involve adding more software to the
-project and building an interface between the PHP scripts and Partridge's
-python backend. The Django framework (\url{http://www.djangoproject.com/}) for Python was also
-considered but it was determined to be overly complicated in terms of
-Partridge's requirements.
-
-\subsubsection{Natural Language Libraries} \label{sec:libschoice}.
-
-It was decided that a pre-existing NLP library should be used to provide
-implementations of existing algorithms and techniques for Partridge. For this
-purpose the The Natural Language Toolkit (NLTK) was selected. The NLTK is a
-simple and intuitive library written for Python. Bird(2009) states that NLTK
-was designed ``to provide an intuitive framework along with substantial
-building blocks, giving users a practical knowledge of
-NLP\cite{bird2009natural}". NLTK provides implementations for sentence
-splitting, tagging (the process of analysing sentences and classifying words as
-verbs, nouns etc.), and information retrieval from text \emph{(Ibid)}. NLTK
-also provides implementations of classifiers and a framework for extracting
-features to be used for classification from text. There is also a free book
-that accompanies the project available at \url{http://nltk.org/book/} which
-provides a huge amount of information on how to implement many popular NLP
-techniques using the library.
-
-Some other libraries were considered\cite{mallet2002}\cite{cunningham2011text}.
-However, these were written for Java and Partridge is a python project. They
-also require a steeper learning curve than NLTK.
-
-\subsection{Prototyping/Current Work}
-
-\subsubsection{ Sourcing Scientific Papers}
-For Partridge to be a success, it is important to include a large variety of
-different scientific papers in its corpus. Therefore, several sources of
-scientific papers were explored and considered.
-
-The most convenient and accessible source is the ART corpus that SAPIENTA was
-trained with\cite{citeulike:11077287}. This corpus is already stored using the
-CoreSC schema and has been pre-annotated. This means that Partridge would not
-need to do any conversion or pre-processing on the papers. These scientific
-papers are all chemistry papers. Therefore, more papers from other scientific
-domains are needed to get a wider variety of topics and make Partridge useful
-to as wide an audience as possible.
-
-The `mega-journals' PLOS ONE \url{http://www.plosone.org/} and arXiv
-\url{http://www.arxiv.org/} were suggested as sources for more open access
-articles that could be added to Partridge. Both of these sites were found to
-contain large volumes of open access papers. However, most of these papers were
-published as PDF files which meant that some conversion would be required to
-make them compatible with Partridge.
-
-\subsubsection{PDF Conversion}
-Most scientific papers available on the internet are formatted as PDF
-documents. However, Partridge uses and stores documents that use the CoreSC
-schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
-spike work was carried out to determine the feasibility of converting papers
-published as PDF documents into XML documents. Townsendi et al(2009) liken converting
-PDF to XML to ``converting hamburgers into cows," they go on to explain that
-PDF documents do not contain any semantic data and documents lose much of their
-explicit structure when they are formatted in this way \cite{Townsend2009}.
-Therefore, to convert PDF documents into an NLP-friendly format, some
-heuristics must be used to detect the document's structure\cite{pdfminer}.
-
-This was the first big challenge in the project. A prototype script was written
-using a Python PDF extraction library called PDFMiner
-(\url{http://www.unixuser.org/~euske/python/pdfminer/index.html}).  This
-toolkit already contains some heuristics about how to extract text from PDF
-documents, grouping together characters that appear very close to each other,
-and separating paragraphs and headings when a larger area of whitespace is
-detected\cite{pdfminer}. Despite these rules, the library still produced some
-extraneous whitespace and newline characters as part of the output. A
-subroutine to trim whitespace and newlines was added to the script to resolve
-this problem.
-
-The next stage was to split the text into sentences in preparation for
-processing with SAPIENTA. With the assistance of the NLTK library, a sentence
-splitting subroutine was implemented. This used a machine learning algorithm
-that had been trained to recognise sentence boundaries to split the text. Each
-sentence was then added to a CoreSC compatible XML document for processing by
-SAPIENTA.
-
-Initially, the PDF conversion subroutine had a very high error rate due to the
-variation in the formatting of scientific papers. It was suggested that PDFX
-(\url{http://pdfx.cs.man.ac.uk/}), a free service hosted by the University of
-Manchester could be used instead of PDFMiner for the initial PDF data
-extraction. The main advantage of PDFX over the PDFMiner library is that it is a
-trained machine learning system that has been trained using a large full-text
-selection of scientific articles; PDFMiner uses more general heuristics
-designed to process a large selection of different types of PDF document.
-
-PDFX also provides output that already has some metadata, such as title,
-author, and abstract, associated with it. PDFMiner did not provide any
-metadata, and it was necessary for the script to guess which passage of text
-was the abstract after the initial text extraction stage.
-
-With the new PDF extraction method in place, the script ran without the need
-to modify either of the whitespace sanitiser or sentence splitter routines. The
-process was much more successful and able to produce SAPIENTA-compatible
-documents from most of the PDF input files that were provided.
-
-\subsubsection{Pre-processing with SAPIENTA}
-
-With a successful PDF conversion script, the next step was to try and run
-SAPIENTA over the converted papers and annotate them, ready for inclusion in
-the Partridge corpus.
-
-By default, SAPIENTA is packaged as a web-based tool, written in Java, that
-can be downloaded (from \url{http://www.sapientaproject.com/software}) and used
-to annotate one paper at a time. Dr Liakata was able to provide information on
-two alternative ways of using the system. One method was to submit a remote
-procedure call (RPC) to a server running SAPIENTA with a batch of papers and
-retrieve the output. The other method was to use an alternative version of the
-code that runs locally in a Python environment and could be modified to process
-papers as a batch.
-
-A script was written to send un-annotated XML documents to the remote SAPIENTA
-server and retrieve a list of annotations. This worked well until the server
-stopped replying to requests. This meant that no further conversions could be
-carried out until the server was repaired and raised concerns about how the
-remote servers might cope with a large number of automated requests from a
-full version of Partridge.
-
-The Python version of SAPIENTA was then downloaded and a test executed.
-Unfortunately there were several data files missing from the package that had
-to be acquired from Dr Liakata.
-
-SAPIENTA for Python also relies upon a package called CRFSuite which implements
-Conditional Random Fields, a method for segmenting and labelling sequence
-data\cite{CRFsuite}. This library did not compile properly on the test
-environment and its creator had to be contacted via a mailing list (See
-Appendix \ref{sec:crfemail}. After a few days, the owner responded and the
-library was compiled successfully.
-
-Once all the data files and libraries were successfully in place, the Python
-version of SAPIENTA was used to process some of the papers converted from PDF.
-This was a great success and the annotations provided by SAPIENTA seemed to be
-accurate.
-
-\subsubsection{Interface Design}
-
-To help in visualising how the final web frontend will appear, some diagrams of
-the user interface have been drawn. You can see these diagrams in Appendix
-\ref{sec:ui_designs}.
-
-\subsubsection{System Processes}
-
-To visualise how some of the system processes will work and how they should be
-programmed, some flow diagrams have been produced and attached in Appendix
-\ref{sec:system_diagrams}
-
-\section{Planning}
-
-\subsection{Development Methodology}
-
-\subsubsection{Existing Methodologies}
-Selecting a suitable development methodology for building Partridge is another
-very important choice for the project.
-
-Under the traditional `Waterfall' Software Development model, Requirements
-Gathering, Analysis, Program Design, Coding, Testing and Operations were all
-defined as formal phases in the development cycle. There is little flexibility
-other than moving back up the waterfall to rectify mistakes after
-testing\cite{Royce:1987:MDL:41765.41801}. This model was very focused on
-paperwork and bureaucracy, trying to maintain a paper trail and manage risk
-through accountability \emph{(Ibed)}. This approach to software development is
-very heavyweight and slow and often produced software that did not match the
-users' needs as a result \cite{Boehm1988}.
-
-As an alternative to the heavyweight Waterfall approach, Beck et al came up
-with the principle of the Agile Manifesto, favouring a lightweight, responsive
-development model over the heavyweight slow waterfall
-system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
-of developers and prioriting communication between team members \emph{(Ibid)}.
-This is most prominent in the Extreme Programming (XP) method of software
-development. Since Partridge is an individual project, XP is not really
-applicable. However, some concepts like rapid prototyping/spike work and
-iterative release cycles will be used as part of the Partridge development
-methodology.
-
-\subsubsection{ Partridge's Development Methodology}
-
-Partridge is an individual project but does involve discussions with
-supervisors. The customers have been identified as the end-users of the system.
-Therefore, a customised methodology has been adopted. Firstly, all design and
-planning documentation have been written up and placed on a wiki which is
-accessible and modifiable by the author and both supervisors. This creates a
-paper trail for all tasks and also allows collaboration between involved
-parties through the Internet. A full printout of the wiki is available in
-Appendix \ref{sec:wiki}.
-
-Weekly meetings are held with both supervisors. The notes from the preceeding
-week are analysed and each task discussed in depth. New tasks are then noted
-down along with any observations that should be documented. These new notes are
-uploaded to the wiki the following day or earlier. Each party present at the
-meeting adds their own observations to the notes page. This page is then
-reviewed at the next meeting. As seen in Appendix \ref{sec:wiki}, this practice
-has already been running for several weeks and has so far proven to be highly
-effective.
-
-Partridge will adopt an Agile approach to release cycles, producing a working
-software package at iterations of one month.  Each iteration, the software will
-include more of the desired functionality discussed above and in the wiki.
-GitHub's issue manager program is being used to track tasks and bugfixes and
-plan which tasks will be carried out in which iteration. Tasks that are created
-in a full iteration (where no development time is left) will be added to a
-backlog and integrated in the next iteration with enough development time to
-contain it. Tasks are also assigned a priority, higher priority issues being
-tackled before low priority ones.
-
-Partridge's testing strategy consists of multiple unit tests that are run at
-integration of new code into the codebase. As soon as the first release is
-built, Partridge will be made available for use by the public and users
-encouraged to test the system and submit any bugs via the GitHub issue manager.
-It is hoped that colleagues at Aberystwyth University and Dr. Liakata's
-colleages at the EBI will try to use the system one it becomes available.
-
-\subsubsection{ Work Timeline }
-
-The tasks involved in Partridge have been carefully calculated and prioritised.
-They were then added to the GitHub issue management system and a report
-generated listing them in the order that they are expected to be
-accomplished. This report can be seen in Appendix \ref{sec:timeline}.
-
-\subsubsection{ Mid-Project Demonstration Plan}
-
-The mid-project demonstration is scheduled for after iteration two of the
-Partridge project. If everything runs to schedule, then at this point it will
-be possible to demonstrate keyword search within the project's database and
-filter based upon the polarity of the paper's results. For redundancy purposes,
-Partridge will be configured to run as a server on multiple computers. Both
-this and the final project demonstration will require a room with Internet
-access. However, should this be unavailable, then Partridge could be run
-locally on the author's laptop.
-
-\subsubsection{ Final Project Demonstration Plan}
-
-The final demonstration of Partridge will be fairly similar to the Mid-Project
-demonstration. However, it should include all of the planned classifiers and if
-there is extra time on the project, the profiling/recommendation engine will
-also be demonstrated. This demonstration will use the same redundancy
-precautions as the Mid-project demonstration above, and will also need a room
-with the internet if available.
-
-%include document appendix
-\input{appendix}
+\pagebreak
+\bibliographystyle{IEEEannot}
+\bibliography{report}
 

### 2013-02-27 partridge/tools/plosget.py
Wrapped plosget inside a main function

@@ -74,11 +74,9 @@ def query( query_params ):
     return response['response']
 
 
-#--------------------------------------------------------------------------------
-
-if __name__ == "__main__":
-    
-
+def main():
+    '''Main script entrypoint for plosget
+    '''
     o = OptionParser()
 
     o.add_option("-q", "--query", dest="query", default="*:*",
@@ -123,3 +121,8 @@ if __name__ == "__main__":
             downloadPaper( doc['id'], opts.directory )
     
 
+
+#--------------------------------------------------------------------------------
+
+if __name__ == "__main__":
+    main()

### 2013-02-27 doc/final_report/implementation.tex
Created files for chapters of diss

%%------------------------------------------------------
%  
%  Implementation include for dissertation
%
%------------------------------------------------------

\subsection{ Data Mining \& Paper Processing}

\subsection{ Web Interface \& Database System}

\subsection{ Paper Type Classification }

### 2013-02-27 doc/final_report/introduction.tex
Created files for chapters of diss

%%%%------------------------------------------------
%
%  Include for chapter one of dissertation: introduction
%
%%%%------------------------------------------------
\subsection{Context}

\subsection{Background}

\subsection{Objectives}

\subsection{Literature Review}

### 2013-02-27 doc/final_report/introduction.tex
Started report - got introduction going

@@
 
-\subsection{Background}
+Since the advent of the 'Digital Age' and the ability of computers to copy and
+reproduce information for a negligible cost, the amount of information
+available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
+estimates that approximately 1.4 Million papers were published in the year 2006
+alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
+publishing (making papers available to readers for free online\cite{Suber2012})
+across most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
+providing scientists and researchers with an even larger volume of information
+to be processed. As available information increases, relevant material becomes
+progressively more difficult to find manually and the need for an automated
+information retrieval tool more apparent. The problem is even more vital for
+General Practitioners. Goldacre (2008:97) points out that ``there have been an
+estimated 15 million medical academic articles published so far, and 5000
+journals published every month... picking out what's relevant is a gargantuan
+task."\cite{goldacre2008bad}.
+
+To assist in information processing and knowledge acquisition within the domain
+of scientific research, a new web-based tool named Partridge was designed. Its
+creation and implementation are discussed in this document.
 
@@
 
-\subsection{Literature Review}
+Partridge's main objective is to provide reading recommendations and
+information retrieval for scientists and researchers. This should reduce the
+amount of extraneous information that users have to read for themselves by
+helping them find information specific to their interests more quickly.
+Partridge will achieve this through the use of several existing techniques in
+Natural Language Processing which are discussed below.
+
+From the point of view of its users, Partridge will assist researchers in two
+ways. The system will provide filtering of papers based upon their
+specific domain (i.e. is the paper primarily concerned with methodology within
+an experiment in chemistry or is it about ethics in psychological studies?) and
+their result, whether the paper yielded positive, negative or inconclusive
+evidence for a hypothesis. Depending upon the time constraints of the
+project, it is hoped that Partridge will also offer a user 'profiling' system
+that provides recommendations for researchers based on their reading history.
+This feature should help users find relevant papers more quickly or find
+research that they may have otherwise overlooked.
+
+\subsection{Background}
+
+\subsubsection{ Related Works }
+
+There are already a large number of information retrieval and recommendation
+systems for scientific publications. A selection of these systems were
+evaluated to find out which features work well and to identify their
+shortcomings.
+
+Several online search systems specifically index scientific papers and other
+publications. One of the most publicised and well known paper search systems is
+Google Scholar (\url{http://scholar.google.com}).  As can be seen in Figure
+\ref{fig:scholar_basic}, This is an adaptation of Google's general search
+engine to specifically index and search scientific papers.  Google offers
+advanced query options specific to Scholar that allow searching by author, year
+and for words that occur only in the document title as shown in figure
+\ref{fig:scholar_advanced}. Whilst this does deal with the problem of
+`information overload' by providing fine control over the information returned
+from searches,  the user is still required to have a very good idea of what
+they are looking for in terms of keywords and/or specific authors. It is
+possible that a user would not know what they are looking for until they've
+seen it. Even if the user has a set of keywords to search for, they can only
+search the title of the paper or the content as a whole. This means that users
+who want to find a particular phrase within a CoreSC part of the paper (e.g.
+only look for this phrase in the `Result' section of the paper) are unable to
+get results at their desired level of detail.
+
+\begin{figure}[!hbt]
+        \centering
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/googlescholar_front.png}
+                \caption{Google Scholar's General front page}
+                \label{fig:scholar_basic}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/googlescholar_advanced.png}
+                \caption{Advanced search features}
+                \label{fig:scholar_advanced}
+        \end{subfigure}
+
+        \caption{Google Scholar's user interface}
+        \label{fig:scholar_interface}
+\end{figure}
+
+Social citation and recommendation engines also provide a partial solution to
+the `information overload' problem.  Services like Goodreads
+(\url{http://www.goodreads.com/}) and CiteUlike
+(\url{http://www.citeulike.org/}) allow you to register your interest in
+specific authors and subjects. This allows the sites to build up a profile of
+the sorts of materials that you might be interested in and provide lists of
+recommendations as in Figure \ref{fig:social_indexes}.
+
+\begin{figure}[!hbt]
+        \centering
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/goodreads_index.png}
+                \caption{Goodreads user profile page}
+                \label{fig:goodreads_index}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/citeulike_index.png}
+                \caption{a CiteULike user profile page}
+                \label{fig:citeulike_index}
+        \end{subfigure}
+
+        \caption{Goodreads and citeulike social recommendation systems}
+        \label{fig:social_indexes}
+\end{figure}
+
+These systems have the ability to make recommendations to the user without
+requiring specific keywords or search terms. They do this by learning the
+user's profile and taking into account the preferences of their 'friends' and
+their browsing history. However, the above-named systems do not take into
+account the content of the paper or book. They only deal with metadata as can
+be seen in Figure \ref{fig:social_searches}. This means that important
+discriminatory information that could be contained within the actual document
+content is overlooked completely.
+
+\begin{figure}[!hbt]
+        \centering
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/goodreads_search.png}
+                \caption{Goodreads advanced search page}
+                \label{fig:goodreads_search}
+        \end{subfigure}%
+        \begin{subfigure}[b]{0.50\textwidth}
+                \centering
+                \includegraphics[width=\textwidth]{images/citeulike_search.png}
+                \caption{CiteULike advanced search options}
+                \label{fig:citeulike_search}
+        \end{subfigure}
+
+        \caption{Goodreads and citeulike search only deal with metadata.}
+        \label{fig:social_searches}
+\end{figure}
+
+None of these systems make full use of the content within the research papers
+that they index. Those systems with filtering and recommendation capabilities
+rely upon users and their activities to provide discriminatory information
+between papers and facilitate `intelligent' behaviour. It is hoped that by
+making full use of the content within scientific papers, Patridge will offer a
+novel, reliable way of displaying relevant papers to users.
+
+\subsection{ Literature Review}
+
+\subsubsection{Natural Language Processing}
+
+Natural Language Processing (NLP)  is a branch of Artificial Intelligence that
+enables the automated extraction of meaningful information from texts written
+in human languages such as French or English. Liddy (2001) defines Natural
+Language Processing as:
+
+\begin{quotation} 
+A theoretically motivated range of computational techniques for analyzing and
+representing naturally occurring texts at one or more levels of linguistic
+analysis for the purpose of achieving human-like language processing for a
+range of tasks or applications \cite{liddy2001natural}.  
+\end{quotation}
+
+Over the last 60 years, NLP has been used in a wide variety of applications
+such as automated translation between languages\cite{hutchins2004first}, the
+engineering of systems for querying databases using natural languages
+\cite{rao2010natural} and for building `chatterbot' systems designed to
+communicate with their users in a human-like way\cite{Alfonsi2006}.
+More recently, NLP has been used for text classification purposes such as
+classifying emotions within phrases and sentences \cite{Wilson05Polarity} and
+even within suicide notes \cite{citeulike:11077287}.
+
+\subsubsection{CISP, CoreSC and SAPIENTA}
+
+Liakata \emph{et al.} (2012) describe a system for automatically processing and
+classifying sentences in a research paper according to the scientific concept
+they describe (e.g. a sentence can be categorised as a hypothesis, background
+information, a method or similar)\cite{citeulike:10444769}. SAPIENTA
+(\url{http://www.sapientaproject.com}) is a machine learning application,
+trained using a corpus of physical chemistry and biochemistry research papers
+that were pre-processed and annotated using Core Information about Scientific
+Papers (CISP)\cite{LIAKATA10.644}.
+
+CISP, Soldatova and Liakata (2007), is a way to formally represent core
+scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
+should be present in the articles in a logical
+ontology\cite{soldatova2007ontology}. Subsequent work implements this set of
+concepts as a three layered sentence based annotation scheme (CoreSC scheme)
+where annotations are encoded in Extended Markup Language
+(XML)\cite{LIAKATA10.644}.

### 2013-02-28 doc/final_report/implementation.tex
Started adding implementation details

@@
 
-\subsection{ Data Mining \& Paper Processing}
+\subsection{Technical Challenges}
 
-\subsection{ Web Interface \& Database System}
+\subsubsection{ Sourcing Scientific Papers}
+For Partridge to be a success, it is important to include a large variety of
+different scientific papers in its corpus. Therefore, several sources of
+scientific papers were explored and considered.
 
-\subsection{ Paper Type Classification }
+The most convenient and accessible source is the ART corpus that SAPIENTA was
+trained with\cite{citeulike:11077287}. This corpus is already stored using the
+CoreSC schema and has been pre-annotated. This means that Partridge would not
+need to do any conversion or pre-processing on the papers. These scientific
+papers are all chemistry papers. Therefore, more papers from other scientific
+domains are needed to get a wider variety of topics and make Partridge useful
+to as wide an audience as possible.
+
+The `mega-journals' PLOS ONE \url{http://www.plosone.org/} and arXiv
+\url{http://www.arxiv.org/} were suggested as sources for more open access
+articles that could be added to Partridge. Both of these sites were found to
+contain large volumes of open access papers. However, most of these papers were
+published as PDF files which meant that some conversion would be required to
+make them compatible with Partridge.
+
+\subsubsection{PDF Conversion}
+Most scientific papers available on the internet are formatted as PDF
+documents. However, Partridge uses and stores documents that use the CoreSC
+schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
+spike work was carried out to determine the feasibility of converting papers
+published as PDF documents into XML documents. Townsendi \emph{et al.} (2009) liken converting
+PDF to XML to ``converting hamburgers into cows," they go on to explain that
+PDF documents do not contain any semantic data and documents lose much of their
+explicit structure when they are formatted in this way \cite{Townsend2009}.
+Therefore, to convert PDF documents into an NLP-friendly format, some
+heuristics must be used to detect the document's structure\cite{pdfminer}.
+
+This was the first big challenge in the project. A prototype script was written
+using a Python PDF extraction library called PDFMiner
+(\url{http://www.unixuser.org/~euske/python/pdfminer/index.html}).  This
+toolkit already contains some heuristics about how to extract text from PDF
+documents, grouping together characters that appear very close to each other,
+and separating paragraphs and headings when a larger area of whitespace is
+detected\cite{pdfminer}. Despite these rules, the library still produced some
+extraneous whitespace and newline characters as part of the output. A
+subroutine to trim whitespace and newlines was added to the script to resolve
+this problem.
+
+The next stage was to split the text into sentences in preparation for
+processing with SAPIENTA. With the assistance of the NLTK library, a sentence
+splitting subroutine was implemented. This used a machine learning algorithm
+that had been trained to recognise sentence boundaries to split the text. Each
+sentence was then added to a CoreSC compatible XML document for processing by
+SAPIENTA.
+
+Initially, the PDF conversion subroutine had a very high error rate due to the
+variation in the formatting of scientific papers. It was suggested that PDFX
+(\url{http://pdfx.cs.man.ac.uk/}), a free service hosted by the University of
+Manchester could be used instead of PDFMiner for the initial PDF data
+extraction. The main advantage of PDFX over the PDFMiner library is that it is a
+trained machine learning system that has been trained using a large full-text
+selection of scientific articles; PDFMiner uses more general heuristics
+designed to process a large selection of different types of PDF document.
+
+PDFX also provides output that already has some metadata, such as title,
+author, and abstract, associated with it. PDFMiner did not provide any
+metadata, and it was necessary for the script to guess which passage of text
+was the abstract after the initial text extraction stage.
+
+With the new PDF extraction method in place, the script ran without the need
+to modify either of the whitespace sanitiser or sentence splitter routines. The
+process was much more successful and able to produce SAPIENTA-compatible
+documents from most of the PDF input files that were provided.
+
+\subsubsection{Pre-processing with SAPIENTA}
+
+With a successful PDF conversion script, the next step was to try and run
+SAPIENTA over the converted papers and annotate them, ready for inclusion in
+the Partridge corpus.
+
+By default, SAPIENTA is packaged as a web-based tool, written in Java, that
+can be downloaded (from \url{http://www.sapientaproject.com/software}) and used
+to annotate one paper at a time. Dr Liakata was able to provide information on
+two alternative ways of using the system. One method was to submit a remote
+procedure call (RPC) to a server running SAPIENTA with a batch of papers and
+retrieve the output. The other method was to use an alternative version of the
+code that runs locally in a Python environment and could be modified to process
+papers as a batch.
+
+A script was written to send un-annotated XML documents to the remote SAPIENTA
+server and retrieve a list of annotations. This worked well until the server
+stopped replying to requests. This meant that no further conversions could be
+carried out until the server was repaired and raised concerns about how the
+remote servers might cope with a large number of automated requests from a
+full version of Partridge.
+
+The Python version of SAPIENTA was then downloaded and a test executed.
+Unfortunately there were several data files missing from the package that had
+to be acquired from Dr Liakata.
+
+SAPIENTA for Python also relies upon a package called CRFSuite which implements
+Conditional Random Fields, a method for segmenting and labelling sequence
+data\cite{CRFsuite}. This library did not compile properly on the test
+environment and its creator had to be contacted via a mailing list (See
+Appendix \ref{sec:crfemail}. After a few days, the owner responded and the
+library was compiled successfully.
+
+Once all the data files and libraries were successfully in place, the Python
+version of SAPIENTA was used to process some of the papers converted from PDF.
+This was a great success and the annotations provided by SAPIENTA seemed to be
+accurate.

### 2013-02-28 partridge/tools/sapienta/testreliability.py
Added small script to test reliability of SAPIENTA classification

@@ -1,0 +1,66 @@
+from crf import runTagger
+import os
+import sys
+
+from xml.dom import minidom
+
+PAPER_PATH = "/home/james/tmp/corpus/combined"
+
+total = 0
+correct = 0
+wrong = 0
+
+for root, dirs, files in os.walk(PAPER_PATH):
+    
+
+    for file in files:
+    
+        sentConcepts = {}
+
+        path = os.path.join(root, file)
+
+        print "Processing file %s " % path
+
+        with open(path,'rb') as f:
+            doc = minidom.parse(f)
+
+        for sEl in doc.getElementsByTagName("s"):
+            sid = sEl.getAttribute("sid") 
+
+            #now get the coresc
+            l = sEl.getElementsByTagName("annotationART")
+
+            if(len(l) < 1):
+                l = sEl.getElementsByTagName("CoreSc1")
+
+            if(len(l) > 0):
+                concept = l[0].getAttribute("type")
+
+                sentConcepts[ sid ] = concept
+
+        print "Found %d sentences" % len(sentConcepts)
+        print "Running tagger"
+
+        #now lets do the tagging and get back each sentence
+        labels = runTagger(path)
+
+        for id, type in labels:
+            
+            if sentConcepts.has_key(id):
+
+                print id
+                
+                if sentConcepts[id] == type:
+                    correct += 1
+                else:
+                    wrong += 1
+
+                total += 1
+
+        corrpercent = (correct * 100) / total
+        wrongpercent = (wrong * 100) / total
+
+        print "Total sentences analysed %d" % total
+        print "total correct %d (%d%%)" % (correct, corrpercent)
+        print "total wrong %d (%d%%)" % (wrong, wrongpercent)
+

### 2013-02-28 doc/final_report/methodology.tex
Added final report stuff

--- 2012-11-18 doc/progress_plan/report.tex
@@
-% Outline Project Specification Report
-
-%The document is a report
-\documentclass[12pt,a4paper]{article}
-
-%define horizontal rule
-\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
-
-\usepackage{fullpage}
-\usepackage{pdfpages}
-%use the listings package
-\usepackage{listings}
-%use the English language
-\usepackage[english]{babel}
-%use graphics
-\usepackage{graphicx}
-%use wrap figures
-\usepackage{wrapfig}
-%geometry stuffs
-\usepackage{lscape}
-%use natbib bibliography package
-%\usepackage[numbers]{natbib}
-%use harvard bibliography package
-%\usepackage{harvard}	
-%use captions
-\usepackage{caption}
-%use multi-row tables
-\usepackage{multirow}
-\usepackage{url}
-\usepackage{subcaption}
-
-\usepackage[nottoc,numbib]{tocbibind}
-
-\begin{document}
-
-%use harvard citations
-%\citationstyle{agsm}
-
-%include the title page
-\input{revision}
-\input{title}
-
-%some definitions for paragraph layout stuff
-\setlength{\parindent}{0pt}
-\setlength{\parskip}{1.5ex plus 0.5ex minus 0.2ex}
-
-\tableofcontents
-
-\pagebreak
-
-\section{Project Summary}
-
-This document describes the creation of Partridge, a new web-based tool
-designed to assist in information processing and knowledge acquisition within
-the domain of scientific research.
-
-Since the advent of the 'Digital Age' and the ability of computers to copy and
-reproduce information for a negligible cost, the amount of information
-available to researchers has been increasing drastically.  B-C Bj\"{o}rk (2009)
-estimates that approximately 1.4 Million papers were published in the year 2006
-alone\cite{bjork2009}. Moreover, the growing popularity of Open Access
-publishing (making papers available to readers for free online\cite{Suber2012}) across
-most scientific disciplines\cite{bjork2009}\cite{harnad2004comparing} is
-providing scientists and researchers with an even larger volume of information to be
-processed. As available information increases, relevant material becomes
-progressively more difficult to find and the need for an automated information
-retrieval tool more apparent. The problem is even more vital for General
-Practitioners. Goldacre (2008:97) points out that ``there have been an
-estimated 15 million medical academic articles published so far, and 5000
-journals published every month... picking out what's relevant is a gargantuan
-task."\cite{goldacre2008bad}
-
-Partridge's main objective is to provide reading recommendations and
-information retrieval for scientists and researchers. This should reduce the
-amount of extraneous information that users have to read for themselves by
-helping them find information specific to their interests more quickly.
-Partridge will achieve this through the use of several existing techniques in
-Natural Language Processing which are discussed below.
-
-From the point of view of its users, Partridge will assist researchers in two
-ways. The system will provide filtering of papers based upon their
-specific domain (i.e. is the paper primarily concerned with methodology within
-an experiment in chemistry or is it about ethics in psychological studies?) and
-their result, whether the paper yielded positive, negative or inconclusive
-evidence for a hypothesis. Depending upon the time constraints of the
-project, it is hoped that Partridge will also offer a user 'profiling' system
-that provides recommendations for researchers based on their reading history.
-This feature should help users find relevant papers more quickly or find
-research that they may have otherwise overlooked.
-
-Search engines such as Google ({\url{http://www.google.com/}}), and social
-citation management tools such as CiteULike ({\url{http://www.citeulike.org}}),
-do offer some assistance in tracking down relevant information. However, these
-tools are often too general or rely upon the user knowing exactly what keywords
-to use before carrying out the search. These drawbacks are further discussed in 
-Section \ref{sec:prior_art} below.
-
-To overcome the drawbacks of these existing systems, Partridge will make use of
-several cutting edge Artificial Intelligence (AI) techniques in order to analyse and
-process the papers in a more in depth way. AI is a very complex and field and
-implementing the above features will be incredibly challenging. To help with
-this, Partridge will build upon the system implemented by Liakata \emph{et al.} for
-recognising hypotheses, methods, results, conclusions and a number of other
-scientific concepts in scientific articles \cite{citeulike:10444769}. The
-Natural Language Toolkit for Python will also be used to build models for
-recognising different fields and topics, classifying results as positive or
-negative and recognising different types of papers, from case studies to
-methodology papers\cite{bird2009natural}.
-
-\section{Current Progress}
-
-\subsection{Background}
-
-\subsubsection{Artificial Intelligence}
-In science fiction literature and films, Artificial Intelligence (AI) and the
-ability of machines to automatically process and understand human language is
-almost always taken for granted. The current state of AI is a long way behind these
-fantastic visions. Dale (2000) comments that ``Even the most ardent exponent of
-artificial intelligence research would have to admit that the likes of HAL in
-Kubrick's 2001: A Space Odyssey remain firmly in the realms of science
-fiction\cite{dale2000handbook}".
-
-Despite lacking behind the imagination of authors and script writers, over the last 60 years there
-has been a huge amount of progress in AI techniques. The phrase `Artificial
-Intelligence' was coined in 1956\cite{russell2010artificial} and can be used as
-an umbrella term, describing many subfields from ``learning and perception
-to... diagnosing diseases\emph{(Ibid.)}."
-
-Turing (1950) proposed a test for determining whether a machine could be
-considered intelligent or not\cite{turing1950computing}. Turing's test is based
-upon whether a computer can communicate in a natural language proficiently
-enough to deceive a human into thinking that the machine is also human. A
-machine able to pass such a test would need to possess the ability to represent
-and learn from knowledge, to be able to reason about what it knows and to be
-able to process natural language\cite{russell2010artificial}.
-
-\subsubsection{Natural Language Processing}
-
-Natural Language Processing (NLP)  enables the automated extraction of
-meaningful information from texts written in human languages such as French or
-English. Liddy (2001) defines Natural Language Processing as:
-
-\begin{quotation} 
-A theoretically motivated range of computational techniques for analyzing and
-representing naturally occurring texts at one or more levels of linguistic
-analysis for the purpose of achieving human-like language processing for a
-range of tasks or applications \cite{liddy2001natural}.  
-\end{quotation}
-
-Over the last 60 years, NLP has been used in a wide variety of applications
-such as automated translation between languages\cite{hutchins2004first}, the
-engineering of systems for querying databases using natural languages
-\cite{rao2010natural} and for building `chatterbot' systems designed to
-communicate with their users in a human-like way\cite{Alfonsi2006}.
-More recently, NLP has been used for text classification purposes such as
-classifying emotions within phrases and sentences \cite{Wilson05Polarity} and
-even within suicide notes \cite{citeulike:11077287}.
-
-\subsubsection{CISP, CoreSC and SAPIENTA}
-
-Liakata \emph{et al.} (2012) describe a system for automatically processing and
-classifying sentences in a research paper according to the scientific concept
-they describe (e.g. a sentence can be categorised as a hypothesis, background
-information, a method or similar)\cite{citeulike:10444769}. SAPIENTA
-(\url{http://www.sapientaproject.com}) is a machine learning application,
-trained using a corpus of physical chemistry and biochemistry research papers
-that were pre-processed and annotated using Core Information about Scientific
-Papers (CISP)\cite{LIAKATA10.644}.
-
-CISP, Soldatova and Liakata (2007), is a way to formally represent core
-scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
-should be present in the articles in a logical
-ontology\cite{soldatova2007ontology}. Subsequent work implements this set of
-concepts as a three layered sentence based annotation scheme (CoreSC scheme)
-where annotations are encoded in Extended Markup Language
-(XML)\cite{LIAKATA10.644}.
-
-\subsection{Related Works}
-\label{sec:prior_art}
-
-\subsubsection{Search Engines}
-
-There are already many existing systems for finding and filtering information
-on the World Wide Web. Search engines are very useful for information retrieval
-in the very large and generalised search domain of the Internet. Most people
-have heard of Google (\url{http://wwww.google.com}), Yahoo
-(\url{http://www.yahoo.co.uk}), Bing (\url{http://www.bing.com}) and Ask
-(\url{http://www.ask.com}).
-
-\begin{figure}[!ht]
-\includegraphics[width=0.80\textwidth]{images/space_rocket_query.png}
-\caption{{Google showing over 7M results for ``effects of gravity on rockets"}}
-\label{fig:rocket_results}
-\end{figure}
-
-Despite their use as general search tools on the World Wide Web, the problem
-space that search engines deal with is usually too big for them to find
-scientific papers and journals given a set of keywords. Internet search engines
-index a huge proportion of irrelevant information compared to useful
-information\cite{Berghel1997}, and as a result, even relatively specific
-queries such as ``effects of gravity on rockets" yield millions of results (as
-shown in Figure \ref{fig:rocket_results}). This shortcoming has already led to
-the development of search engines designed specifically to find scientific
-papers.
-
-\subsubsection{Scientific Paper Search Engines}
-
-There are also a number of search and indexing systems that specifically look
-for scientific papers as opposed to web pages. One of the most publicised and
-well known paper search systems is Google Scholar
-(\url{http://scholar.google.com}).  As can be seen in Figure
-\ref{fig:scholar_basic}, This is an adaptation of Google's general search
-engine (discussed above) to specifically index and search scientific papers.
-Google also offers advanced query options specific to Scholar that allow
-searching by author, year and for words that occur only in the document title
-as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
-problem of `information overload' and provides even more fine control over the
-information returned from searches,  the user is still required to have a very
-good idea of what they are looking for in terms of keywords and/or specific
-authors. It is possible that a user would not know what they are looking for
-until they've seen it. Even if the user has a set of keywords to search for,
-they can only search the title of the paper or the content as a whole. This
-means that users who want to find a particular phrase within a CoreSC part of
-the paper (e.g. only look for this phrase in the `Result' section of the
-paper) are unable to get results at their desired level of detail.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/googlescholar_front.png}
-                \caption{Google Scholar's General front page}
-                \label{fig:scholar_basic}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/googlescholar_advanced.png}
-                \caption{Advanced search features}
-                \label{fig:scholar_advanced}
-        \end{subfigure}
-
-        \caption{Google Scholar's user interface}
-        \label{fig:scholar_interface}
-\end{figure}
-
-\subsubsection{Social Citation and Recommendation Engines}
-Social citation and recommendation engines also provide a partial solution to
-the `information overload' problem.  Services like Goodreads
-(\url{http://www.goodreads.com/}) and CiteUlike
-(\url{http://www.citeulike.org/}) allow you to register your interest in
-specific authors and subjects. This allows the sites to build up a profile of
-the sorts of materials that you might be interested in and provide lists of
-recommendations as in Figure \ref{fig:social_indexes}.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/goodreads_index.png}
-                \caption{Goodreads user profile page}
-                \label{fig:goodreads_index}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/citeulike_index.png}
-                \caption{a CiteULike user profile page}
-                \label{fig:citeulike_index}
-        \end{subfigure}
-
-        \caption{Goodreads and citeulike social recommendation systems}
-        \label{fig:social_indexes}
-\end{figure}
-
-These systems have the ability to make recommendations to the user without
-requiring specific keywords or search terms. They do this by learning the
-user's profile and taking into account the preferences of their 'friends' and
-their browsing history. However, the above-named systems do not take into
-account the content of the paper or book. They only deal with metadata as can
-be seen in Figure \ref{fig:social_searches}. This means that important
-discriminatory information that could be contained within the actual document
-content is overlooked completely.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/goodreads_search.png}
-                \caption{Goodreads advanced search page}
-                \label{fig:goodreads_search}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/citeulike_search.png}
-                \caption{CiteULike advanced search options}
-                \label{fig:citeulike_search}
-        \end{subfigure}
-
-        \caption{Goodreads and citeulike search only deal with metadata.}
-        \label{fig:social_searches}
-\end{figure}
-
-\subsection{Methodology}
-
-The language that Partridge will be written in is one of the most fundamental
-and important choices to be made. The language choice effects not only the end
-performance of the application, but the speed at which the project is developed
-and the portability of the end code \cite{britton2008}. It was decided that
-Python would be the best language for developing Partridge.
-
-Python is a programming language with a famously shallow learning curve,
-readable syntax and dynamic inspection that facilitates rapid prototyping
-\cite{bird2009natural}. The language was invented by Guido Van Rossum as a
-multi-use, flexible, interpreted scripting language, extensible via compiled C
-modules\cite{An93pythonfor}. Developing Partridge in python
-would provide a flexible prototyping environment and readable syntax allowing
-for investigative work to be carried out quickly and efficiently with minimal
-overheads for writing boiler-plate code and debugging. The ability to extend
-the language using native code would give Partridge an even greater advantage.
-Since NLP techniques can be quite processor intensive and Python is an
-interpreted language, and in its very nature, slower than a compiled language,
-inefficient sections of Python code could be re-written as C extensions and
-compiled into the application.
-
-Other languages that were considered were Java and C. However, it was decided
-that Python's clean syntax and ease of use for prototyping were preferable to
-the C and Java style syntax. As stated above, C may still be used in part for
-developing Python extensions to improve the overall performance of the
-application.
-
-\subsubsection{Web Presentation Frameworks}
-
-Partridge's web frontend will be used by researchers to wish to query the
-system for information on scientific papers. As it is a web tool, Partridge
-will be presented as a set of HTML web pages.
-
-For this purpose, the Flask (\url{http://flask.pocoo.org}) library was chosen.
-Flask is a python `microframework' for web development. Ronacher (2012) writes
-that ``Flask aims to keep the core simple but extensible...[and] won't make any
-decisions for you\cite{flask2012}." It uses a simple templating system that can
-optionally be swapped out for an equivalent system and does not impose any
-limitations or requirements on the layout of the program or the type of
-database that is used. Flask also integrates very simply into existing software
-using Python annotations\emph{(Ibid.)}.
-
-An alternative approach that was considered was using a separate software
-stack such as the Apache web server (\url{http://httpd.apache.org/}) and PHP 
-(\url{http://www.php.net}). However, this would involve adding more software to the
-project and building an interface between the PHP scripts and Partridge's
-python backend. The Django framework (\url{http://www.djangoproject.com/}) for Python was also
-considered but it was determined to be overly complicated in terms of
-Partridge's requirements.
-
-\subsubsection{Natural Language Libraries} \label{sec:libschoice}.
-
-It was decided that a pre-existing NLP library should be used to provide
-implementations of existing algorithms and techniques for Partridge. For this
-purpose the The Natural Language Toolkit (NLTK) was selected. The NLTK is a
-simple and intuitive library written for Python. Bird (2009) states that NLTK
-was designed ``to provide an intuitive framework along with substantial
-building blocks, giving users a practical knowledge of
-NLP\cite{bird2009natural}". NLTK provides implementations for sentence
-splitting, tagging (the process of analysing sentences and classifying words as
-verbs, nouns etc.), and information retrieval from text \emph{(Ibid.)}. NLTK
-also provides implementations of classifiers and a framework for extracting
-features to be used for classification from text. There is also a free book
-that accompanies the project available at \url{http://nltk.org/book/} which
-provides a huge amount of information on how to implement many popular NLP
-techniques using the library.
-
-Some other libraries were considered\cite{mallet2002}\cite{cunningham2011text}.
-However, these were written for Java and Partridge is a python project. They
-also require a steeper learning curve than NLTK.
-
-\subsection{Prototyping/Current Work}
-
-\subsubsection{ Sourcing Scientific Papers}
-For Partridge to be a success, it is important to include a large variety of
-different scientific papers in its corpus. Therefore, several sources of
-scientific papers were explored and considered.
-
-The most convenient and accessible source is the ART corpus that SAPIENTA was
-trained with\cite{citeulike:11077287}. This corpus is already stored using the
-CoreSC schema and has been pre-annotated. This means that Partridge would not
-need to do any conversion or pre-processing on the papers. These scientific
-papers are all chemistry papers. Therefore, more papers from other scientific
-domains are needed to get a wider variety of topics and make Partridge useful
-to as wide an audience as possible.
-
-The `mega-journals' PLOS ONE \url{http://www.plosone.org/} and arXiv
-\url{http://www.arxiv.org/} were suggested as sources for more open access
-articles that could be added to Partridge. Both of these sites were found to
-contain large volumes of open access papers. However, most of these papers were
-published as PDF files which meant that some conversion would be required to
-make them compatible with Partridge.
-
-\subsubsection{PDF Conversion}
-Most scientific papers available on the internet are formatted as PDF
-documents. However, Partridge uses and stores documents that use the CoreSC
-schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
-spike work was carried out to determine the feasibility of converting papers
-published as PDF documents into XML documents. Townsendi \emph{et al.} (2009) liken converting
-PDF to XML to ``converting hamburgers into cows," they go on to explain that
-PDF documents do not contain any semantic data and documents lose much of their
-explicit structure when they are formatted in this way \cite{Townsend2009}.
-Therefore, to convert PDF documents into an NLP-friendly format, some
-heuristics must be used to detect the document's structure\cite{pdfminer}.
-
-This was the first big challenge in the project. A prototype script was written
-using a Python PDF extraction library called PDFMiner
-(\url{http://www.unixuser.org/~euske/python/pdfminer/index.html}).  This
-toolkit already contains some heuristics about how to extract text from PDF
-documents, grouping together characters that appear very close to each other,
-and separating paragraphs and headings when a larger area of whitespace is
-detected\cite{pdfminer}. Despite these rules, the library still produced some
-extraneous whitespace and newline characters as part of the output. A
-subroutine to trim whitespace and newlines was added to the script to resolve
-this problem.
-
-The next stage was to split the text into sentences in preparation for
-processing with SAPIENTA. With the assistance of the NLTK library, a sentence
-splitting subroutine was implemented. This used a machine learning algorithm
-that had been trained to recognise sentence boundaries to split the text. Each
-sentence was then added to a CoreSC compatible XML document for processing by
-SAPIENTA.
-
-Initially, the PDF conversion subroutine had a very high error rate due to the
-variation in the formatting of scientific papers. It was suggested that PDFX
-(\url{http://pdfx.cs.man.ac.uk/}), a free service hosted by the University of
-Manchester could be used instead of PDFMiner for the initial PDF data
-extraction. The main advantage of PDFX over the PDFMiner library is that it is a
-trained machine learning system that has been trained using a large full-text
-selection of scientific articles; PDFMiner uses more general heuristics
-designed to process a large selection of different types of PDF document.
-
-PDFX also provides output that already has some metadata, such as title,
-author, and abstract, associated with it. PDFMiner did not provide any
-metadata, and it was necessary for the script to guess which passage of text
-was the abstract after the initial text extraction stage.
-
-With the new PDF extraction method in place, the script ran without the need
-to modify either of the whitespace sanitiser or sentence splitter routines. The
-process was much more successful and able to produce SAPIENTA-compatible
-documents from most of the PDF input files that were provided.
-
-\subsubsection{Pre-processing with SAPIENTA}
-
-With a successful PDF conversion script, the next step was to try and run
-SAPIENTA over the converted papers and annotate them, ready for inclusion in
-the Partridge corpus.
-
-By default, SAPIENTA is packaged as a web-based tool, written in Java, that
-can be downloaded (from \url{http://www.sapientaproject.com/software}) and used
-to annotate one paper at a time. Dr Liakata was able to provide information on
-two alternative ways of using the system. One method was to submit a remote
-procedure call (RPC) to a server running SAPIENTA with a batch of papers and
-retrieve the output. The other method was to use an alternative version of the
-code that runs locally in a Python environment and could be modified to process
-papers as a batch.
-
-A script was written to send un-annotated XML documents to the remote SAPIENTA
-server and retrieve a list of annotations. This worked well until the server
-stopped replying to requests. This meant that no further conversions could be
-carried out until the server was repaired and raised concerns about how the
-remote servers might cope with a large number of automated requests from a
-full version of Partridge.
-
-The Python version of SAPIENTA was then downloaded and a test executed.
-Unfortunately there were several data files missing from the package that had
-to be acquired from Dr Liakata.
-
-SAPIENTA for Python also relies upon a package called CRFSuite which implements
-Conditional Random Fields, a method for segmenting and labelling sequence
-data\cite{CRFsuite}. This library did not compile properly on the test
-environment and its creator had to be contacted via a mailing list (See
-Appendix \ref{sec:crfemail}. After a few days, the owner responded and the
-library was compiled successfully.
-
-Once all the data files and libraries were successfully in place, the Python
-version of SAPIENTA was used to process some of the papers converted from PDF.
-This was a great success and the annotations provided by SAPIENTA seemed to be
-accurate.
-
-\subsubsection{Interface Design}
-
-To help in visualising how the final web frontend will appear, some diagrams of
-the user interface have been drawn. You can see these diagrams in Appendix
-\ref{sec:ui_designs}.
-
-\subsubsection{System Processes}
-
-To visualise how some of the system processes will work and how they should be
-programmed, some flow diagrams have been produced and attached in Appendix
-\ref{sec:system_diagrams}
-
-\section{Planning}
-
 \subsection{Development Methodology}
@@
 with the internet if available.
-
-%include document appendix
-\input{appendix}
-
-\end{document}

### 2013-02-28 doc/final_report/testing.tex
Created files for chapters of diss
Added final report stuff

--- 2013-02-27 doc/final_report/implementation.tex
@@
 %  
-%  Implementation include for dissertation
+%  Testing include for dissertation
 %
@@
 
-\subsection{ Data Mining \& Paper Processing}
+\subsection{ Unit Testing }
 
-\subsection{ Web Interface \& Database System}
+\subsection{ User Testing }
 
-\subsection{ Paper Type Classification }
+Once a basic user interface had been implemented, the system was opened for
+user testing. The main Patridge instance
+(\url{http://farnsworth.papro.org.uk/}) was advertised using several social
+media streams and users encouraged to submit bug reports if they experienced
+any problems whilst using the site.
+
+\subsection{ Testing Learning Algorithms }
+
+Patridge uses machine learning algorithms to classify the type of research
+papers added to its database. It was therefore necessary to test that these
+algorithms were sufficiently trained and provide accurate classification.
+Unlike

### 2013-03-01 doc/final_report/testing.tex
Added some blurb about ML testing

@@
 \subsection{ Unit Testing }
+
+\subsubsection{ Nose and Sniffer }
+
+\subsubsection{ Selenium }
 
@@
 
-Patridge uses machine learning algorithms to classify the type of research
-papers added to its database. It was therefore necessary to test that these
-algorithms were sufficiently trained and provide accurate classification.
-Unlike
+Patridge uses supervised machine learning algorithms to classify the type of
+research papers added to its database. It was therefore necessary to test that
+these algorithms provide accurate classification given the training and
+features used in its model.  Unlike traditional procedural algorithms that can
+be unit tested and in some cases formally proven to behave uniformly at
+runtime\cite{filliatre2007formal}, supervised learning algorithms are imperfect
+systems that build `working models' from known data. This makes the performance
+of supervised learning systems much more difficult to assess. Russell and
+Norvig(2010) suggest that ``a learning system is good if it produces hypotheses
+that do a good job of predicting the classification of unseen
+examples\cite{russell2010artificial}." It is suggested that when training a
+supervised learning system, some pre-classified examples should not be used in
+the training example and instead, the system is used to classify these
+remaining examples, its decision compared to the actual, known class of
+each\cite{alpaydin2004introduction}\cite{russell2010artificial}.
+
+\subsubsection{ Partitioned Data Sets}
+
+After a suitably large number of papers were collected and annotated, the
+papers were partitioned into disjoint \emph{training} set and a \emph{testing}
+sets.

### 2013-03-01 doc/final_report/testing.tex
Added more documentation for testing

@@
 
+Nose for python is an extension of Python's built in Unit testing module that
+is supposed to make setting up a testing environment and reusing test code
+easier. Unit tests for Patridge's webserver backend and paper preprocessor were
+written and maintained throughout the project. As each new feature was added to
+the system, the whole suite of tests was executed to provide integration
+coverage and make sure that new features did not break existing code.
+
 \subsubsection{ Selenium }
+
+The frontend parts of Partridge that were written in Javascript and HTML5 also
+had to be tested to verify that the query and upload forms behaved as expected.
 
@@
 After a suitably large number of papers were collected and annotated, the
-papers were partitioned into disjoint \emph{training} set and a \emph{testing}
-sets.
+papers were partitioned into disjoint \emph{training} and \emph{testing}
+sets. The decision tree that is used to classify a paper's "type"

### 2013-03-03 partridge/tests/preprocessor/test_fs.py
Started writing some tests

@@ -1,0 +1,74 @@
+"""
+Test the partridge filesystem
+"""
+import os
+import tempfile
+import time
+import logging
+
+from unittest import TestCase
+
+from partridge.preprocessor.fs import FilesystemWatcher, PaperProcesser
+
+#---------------------------------------------------------------------------
+class MockPaperProcessor:
+    
+    def process_IN_CLOSE_WRITE(self, evt):
+        pass
+
+
+#---------------------------------------------------------------------------
+
+class FileSystemWatchTester(TestCase):
+
+    @classmethod
+    def setUpClass(self):
+        self.watchpath = tempfile.mkdtemp()
+        self.fsw = FilesystemWatcher(logging.getLogger("test"))
+        self.fsw.watch_directory(self.watchpath)
+        self.fsw.start()
+
+
+
+    @classmethod
+    def tearDownClass(self):
+        self.fsw.stop()
+
+        for root,dirs,files in os.walk(self.watchpath):
+            for file in files:
+                os.unlink(os.path.join(root, file))
+
+        os.rmdir(self.watchpath)
+        
+
+    def test_add_valid_paper(self): 
+        """Test the filesystem watcher adds pdf and xml"""
+
+        tests = ['test.xml', 'test.pdf']
+
+        for n in [ os.path.join(self.watchpath, x) for x in tests]:
+            with file(n, 'wb') as f:
+                f.write("hello!")
+
+            assert self.fsw.paper_queue.get() == n
+
+
+    def test_queue_files(self):
+        """Test that queuing up files works """
+
+        files = []
+
+        #add some files to the directory
+        for n in range(0,20):
+            path = os.path.join(self.watchpath, "test_%d.xml" % n)
+
+            with file(path, 'wb') as f:
+                f.write("testdata")
+
+            files.append(path)
+
+        #now make sure that all the files are queued 
+        for f in files:
+            assert self.fsw.paper_queue.get() == f
+
+   

### 2013-03-03 partridge/tests/preprocessor/test_fs.py
Added test for invalid doc format

@@ -6,7 +6,11 @@ import tempfile
 import time
 import logging
 
+from Queue import Empty
+
 from unittest import TestCase
+
+from nose.tools import raises
 
 from partridge.preprocessor.fs import FilesystemWatcher, PaperProcesser
 
@@ -51,6 +55,17 @@ class FileSystemWatchTester(TestCase):
                 f.write("hello!")
 
             assert self.fsw.paper_queue.get() == n
+
+    @raises(Empty)
+    def test_add_invalid_paper(self):
+        """Add a load of invalid papers and make sure they don't queue"""
+        
+        filename = os.path.join(self.watchpath, "test.blob")
+
+        with file(filename,'wb') as f:
+            f.write("blah blah")
+
+        self.fsw.paper_queue.get(block=False)
 
 
     def test_queue_files(self):

### 2013-03-03 partridge/tests/preprocessor/test_daemon.py
started writing tests for making sure preprocessor daemon works

@@ -1,0 +1,34 @@
+"""A set of tests for testing the behaviour of the preprocessor daemon
+
+This module tests each of the constituent behaviours of the partridge
+preprocessor daemon.
+
+"""
+import logging
+import unittest
+import tempfile
+
+from mock import patch, MagicMock, call
+
+from partridge.preprocessor.daemon import PaperDaemon
+
+class TestPaperDaemon(unittest.TestCase):
+
+    @classmethod
+    def setUpClass(self):
+        self.watchdir = tempfile.mkdtemp()
+        self.outdir   = tempfile.mkdtemp()
+
+        self.daemon = PaperDaemon(self.watchdir, 
+            self.outdir,
+            logging.getLogger(__name__))
+
+    def test_paper_exists(self):
+        '''Make sure that the right method is called '''
+
+        with patch("partridge.preprocessor.daemon.PaperParser") as mock:
+
+            self.daemon.paperExists("/path/to/file.xml")
+
+            assert call().paperExists('/path/to/file.xml') in mock.mock_calls
+

### 2013-03-03 partridge/tests/preprocessor/test_daemon.py
Added teardown function that deletes test directories from test_daemon

@@ -4,6 +4,7 @@ This module tests each of the constituent behaviours of the partridge
 preprocessor daemon.
 
 """
+import os
 import logging
 import unittest
 import tempfile
@@ -23,6 +24,16 @@ class TestPaperDaemon(unittest.TestCase):
             self.outdir,
             logging.getLogger(__name__))
 
+    @classmethod
+    def tearDownClass(self):
+
+        for d in [self.watchdir, self.outdir]:
+            for root,dirs,files in os.walk(d):
+                for file in files:
+                    os.unlink(os.path.join(root, file))
+
+            os.rmdir(d)
+
     def test_paper_exists(self):
         '''Make sure that the right method is called '''
 
@@ -32,3 +43,5 @@ class TestPaperDaemon(unittest.TestCase):
 
             assert call().paperExists('/path/to/file.xml') in mock.mock_calls
 
+    def test_split_xml(self):
+        '''Ensure that '''

### 2013-03-03 partridge/tests/preprocessor/test_daemon.py
finished testing paperdaemon

@@ -15,6 +15,9 @@ from partridge.preprocessor.daemon import PaperDaemon
 
 class TestPaperDaemon(unittest.TestCase):
 
+
+#-----------------------------------------------------------------------------
+
     @classmethod
     def setUpClass(self):
         self.watchdir = tempfile.mkdtemp()
@@ -24,6 +27,8 @@ class TestPaperDaemon(unittest.TestCase):
             self.outdir,
             logging.getLogger(__name__))
 
+#-----------------------------------------------------------------------------
+ 
     @classmethod
     def tearDownClass(self):
 
@@ -34,8 +39,11 @@ class TestPaperDaemon(unittest.TestCase):
 
             os.rmdir(d)
 
+
+#-----------------------------------------------------------------------------
+
     def test_paper_exists(self):
-        '''Make sure that the right method is called '''
+        '''Make sure that the right paper exists db method is called '''
 
         with patch("partridge.preprocessor.daemon.PaperParser") as mock:
 
@@ -43,5 +51,112 @@ class TestPaperDaemon(unittest.TestCase):
 
             assert call().paperExists('/path/to/file.xml') in mock.mock_calls
 
+#-----------------------------------------------------------------------------
+
     def test_split_xml(self):
-        '''Ensure that '''
+        '''Ensure that the right split methods are called'''
+
+        with patch("partridge.preprocessor.daemon.SentenceSplitter") as mock:
+            
+            infile  = "example.xml"
+            outfile = os.path.join(self.outdir, "example_split.xml" )
+
+            #inject some data into paper daemon
+            self.daemon.name = "example"
+            self.daemon.paper_files = []
+
+            self.daemon.splitXML(infile)
+
+            #make sure the SentenceSplitter.split() method was called
+            assert call().split(infile,outfile) in mock.mock_calls
+
+            #make sure the paper daemon has a paper files entry to be deleted
+            assert self.daemon.paper_files.pop() == (outfile, 'delete')
+
+
+#-----------------------------------------------------------------------------
+
+    def test_convert_pdf(self):
+        '''Ensure that the PDF conversion routine works'''
+
+        with patch("partridge.preprocessor.daemon.PDFXConverter") as mock:
+            
+            infile = "example.pdf"
+            outfile = os.path.join(self.outdir, "example.xml")
+
+            #inject some data
+            self.daemon.name = "example"
+            self.daemon.paper_files = []
+
+            self.daemon.convertPDF(infile)
+
[…]

### 2013-03-03 partridge/tests/preprocessor/test_fs.py

@@ -14,15 +14,6 @@ from nose.tools import raises
 
 from partridge.preprocessor.fs import FilesystemWatcher, PaperProcesser
 
-#---------------------------------------------------------------------------
-class MockPaperProcessor:
-    
-    def process_IN_CLOSE_WRITE(self, evt):
-        pass
-
-
-#---------------------------------------------------------------------------
-
 class FileSystemWatchTester(TestCase):
 
     @classmethod

### 2013-03-03 partridge/tests/models/test_models.py
Started some unit tests for other aspects of partridge

@@ -1,0 +1,2 @@
+"""Set of test utilities for testing the data model
+"""

### 2013-03-03 partridge/tests/views/test_paper.py

@@ -1,0 +1,16 @@
+"""
+Set of tests for making sure the main web server behaves properly
+
+"""
+
+import unittest
+
+from partridge.views.paper import paper_profile
+
+class FlaskTestCase( unittest.TestCase ):
+
+    def setUp(self):
+        pass
+
+    def tearDown(self):
+        pass

### 2013-03-04 doc/final_report/methodology.tex
Wrote abstract and got the main layout looking a bit nicer

@@
 This is most prominent in the Extreme Programming (XP) method of software
-development. Since Partridge is an individual project, XP is not really
+development. Since Partridge is an individual project, XP was not really
 applicable. However, some concepts like rapid prototyping/spike work and
-iterative release cycles will be used as part of the Partridge development
+iterative release cycles were used as part of the Partridge development
 methodology.
@@
 
-Partridge is an individual project but does involve discussions with
-supervisors. The customers have been identified as the end-users of the system.
-Therefore, a customised methodology has been adopted. Firstly, all design and
-planning documentation have been written up and placed on a wiki which is
-accessible and modifiable by the author and both supervisors. This creates a
-paper trail for all tasks and also allows collaboration between involved
-parties through the Internet. A full printout of the wiki is available in
-Appendix \ref{sec:wiki}.
+A custom methodology was used for keeping track of development within
+Partridge.  All design and planning documentation have been written up and
+placed on a wiki which is accessible and modifiable by the author and both
+supervisors. This creates a paper trail for all tasks and also allows
+collaboration between involved parties through the Internet.
 
-Weekly meetings are held with both supervisors. The notes from the preceeding
-week are analysed and each task discussed in depth. New tasks are then noted
-down along with any observations that should be documented. These new notes are
-uploaded to the wiki the following day or earlier. Each party present at the
-meeting adds their own observations to the notes page. This page is then
-reviewed at the next meeting. As seen in Appendix \ref{sec:wiki}, this practice
-has already been running for several weeks and has so far proven to be highly
-effective.
+Throughout the project, weekly meetings were held with both project
+supervisors. The notes from the preceeding week were analysed and each task
+discussed in depth. New tasks were then noted down along with any observations
+that should be documented. These were then uploaded to the wiki the following
+day or earlier. Each party present at the meeting adds their own observations
+to the notes page. This page is then reviewed at the next meeting.
 
-Partridge will adopt an Agile approach to release cycles, producing a working
-software package at iterations of one month.  Each iteration, the software will
-include more of the desired functionality discussed above and in the wiki.
-GitHub's issue manager program is being used to track tasks and bugfixes and
-plan which tasks will be carried out in which iteration. Tasks that are created
-in a full iteration (where no development time is left) will be added to a
-backlog and integrated in the next iteration with enough development time to
-contain it. Tasks are also assigned a priority, higher priority issues being
-tackled before low priority ones.
-
-Partridge's testing strategy consists of multiple unit tests that are run at
-integration of new code into the codebase. As soon as the first release is
-built, Partridge will be made available for use by the public and users
-encouraged to test the system and submit any bugs via the GitHub issue manager.
-It is hoped that colleagues at Aberystwyth University and Dr. Liakata's
-colleages at the EBI will try to use the system one it becomes available.
+Partridge made use of an agile, `iterative' development process. A working
+version of the system was released at the end of each month. Tasks to be
+undertaken in each iteration were stored in GitHub's issue manager program.
+Priority was given to those tasks that provided the most value for the least
+time investment. Test users were also allowed to submit bug reports to the
+tracker system, and these were given priority if they were serious.
 
@@
 accomplished. This report can be seen in Appendix \ref{sec:timeline}.
-
-\subsubsection{ Mid-Project Demonstration Plan}
-
-The mid-project demonstration is scheduled for after iteration two of the
-Partridge project. If everything runs to schedule, then at this point it will
-be possible to demonstrate keyword search within the project's database and
-filter based upon the polarity of the paper's results. For redundancy purposes,
-Partridge will be configured to run as a server on multiple computers. Both
-this and the final project demonstration will require a room with Internet
-access. However, should this be unavailable, then Partridge could be run
-locally on the author's laptop.
-
-\subsubsection{ Final Project Demonstration Plan}
-
-The final demonstration of Partridge will be fairly similar to the Mid-Project
-demonstration. However, it should include all of the planned classifiers and if
-there is extra time on the project, the profiling/recommendation engine will
-also be demonstrated. This demonstration will use the same redundancy
-precautions as the Mid-project demonstration above, and will also need a room
-with the internet if available.

### 2013-03-04 partridge/preprocessor/daemon.py
made some functional changes to the preprocessor

@@ -22,6 +22,9 @@ from partridge.tools.converter import PDFXConverter
 from partridge.tools.annotate import RemoteAnnotator
 from partridge.tools.split import SentenceSplitter
 
+class PaperExistsException(Exception):
+    pass
+
 
 class PaperDaemon(Thread):
     """The paper daemon handles conversion and preprocessing of papers
@@ -57,12 +60,14 @@ class PaperDaemon(Thread):
                     for line in traceback.format_tb(exc_tb):
                         self.logger.error(line)
 
-                    try:
-                        #send the error report
-                        send_error_report( e, exc_tb, 
-                            [file for file,action in self.paper_files])
-                    except Exception as e:
-                        self.logger.error("ERROR SENDING EMAIL: %s", e)
+                    if not isinstance(e, PaperExistsException):
+                    
+                        try:
+                            #send the error report
+                            send_error_report( e, exc_tb, 
+                                [file for file,action in self.paper_files])
+                        except Exception as e:
+                            self.logger.error("ERROR SENDING EMAIL: %s", e)
 
                     #set paperObj to none for file cleanup
                     paperObj = None
@@ -101,7 +106,7 @@ class PaperDaemon(Thread):
 
         #see if the paper already exists
         if(self.paperExists(infile)):
-            raise Exception("Paper already exists")
+            raise PaperExistsException("Paper already exists")
 
         #run XML splitting and annotating
         infile = self.splitXML(infile)

### 2013-03-04 partridge/tools/paperstore.py

@@ -13,14 +13,13 @@ class PaperParser:
         with open(filename, 'rb') as f:
             self.doc = xml.dom.minidom.parse(f)
 
-        self.paper = Paper()
-        self.extractTitle()
-        self.extractAuthors()
+        title = self.extractTitle()
+        authors = self.extractAuthors()
 
-        author_surnames = [ x.surname for x in self.paper.authors]
+        author_surnames = [ x.surname for x in authors]
 
         results = Paper.query.join("authors").filter(
-            Paper.title == self.paper.title,
+            Paper.title == title,
             Author.surname.in_( author_surnames) )
 
         return results.count() > 0
@@ -32,21 +31,21 @@ class PaperParser:
             self.doc = xml.dom.minidom.parse(f)
 
         #extract metadata
-        self.paper = Paper()
-        self.extractTitle()
-        self.extractAbstract()
+        paper = Paper()
+        paper.title    = self.extractTitle()
+        paper.abstract = self.extractAbstract()
 
         #add authors
-        self.extractAuthors()
+        paper.authors.extend(self.extractAuthors())
         
         #get sentence information
-        self.extractSentences()
+        paper.sentences.extend( self.extractSentences() )
 
         #store the updated database info
-        db.session.add(self.paper)
+        db.session.add(paper)
         db.session.commit()
 
-        return self.paper
+        return paper
 
     def extractSentences(self):
         """Extract sentences and relative coresc concept from xml"""
@@ -63,7 +62,7 @@ class PaperParser:
 
             db.session.add(sent)
 
-            self.paper.sentences.append(sent)
+            yield sent
 
     def extractAbstract(self):
         """Extract the paper abstract from xml"""
@@ -74,7 +73,7 @@ class PaperParser:
         else:
             abEl = self.doc.getElementsByTagName("ABSTRACT")[0]
 
-        self.paper.abstract = self.extractText(abEl)
+        return self.extractText(abEl)
 
 
     def extractAuthors(self):
@@ -98,9 +97,7 @@ class PaperParser:
                     forenames = " ".join(names[0:-1])
 
 
-                author = self.lookupAuthor(surname, forenames)
-                self.paper.authors.append(author)
-
+                yield self.lookupAuthor(surname, forenames)
         
         authEls = self.doc.getElementsByTagName("CURRENT_AUTHOR")
         authEls.extend(self.doc.getElementsByTagName("AUTHOR"))
@@ -134,9 +131,8 @@ class PaperParser:
[…]

### 2013-03-04 doc/final_report/evaluation.tex

--- 2013-02-28 doc/final_report/testing.tex
@@
 %  
-%  Testing include for dissertation
+%  Evaluation include for dissertation
 %
@@
 
-\subsection{ Unit Testing }
+\subsection{ Achievements }
 
-\subsection{ User Testing }
+\subsection{ Limitations and Potential Improvements }
 
-Once a basic user interface had been implemented, the system was opened for
-user testing. The main Patridge instance
-(\url{http://farnsworth.papro.org.uk/}) was advertised using several social
-media streams and users encouraged to submit bug reports if they experienced
-any problems whilst using the site.
-
-\subsection{ Testing Learning Algorithms }
-
-Patridge uses machine learning algorithms to classify the type of research
-papers added to its database. It was therefore necessary to test that these
-algorithms were sufficiently trained and provide accurate classification.
-Unlike
+\subsection{ Further Research }

### 2013-03-05 partridge/mltest/paper_tree.py
added dtree classification stuff to version control

@@ -1,0 +1,139 @@
+import Orange,orngTree
+import os
+
+from partridge.config import config
+from flask import Flask
+from flask.ext.sqlalchemy import SQLAlchemy
+
+from partridge.models import db
+from partridge.models.doc import Paper, PaperFile, Sentence, C_ABRV
+
+def find_paper_ids( dir ):
+
+    ids = []
+
+    for root, dirs, files in os.walk(dir):
+        
+        for file in files:
+            name,ext = os.path.splitext(file)
+
+            if ext == ".xml":
+                pfile = PaperFile.query.filter(
+                    PaperFile.path.like("%%%s%%" % name)).first()
+
+                if(pfile != None):
+                    ids.append(pfile.paper_id)
+
+    return ids
+
+
+app = Flask(__name__)
+app.config.update(config)
+
+db.app = app
+db.init_app(app)
+
+#find paper sources
+REVIEW_DIR   = "/home/james/dissertation/papers/training/review"
+RESEARCH_DIR = "/home/james/dissertation/papers/training/research"
+CASE_DIR     = "/home/james/dissertation/papers/training/case"
+
+
+research_ids = set( find_paper_ids( RESEARCH_DIR ) )
+print "Found %d research papers" % len(research_ids)
+
+review_ids   = set( find_paper_ids( REVIEW_DIR ) )
+print "Found %d review papers" % len(review_ids)
+
+
+case_ids   = set( find_paper_ids( CASE_DIR ) )
+print "Found %d case study papers" % len(case_ids)
+
+all_ids = review_ids.union(research_ids).union(case_ids)
+
+papers = Paper.query.filter(Paper.id.in_(all_ids)).all()
+
+#set up data domain
+class_var = Orange.feature.Discrete("type")
+class_var.add_value("Research")
+class_var.add_value("Review")
+class_var.add_value("Case Study")
+
+corescs = ['Bac', 'Mot', 'Met'] #C_ABRV.keys()
+domain = Orange.data.Domain([Orange.feature.Continuous(x) for x in corescs], 
+class_var)
+
+
+paper_table = Orange.data.Table(domain)
+print "Loading Data..."
+
+for paper in papers:
+    
+
+    if len(paper.sentences) < 1:
+        continue
+
+    inst_list = []
+    sentdist = paper.sentenceDistribution(True)
+    for coresc in corescs:
+        inst_list.append( sentdist[coresc] * 100 / len(paper.sentences) )
+        
[…]

### 2013-03-05 partridge/mltest/papertype.py

@@ -1,0 +1,67 @@
+"""
+A small utility that can be used to guess a paper's type using the forest model
+
+"""
+
+import os
+import sys
+import cPickle
+import Orange
+
+from partridge.config import config
+from flask import Flask
+from flask.ext.sqlalchemy import SQLAlchemy
+
+from partridge.models import db
+from partridge.models.doc import Paper
+
+app = Flask(__name__)
+app.config.update(config)
+
+db.app = app
+db.init_app(app)
+
+PAPER_TYPE_MODEL_PATH = os.path.join(config['MODELS_DIR'], "paper_types.model")
+
+FEATURES = ['Bac', 'Mot', 'Met']
+
+class PaperClassifier:
+
+    def __init__(self):
+
+        with open(PAPER_TYPE_MODEL_PATH, 'rb') as f:
+            self.classifier = cPickle.load(f)
+
+    def get_paper_by_id(self, id):
+        return Paper.query.filter(Paper.id == id).first()
+
+
+    def classify_paper_id( self, id ):
+        return self.classify_paper(self.get_paper_by_id(paper))
+
+    def classify_paper( self, paper ):
+        inst = self.instance_from_paper(paper)
+        return self.classifier( inst )
+    
+    def instance_from_paper( self, paper ):
+        inst_list = []
+        sentdist = paper.sentenceDistribution(True)
+
+        for feature in FEATURES:
+            inst_list.append( sentdist[feature] * 100 / len(paper.sentences) )
+
+        inst_list.append("")
+
+        return Orange.data.Instance(self.classifier.domain, inst_list)
+
+
+if __name__ == "__main__":
+
+    c = PaperClassifier()
+    p = c.get_paper_by_id(sys.argv[1])
+    
+    print p.title
+    for author in p.authors:
+        print "\t\t" + author.surname
+    
+    print "Predicted Class:" + str( c.classify_paper(p) )

### 2013-03-05 partridge/tools/paperstore.py

@@ -89,12 +89,15 @@ class PaperParser:
                     forenameEl = contrib.getElementsByTagName("given-names")[0]
                     surname = self.extractText(surnameEl)
                     forenames = self.extractText(forenameEl)
-                else:
+                elif(len(contrib.getElementsByTagName("name")) > 0):
                     #try and extract names from 'name' tag
                     nameEle = contrib.getElementsByTagName("name")[0]
                     names = self.extractText(nameEle).split(" ")
                     surname = names[-1]
                     forenames = " ".join(names[0:-1])
+                else:
+                    #could be acknowledgement that this is a collaboration
+                    continue
 
 
                 yield self.lookupAuthor(surname, forenames)

### 2013-03-05 partridge/mltest/paper_tree.py
DTrees now classifying at 85% accuracy, added paper type attribute

@@ -59,7 +59,7 @@ class_var.add_value("Research")
 class_var.add_value("Review")
 class_var.add_value("Case Study")
 
-corescs = ['Bac', 'Mot', 'Met'] #C_ABRV.keys()
+corescs =  C_ABRV.keys() #['Bac', 'Mot', 'Met']
 domain = Orange.data.Domain([Orange.feature.Continuous(x) for x in corescs], 
 class_var)
 

### 2013-03-05 partridge/models/doc.py

@@ -39,6 +39,8 @@ class Paper( db.Model ):
   authors = relationship("Author", secondary=paper_authors, backref="papers")
   abstract = Column(Text())
 
+  type = Column(String(25))
+
   def sentenceDistribution(self, returnCounter=False):
     totalSentences = len(self.sentences)
 

### 2013-03-05 partridge/preprocessor/daemon.py
system now guesses paper type during preprocessing

@@ -21,6 +21,7 @@ from partridge.tools.paperstore import PaperParser
 from partridge.tools.converter import PDFXConverter
 from partridge.tools.annotate import RemoteAnnotator
 from partridge.tools.split import SentenceSplitter
+from partridge.tools.papertype import PaperClassifier
 
 class PaperExistsException(Exception):
     pass
@@ -38,6 +39,7 @@ class PaperDaemon(Thread):
         self.fsw.watch_directory(watchdir)
         self.outdir = outdir
         self.logger = logger
+        self.paper_classifier = PaperClassifier()
 
     def run(self):
         """This is the main loop for the paper daemon"""
@@ -114,8 +116,11 @@ class PaperDaemon(Thread):
         #run XML annotation
         infile = self.annotateXML(infile)
 
-        #Finally do some analysis and store the paper in the DB
-        return self.storePaperData(infile)
+        #do some analysis and store the paper in the DB
+        paper = self.storePaperData(infile)
+
+        #finally add paper type to the database
+        return self.classifyPaper(paper)
 
     def paperExists(self, infile):
         """Return true if paper with same authors and title already in db"""
@@ -128,6 +133,19 @@ class PaperDaemon(Thread):
         paper = parser.storePaper(infile)
         self.logger.info("Added paper '%s' to database", paper.title)
         return paper
+
+    def classifyPaper(self, paper):
+        """Decide what 'type' the paper is - case study, research or review"""
+        
+        type = str(self.paper_classifier.classify_paper(paper))
+        self.logger.info("Determined paper %s is of type %s", paper.title,
+            type)
+
+        paper.type = type
+
+        return db.session.merge(paper)
+        
+
     
     def annotateXML(self, infile):
         """Routine to start the SAPIENTA process call"""

### 2013-03-05 partridge/tools/papertype.py

@@ -8,22 +8,19 @@ import sys
 import cPickle
 import Orange
 
+
+from optparse import OptionParser
+
 from partridge.config import config
 from flask import Flask
 from flask.ext.sqlalchemy import SQLAlchemy
 
 from partridge.models import db
-from partridge.models.doc import Paper
-
-app = Flask(__name__)
-app.config.update(config)
-
-db.app = app
-db.init_app(app)
+from partridge.models.doc import Paper, C_ABRV
 
 PAPER_TYPE_MODEL_PATH = os.path.join(config['MODELS_DIR'], "paper_types.model")
 
-FEATURES = ['Bac', 'Mot', 'Met']
+FEATURES = C_ABRV.keys()
 
 class PaperClassifier:
 
@@ -41,6 +38,7 @@ class PaperClassifier:
 
     def classify_paper( self, paper ):
         inst = self.instance_from_paper(paper)
+
         return self.classifier( inst )
     
     def instance_from_paper( self, paper ):
@@ -57,11 +55,49 @@ class PaperClassifier:
 
 if __name__ == "__main__":
 
+
+    app = Flask(__name__)
+    app.config.update(config)
+
+    db.app = app
+    db.init_app(app)
+
+
+    parser = OptionParser()
+
+    parser.add_option("-a", "--all", action="store_true", dest="all",
+        help="If is set, updates all unknown papers in database")
+
+
+    options,args = parser.parse_args()
+
     c = PaperClassifier()
-    p = c.get_paper_by_id(sys.argv[1])
+
+    if(options.all):
+        print "ignoring ID arguments and retrieving all papers"
+        papers = Paper.query.all()
+    else:
+        print "Retrieving papers with IDs in %s" % args
+        papers = Paper.query.filter(Paper.id.in_(args)).all()
+
+    for p in papers:
+
+        if( p.type != None ):
+            print "Skipping paper %s" % p.title
+            continue
+        
+        print p.title
+        for author in p.authors:
+            print "\t\t" + author.surname
+
+        cls = str(c.classify_paper(p))
+        
+        print "Predicted Class:" + cls
+
+        print "Saving paper type in database"
+        p.type = cls
+        db.session.merge(p)
     
-    print p.title
-    for author in p.authors:
-        print "\t\t" + author.surname
-    
-    print "Predicted Class:" + str( c.classify_paper(p) )
+    #commit the database session at the end of the run
+    db.session.commit()
+

### 2013-03-05 partridge/mltest/paper_tree.py
Set paper tree to use all corescs as features

@@ -59,8 +59,9 @@ class_var.add_value("Research")
 class_var.add_value("Review")
 class_var.add_value("Case Study")
 
-corescs =  C_ABRV.keys() #['Bac', 'Mot', 'Met']
-domain = Orange.data.Domain([Orange.feature.Continuous(x) for x in corescs], 
+FEATURES = C_ABRV.keys()
+
+domain = Orange.data.Domain([Orange.feature.Continuous(x) for x in FEATURES], 
 class_var)
 
 
@@ -75,7 +76,7 @@ for paper in papers:
 
     inst_list = []
     sentdist = paper.sentenceDistribution(True)
-    for coresc in corescs:
+    for coresc in FEATURES:
         inst_list.append( sentdist[coresc] * 100 / len(paper.sentences) )
         
     if(paper.id in review_ids):
@@ -103,9 +104,6 @@ class SimpleTreeLearnerSetProb():
         return self.wrapped(examples)
 
 
-#l = orngTree.TreeLearner( paper_table )
-
-#orngTree.printTxt(l)
 
 tree = Orange.classification.tree.TreeLearner(min_instances=5, measure="gainRatio")
 rf_def = Orange.ensemble.forest.RandomForestLearner(trees=50, base_learner=tree, name="for_gain")
@@ -133,7 +131,7 @@ print "Storing tree learned from data"
 
 import cPickle
 
-tree = rf_def( paper_table)
+tree = rf_simple( paper_table)
 
-with open("forestmodel.model",'wb') as f:
+with open("paper_types.model",'wb') as f:
     cPickle.dump(tree, f)

### 2013-03-05 partridge/tools/pmedget.py
Done some general tidying up of utilities and tools

@@ -1,0 +1,44 @@
+""" Retrieve papers from Pubmed
+
+"""
+import sys
+from optparse import OptionParser
+import os
+from urllib2 import urlopen
+
+apiURL = """http://www.pubmedcentral.gov/oai/oai.cgi?verb=GetRecord&identifier=oai:pubmedcentral.nih.gov:%s&metadataPrefix=pmc"""
+
+def downloadPaper( paper_id, folder):
+    
+    outfilename = os.path.join(folder, "pmc" + paper_id + ".xml")
+
+    if (os.path.exists(outfilename)):
+        print "Paper %s exists, skipping" % paper_id
+
+    u = urlopen(apiURL % id)
+
+    print "Downloading paper at %s" % ( apiURL % id) 
+    
+    with open (outfilename,'wb') as f:
+        f.write(u.read())
+
+
+if __name__ == "__main__":
+
+
+    o = OptionParser()
+
+    
+    o.add_option("-d", "--directory", dest="directory", 
+        help = "Directory to save papers into",default="papers")
+
+    
+    opts, args = o.parse_args()
+
+    for id in args:
+
+        if id.startswith("PMC"):
+            id = id[3:]
+        
+        downloadPaper(id, opts.directory)
+        

### 2013-03-06 doc/final_report/report.tex
Created files for chapters of diss
Started report - got introduction going
Started adding implementation details
Made some changes to the intro

@@
 %The document is a report
-\documentclass[11pt,a4paper]{article}
+\documentclass[11pt,a4paper,oneside]{book}
 
@@
 
+\usepackage{fancyhdr}
+\setlength{\headheight}{15pt}
+
+\pagestyle{fancy}
+
 \begin{document}
@@
 
-%TODO: STATEMENT OF ORIGINALITY
+\thispagestyle{plain}
 
-%TODO: ACKNOWLEDGEMENTS
+\begin{center}
+\textsc{\large Statement of Originality}
+\end{center}
 
-%TODO: ABSTRACT
+This submission is my own work, except where clearly indicated.
+
+I understand that there are severe penalties for plagiarism and other unfair
+practice, which can lead to loss of marks or even the withholding of a degree.
+I have read the sections on unfair practice in the Students’ Examinations
+Handbook and the relevant sections of the current Student Handbook of the
+Department of Computer Science.
+
+I understand and agree to abide by the University’s regulations governing these
+issues.\\\\
+
+........................................
+
+\pagebreak
+\thispagestyle{plain}
+
+\begin{center}
+\textsc{\large Acknowledgements}
+\end{center}
+
+I would like to take this opportunity to say thank you to both of my
+supervisors, Amanda Clare and Maria Liakata, for giving up so much of their
+time to support me in designing and developing this project.
+
+Thanks to the users who tested Partridge once it was made generally available
+and for their feedback in the form of bug reports and suggestions.
+
+Finally, I am eternally grateful for the support of my family and friends who
+have put up with my gripes and moans throughout the duration of this project
+and without whom, I couldn't have achieved such an ambitious project.
+
+\pagebreak
+\thispagestyle{plain}
+
+\begin{center}
+\textsc{\large Abstract}
+\end{center}
+
+When faced with the great number of scientific papers made general available on
+the internet, it is often very difficult for researchers to find relevant
+scientific literature. This project aimed to build an information retrieval and
+recommendation tool that uses Natural Language Processing and Machine Learning
+techniques to present the most relevant scientific papers to a user based upon
+their search criteria and preferences.
+
+A preprocessing system system that exploits existing tools such as SAPIENTA and
+PDFX was used to analyse a large sample of research papers, labelling the
+presence of core scientific concepts (CoreSCs) within each paper and extracting
+metadata. Decision trees were also trained to classify papers into categories
+such as `Research Paper', `Review Paper' and `Case Study' based upon the
+relative proportions of core scientific concepts in the papers.
+
+A web interface was built to facilitate user search of papers based upon the
+contents of specific CoreSCs. Filtering of papers using their type as
+determined by the preprocessor was also built in and a page allowing authors and
+rightsholders to submit their own papers for analysis was created to allow
+the scientific community to extend the utility of the system.
 
@@
 
-\section{Introduction}
+\mainmatter
+
+\chapter{Introduction}
+\input{introduction}
+
+\chapter{ Development Methodology }
+\input{methodology}
+
+\chapter{Design}
+\input{design}
+
+\chapter{Implementation}
+\input{implementation}
+
+\chapter{Testing}
+\input{testing}
+
+\chapter{Evaluation}
+\input{evaluation}
 
@@
 
+\appendix
+\input{appendix}
+
 \end{document}

### 2013-03-06 partridge/views/query.py

@@ -14,9 +14,14 @@ def query():
 
     searchterms = request.args.get('q','')
 
-    r = db.session.query(func.count(Paper.id))
+    papercount = Paper.query.count()
 
-    papercount = r.first()[0]
+    #do paper counts for all paper types
+    paper_types = {'Review':0, 'Research': 0, 'Case Study': 0}
+
+    for k in paper_types:
+        paper_types[k] = str(Paper.query.filter(Paper.type == k).count())
+
 
     if(searchterms != ''):
 
@@ -37,6 +42,10 @@ def query():
 
             if(attr == "offset"):
                 offset = value
+
+            if(attr == "papertype"):
+                if value != "":
+                    clauses.append( Paper.type == value )
 
             if(attr == "author"):
                 paper_q = paper_q.join("authors")
@@ -60,4 +69,5 @@ def query():
         return render_template("query.html", 
             paper_count=papercount,
             limit=PAGE_LIMIT,
-            corescs=C_ABRV)
+            corescs=C_ABRV,
+            paper_types=paper_types)

### 2013-03-06 doc/final_report/design.tex

%%-----------------------------------------------
%
% Include for design chapter of dissertation
%
%%----------------------------------------------

\subsection{ Process Model }

\subsection{ System Design }

\subsection{}

### 2013-03-06 doc/final_report/implementation.tex

@@
 
-The `mega-journals' PLOS ONE \url{http://www.plosone.org/} and arXiv
+The `mega-journals' PLOSOne \url{http://www.plosone.org/} and arXiv
 \url{http://www.arxiv.org/} were suggested as sources for more open access
 articles that could be added to Partridge. Both of these sites were found to
-contain large volumes of open access papers. However, most of these papers were
-published as PDF files which meant that some conversion would be required to
-make them compatible with Partridge.
+contain large volumes of open access papers. Most of the journals stored on the
+arXiv site were in PDF format which, as discussed below, are difficult to
+convert and annotate. However, PLOSOne use the SciXML markup language for
+papers published through their journal, which made converting and annotating
+them a lot simpler for Patridge. PLOSOne also publish all of their papers under
+the Creative Commons Share-Alike-By-Attribution license\cite{ccbyattr}. This
+meant that as long as the author information was left intact, all of the papers
+could be used for data mining purposes.
+
+\subsubsection{Acquiring Scientific Papers}
+Once PLOSOne was identified as a suitable source of papers, a method for
+acquiring large batches of papers to be processed was formulated.
 

### 2013-03-06 doc/final_report/introduction.tex
Wrote abstract and got the main layout looking a bit nicer

@@
 %%%%------------------------------------------------
-\subsection{Context}
+\section{Context}
 
@@
 
-\subsection{Objectives}
+\section{Objectives}
 
@@
 
-From the point of view of its users, Partridge will assist researchers in two
-ways. The system will provide filtering of papers based upon their
+From the point of view of its users, Partridge was designed to assist
+researchers in three principal ways.
+
+\begin{itemize}
+\item The system should provide search within specific CoreSC regions of a given
+paper. This would allow users to find the most relevant papers to them. For
+example a user may search for "mass spectrometer" within the methodology
+section of a paper.
+\item The system should provide filtering of papers based upon their
 specific domain (i.e. is the paper primarily concerned with methodology within
@@
 their result, whether the paper yielded positive, negative or inconclusive
-evidence for a hypothesis. Depending upon the time constraints of the
+evidence for a hypothesis. 
+\item Depending upon the time constraints of the
 project, it is hoped that Partridge will also offer a user 'profiling' system
@@
 
-\subsection{Background}
+\end{itemize}
 
-\subsubsection{ Related Works }
+\section{Background}
+
+\subsection{ Related Works }
 
@@
 
-\subsection{ Literature Review}
+\section{ Literature Review}
 
-\subsubsection{Natural Language Processing}
+\subsection{Natural Language Processing}
 
@@
 
-\subsubsection{CISP, CoreSC and SAPIENTA}
+\subsection{CISP, CoreSC and SAPIENTA}
 

### 2013-03-06 doc/final_report/report.tex

@@
 have put up with my gripes and moans throughout the duration of this project
-and without whom, I couldn't have achieved such an ambitious project.
+and without whom, I may have given up hope on my dissertation.
 

### 2013-03-06 partridge/views/remote.py
initial commit of remote downloader

@@ -1,0 +1,19 @@
+"""Accept remote URL as a paper file and download it """
+
+import pycurl
+
+from flask import current_app
+
+def download_paper( the_url ):
+
+    
+    c = pycurl.Curl()
+    c.setopt(pycurl.URL, the_url)
+    c.setopt(pycurl.FOLLOWLOCATION, True)
+    
+    
+    
+    
+    
+    
+    return "The url you gave me was %s " % the_url

### 2013-03-06 partridge/__init__.py
Got remote downloader working nicely

@@ -21,6 +21,7 @@ def create_app( config ):
     import views.upload
     import views.paper
     import views.query
+    import views.remote
 
     app.url_map.converters["paper"] = PaperConverter
     app.url_map.converters["file"] = FileConverter
@@ -30,6 +31,12 @@ def create_app( config ):
 
     app.add_url_rule("/upload", methods=['GET','POST'], 
         view_func = views.upload.upload)
+
+    app.add_url_rule("/remote", methods=['GET'],
+        view_func = views.remote.scan_url)
+
+    app.add_url_rule("/remote", methods=['POST'],
+        view_func = views.remote.download_papers)
 
     app.add_url_rule("/paper/<paper:the_paper>", 
         view_func=views.paper.paper_profile)

### 2013-03-06 partridge/views/remote.py

@@ -1,19 +1,93 @@
 """Accept remote URL as a paper file and download it """
 
-import pycurl
+import os
+import uuid
 
-from flask import current_app
+from urllib2 import urlopen
 
-def download_paper( the_url ):
+from flask import current_app, render_template, request, jsonify
 
+from partridge.tools.paperstore import PaperParser
+
+def scan_url( the_url=None ):
+    """Scan the URL for papers to download"""
     
-    c = pycurl.Curl()
-    c.setopt(pycurl.URL, the_url)
-    c.setopt(pycurl.FOLLOWLOCATION, True)
+    return render_template("remote_form.html")
+    
+
+def download_papers():
+
+    if "url" in request.form:
+        
+        return do_scan( request.form['url'])
+    elif "download_url" in request.form:
+         url = request.form['download_url']
+
+         try:
+            download_paper( url )
+            return jsonify({"status" : "ok"})
+         except Exception as e:
+            return jsonify({"status" : "error", "message" : str(e)})
+
+def download_paper( url ):
+    """Download the paper at URL and save to uploads folder"""
+
+    destdir = current_app.config['PAPER_UPLOAD_DIR']
+
+    u = urlopen( url )
+    headers = u.info()
+    type = headers['Content-type']
+
+    if type.startswith("text/xml"):
+        ext = ".xml"
+    elif type.startswith("application/pdf"):
+        ext = ".pdf"
+
+    else:
+        raise Exception("URL is not a supported content type")
+
+    with open(os.path.join(destdir,  str(uuid.uuid4()) + ext), 'wb') as f:
+        f.write(u.read())
+
+    u.close()
+
+
+
+def do_scan( url ):
+    """Do the URL scan on the given site and get some json back.
+    """
+
+    #run a load of checks on the URL - it might be a paper
+
+
+    u = urlopen( url )
+
+    #get the headers
+    headers = u.info()
+    type = headers['Content-type']
     
     
-    
-    
-    
-    
-    return "The url you gave me was %s " % the_url
+    #get content type see if HTML, XML etc
+    if type.startswith("text/html"):
+        print "Its a page"
+    elif type.startswith("text/xml"):
+        
+        p = PaperParser()
+        p.parseFileObject( u )
+        
+        u.close()
+
+        return render_template("remote_download.html", the_url=url,
+            filetype="xml", paper_title=p.extractTitle(),
+            authors=p.extractAuthors(),
+            abstract=p.extractAbstract())
+
+
[…]

### 2013-03-06 partridge/util/remote.py
Support harvesting URLS from plos paper profiles

@@ -1,0 +1,69 @@
+""" Set of utility functions for the remote paper downloader
+"""
+import os
+import uuid
+from partridge.tools.paperstore import PaperParser
+
+from HTMLParser import HTMLParser
+from flask import render_template
+
+def download_paper( url, destdir ):
+    """Download the paper at URL and save to uploads folder"""
+
+    u = urlopen( url )
+    headers = u.info()
+    type = headers['Content-type']
+
+    if type.startswith("text/xml"):
+        ext = ".xml"
+    elif type.startswith("application/pdf"):
+        ext = ".pdf"
+
+    else:
+        raise Exception("URL is not a supported content type")
+
+    with open(os.path.join(destdir,  str(uuid.uuid4()) + ext), 'wb') as f:
+        f.write(u.read())
+
+    u.close()
+
+
+def paper_preview( url, file_object ):
+    """Render a paper preview from a filelike object
+    """
+    
+    p = PaperParser()
+    p.parseFileObject( file_object )
+
+    return render_template("remote_download.html", the_url=url,
+        filetype="xml", paper_title=p.extractTitle(),
+        authors=p.extractAuthors(),
+        abstract=p.extractAbstract())
+
+
+class PlosScanner(HTMLParser):
+    
+    link = ""
+    
+    def handle_starttag(self, tag, attrs):
+        if tag == "a":
+            
+            title = ""
+            href = ""
+
+            for key, value in attrs:
+               if key == "title": title = value
+               if key == "href" : href = value
+                
+            if title == "Download article XML":
+                self.link = href
+
+
+def find_paper_plos_page( html ):
+    """Scan the input plos HTML and return a paper URL if possible"""
+    
+    p = PlosScanner()
+    p.feed(html)
+
+    return p.link
+    

### 2013-03-06 partridge/views/remote.py

@@ -1,13 +1,15 @@
 """Accept remote URL as a paper file and download it """
 
 import os
-import uuid
 
 from urllib2 import urlopen
 
+import urlparse
+
 from flask import current_app, render_template, request, jsonify
 
-from partridge.tools.paperstore import PaperParser
+from partridge.util.remote import download_paper, paper_preview, \
+find_paper_plos_page
 
 def scan_url( the_url=None ):
     """Scan the URL for papers to download"""
@@ -18,40 +20,16 @@ def scan_url( the_url=None ):
 def download_papers():
 
     if "url" in request.form:
-        
         return do_scan( request.form['url'])
+
     elif "download_url" in request.form:
          url = request.form['download_url']
 
          try:
-            download_paper( url )
+            download_paper( url, current_app.config['PAPER_UPLOAD_DIR'] )
             return jsonify({"status" : "ok"})
          except Exception as e:
             return jsonify({"status" : "error", "message" : str(e)})
-
-def download_paper( url ):
-    """Download the paper at URL and save to uploads folder"""
-
-    destdir = current_app.config['PAPER_UPLOAD_DIR']
-
-    u = urlopen( url )
-    headers = u.info()
-    type = headers['Content-type']
-
-    if type.startswith("text/xml"):
-        ext = ".xml"
-    elif type.startswith("application/pdf"):
-        ext = ".pdf"
-
-    else:
-        raise Exception("URL is not a supported content type")
-
-    with open(os.path.join(destdir,  str(uuid.uuid4()) + ext), 'wb') as f:
-        f.write(u.read())
-
-    u.close()
-
-
 
 def do_scan( url ):
     """Do the URL scan on the given site and get some json back.
@@ -59,8 +37,10 @@ def do_scan( url ):
 
     #run a load of checks on the URL - it might be a paper
 
-
-    u = urlopen( url )
+    try:
+        u = urlopen( url )
+    except:
+        return "Invalid URL. Try again!"
 
     #get the headers
     headers = u.info()
@@ -69,18 +49,37 @@ def do_scan( url ):
     
     #get content type see if HTML, XML etc
     if type.startswith("text/html"):
-        print "Its a page"
-    elif type.startswith("text/xml"):
-        
-        p = PaperParser()
-        p.parseFileObject( u )
-        
-        u.close()
 
+        #see if its a PLOS page and whether we can harvest links
+
+        if( url.find("www.plosone.org/article/info") > -1):
+            #try extracting links to XML doc
+            path = find_paper_plos_page( u.read() )
[…]

### 2013-03-06 partridge/static/js/bookmarklet.js
Added bookmarklet

@@ -1,0 +1,73 @@
+/**
+ *  This is a bookmarklet for Partridge remote paper adder
+ *
+ * Code based upon http://coding.smashingmagazine.com/2010/05/23/make-your-own-bookmarklets-with-jquery/
+ *
+ */ 
+
+(function(){
+
+        // the minimum version of jQuery we want
+        var v = "1.3.2";
+
+        // check prior inclusion and version
+        if (window.jQuery === undefined || window.jQuery.fn.jquery < v) {
+                var done = false;
+                var script = document.createElement("script");
+                script.src = "http://ajax.googleapis.com/ajax/libs/jquery/" + v + "/jquery.min.js";
+                script.onload = script.onreadystatechange = function(){
+                        if (!done && (!this.readyState || this.readyState == "loaded" || this.readyState == "complete")) {
+                                done = true;
+                                initMyBookmarklet();
+                        }
+                };
+                document.getElementsByTagName("head")[0].appendChild(script);
+        } else {
+                initMyBookmarklet();
+        }
+        
+        function initMyBookmarklet() {
+                (window.myBookmarklet = function() {
+
+                loc = encodeURI(window.location.href);
+
+                var remoteLoc = "http://localhost:5000/remote#url=" + loc;
+
+                if(jQuery("#partridgeFrame").length == 0){
+
+
+                    //initialise partridge frame
+                    jQuery("body").append("\
+                        <div id='partridgeFrame'>\
+                            <div id='partridgeFrame_veil' style=''>\
+                                    <p>Loading...</p>\
+                            </div>\
+                            <iframe src='"+remoteLoc+"' onload=\"jQuery('#partridgeFrame iframe').slideDown(500);\">Enable iFrames.</iframe>\
+                            <style type='text/css'>\
+                                    #partridgeFrame_veil { display: none; position: fixed; width: 100%; height: 100%; top: 0; left: 0; background-color: rgba(255,255,255,.25); cursor: pointer; z-index: 900; }\
+                                    #patridgeFrame_veil p { color: black; font: normal normal bold 20px/20px Helvetica, sans-serif; position: absolute; top: 50%; left: 50%; width: 10em; margin: -10px auto 0 -5em; text-align: center; }\
+                                    #partridgeFrame iframe { display: none; position: fixed; top: 10%; left: 10%; width: 80%; height: 80%; z-index: 999; border: 10px solid rgba(0,0,0,.5); margin: -5px 0 0 -5px; }\
[…]

### 2013-03-06 partridge/util/remote.py
Made important changes to remote.py

@@ -4,6 +4,9 @@ import os
 import uuid
 from partridge.tools.paperstore import PaperParser
 
+
+from urllib2 import urlopen
+
 from HTMLParser import HTMLParser
 from flask import render_template
 

### 2013-03-06 partridge/__init__.py
Finished making the bookmarklet code nice

@@ -38,6 +38,8 @@ def create_app( config ):
     app.add_url_rule("/remote", methods=['POST'],
         view_func = views.remote.download_papers)
 
+    app.add_url_rule("/bookmarklet", view_func = views.remote.bookmarklet)
+
     app.add_url_rule("/paper/<paper:the_paper>", 
         view_func=views.paper.paper_profile)
 

### 2013-03-06 partridge/templates/bookmarklet.js

@@ -31,7 +31,7 @@
 
                 loc = encodeURI(window.location.href);
 
-                var remoteLoc = "http://localhost:5000/remote#url=" + loc;
+                var remoteLoc = "{{ url_for('.scan_url', _external=True) }}#url=" + loc;
 
                 if(jQuery("#partridgeFrame").length == 0){
 

### 2013-03-06 partridge/views/remote.py

@@ -6,7 +6,7 @@ from urllib2 import urlopen
 
 import urlparse
 
-from flask import current_app, render_template, request, jsonify
+from flask import current_app, render_template, request, jsonify, make_response
 
 from partridge.util.remote import download_paper, paper_preview, \
 find_paper_plos_page
@@ -15,6 +15,12 @@ def scan_url( the_url=None ):
     """Scan the URL for papers to download"""
     
     return render_template("remote_form.html")
+
+def bookmarklet():
+    """Serve up the bookmarklet script"""
+    response = make_response(render_template("bookmarklet.js"))
+    response.headers['Content-type'] = "text/javascript"
+    return response
     
 
 def download_papers():

### 2013-03-06 doc/final_report/introduction.tex

@@
 
-From the point of view of its users, Partridge was designed to assist
-researchers in three principal ways.
+Partridge is designed to help and facilitate researchers and authors of
+scientific papers in the following principal ways:
 
@@
 section of a paper.
+\item Partridge should allow authors and rightsholders of scientific papers to
+upload their papers to the system for inclusion into the search system. This
+would give Partridge itself more utility and would make involved authors more
+accessible.
 \item The system should provide filtering of papers based upon their
@@
 \item Depending upon the time constraints of the
-project, it is hoped that Partridge will also offer a user 'profiling' system
+project, it was hoped that Partridge will also offer a user 'profiling' system
 that provides recommendations for researchers based on their reading history.
 This feature should help users find relevant papers more quickly or find
-research that they may have otherwise overlooked.
+research that they may have otherwise overlooked.a
+\end{itemize}
 
-\end{itemize}
+As well as helping users locate files, Partridge will also
 

### 2013-03-06 partridge/util/remote.py
Got PMC paper pulling working now

@@ -70,3 +70,4 @@ def find_paper_plos_page( html ):
 
     return p.link
     
+

### 2013-03-06 partridge/views/remote.py

@@ -1,6 +1,7 @@
 """Accept remote URL as a paper file and download it """
 
 import os
+import re
 
 from urllib2 import urlopen
 
@@ -10,6 +11,8 @@ from flask import current_app, render_template, request, jsonify, make_response
 
 from partridge.util.remote import download_paper, paper_preview, \
 find_paper_plos_page
+
+PMC_OSI = "http://www.pubmedcentral.gov/oai/oai.cgi?verb=GetRecord&identifier=oai:pubmedcentral.nih.gov:%s&metadataPrefix=pmc"
 
 def scan_url( the_url=None ):
     """Scan the URL for papers to download"""
@@ -43,6 +46,19 @@ def do_scan( url ):
 
     #run a load of checks on the URL - it might be a paper
 
+
+    if( url.find("ncbi.nlm.nih.gov/pmc/articles/") > -1):
+       
+        #get paper by PMC
+        m = re.search("PMC([0-9]+)", url)
+        
+        if m != None:
+            id = m.group(1)
+
+            url = PMC_OSI % id
+
+    print url
+
     try:
         u = urlopen( url )
     except:
@@ -75,6 +91,8 @@ def do_scan( url ):
                 u.close()
                 
                 return output
+
+
 
         ##-----Otherwise if we got to this stage, no HTML handler is set up
         

### 2013-03-06 alembic/versions/4abc902af771_added_paper_listener.py
Created paper watchers

@@ -1,0 +1,30 @@
+"""Added paper listeners/watchers table
+
+Revision ID: 4abc902af771
+Revises: 254c397fb9c5
+Create Date: 2013-03-06 21:21:22.816434
+
+"""
+
+# revision identifiers, used by Alembic.
+revision = '4abc902af771'
+down_revision = '254c397fb9c5'
+
+from alembic import op
+import sqlalchemy as sa
+
+
+def upgrade():
+    ### commands auto generated by Alembic - please adjust! ###
+    op.create_table('paper_watchers',
+    sa.Column('filename', sa.String(length=50), nullable=False),
+    sa.Column('email', sa.String(length=50), nullable=True),
+    sa.PrimaryKeyConstraint('filename')
+    )
+    ### end Alembic commands ###
+
+
+def downgrade():
+    ### commands auto generated by Alembic - please adjust! ###
+    op.drop_table('paper_watchers')
+    ### end Alembic commands ###

### 2013-03-06 partridge/models/doc.py

@@ -115,4 +115,10 @@ class Author( db.Model ):
 
 #-----------------------------------------------------------------------------
 
+class PaperWatcher( db.Model ) :
 
+    __tablename__ = "paper_watchers"
+
+    filename = Column(String(50), primary_key=True)
+    email = Column(String(50))
+    

### 2013-03-06 partridge/preprocessor/daemon.py
added email handling to remote backend

@@ -12,10 +12,11 @@ from multiprocessing import Queue
 from Queue import Empty
 
 from partridge.preprocessor.fs import FilesystemWatcher
-from partridge.preprocessor.notification import send_error_report
+from partridge.preprocessor.notification import send_error_report, \
+send_success_report
 
 from partridge.models import db
-from partridge.models.doc import PaperFile
+from partridge.models.doc import PaperFile, PaperWatcher
 
 from partridge.tools.paperstore import PaperParser
 from partridge.tools.converter import PDFXConverter
@@ -53,6 +54,9 @@ class PaperDaemon(Thread):
                 self.logger.info("Processing %s", paper)
                 try:
                     paperObj = self._process_paper(paper)
+
+                    self.informWatcher( paper,paperObj=paperObj)
+
                 except Exception as e:
                     #get exception information and dump to user
                     exc_type, exc_obj, exc_tb = sys.exc_info()
@@ -62,12 +66,20 @@ class PaperDaemon(Thread):
                     for line in traceback.format_tb(exc_tb):
                         self.logger.error(line)
 
+                    self.informWatcher( paper, 
+                        exception=e, 
+                        tb=exc_tb,
+                        files=[file for file,action in self.paper_files])
+
                     if not isinstance(e, PaperExistsException):
                     
                         try:
                             #send the error report
                             send_error_report( e, exc_tb, 
                                 [file for file,action in self.paper_files])
+
+
+
                         except Exception as e:
                             self.logger.error("ERROR SENDING EMAIL: %s", e)
 
@@ -75,6 +87,7 @@ class PaperDaemon(Thread):
                     paperObj = None
 
                 finally:
+
                     self.cleanupFiles(paperObj)
 
             except Empty:
@@ -83,6 +96,28 @@ class PaperDaemon(Thread):
 
         # stop the filesystem watcher
         self.fsw.stop()
+
+    def informWatcher(self, papername, **kwargs):
+        '''Inform watchers of papers what happened to them''' 
+
+        basename = os.path.basename(papername)
+
+        q = PaperWatcher.query.filter(PaperWatcher.filename == basename)
+
+        if(q.count() > 0):
+            w = q.first()
+
+            self.logger.info("Informing %s about paper %s", w.email, w.filename) 
+
+            if "paper" in kwargs:
+                send_success_report( kwargs['paperObj'], w.email)
+            else:
+                send_error_report( kwargs['exception'], kwargs['tb'],
[…]

### 2013-03-06 partridge/preprocessor/notification.py

@@ -3,10 +3,11 @@ import traceback
 
 from email.mime.multipart import MIMEMultipart
 from email.mime.text import MIMEText
-
 from partridge.config import config
 
-def send_error_report( error, tb, paper_files):
+from flask import url_for
+
+def send_error_report( error, tb, paper_files, to=config['NOTIFICATION_ADDRESS']):
     """ Send an email report when a paper fails to process
     """
 
@@ -15,10 +16,8 @@ def send_error_report( error, tb, paper_files):
     msg = MIMEMultipart()
     msg['Subject'] = "Partridge Failed to process a paper"
     msg['From']  = config['NOTIFICATION_FROM']
-    msg['To'] = config['NOTIFICATION_ADDRESS']
+    msg['To'] = to
     msg.preamble = "Message from the partridge paper processing daemon"
-
-    
 
     #encode the message
     text = "Failed to process a paper because %s \n" % error
@@ -36,11 +35,40 @@ def send_error_report( error, tb, paper_files):
         attachment.add_header('Content-Disposition', 'attachment',filename=file)
         msg.attach(attachment)
 
+    send_mail( msg )
+
+#-----------------------------------------------------------------------------
+
+def send_success_report( paperObj, to=config['NOTIFICATION_ADDRESS']):
+   
+    url = url_for(".paper_profile", paper=paperObj, _external=True)
+
+    txt = """Hi There,
+
+Thanks for submitting your paper to Partridge. We've done some analysis and
+your paper has been included into our corpus.
+
+Paper Title: %s
+Paper Type: %s
+
+You can see it here %s
+
+Thanks,
+
+The Partridge Paper Processing Monkey """ % (paperObj.title, paperObj.type, url)
+
+    msg = MIMEText(txt)
+    msg['Subject'] = "Partridge Paper Success Notification"
+    msg['From']  = config['NOTIFICATION_FROM']
+    msg['To'] = to
+
+    send_mail( msg )
+#-----------------------------------------------------------------------------
+
+def send_mail( msg ):
     s = smtplib.SMTP(config['NOTIFICATION_SMTP_SERVER'])
     s.login(config['NOTIFICATION_SMTP_USER'], 
         config['NOTIFICATION_SMTP_PASWD'])
     s.sendmail(config['NOTIFICATION_FROM'], config['NOTIFICATION_ADDRESS'],msg.as_string())
     s.quit()
 
-
-            

### 2013-03-06 partridge/util/remote.py

@@ -25,10 +25,14 @@ def download_paper( url, destdir ):
     else:
         raise Exception("URL is not a supported content type")
 
-    with open(os.path.join(destdir,  str(uuid.uuid4()) + ext), 'wb') as f:
+    filename = str(uuid.uuid4()) + ext
+
+    with open(os.path.join(destdir,  filename), 'wb') as f:
         f.write(u.read())
 
     u.close()
+
+    return filename
 
 
 def paper_preview( url, file_object ):

### 2013-03-06 partridge/views/remote.py

@@ -12,6 +12,9 @@ from flask import current_app, render_template, request, jsonify, make_response
 from partridge.util.remote import download_paper, paper_preview, \
 find_paper_plos_page
 
+from partridge.models import db
+from partridge.models.doc import PaperWatcher
+
 PMC_OSI = "http://www.pubmedcentral.gov/oai/oai.cgi?verb=GetRecord&identifier=oai:pubmedcentral.nih.gov:%s&metadataPrefix=pmc"
 
 def scan_url( the_url=None ):
@@ -34,8 +37,20 @@ def download_papers():
     elif "download_url" in request.form:
          url = request.form['download_url']
 
+
          try:
-            download_paper( url, current_app.config['PAPER_UPLOAD_DIR'] )
+            paper = download_paper( url, 
+                current_app.config['PAPER_UPLOAD_DIR'])
+
+            if "email" in request.form:
+                watcher = PaperWatcher()
+                watcher.email = request.form['email']
+                watcher.filename = paper
+
+                db.session.add(watcher)
+                db.session.commit()
+
+
             return jsonify({"status" : "ok"})
          except Exception as e:
             return jsonify({"status" : "error", "message" : str(e)})
@@ -56,8 +71,6 @@ def do_scan( url ):
             id = m.group(1)
 
             url = PMC_OSI % id
-
-    print url
 
     try:
         u = urlopen( url )

### 2013-03-07 partridge/preprocessor/daemon.py
Email notifications for remote papers now working

@@ -54,8 +54,14 @@ class PaperDaemon(Thread):
                 self.logger.info("Processing %s", paper)
                 try:
                     paperObj = self._process_paper(paper)
-
-                    self.informWatcher( paper,paperObj=paperObj)
+                    
+                    try:
+                        self.informWatcher( paper,paperObj=paperObj)
+                    except Exception as e:
+                        self.logger.warn("Watcher couldn't be informed: %s", e)
+                        exc_type, exc_obj, exc_tb = sys.exc_info()
+                        for line in traceback.format_tb(exc_tb):
+                            self.logger.error(line)
 
                 except Exception as e:
                     #get exception information and dump to user
@@ -66,10 +72,16 @@ class PaperDaemon(Thread):
                     for line in traceback.format_tb(exc_tb):
                         self.logger.error(line)
 
-                    self.informWatcher( paper, 
-                        exception=e, 
-                        tb=exc_tb,
-                        files=[file for file,action in self.paper_files])
+                    try:
+                        self.informWatcher( paper, 
+                            exception=e, 
+                            tb=exc_tb,
+                            files=[file for file,action in self.paper_files])
+                    except Exception as emailError:
+                        self.logger.error("Error sending message %s",
+                            emailError)
+
+
 
                     if not isinstance(e, PaperExistsException):
                     
@@ -77,8 +89,6 @@ class PaperDaemon(Thread):
                             #send the error report
                             send_error_report( e, exc_tb, 
                                 [file for file,action in self.paper_files])
-
-
 
                         except Exception as e:
                             self.logger.error("ERROR SENDING EMAIL: %s", e)
@@ -109,7 +119,7 @@ class PaperDaemon(Thread):
 
             self.logger.info("Informing %s about paper %s", w.email, w.filename) 
 
-            if "paper" in kwargs:
+            if "paperObj" in kwargs:
                 send_success_report( kwargs['paperObj'], w.email)
             else:
                 send_error_report( kwargs['exception'], kwargs['tb'],
@@ -229,6 +239,9 @@ class PaperDaemon(Thread):
 
         if(paper == None):
             self.logger.warn("Paper was not processed, removing files")
+        else:
+            #make sure the paper is bound to the session
+            db.session.add(paper)
 
         def keep_file( filename ):
             fileObj = PaperFile( path=filename )

### 2013-03-07 partridge/preprocessor/notification.py

@@ -1,11 +1,16 @@
 import smtplib
 import traceback
+import os
 
 from email.mime.multipart import MIMEMultipart
 from email.mime.text import MIMEText
 from partridge.config import config
 
 from flask import url_for
+
+from partridge.models import db
+
+app = db.app
 
 def send_error_report( error, tb, paper_files, to=config['NOTIFICATION_ADDRESS']):
     """ Send an email report when a paper fails to process
@@ -20,7 +25,18 @@ def send_error_report( error, tb, paper_files, to=config['NOTIFICATION_ADDRESS']
     msg.preamble = "Message from the partridge paper processing daemon"
 
     #encode the message
-    text = "Failed to process a paper because %s \n" % error
+    text = """Hi There,
+
+Thanks for submitting your paper to Partridge for processing. Unfortunately,
+there was an error handling your paper and it couldn't be added to the
+database. The error message is below as well as the paper files that you
+uploaded/requested.
+
+Thanks,
+
+The Partridge Paper Processing Monkey
+    
+Failed to process a paper because %s \n""" % error
 
     for line in traceback.format_tb(tb):
         text += line
@@ -31,18 +47,25 @@ def send_error_report( error, tb, paper_files, to=config['NOTIFICATION_ADDRESS']
     for file in paper_files:
         with open(file, 'rb') as f:
             attachment = MIMEText(f.read(), _subtype="xml")
+        
+        basename = os.path.basename(file)
 
-        attachment.add_header('Content-Disposition', 'attachment',filename=file)
+        attachment.add_header('Content-Disposition',
+            'attachment',filename=basename)
+
         msg.attach(attachment)
 
-    send_mail( msg )
+    send_mail( msg, to)
 
 #-----------------------------------------------------------------------------
 
 def send_success_report( paperObj, to=config['NOTIFICATION_ADDRESS']):
    
-    url = url_for(".paper_profile", paper=paperObj, _external=True)
-
+    ctx=app.test_request_context()
+    ctx.push()
+    url = url_for(".paper_profile", the_paper=paperObj, _external=True)
+    ctx.pop()
+ 
     txt = """Hi There,
 
 Thanks for submitting your paper to Partridge. We've done some analysis and
@@ -51,7 +74,8 @@ your paper has been included into our corpus.
 Paper Title: %s
[…]

### 2013-03-07 partridge/static/js/remote.js

@@ -101,15 +101,23 @@ function onDownloadPaper( data, status){
 
 function downloadPaper(){
 
-    url = downloads.pop();
+    var email = $("#email").val()
+
+    var url = downloads.pop();
     currentDownload = url;
+
+    var data = {"download_url" : url}
+
+    if( email != "" ){
+        data['email'] = email
+    }
 
     $("#downloadLog").append("\n Downloading " + url  + "...");
 
     $.ajax({
         "url": remote_paper_backend,
         "type" : "POST",
-        "data" : {"download_url" : url},
+        "data" : data,
         "success" : onDownloadPaper
     });
 

### 2013-03-07 partridge/views/remote.py

@@ -7,7 +7,7 @@ from urllib2 import urlopen
 
 import urlparse
 
-from flask import current_app, render_template, request, jsonify, make_response
+from flask import current_app as app, render_template, request, jsonify, make_response
 
 from partridge.util.remote import download_paper, paper_preview, \
 find_paper_plos_page
@@ -36,19 +36,26 @@ def download_papers():
 
     elif "download_url" in request.form:
          url = request.form['download_url']
+         
+         paper = download_paper( url, 
+                app.config['PAPER_UPLOAD_DIR'])
 
 
          try:
-            paper = download_paper( url, 
-                current_app.config['PAPER_UPLOAD_DIR'])
+            app.logger.info("Downloading paper at %s", url)
+
 
             if "email" in request.form:
+                app.logger.info("Registering watcher for paper at email %s",
+                    request.form['email'])
+
                 watcher = PaperWatcher()
                 watcher.email = request.form['email']
                 watcher.filename = paper
 
                 db.session.add(watcher)
                 db.session.commit()
+
 
 
             return jsonify({"status" : "ok"})

### 2013-03-07 partridge/views/upload.py
Upload from local now provides email notification

@@ -5,6 +5,8 @@ import uuid
 from flask import render_template, request, current_app
 from werkzeug import secure_filename
 
+from partridge.models import db
+from partridge.models.doc import PaperWatcher
 
 ALLOWED_EXTENSIONS = ['.xml','.pdf']
 
@@ -15,7 +17,7 @@ def upload():
 
     if(request.method == "POST"):
 
-        
+
         destdir = current_app.config['PAPER_UPLOAD_DIR']
 
         for f in request.files:
@@ -27,6 +29,20 @@ def upload():
             if ext in ALLOWED_EXTENSIONS:
                 fname = str(uuid.uuid4()) + ext
                 file.save(os.path.join(destdir,fname))
+
+            if ("email" in request.args) & (request.args['email'] != ""):
+                
+                current_app.logger.info("Registering watcher for paper at email %s",
+                request.args['email'])
+
+                watcher = PaperWatcher()
+                watcher.email = request.args['email']
+                watcher.filename = fname
+
+                db.session.add(watcher)
+                db.session.commit()
+            
+
 
 
 

### 2013-03-07 partridge/views/query.py
Fixed query behaviour replacing or_ with and_

@@ -4,7 +4,7 @@ from flask import render_template,request,jsonify
 from partridge.models import db
 from partridge.models.doc import Paper,Sentence,Author, C_ABRV
 
-from sqlalchemy import func, or_
+from sqlalchemy import func, or_, and_
 
 PAGE_LIMIT = 10
 
@@ -57,7 +57,7 @@ def query():
                 clauses.append( ( Sentence.coresc == attr ) & 
                     Sentence.text.like("%%%s%%" % value))
         
-        paper_q = paper_q.filter(or_(*clauses))
+        paper_q = paper_q.filter(and_(*clauses))
 
         papers = paper_q.limit(PAGE_LIMIT).offset(offset).all()
         

### 2013-03-15 doc/final_report/testing.tex
Added a whole load of stuff on testing machine algorithms

--- 2013-02-28 doc/final_report/testing.tex
@@
 
-\subsection{ Unit Testing }
+\section{ Unit Testing }
 
-\subsection{ User Testing }
+At the beginning of the project, Unit tests for Patridge's server and paper
+preprocessing components were written in order to test that the main bulk of
+the application worked before it was deployed to the production system at
+\url{http://farnsworth.papro.org.uk}. These tests were written and maintained
+throughout the project and occasionally had to be changed as code was
+refactored. As each new feature was added to the system, the whole suite of
+tests was executed to provide integration coverage and make sure that new
+features did not break existing code.
+
+\subsection{ Backend \& Infrastructure Testing}
+
+The backend of the system was tested using Python unit tests based upon the
+built in \emph{unittest} module and a third party testing library called
+\emph{Nose} which provided automated test discovery. This meant that a user who
+ran the command \emph{nose} from the project directory could automatically find
+and run all of the unit tests in the project without having to set up
+boilerplate test suites as in \emph{JUnit}.
+
+\subsection{ Selenium \& Frontend Testing }
+
+The frontend parts of Partridge that were written in Javascript and HTML5 also
+had to be tested to verify that the query and upload forms behaved as expected.
+
+\section{ User Testing }
 
@@
 
-\subsection{ Testing Learning Algorithms }
+\section{ Evaluating Learning Algorithms }
 
-Patridge uses machine learning algorithms to classify the type of research
-papers added to its database. It was therefore necessary to test that these
-algorithms were sufficiently trained and provide accurate classification.
-Unlike
+As discussed above, Patridge uses a supervised learning algorithm, a Random
+Decision Forest, to classify the type of each of the scientific papers added to
+its database. Unlike traditional procedural algorithms that can be unit tested
+and in some cases formally proven to behave uniformly at
+runtime\cite{filliatre2007formal}, supervised learning algorithms are imperfect
+systems that build `working models' from known data. This makes the performance
+of supervised learning systems much more difficult to assess. Russell and
+Norvig(2010) suggest that ``a learning system is good if it produces hypotheses
+that do a good job of predicting the classification of unseen
+examples\cite{russell2010artificial}." It is suggested that when training a
+supervised learning system, some of the example data should be kept back when
+during the training phase and instead, used as `unseen examples' and classified
+by the newly trained system to judge its accuracy
+\cite{alpaydin2004introduction}\cite{russell2010artificial}.
+
+A common technique for partitioning data into `seen' and `unseen' or training
+and test data sets is to simply split the data into two sets through the use of
+random sampling.  A 60:40 divide between training and test data is common.
+Witten explains that ``it is better to use more than half the data for
+training, even at the expense of test data\cite{witten2005data}."
+
+\subsection{ Three Fold Validation }
+
+Three fold validation is a commonly used method for using all of the available
+data for both testing and training whilst still maintaining . As the name
+suggests, test data is split into three disjoint sets and then the classifier
+is trained on two of the sets and tested with the third. This is repeated three
+times so that all sets are used for both training and testing. Results from
+each of the folds can be represented separately or an average taken.
+
+\subsection{ Result Presentation }
+
+Results from the evaluation methods discussed above can be presented in a
+number of ways. When working with machine learning systems, it is important to
+analyse performance using a selection of techniques in order to get a
+comprehensive image of the capabilities and restrictions of the system.
+
+Classifier Accuracy (CA), Receiver Operating Characteristics
+(ROC) charts and Area Under the Curve (AUC) give a general overview of the
+classifier's behaviour, whilst confusion matrices, recall, precision and
+f-measure give a detailed view of which specific data types were most
+frequently misclassified and what they were mistaken for.
+
+\subsubsection{ Classifier Accuracy }
+
+The CA of a supervised classifier is simply represented as the percentage of
+the test data that the classifier was able to predict correctly. CA values that
+tend towards 1.0 correspond to a more accurate classifier. In a Three Fold
+validation, the CA for the classifier is calculated by taking the mean of the
+individual performance values from each of the test/train cycles.
+
+3 Fold Validation on the Partridge corpus
+
+\subsubsection{ Receiver Operating Characteristics Chart}
+
+Receiver Operating Characteristics (ROC) Charts are used to visually represent
+the trade-off between True Positives(TP) and False Positives(FP) as identified
+by the classifier under evaluation. Witten(2005) explains that ROC is a method
+reappropriated from signal processing analysts who use it to visualise ``...hit
+rate and false alarm rate over noisy communication
+channels\cite{witten2005data}." The ratio of TP to FP classifications is
+measured with increasing numbers of test samples from left to right.
+
+ROC charts are often divided into halves diagonally by a line indicating where
+the TP-FP ratio is equal. There may be multiple plots on the axes if several
+learning algorithms are under evaluation. A graph plot that presents a steep
+curve that mostly fits into the upper left half of the graph shows a high TP-FP
+ratio which is a sign that the classifier is working well.  Figure
+\ref{fig:roc_random_forest} shows the ROC Chart for Partridge's Topic
+Classifier after training on 60\% of the Partridge corpus and testing on 40\%.
+
+\begin{figure}[!h]
+\begin{center}
+\includegraphics[width=0.65\textwidth]{images/testing/ROC.png}
+\caption{ ROC Curve for Partridge's Random Forest Topic Classifier}
+\label{fig:roc_random_forest}
+\end{center}
+\end{figure}
+
+\subsubsection{ Area Under Curve }
+
+The Area Under the Curve (AUC) measure is calculated as a percentage of  the
+area underneath a ROC curve. This can again be used to give an indication of
+the trade-off between true positive and false positive classification. It is a
+percentage measurement, where 100\% indicates a high TP-FP ratio. AUC is often
+used instead of visualising a ROC graph for brevity or where average
+performance of a classifier over several train-test cycles is to be calculated.
+The average AUC for Partridge's Random Tree Paper Type classifier after is
+96.6\% after three fold validation is executed over the whole set of papers.
+
+Comparison of this result with the above graph does show discrepancies between
+simple 60:40 proportional validation and 3-fold validation - the average
+performance of the latter seems to be slightly more accurate. This may be
+because a slightly higher number of training examples (66\% rather than 60\%)
+were used to train the classifiers during 3-fold validation and that the errors
+were averaged out at the end of the process.
+
+\subsubsection{ Confusion Matrices}
+
+Confusion Matrices are a way of showing comprehensively which classes a machine
+learning system struggles to discriminate between the most. Known classes are
+shown on the vertical axis of the matrix and predicted classes are shown across
+the horizontal. This allows inference of which data classes a trained
+classifier struggles to label most frequently and any classes that it commonly
+confuses them with. A set of confusion matrices for the Paper Type Classifier
+in Partridge can be seen in Figure \ref{fig:conf_matrices} below.
+
+\begin{figure}[!h]
+
+\centering
+
+\begin{subfigure}[b]{\textwidth}
+
+\caption{Fold 1 Results}
+\centering
+\begin{tabular}{| l || l | l | l |}
+\hline
+	&	Case Study&	Research&	Review\\
+\hline
+\hline
+Case Study&	83&		2&		12\\
+\hline
+Research&	3&		255&		0\\
+\hline
+Review&		4&		2&		159\\
+\hline
+
+\end{tabular}
+\end{subfigure}
+
+\begin{subfigure}[b]{\textwidth}
+
+\caption{Fold 2 Results}
+\centering
+\begin{tabular}{| l || l | l | l |}
+\hline
+&	        Case Study&     Research&	Review\\
+\hline
+\hline
+Case Study&     85    &         2&		10\\
+\hline
+Research&	0   &		256&		2\\
+\hline
+Review&		5&		1&		159\\
+\hline
+\end{tabular}
+
+\end{subfigure}
+
+\begin{subfigure}[b]{\textwidth}
+
+\caption{Fold 3 Results}
+\centering
+\begin{tabular}{| l || l | l | l |}
+\hline
+&		Case Study&	Research&	Review\\
+\hline
+\hline
+Case Study&	82&		3	&	12 \\
+Research&	0&		257	&	1\\
+Review&		7&		2	&	156\\
+\hline
+\end{tabular}
+
+\end{subfigure}
+
+\caption{ Confusion matricies for the 3-Fold validation process}
+\label{fig:conf_matrices}
+
+\end{figure}
+
+These results show that Partridge's decision tree is very effective at
+classifying the three document types in its database. It is also clear however,
+that whilst the classifier is outstanding at recognising Research papers, it
+sometimes struggles to discriminate between Case Study and review papers. This
+may be because case studies can be considered a specific type of review paper
+and the two classes share more similar CoreSC features than they do with
+research papers.
+
+\subsubsection{ Precision, Recall and F-Measure }
+
+From a classifier's confusion matrices, it is possible to calculate its
+Precision, Recall and F-Measure values. These can be used to make further
+assertions about the validity of a classifier's behaviour
+\cite{witten2005data}.
+
+The Precision of a classifier is the fraction of data samples retrieved that
+were correctly classified. This is defined as:
+\[Precision = \frac{tp}{tp+fp} \]
+
+The Recall of a classifier is the proportion of samples within a given class
+that the classifier is able to correctly classify. For example: the number of
+apples that a classifier identifies as apples within a training set of fruit.
+This is defined as:
+\[Recall = \frac{tp}{tp+fn} \]
+
+The F-Measure of a classifier is used to characterise both Recall and Precision
+in a single value. The F-Measure of a classifer can be defined as:
+\[
+F-Measure = \frac{ 2 \times Recall \times Precision} { Recall + Precision } = 
+\frac{2 . TP}{ 2 . TP + FP + FN }
+\]
+
+\begin{figure}[!th]
+
+\centering
+\begin{tabular}{| l | l | l | l | l |}
+\hline
+&        &\textbf{Recall}&\textbf{Precision}&\textbf{F-Measure}\\
+\hline
+\hline
+\multirow{4}{*}{Fold 1} & Case Study & 0.85 & 0.92 & 0.89 \\
+                        & Review     & 0.96 & 0.92 & 0.94 \\
+                        & Research   & 0.98 & 0.98 & 0.98 \\
+\hline
+
+\multirow{4}{*}{Fold 2} & Case Study & 0.87 & 0.94 & 0.91 \\
+                        & Review     & 0.96 & 0.92 & 0.94 \\
+                        & Research   & 0.99 & 0.98 & 0.99 \\
+
+\hline
+
+\multirow{4}{*}{Fold 3} &Case Study & 0.84 & 0.92 & 0.88 \\
+                        & Review    & 0.95 & 0.92 & 0.93 \\
+                        & Research  & 0.99 & 0.98 & 0.99 \\
+
+\hline
+
+\end{tabular}
+
+\caption{Recall Precision and F-Measure values for Partridge Topic Classifier}
+\label{fig:fmeasure_table}
+
+\end{figure}
+
+Recall, Precision and F-Measure was calculated for each of the classes and in
+each iteration of the three fold validation sequence. The results in Figure
+\ref{fig:fmeasure_table} show good recall, precision and f-measure for all
+three document types within Partridge. These results verify that Case Study is
+the hardest document type to classify as discussed above.

### 2013-03-15 partridge/mltest/clustertest.py

@@ -1,6 +1,10 @@
 import Orange
 import os
 import logging
+import sys
+
+import matplotlib.pyplot as plt
+from mpl_toolkits.mplot3d import Axes3D
 
 from partridge.config import config
 from flask import Flask
@@ -42,18 +46,49 @@ art_ids = []
 for features in combinations(corescs, 3):
    
 
-   print "Testing with features %s" % str(features)
-   paper_table = build_table(papers, features)
+    print "Testing with features %s" % str(features)
+    paper_table = build_table(papers, features)
 
-   k,score = get_best_k(paper_table)
+    k,score = get_best_k(paper_table)
 
-   if score > best_score:
+    km = Orange.clustering.kmeans.Clustering(paper_table, 3, maxiters=10,
+                minscorechange=0)
+
+    if score > best_score:
         print "%s are now best features with silhouette of %f for K=%d" % (
             str(features), score, k )
 
         best_features = features
         best_score = score
         best_k = k
+
+    filename = "graphs/%s_%s_%s.png" % features
+
+    fig = plt.figure()
+    ax = fig.add_subplot(111, projection='3d')
+
+    colours = ['r','g','b']
+    j = 0
+
+    clusters = km.clusters
+
+    for i in range(0, len(paper_table)):
+
+        ax.scatter(paper_table[i][0],paper_table[i][1],paper_table[i][2],
+        c=colours[clusters[i]])
+
+        j += 1
+
+    ax.set_xlabel(features[0])
+    ax.set_ylabel(features[1])
+    ax.set_zlabel(features[2])
+    fig.savefig(filename)
+    plt.close()
+
+
+
+
+
 
 print "-----------------------------------------------------------"
 

### 2013-03-15 partridge/mltest/paper_tree.py

@@ -1,9 +1,15 @@
+from __future__ import division
+
 import Orange,orngTree
 import os
+import sys
+
 
 from partridge.config import config
 from flask import Flask
 from flask.ext.sqlalchemy import SQLAlchemy
+
+from matplotlib import pyplot as plt
 
 from partridge.models import db
 from partridge.models.doc import Paper, PaperFile, Sentence, C_ABRV
@@ -25,6 +31,45 @@ def find_paper_ids( dir ):
                     ids.append(pfile.paper_id)
 
     return ids
+
+
+def printConfusion(confusion,classes):
+    cs = sorted(classes)
+    print 'conf\t\t' + '\t\t'.join(cs)
+    for c in cs:
+        sys.stdout.write(c)
+        for p in cs:
+            sys.stdout.write('\t\t' + str(confusion[c][p]))
+        print
+    print
+
+def printMeasures( confusion ):
+    
+    print "Class\t\tRecall\t\tPrecision\t\tF-measure"
+    print "-----------------------------------------------"
+
+    for c in confusion:
+        recall  = confusion[c][c] / sum(confusion[c].values())
+        prec = confusion[c][c] / sum( [ klass[c] for klass in confusion.values()] )
+        fm     = (2 * prec * recall) / (prec + recall)
+
+        print "%s\t\t%f\t\t%f\t\t%f" % ( c, recall, prec, fm)
+    
+def printResults(tabledata, tree, classes):
+    confusion = {}
+    # Set up empty confusion matrix 
+    for c1 in classes:
+        confusion[c1] = {}
+        for c2 in classes:
+            confusion[c1][c2] = 0
+    # Fill it with results
+    for d in tabledata:
+        correctclass = d.getclass()
+        predclass    = tree(d)
+        confusion[str(correctclass)][str(predclass)] += 1
+
+    printConfusion( confusion, classes )
+    printMeasures( confusion )
 
 
 app = Flask(__name__)
@@ -116,16 +161,38 @@ rf_simple = Orange.ensemble.forest.RandomForestLearner(learner=stp, trees=50, na
 learners = [ rf_def, rf_simple ]
 
 
+results = Orange.evaluation.testing.proportion_test([rf_def,rf_simple], paper_table, times=1)
+points = Orange.evaluation.scoring.compute_ROC(results)[0]
+
+xs = [ p[0] for p in points ]
+ys = [ p[1] for p in points ]
+
[…]

### 2013-03-15 doc/final_report/testing.tex
Added some blurb about unit testing to final report

@@
 boilerplate test suites as in \emph{JUnit}.
+
+In cases where Partridge calls remote services, reuses code that has already
+been tested, or calls code that runs heavy computation, it can be inconvenient
+or unhelpful to run unit tests that trigger these behaviours. To save time,
+\emph{Mock}\cite{mock2013} was used for verifying these behaviours were being
+called correctly instead.  \emph{Mock} allows the arbitrary replacement of Python
+routines and objects with `mock' objects that mimic the behaviour of the
+original routine and store information on how they were called or used. This
+meant that calls to long-running routines and functions that already have tests
+can be validated and a fake return value sent back to the caller, without
+having to actually execute the code. This technique was used heavily in the
+paper processor which calls SAPIENTA and PDFX and also wraps several data
+classes which have their own unit tests.
 

### 2013-03-18 doc/final_report/design.tex
Finished first draft of testing chapter and rearranged contents

@@
 
-\subsection{ Process Model }
+\section{ System Architecture}
 
-\subsection{ System Design }
+It was decided from the outset that Partridge would be a web-based tool.
+Web-based systems can generally be run on any computer with access to the
+internet and a modern web browser. This also means that there is no need for
+the end user to install or configure extra software on their computers, making
+Partridge accessible to non-technical users and those who have aggressive
+software restrictions on their computers, such as GPs and users of public
+computers in libraries or on academic sites.
 
-\subsection{}
+\section{ Subsystem Design }
+
+\subsection{ Preprocessor }
+
+\subsection{ Web Backend }
+
+\subsection{ Web Frontend }

### 2013-03-18 doc/final_report/implementation.tex
Finished first draft of testing chapter and rearranged contents

@@
 
-\subsection{Technical Challenges}
+\section{Paper Preprocessor}
 
-\subsubsection{ Sourcing Scientific Papers}
+\subsection{ Sourcing and Acquiring Scientific Papers}
 For Partridge to be a success, it is important to include a large variety of
@@
 
-\subsubsection{Acquiring Scientific Papers}
-Once PLOSOne was identified as a suitable source of papers, a method for
-acquiring large batches of papers to be processed was formulated.
-
-\subsubsection{PDF Conversion}
+\subsection{Format Conversion}
 Most scientific papers available on the internet are formatted as PDF
@@
 
-\subsubsection{Pre-processing with SAPIENTA}
+\subsection{Pre-processing with SAPIENTA}
 
@@
 accurate.
+
+\subsection{Paper Type Classification}
+
+\subsection{ Paper Processing Notifications }
+
+\section{ Web Backend }
+
+\subsection{ Server Views }
+
+\subsection{Database Interaction \& SQLAlchemy}
+
+\subsection{Data version control \& Alembic}
+
+\subsection{WSGI and Apache Integration}
+
+\section{Web Frontend}
+
+\subsection{Query Interface}
+
+\subsection{ Paper Upload Interface }
+
+\subsection{ Bookmarklet }

### 2013-03-18 doc/final_report/introduction.tex
Finished first draft of testing chapter and rearranged contents

@@
 creation and implementation are discussed in this document.
-
-\section{Objectives}
-
-Partridge's main objective is to provide reading recommendations and
-information retrieval for scientists and researchers. This should reduce the
-amount of extraneous information that users have to read for themselves by
-helping them find information specific to their interests more quickly.
-Partridge will achieve this through the use of several existing techniques in
-Natural Language Processing which are discussed below.
-
-Partridge is designed to help and facilitate researchers and authors of
-scientific papers in the following principal ways:
-
-\begin{itemize}
-\item The system should provide search within specific CoreSC regions of a given
-paper. This would allow users to find the most relevant papers to them. For
-example a user may search for "mass spectrometer" within the methodology
-section of a paper.
-\item Partridge should allow authors and rightsholders of scientific papers to
-upload their papers to the system for inclusion into the search system. This
-would give Partridge itself more utility and would make involved authors more
-accessible.
-\item The system should provide filtering of papers based upon their
-specific domain (i.e. is the paper primarily concerned with methodology within
-an experiment in chemistry or is it about ethics in psychological studies?) and
-their result, whether the paper yielded positive, negative or inconclusive
-evidence for a hypothesis. 
-\item Depending upon the time constraints of the
-project, it was hoped that Partridge will also offer a user 'profiling' system
-that provides recommendations for researchers based on their reading history.
-This feature should help users find relevant papers more quickly or find
-research that they may have otherwise overlooked.a
-\end{itemize}
-
-As well as helping users locate files, Partridge will also
 
@@
 (XML)\cite{LIAKATA10.644}.
+
+\section{Objectives}
+
+Partridge's main objective is to provide reading recommendations and
+information retrieval for scientists and researchers. This should reduce the
+amount of extraneous information that users have to read for themselves by
+helping them find information specific to their interests more quickly.
+Partridge will achieve this through the use of several existing techniques in
+Natural Language Processing and utilisation of SAPIENTA as discussed above.
+
+Partridge is designed to help and facilitate researchers and authors of
+scientific papers in the following principal ways:
+
+\begin{itemize}
+\item The system should provide search within specific CoreSC regions of a given
+paper. This would allow users to find the most relevant papers to them. For
+example a user may search for "mass spectrometer" within the methodology
+section of a paper.
+\item Partridge should allow authors and rightsholders of scientific papers to
+upload their papers to the system for inclusion into the search system. This
+would give Partridge itself more utility and would make involved authors more
+accessible.
+\item The system should provide filtering of papers based upon their
+specific domain (i.e. is the paper primarily concerned with methodology within
+an experiment in chemistry or is it about ethics in psychological studies?) and
+their result, whether the paper yielded positive, negative or inconclusive
+evidence for a hypothesis. 
+\item Depending upon the time constraints of the
+project, it was hoped that Partridge will also offer a user 'profiling' system
+that provides recommendations for researchers based on their reading history.
+This feature should help users find relevant papers more quickly or find
+research that they may have otherwise overlooked.a
+\end{itemize}

### 2013-03-18 doc/final_report/methodology.tex
Finished first draft of testing chapter and rearranged contents

@@
-\subsection{Development Methodology}
-
-\subsubsection{Existing Methodologies}
+\section{Existing Methodologies}
 Selecting a suitable development methodology for building Partridge is another
@@
 
-\subsubsection{ Partridge's Development Methodology}
+\section{ Partridge's Development Methodology}
 
@@
 
-\subsubsection{ Work Timeline }
+\subsection{ Work Timeline }
 

### 2013-03-18 doc/final_report/testing.tex
Finished first draft of testing chapter and rearranged contents

@@
 
-\subsection{ Backend \& Infrastructure Testing}
+\subsection{ Back-end \& Infrastructure Testing}
 
@@
 \emph{Mock}\cite{mock2013} was used for verifying these behaviours were being
-called correctly instead.  \emph{Mock} allows the arbitrary replacement of Python
-routines and objects with `mock' objects that mimic the behaviour of the
+called correctly instead.  \emph{Mock} allows the arbitrary replacement of
+Python routines and objects with `mock' objects that mimic the behaviour of the
 original routine and store information on how they were called or used. This
@@
 can be validated and a fake return value sent back to the caller, without
-having to actually execute the code. This technique was used heavily in the
-paper processor which calls SAPIENTA and PDFX and also wraps several data
-classes which have their own unit tests.
+having to actually execute the code. This technique also allows the isolation
+of problems within the caller code and its commmunication with the target
+functions and will pass even if the target code is broken provided that the
+caller code is correct\cite{saff2004mock}. The Mock testing technique was used
+heavily in the paper processor which calls SAPIENTA and PDFX and also wraps
+several data classes which have their own unit tests.
 
-\subsection{ Selenium \& Frontend Testing }
+Partridge's web views were tested using \emph{Flask}'s in-built test client.
+This is an object attached to the \emph{Flask} app that can be used to emulate
+a call to a particular view\cite{flask2012}. Cookies and form information can also be
+manipulated through this client, enabling comprehensive testing of each of the backends
+for Partridge's query, paper upload and bookmarklet capabilities.
+
+\subsection{ Selenium \& Front-end Testing }
 
@@
 had to be tested to verify that the query and upload forms behaved as expected.
+Selenium\cite{seleniumide} was selected to facilitate these tests.
+
+Selenium is a browser-based unit testing framework that allows developers to
+script actions that a user might undertake whilst browsing a website. Tests for
+selenium can be written in Firefox using the Selenium IDE framework. These
+tests can then be exported as HTML files with embedded javascript instructions
+and executed in any other browser to test compatibility with the product under
+test.
+
+During the development of Partridge, several suites of tests were written using
+Selenium to verify that the query form, paper upload form and bookmarklet code
+behave as expected. Not only do these tests verify the behaviour of the HTML
+and javascript interface, but they also helped to check the higher level
+functionality of Partridge. For example, the test suite for the Partridge query
+form also helps to verify that query backend is working correctly. The Selenium
+tests were executed as part of the integration process when a new feature was
+added to Partridge.
 
@@
 
-Once a basic user interface had been implemented, the system was opened for
-user testing. The main Patridge instance
-(\url{http://farnsworth.papro.org.uk/}) was advertised using several social
-media streams and users encouraged to submit bug reports if they experienced
-any problems whilst using the site.
+Raymond(1999) suggests that as the developer of an open source project,
+``Treating your users as co-developers is your least-hassle route to rapid code
+improvement and effective debugging\cite{raymond1999cathedral}." Partridge
+hasn't been developed using an open methodology since, as a dissertation
+project, it has been necessary to avoid complications around work ownership.
+However, Raymond's notion that software should be released early and often and
+tested on its user-base is an effective one and has been widely adopted by both
+open and closed source developers\cite{linux2013}\cite{unity2013}.
+
+As soon as Iteration 1 was complete, Partridge was made open for user testing
+and the primary Patridge instance (\url{http://farnsworth.papro.org.uk/}) was
+advertised using several social media streams. It was made clear to any early
+adopting users that the system was still in development and they were
+encouraged to submit bug reports if they experienced any problems whilst using
+the site. This was a great success and a number of bugs and suggested
+improvements were raised both via the GitHub repository\cite{softlybug2013} and
+in conversation, helping to improve Partridge and find some defects that had
+previously been overlooked.
 
@@
 
-\subsection{ Result Presentation }
+\subsection{ Evaluation Result Analysis }
 
@@
 
-\subsubsection{ Classifier Accuracy }
+\subsection{ Classifier Accuracy }
 
@@
 
-\subsubsection{ Receiver Operating Characteristics Chart}
+\subsection{ Receiver Operating Characteristics Chart}
 
@@
 
-\subsubsection{ Area Under Curve }
+\subsection{ Area Under Curve }
 
@@
 
-\subsubsection{ Confusion Matrices}
+\subsection{ Confusion Matrices}
 
@@
 
-\subsubsection{ Precision, Recall and F-Measure }
+\subsection{ Precision, Recall and F-Measure }
 

### 2013-03-19 doc/final_report/design.tex
Started some comprehensive design documentation

@@
 
-\section{ System Architecture}
+\section{ Target Platform \& High Level Considerations }
+
+\subsection{Use Case Analysis}
+
+Given the project objectives identified above, four primary use cases were
+identified for Partridge as shown in Figure \ref{fig:use_cases}. Users can be
+identified as researchers and people interested in finding and reading
+scientific papers that interested them. This would involve querying the
+database for relevant papers, viewing metrics on the papers that have been used
+to classify them and also downloading the original paper for reading. A subset
+of users were identified as authors who might be interested in adding their own
+papers to the Partridge instance.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.4\textwidth]{images/design/use_cases.png}
+\caption{Use Case Diagram for Partridge Project}
+\label{fig:use_cases}
+\end{figure}
+
+\subsection{ Target Platform}
 
@@
 
-\section{ Subsystem Design }
+In order to function as a website, Partridge needed to be developed as a server
+application that produced Hyper Text Markup Language (HTML) output that a web
+browser could interpret and display. The browser rendering the forms must then
+communicate with a backend system capable of querying and returning papers to
+the user based on their input. This lead to the decision to split development
+of Partridge into two core components: the Web Frontend comprising of user
+interface elements and presentation logic and the Web Backend comprising of
+intelligent systems to classify, filter and query papers using some of the NLP
+techniques discussed previously.
+
+One of the main requirements for a web server is that it responds to requests
+relatively quickly, ideally within 10 seconds or less. If they don't, the user
+may get impatient and give up trying to use the system, or in some cases, their
+web browser may timeout and stop trying to load the page. Many of the processes
+involved in extracting meaningful CoreSC information from papers are very slow
+slow. This means that processing papers during web requests is not really
+feasible, since it may take several minutes for a single paper to be annotated
+and classified. Therefore, a third core component was identified: a paper
+preprocessor service that runs on the server and converts, annotates and
+classifies papers as soon as they are uploaded.
+
+\subsection{ Programming and Development Environment }
+
+Rather than building a web server from the ground up, most modern web
+applications are written in higher level languages that run on top of standard,
+open source web servers such as Apache or nginx. Common language choices
+include PHP, Python, Perl and Java, all of these languages supported by large
+communities of developers and users who provide with excellent documentation
+and support if required.  For the implementation of Partridge, Python was
+selected as the programming language of choice. This was partially due to the
+author's familiarity with the language and also due to the availability of
+stable data mining\cite{curk05} and natural language
+processing\cite{bird2009natural} libraries for the Python programming
+environment. Python is an interpreted cross-platform language, minimising
+deployment problems and supports natively compiled C and C++ extension
+libraries allowing intensive processing  and number crunching to be offloaded
+to native plugins, increasing application processing speed.
+
+To further increase development speed, a Python framework for developing web
+applications called \emph{Flask\cite{flask2012}} would be used to build the web
+backend.
+
+The development of the application would be carried out on a Linux desktop
+computer. However, the portable nature of Python, Apache and the required
+libraries meant that Partridge could theoretically be deployed to Windows and
+Mac computer systems if required.
+
+The Web Frontend for the system would need to be written using a combination of
+HTML markup and JavaScript. HTML is not a programming language in itself and
+doesn't contain any logic. It is merely a code representation of the interface
+to be rendered in the browser window which is interpreted once it has been
+downloaded from the web server. In order to carry out actions on the HTML such
+as validating user input and manipulating parts of the display, JavaScript is
+also downloaded from the web server and interpreted by the browser. Although
+this requires the developer to have knowledge of two extra technologies on top
+of Python, it also makes enforcing the design principle of keeping presentation
+and logic separate a lot easier.
+
+Due to the large number of popular web browsers on the market, implementing
+JavaScript in a slightly different way, Javascript can be very difficult to
+write in a cross-browser compatible way.  To maximise compatibility and reduce
+development time, it was decided that libraries such as jQuery which are
+designed to carry out HTML manipulation behaviours in a uniform way cross all
+compatible browsers.  As of February 2013, it is estimated that Chrome and
+Firefox are currently the most popular web browsers, holding 50\% and 29.6\% of
+the market share respectively\cite{browserstats2013}. Internet Explorer is the
+third most popular browser. However, there are several well known compatibility
+issues with Internet Explorer, Microsoft themselves condemning version 6.0 of
+their browser\cite{ie6death}. For this reason, it was decided that Partridge
+would only support Firefox and Chrome. A working interface in modern editions
+of the Internet Explorer family of browsers would be a bonus.  However, no time
+was allocated to ensuring compatibility of Partridge with Internet Explorer.
+
+\section{ System Architecture }
+
+\begin{figure}[!ht]
+\center
+\includegraphics[width=0.9\textwidth]{images/design/components_high_level.png}
+\caption{High Level Component Layout for Partridge}
+\label{fig:high_level_components}
+\end{figure}
+
+Figure \ref{fig:high_level_components} shows a very high level description of
+the system's three main components, the database server and the ways that they
+communicate. Communication between the Web Interface and the other two
+components is carried out via HTTP requests to the underlying Apache server.
+Communication between the web backend and the paper preprocessor is implicit
+via the data storage system. Direct communication between these components is
+redundant since the web backend cannot gain any extra information from the
+paper preprocessor while a paper is still being analysed and all finished
+papers are added to the database which the web backend has full access to
+anyway.
+
+\subsection{ Data Storage }
 

### 2013-03-19 doc/final_report/design.tex
Added new preprocessor sections

@@
 
+The preprocessor module is used to annotate and analyse new papers once they 
+have been uploaded by the user via the web interface. The preprocessor is designed 
+as a daemon which uses pyinotify to hook into the operating system and monitor a directory 
+for new papers that have been uploaded. As new papers are detected within the upload directory, 
+they are placed into a process queue and the preprocessor analyses them on a first in first out basis.
+
+When a paper is taken from the queue, a series of processes are run upon it to prepare 
+it for storage in the database.
+
+\subsubsection{Conversion}
+
+\subsubsection{Sentence Splitting}
+
+\subsubsection{SAPIENTA Annotation}
+
+\subsubsection{Type Analysis}
+
 \subsection{ Web Backend }

### 2013-03-26 doc/final_report/design.tex
Made some crucial changes to the testing chapter and worked in intro and summary

@@
 
-\subsection{ Data Storage }
-
 \subsection{ Preprocessor }
@@
 The preprocessor module is used to annotate and analyse new papers once they
-have been uploaded by the user via the web interface. The preprocessor is designed 
-as a daemon which uses pyinotify to hook into the operating system and monitor a directory 
-for new papers that have been uploaded. As new papers are detected within the upload directory, 
-they are placed into a process queue and the preprocessor analyses them on a first in first out basis.
+have been uploaded by the user via the web interface. The preprocessor is
+designed as a daemon which hooks into the operating system in order to monitor
+a directory for new papers that have been uploaded. As new papers are detected
+within the upload directory, they are placed into a process queue and the
+preprocessor analyses them on a first in first out basis. When a paper is taken
+from the queue, a series of processes are run upon it to prepare it for storage
+in the database. These processes are illustrated in Figure
+\ref{fig:flow_preprocessor}.
 
-When a paper is taken from the queue, a series of processes are run upon it to prepare 
-it for storage in the database.
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.6\textwidth]{images/design/flow_preprocessor.png}
+\caption{A flowchart illustrating the preprocessor processes}
+\label{fig:flow_preprocessor}
+\end{figure}
 
-\subsubsection{Conversion}
+\subsubsection{PDF Conversion}
+
+The first process in the processing pipeline is conversion of the papers to a
+format that can be analysed by SAPIENTA. Currently, SAPIENTA supports the
+SciXML\cite{rupp2006flexible} and PubMed Central\cite{pubmedDTD} DTDs. However,
+papers stored in PDF format must still be converted in order to be processed.
+PDF Files will passed through a routine which extracts text from the paper and
+adds the relevant XML tags to make the document SAPIENTA compatible. This
+document is then passed forward to the splitter. Papers that are already in a
+compatible format are passed forward without any action being taken.
 
@@
 
+SAPIENTA allocates each sentence within a paper a separate CoreSC label.
+However, the sentence boundaries must be detected before the document is passed
+into SAPIENTA for annotation. The sentence splitter uses a regular expression
+to split the sentences within the document and then adds the necessary
+\verb|<s>| tags to the markup to indicate the location of each sentence.
+
 \subsubsection{SAPIENTA Annotation}
 
-\subsubsection{Type Analysis}
+Once the paper has been split, SAPIENTA is used to annotate each sentence with
+a relevant CoreSC allocation. These labels are calculated based upon the
+sentence's location within the paper as well pairs and triplets of words found
+consecutively within the sentence. After this stage, the paper is passed
+forwards to be further classified by Partridge.
+
+\subsubsection{Feature Extraction and Classifiers}
+
+The final stage in the preprocessor pipeline is paper classification. During
+this stage, features are extracted from the papers and used to classify the
+paper in three different ways. The paper's type: case study or review paper
+etc. is determined using the presence or absence of different CoreSC labels
+within the paper and their relative proportions. The type of paper is
+determined by the presence of domain specific nouns and adjectives within the
+paper. For example, a biology paper might contain words such as enzyme or amino
+acid. The result of the paper, i.e. whether the paper was conclusive and if the
+results were positive or negative, are detected through the presence or absense
+of words with a strong sentiment polarity as discussed by Wilson et al
+(2005)\cite{Wilson05Polarity}. The results from the whole process are then
+passed into the data store and saved.
+
+\subsubsection{File Retention and Error Handling}
+
+Each of the independent processes described above generate new files which are
+temporarily stored on the server until all of the sub-processes are complete.
+Once a paper analysis cycle has finished, the preprocessor triggers a cleanup
+operation that removes intermediate files from the system, storing only the
+initially uploaded file (which may be a PDF) and the final annotated file in a
+permanent location on the filesystem.  The whole analysis process for a single
+paper is also wrapped within an error handling block that automatically run the
+cleanup routine if something goes wrong. This prevents the system filling up
+with invalid files. This mechanism is shown in Figure
+\ref{fig:preprocessor_overview}.
+
+\begin{figure}[!h]
+\vspace{5mm}
+\centering
+\includegraphics[width=0.6\textwidth]{images/design/paper_processor_overview.png}
+\caption{Preprocessor System Overview}
+\label{fig:preprocessor_overview}
+\end{figure}
+
+\subsection{ Data Storage }
+It is expected that a given Partridge instance may grow in size to contain
+thousands of individual papers that have been annotated and are available to
+the web backend for inclusion into a user's search results. Reading in and
+parsing each individual XML file stored in the system is not really feasible
+when handling a HTTP request from the web frontend, this sort of process would
+take a long time to execute. To provide fast search and retrieval of paper
+data, a Relational Database Management server (RDBMS) was chosen for storage of
+papers that have been preprocessed using the system described above. An
+overview of the database schema is illustrated in Figure \ref{fig:e-r-diagram}.
+
+\begin{figure}[th]
+\vspace{5mm}
+\centering
+\includegraphics[width=0.8\textwidth]{images/design/e-r-diagram.png}
+\caption{Entity Relationship Diagram for Partridge's RDBMS}
+\label{fig:e-r-diagram}
+\end{figure}
+
+Partridge's database is required to keep track of all of the papers that have
+been added to the system. The Paper entity represents a single paper stored in
+Partridge. Information extracted by the classifiers such as the paper's type,
+topic and result are stored as part of the main paper entity. The title and
+topic are also stored for easy retrieval. One of the key requirements of
+Partridge is querying within a CoreSC field of a paper. Therefore, all
+sentences are stored as entities along with their CoreSC annotation. The sentence
+text is an index field to facilitate fast recall from the database.
+
+It is probable that any given author may have contributed to multiple papers
+stored within the system.  Therefore authors are treated as entities within the
+RDBMS and the many to many relationship between papers and authors is
+facilitated using the intermediary table PaperAuthors. A PaperAuthor record
+contains a boolean field used to indicate whether an author linked to a
+specific paper was the primary author on that paper.
+
+As discussed above, two or more files per paper are always stored within
+partridge so that a user can retrieve them for reading. Therefore files are
+kept in their own table along with a record of their type (eg. XML or PDF).
 
@@
 
+Partridge's web backend component is used to initially serve the HTML and
+JavaScript used to represent the User interface and to communicate with the
+JavaScript frontend running inside the browser via HTTP requests. It is used to
+interpret HTTP request fields into SQL queries and mediate queries made to the
+RDBMS on behalf of the user. An example use of the backend system can be seen
+in Figure \ref{fig:backend_sequence}.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.75\textwidth]{images/design/backend_sequence.png}
+\caption{Sequence Diagram for a Query in Partridge}
+\label{fig:backend_sequence}
+\end{figure}
+
+The Flask web framework uses a model view controller-like architecture. Each
+behaviour of the server: handling paper uploads, displaying paper query
+results, allowing users to download papers, can be considered a `view'. Views
+register themselves with Flask under a specific URL. When flask receives a
+request to any such URL, it automatically routes the request through to the
+View object\cite{flask2012}.
+
+\subsubsection{Query View Backend}
+The query view is has two key responsibilities. The first is to display the
+query form to the user. This is a simple matter of sending an HTML file stored
+on the server to the browser that made the request.
+
+The key responsibility of the query view is to translate incoming HTTP requests
+into search queries, retrieve a set of papers from the RDBMS  and return human
+readable results to the user. One of the most important steps in this process
+is to cleanse the incoming data and prevent SQL injection attacks that
+unscrupulous users may attempt to use to damage or purge the Partridge
+database. The system must also be capable of interpreting data retrieved from
+the database into HTML to be returned to the user's browser. The server
+mechanism utilises Flask's built in templating mechanism in order to quickly
+transform Python-specific data structures into valid HTML markup and return it
+to the user\cite{flask2012}.
+
+\subsubsection{Paper Upload View Backend}
+
+The paper upload view backend is responsible for handling file uploads from the
+HTML form and ensuring that files are placed in the right place so that the
+preprocessor can find them. The main challenge for this submodule is storing
+the file using a unique name so that different users uploading files don't
+overwrite each other's data. This is handled through the use of the Python UUID
+module which generates universally unique 128-bit identifiers as detailed in RFC
+4122\cite{rfc4122}. The low rate of collisions between UUID values should
+insure that the chances of two paper filenames colliding is very low.
+
+The view also carries out validation on the filename to ensure that it is an
+XML or PDF file. No further validation is carried out by this system since the
+paper processor carries out file contents inspection and removes invalid file
+types automatically.
+
 \subsection{ Web Frontend }
+
+The web frontend consists of sets of HTML and JavaScript interfaces that are
+equipped to communicate with their relevant backend system using
+
+\subsubsection{ Query Form }
+
+\subsubsection{ Results Page }
+
+\subsubsection{ Paper Profile Page }
+
+\subsubsection{Paper Upload Form}
+Paper uploading is a

### 2013-03-26 doc/final_report/testing.tex
Made some crucial changes to the testing chapter and worked in intro and summary

@@
 %------------------------------------------------------
+
+%introduction to testing
+Throughout the implementation of the project, testing has remained a very
+important aspect of Partridge's development. A number of testing techniques
+have been used in order to evaluate the individual behaviours of Partridge's
+key components both separately and the system as a whole. This chapter
+discusses the techniques used to test Partridge, the results from these tests
+and any implications that these results have had upon development of the
+project. Combining all of these testing and evaluation techniques provides an
+in depth view of how useful Partridge is and how it can be improved upon.
 
@@
 
-\section{ User Testing }
-
-Raymond(1999) suggests that as the developer of an open source project,
-``Treating your users as co-developers is your least-hassle route to rapid code
-improvement and effective debugging\cite{raymond1999cathedral}." Partridge
-hasn't been developed using an open methodology since, as a dissertation
-project, it has been necessary to avoid complications around work ownership.
-However, Raymond's notion that software should be released early and often and
-tested on its user-base is an effective one and has been widely adopted by both
-open and closed source developers\cite{linux2013}\cite{unity2013}.
-
-As soon as Iteration 1 was complete, Partridge was made open for user testing
-and the primary Patridge instance (\url{http://farnsworth.papro.org.uk/}) was
-advertised using several social media streams. It was made clear to any early
-adopting users that the system was still in development and they were
-encouraged to submit bug reports if they experienced any problems whilst using
-the site. This was a great success and a number of bugs and suggested
-improvements were raised both via the GitHub repository\cite{softlybug2013} and
-in conversation, helping to improve Partridge and find some defects that had
-previously been overlooked.
-
 \section{ Evaluating Learning Algorithms }
@@
 Three fold validation is a commonly used method for using all of the available
-data for both testing and training whilst still maintaining . As the name
-suggests, test data is split into three disjoint sets and then the classifier
-is trained on two of the sets and tested with the third. This is repeated three
-times so that all sets are used for both training and testing. Results from
-each of the folds can be represented separately or an average taken.
+data for both testing and training whilst still maintaining the separation
+between training and testing data. As the name suggests, test data is split
+into three disjoint sets and then the classifier is trained on two of the sets
+and tested with the third. This is repeated three times so that all sets are
+used for both training and testing. Results from each of the folds can be
+represented separately or an average taken.
 
@@
 
-3 Fold Validation on the Partridge corpus
+3 Fold Validation on the Partridge corpus using the Random Forest Classifier
+for paper type gives a CA measure of 87.9\%. While this provides a positive,
+general overview of the classifier performance. It does not provide detail on
+what data was incorrectly classifier nor any insight on how the system could be
+improved. The following sections discuss techniques that provide more useful
+measures of performance for machine learning classifiers.
 
@@
 ratio which is a sign that the classifier is working well.  Figure
-\ref{fig:roc_random_forest} shows the ROC Chart for Partridge's Topic
+\ref{fig:roc_random_forest} shows the ROC Chart for Partridge's Paper Type
 Classifier after training on 60\% of the Partridge corpus and testing on 40\%.
@@
 \centering
-\begin{tabular}{| l || l | l | l |}
+\begin{tabular}{ | r l l l l |}
 \hline
-	&	Case Study&	Research&	Review\\
-\hline
-\hline
-Case Study&	83&		2&		12\\
-\hline
-Research&	3&		255&		0\\
-\hline
-Review&		4&		2&		159\\
+\multirow{5}{*}{\begin{sideways}{Actual Class}\end{sideways}}
+&&\multicolumn{3}{c|}{Predicted Class} \\
+&& \multicolumn{1}{c}{Case Study} &	Research&	\multicolumn{1}{c|}{Review}\\
+\cline{3-5}
+& \multicolumn{1}{c|}{Case Study} &	83&		2&		12\\
+&\multicolumn{1}{c|}{Research}&	3&		255&		0\\
+&\multicolumn{1}{c|}{Review}&	4&		2&		159\\
 \hline
@@
 \centering
-\begin{tabular}{| l || l | l | l |}
+\begin{tabular}{ | r l l l l |}
 \hline
-&	        Case Study&     Research&	Review\\
-\hline
-\hline
-Case Study&     85    &         2&		10\\
-\hline
-Research&	0   &		256&		2\\
-\hline
-Review&		5&		1&		159\\
+\multirow{5}{*}{\begin{sideways}{Actual Class}\end{sideways}}
+&&\multicolumn{3}{c|}{Predicted Class} \\
+&& \multicolumn{1}{c}{Case Study} &	Research&	\multicolumn{1}{c|}{Review}\\
+\cline{3-5}
+&\multicolumn{1}{c|}{Case Study}&   85    &         2&		10\\
+&\multicolumn{1}{c|}{Research}&	0   &		256&		2\\
+&\multicolumn{1}{c|}{Review}&	5&		1&		159\\
 \hline
@@
 \centering
-\begin{tabular}{| l || l | l | l |}
+\begin{tabular}{ | r l l l l |}
 \hline
-&		Case Study&	Research&	Review\\
-\hline
-\hline
-Case Study&	82&		3	&	12 \\
-Research&	0&		257	&	1\\
-Review&		7&		2	&	156\\
+\multirow{5}{*}{\begin{sideways}{Actual Class}\end{sideways}}
+&&\multicolumn{3}{c|}{Predicted Class} \\
+&& \multicolumn{1}{c}{Case Study} &	Research&	\multicolumn{1}{c|}{Review}\\
+\cline{3-5}
+&\multicolumn{1}{c|}{Case Study}&	82&		3	&	12 \\
+&\multicolumn{1}{c|}{Research}&	0&		257	&	1\\
+&\multicolumn{1}{c|}{Review}&		7&		2	&	156\\
 \hline
@@
 the hardest document type to classify as discussed above.
+
+\section{ User Testing }
+
+Raymond(1999) suggests that for developers of open source projects, ``Treating
+your users as co-developers is your least-hassle route to rapid code
+improvement and effective debugging\cite{raymond1999cathedral}." Partridge
+hasn't been developed using an open methodology since, as a dissertation
+project, it has been necessary to avoid complications around work ownership.
+However, Raymond's notion that software should be released early and often and
+tested on its user-base is an effective one and has been widely adopted by both
+open and closed source developers\cite{linux2013}\cite{unity2013}.
+
+A publicly available instance of Partridge that can be accessed at
+(\url{http://farnsworth.papro.org.uk/}) was made available as soon as iteration
+1 was complete and advertised using several social media streams. This was an
+effort to attract as many users to Partridge as possible in the early stages of
+the project in order to provide user testing. It was made clear to any early
+adopting users that the system was still in development and they were
+encouraged to submit bug reports if they experienced any problems whilst using
+the site. This was a great success and a number of bugs and suggested
+improvements were raised both via the GitHub repository and in conversation,
+helping to improve Partridge and find some defects that had previously been
+overlooked. For example, one user noticed that the full text search within
+Partridge was not behaving as expected and returning all papers regardless of
+their contents.  The relevant code was repaired and the bug marked as resolved
+on GitHub\cite{softlybug2013}.
+
+\subsection{Intrinsic Feedback}
+
+Intelligent information retrieval using machine learning techniques is a
+complicated and multifaceted process. Partridge attempts to encode this complex set of
+procedures into a usable and understandable interface designed for the use of
+non-programmers. It was therefore important to understand how usable the
+interface is for non-technical users.
+
+Most users who commented on the system found that the query form made a lot of
+sense and helped them to identify relevant papers very quickly.
+
+There were a few comments on how the uploader system could be improved. Users
+were confused by the preprocessor and wondered why their paper didn't appear in
+the corpus as soon as they submitted it. The most popular solution to this was
+to add an email field to the uploader so that people who submit papers to the
+corpus are notified when their paper is incorporated. This also provided
+feedback for users whose papers could not be added to the corpus due to errors
+or rights ownership issues.
+
+Another suggestion was to add a twitter bot to announce when new papers have
+been added to the system. This would provide another way of issuing user
+feedback when a paper is submitted and would also help to draw users to
+Partridge - especially when high profile papers are successfully added to the
+system.
+
+\subsection{Extrinsic Feedback}
+
+As well as finding out how Partridge performs as a system, it was interesting
+to find out how Partridge blended in to the information retrieval ecosystem around
+it and how effectively it could be used day to day or in combination with any other
+online tools.
+
+One of the most important suggestions made was the addition of the Bookmarklet
+tool. This had the effect of making paper submission to Partridge a lot more
+convenient and intuitive. It also helped reduce confusion over paper
+rights since the bookmarklet only works on sites which license
+their papers under permissive licenses and allow data mining.
+
+\section{Summary}
+
+The extensive range of testing methodologies used throughout the project meant
+that Partridge has been developed into a mature, stable and highly usable
+product. Unit testing has ensured that all procedural and scripted
+functionality within Partridge is predictable and reliable. Machine Learning
+Evaluation has ensured that an accurate and precise paper type classification
+mechanism has been developed and User Testing has ensured that non-technical
+users are able to use Partridge effectively.
+
+Testing has been highly effective throughout the project and any potential
+issues with the system were identified very early on and resolved due to the
+`open-source-esque' development lifecycle used during the project.  Testing has
+also provided a great deal of understanding about just how useful Partridge is
+as well as highlighting its limitations. It also raises questions as to the
+future development of the project and provides a number of ideas for future
+improvements.

### 2013-03-26 doc/final_report/design.tex
Finished design chapter

@@
 The web frontend consists of sets of HTML and JavaScript interfaces that are
-equipped to communicate with their relevant backend system using
+equipped to communicate with the backend systems discussed above using HTTP
+requests. The most important aspect in designing the frontend was insuring that
+the interfaces are intuitive and usable from the perspective of a non-technical
+user. It was suggested that the system should look as similar as possible to
+other online search and information retrieval systems in order to help users
+who are already familiar with other systems in learning to use Partridge more
+quickly.
 
@@
 
+\begin{figure}[!htb]
+\vspace{5mm}
+\centering
+\includegraphics[width=\textwidth]{images/design/query_mockup.png}
+\caption{Mockup image for the Partridge Query Interface}
+\label{fig:query_mockup}
+\end{figure}
+
+Figure \ref{fig:query_mockup} shows the initial design of the Partridge query
+interface. The interface tries to make it easy for the user to both filter and
+query papers in an intuitive way.
+
+The filter interface on the left hand side of the query form allows the user to
+use Partridge's machine learning classifiers to return subsets of the papers.
+The selection box control in the top left of the form contains a list of each
+of the types of paper within the database. The user should select one of these
+types of paper to restrict their query to that type. There is also an ``All
+Types" option in case they don't wish to use this filter.
+
+The paper topic filtering system is displayed in the bottom left of the query
+form. There is a `master list' of all paper topics in the corpus on the left
+and a `query list' containing topics that the user wants to be included into
+their search results on the right. The user selects items from each list and
+can use the arrow buttons in between to move them depending on their query.
+
+The search or `Keywords' section of the form shows a set of controls for
+specifying terms that must appear within sections of a document for it to show
+up in the search results. The user enters a search term in the input box on the
+top right of the form and then selects which section of the paper the term
+should appear within. This could be any of the CoreSC zones within the paper or
+within the abstract. The user could also specify a specific author's name. Once
+they are happy with their keywords and section, they click ``Add" and the
+keyword/section pair are inserted into the table on the bottom right. If they
+wish to remove a query constraint from this table, they can select it and click
+the ``Delete" button.
+
+Once the user is happy with their search, they can click the ``Search" button
+at the extreme top right of the form to carry out the query and see the
+results.
+
 \subsubsection{ Results Page }
+
+Once a user has made their query, the results are displayed for them to peruse
+and find relevant papers to read. Figure \ref{fig:results_mockup} shows a
+mockup of the results view. This simplistic page lists all of the papers found
+during the query in relevence order. The results are paginated so that the user
+does not have to wait for a large page to render. It is hoped that users will
+run specific queries that do not return a high number of results. There is a
+prominent link at the top of the page that allows the user to go back to the
+query form and amend their query if the results are not satisfactory.
+
+\begin{figure}[!htb]
+\vspace{5mm}
+\centering
+\includegraphics[width=\textwidth]{images/design/results_mockup.png}
+\caption{Mockup image for the Partridge Search Results Interface}
+\label{fig:results_mockup}
+\end{figure}
+
+Each paper is listed by title and author and the first few sentences of the
+extract are also dislayed. The user can click on the paper title to be taken to
+the Profile Page for that paper.
 
@@
 
+The paper profile page is used to display all information about a specific
+paper in the Partridge corpus to the user. A mockup of the Paper Profile page
+can be seen in Figure \ref{fig:paper_profile}
+
+\begin{figure}[!htb]
+\vspace{5mm}
+\centering
+\includegraphics[width=\textwidth]{images/design/profile_mockup.png}
+\caption{Mockup image for the Partridge Paper Profile Page}
+\label{fig:paper_profile}
+\end{figure}
+
+The paper's title and author are displayed prominently in the top left hand
+corner of the page. The full abstract text is shown so that the user can read
+it and determine the paper's relevance to them. There is also a graph showing
+each of the CoreSC types and proportion within the paper. If the user is
+interested in the paper, they can click the Download link at the top of the
+page to access the annotated XML file stored in the system.
+
 \subsubsection{Paper Upload Form}
-Paper uploading is a
+Paper uploading is another highly important user activity within Partridge.
+Without users uploading papers, Partridge has no data to work with. It was
+therefore, very important to make paper uploading as simplistic as possible to
+the end user. Figure \ref{fig:paper_upload} shows Partridge's main paper upload
+form.
+
+\begin{figure}[!htb]
+\vspace{5mm}
+\centering
+\includegraphics[width=\textwidth]{images/design/upload_mockup.png}
+\caption{Mockup image for the Partridge Paper Upload Form}
+\label{fig:paper_upload}
+\end{figure}
+
+The papers are selected using the familiar File Upload dialog used in any
+website that requires users to upload files to the server. Multiple papers can
+be selected for batch upload if required. Once the relevant papers are
+selected, the user selects the Upload button to begin the process.
+
+Once the upload process has started, the upload file browser and submit button
+are disabled and a progress indicator as well as a text summary are displayed
+directly underneath. Once the progress bar reaches 100\%, the upload file
+browser becomes available again, or the user can navigate away from the page.
+
+\section{ Summary}
+
+All of Partridge's subsystems have carefully been designed in order to make
+programming and implementing the project efficient and easy for the programmer.
+The system architecture allows the implementation of modules independantly of
+each other with minimal coupling and communication. Cohesion within the modules
+is maximised, with related behaviours grouped together as far as possible.
+
+The user interface has been designed to maximise usability for non-technical
+users whilst effectively encoding the complicated nature of Partridge's
+internal processes in a set of HTML forms.
+
+Partridge has been developed using an iterative methodology and therefore some
+of the designs descussed in this chapter have been modified during the
+development of the project. However, these designs did provide an excellent
+starting point for the implementation of the project.

### 2013-03-26 doc/final_report/design.tex
Started writing the implementation chapter

@@
 %%----------------------------------------------
+
+Despite the use of an iterative development methodology, some of the key
+components within Partridge were designed up front in order to accelerate
+implementation and reduce time overheads when adding new components to the
+system. The components that make up Partridge and the ways in which they react
+are described and analysed below. Choices regarding the type of application,
+the target audience and the programming environment are also discussed.
 

### 2013-03-26 doc/final_report/implementation.tex
Started writing the implementation chapter

@@
 
+Implementing Partridge from a set of initial designs proved to be a
+challenging but rewarding process. There were a great number of technical
+challenges involved in building the system, a large proportion of the
+implementation time was spent working on the paper preprocessor module.
+However, some aspects of the web interface and backend were also quite
+difficult to tackle.
+
 \section{Paper Preprocessor}
@@
 \subsection{ Sourcing and Acquiring Scientific Papers}
-For Partridge to be a success, it is important to include a large variety of
-different scientific papers in its corpus. Therefore, several sources of
-scientific papers were explored and considered.
 
-The most convenient and accessible source is the ART corpus that SAPIENTA was
-trained with\cite{citeulike:11077287}. This corpus is already stored using the
-CoreSC schema and has been pre-annotated. This means that Partridge would not
-need to do any conversion or pre-processing on the papers. These scientific
-papers are all chemistry papers. Therefore, more papers from other scientific
-domains are needed to get a wider variety of topics and make Partridge useful
-to as wide an audience as possible.
+In order to provide a useful service to researchers looking for papers, growing
+a large corpus of scientific literature was made a high priority during the
+project. This was especially important when training the Machine Learning
+models since training data sets need to be statistically significant in order
+to provide any meaninful results. Users are given the option, and actively
+encouraged, to upload papers that they own or publish on another author's
+behalf to the Partridge instance. However, to speed up this process, a number
+of papers were acquired from various open access sources.
+
+The most convenient and accessible source was the ART corpus that SAPIENTA was
+trained with\cite{citeulike:11077287}. This corpus was already stored using the
+CoreSC schema and had been pre-annotated. This meant that Partridge would not
+need to do any conversion or pre-processing on the papers. The papers in this
+corpus were all of a similar type and covered similar subject areas within the
+domain of Biochemistry. There were also approximately 260 papers in the
+collection. These papers were used to help establish a conversion process from
+PDF to annotated XML. However, they only formed part of the final corpus.
+Including a large number of papers from other sources provided a more
+comprehensive collection of data for Partridge to learn from.
 
@@
 articles that could be added to Partridge. Both of these sites were found to
-contain large volumes of open access papers. Most of the journals stored on the
+contain large volumes of open access papers. Most of the articles stored on the
 arXiv site were in PDF format which, as discussed below, are difficult to
@@
 
-\subsection{Format Conversion}
-Most scientific papers available on the internet are formatted as PDF
-documents. However, Partridge uses and stores documents that use the CoreSC
-schema by Soldatova and Liakata\cite{liakata2008guidelines}. Therefore some
-spike work was carried out to determine the feasibility of converting papers
-published as PDF documents into XML documents. Townsendi \emph{et al.} (2009) liken converting
-PDF to XML to ``converting hamburgers into cows," they go on to explain that
-PDF documents do not contain any semantic data and documents lose much of their
-explicit structure when they are formatted in this way \cite{Townsend2009}.
-Therefore, to convert PDF documents into an NLP-friendly format, some
-heuristics must be used to detect the document's structure\cite{pdfminer}.
+A third mega-journal used for downloading papers was the PubMed Centrala (PMC)
+repository \url{http://www.ncbi.nlm.nih.gov/pmc/}. Not all of
+the papers available for viewing at the PMC website are open access. However,
+they do offer a listing for the subset of open access papers available on their
+website. The PubMed Central format is also very similar to the SciXML format
+and compatible with SAPIENTA. Therefore, a large number of PubMed papers were
+also used for the initial training of Partridge.
+
+\subsection{Format Conversion} Most scientific papers available on the internet
+are formatted as PDF documents. However, Partridge uses and stores documents as
+XML markup and uses the CoreSC schema by Soldatova and
+Liakata\cite{liakata2008guidelines} for annotation. Therefore some spike work
+was carried out to determine the feasibility of converting papers published as
+PDF documents into XML documents. Townsend \emph{et al.} (2009) liken
+converting PDF to XML to ``converting hamburgers into cows," they go on to
+explain that PDF documents do not contain any semantic data and documents lose
+much of their explicit structure when they are formatted in this way
+\cite{Townsend2009}.  Therefore, to convert PDF documents into an NLP-friendly
+format, some heuristics must be used to detect the document's
+structure\cite{pdfminer}.
 
@@
 version of SAPIENTA was used to process some of the papers converted from PDF.
-This was a great success and the annotations provided by SAPIENTA seemed to be
-accurate.
+This appeared to have been successful. However, after applying some machine
+learning evaluation techniques as discussed in Chapter \ref{chapter:testing},
+it was clear that the Python version of SAPIENTA was not accurate enough to
+provide CoreSC annotations, scoring 44\% accuracy on average. After discussion
+with its author, it became apparent that some of the features provided in the
+server-side version of SAPIENTA had not been implemented in the Python code
+yet. Therefore, it was necessary to switch bak to remote annotation.
 
 \subsection{Paper Type Classification}
+
+Once a large number of papers had been acquired from ART, PlosOne and PubMed
+Central, work could begin on implementing a paper type classifier able to
+discriminate between ``Case Study", ``Research" and ``Review" papers. However,
+for a machine learning classifier to discriminate between classes of data, it
+is necessary to choose a set of features that differ as much as possible
+between the classes. For example, to discriminate between cats and dogs,
+``number of legs" is a poor feature since both species normally have 4.
+However, the noise that these animals make may be a good discriminative feature
+since cats tend to mew and dogs bark.
+
+\subsubsection{ Feature Selection and Clustering}
+
+There are several well established features used for classifying text within
+the NLP community. However, since Partridge has access to CoreSC annotations
+for each paper, an investigation was carried out into how useful CoreSC data
+can be as a feature for paper type discrimination. Every sentence in a given
+annotated paper has an associated CoreSC label. It is therefore trivial to
+calculate the proportion of a paper made up of sentences with a specified
+CoreSC type. Several papers were manually inspected and the proportions of each
+CoreSC represented within were calculated. A pattern quickly emerged between
+the types of paper and the proportions of each CoreSC within them.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.6\textwidth]{images/implementation/review_corescs.png}
+\caption{Contrasting CoreSC content of Review and Research Papers}
+\label{fig:coresc_pies}
+\end{figure}
+
+Figure \ref{fig:coresc_pies} shows the CoreSC content of a review aper and a
+research paper randomly selected from the corpus. The review papers tend to be
+made up almost entirely from Background CoreSC sentences. However, research
+papers are much more evenly spread, made up of several different types of
+CoreSC. This investigation suggested that there is almost certainly a discriminative
+relationship between CoreSC categories and a paper's type.
+
+Although all of the CoreSC types could be influential in determining a paper's
+type, it was likely that some were more important than others. A further
+investigation was carried out to discover the most effective features for
+categorising the data. Since no classifier model had been trained at this
+point, the data was clustered into three unlabelled groups using the K-means
+clustering algorithm. This algorithm was run with three CoreSC
 
@@
 
+During the development of Partridge, the structure of the SQL database
+
 \subsection{WSGI and Apache Integration}
@@
 \subsection{ Bookmarklet }
+
+One of the most important user suggestions for improving the usability of
+Partridge and facilitating the rapid expansion of the paper corpus was the
+Paper Upload Bookmarklet. The bookmarklet was not in the initial system design
+and was added as an extra feature towards the end of the project. It allows
+users browsing sites such as PubMed Central and PlosOne to add papers that
+interest them to Partridge without having to download the paper from the
+journal and upload it to the Partridge server manually.
+
+The system is implemented as a standard web page wrapped inside a javascript
+bootstrap module that can be added as a bookmark to a user's web browser. When
+the user finds a paper that they wish to add to Partridge on one of the
+compatible journal sites, they click the bookmark, loading an embedded frame in
+their current browser window and automatically uploading the paper that the
+user is looking at to Partridge's server.
+
+The bookmarklet trivialises the act of adding new papers to Partridge and this
+should help to encourage users to help grow Partridge's paper corpus.

### 2013-03-26 doc/final_report/methodology.tex
Started writing the implementation chapter

@@
+Chosing an effective development methodology can play a very large part in the
+success or failure of a software project. A number of existing development
+methodologies have been developed and used very effectively over the last 50
+years. However, custom methodologies are also commonly used for projects that
+aren't suited to one of the commonly used approaches. Some common approaches to
+software development and the formulation of a custom methodology for Partridge
+are discussed below.
+
 \section{Existing Methodologies}
-Selecting a suitable development methodology for building Partridge is another
-very important choice for the project.
 
@@
 
-As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.} came up
-with the principle of the Agile Manifesto, favouring a lightweight, responsive
-development model over the heavyweight slow waterfall
+As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.}
+came up with the principle of the Agile Manifesto, favouring a lightweight,
+responsive development model over the heavyweight slow waterfall
 system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team
@@
 
-\subsection{ Work Timeline }
+Programming tasks were added to the GitHub project tracker facility in the
+same place as the Wiki was hosted. The `milestones' feature, which allows tasks
+to be split into groups that must be completed by an arbitrary date, was used
+to plan iterations and could be used to provide precise summaries of how the
+project was progressing. In January, the project ran behind by a few weeks.
+The time tracker explained that the project was precisely 17 days behind and
+highlighted the set of tasks that needed to be completed to bring the project
+back up to speed.
 
-The tasks involved in Partridge have been carefully calculated and prioritised.
-They were then added to the GitHub issue management system and a report
-generated listing them in the order that they are expected to be
-accomplished. This report can be seen in Appendix \ref{sec:timeline}.
+\section{ Initial Plan and Project Timeline }
+
+During the early stages of the Partridge project, an initial system design was
+drawn up and a set of tasks that covered the system's implementation were
+formulated. These tasks were divided up into iterations and added to the
+project planner on GitHub. Each task's dependencies were carefully considered
+in order to prioritise tasks properly. The initial project plan can be seen in
+Appendix \ref{sec:timeline}.

### 2013-03-26 doc/final_report/implementation.tex
hit the 10k words barrier

@@
 
-During the development of Partridge, the structure of the SQL database
+During the development of Partridge, the structure of the SQL database used to
+store the papers changed a lot due to modifications to the ORM modules as
+discussed above. These structural changes meant that the production database at
+\url{http://farnsworth.papro.org.uk/} and the development database were not
+compatible and that updates to the code on the development server would break
+the application on the prodution server unless the database structure was also
+updated.
 

### 2013-03-27 doc/final_report/crfletter.tex
Finished implementation section on clustering and paper type classification

\begin{verbatim}
Hi All,

I'm trying to build CRFSuite's python extension 
(http://www.chokkan.org/software/crfsuite/) on an Arch Linux 64-bit 
environment using Swig 2.0.8 (PCRE enabled).

When I run SWIG, I get the following output:

<<OUTPUT OMITTED FOR BREVITY>>

Full output available at http://sourceforge.net/mailarchive/message.php?msg_id=30024209

As far as I can see, all of these problems stem from this declaration in 
the SWIG input file (http://pastebin.com/9JipJ1C1):
%template(ItemSequence) std::vector<CRFSuite::Item>;

I've had a look around on google and on this mailing list and the only 
other "cannot copy typemap" errors I've encountered have been where 
people have excluded the std namespace in favour of a 'using' statement. 
As you can see, this example uses absolute class names so that isn't the 
issue here. I haven't had any luck contacting the software maintainer 
for CRFSuite yet either.

As you might expect, if I continue to compile the extension without 
heeding these errors, when I try to make use of the ItemSequence object 
I get the following python error:
TypeError: in method 'ItemSequence_append', argument 2 of type 
'std::vector< CRFSuite::Item >::value_type const &'

I'm going to keep trying to sort this out and if I find the solution 
independantly, I'll make sure to post a follow-up email. However, if 
anyone else has any ideas about what might be happening here, please let 
me know.

Thanks,

James Ravenscroft
AI & Robotics Undergraduate
Aberystwyth University
\end{verbatim}

### 2013-03-27 doc/final_report/implementation.tex
Finished paper preprocessing section in testing and started writing stuff for web backend

@@
 \section{Paper Preprocessor}
+
+Partridge's Paper Preprocessor module was the most difficult part of the
+project to implement. From acquiring papers for use in the project to teaching
+a machine learning system to recognise different types of scientific
+publication, a number of technical challenges were encountered.
 
@@
 
-\subsection{Pre-processing with SAPIENTA}
+\subsection{Annotating with SAPIENTA}
 
@@
 environment and its creator had to be contacted via a mailing list (See
-Appendix \ref{sec:crfemail}. After a few days, the owner responded and the
+Appendix \ref{sec:crfemail}). After a few days, the owner responded and the
 library was compiled successfully.
@@
 
-\subsubsection{ Feature Selection and Clustering}
+\subsubsection{Feature Selection and CoreSCs}
 
@@
 \centering
-\includegraphics[width=0.6\textwidth]{images/implementation/review_corescs.png}
+\begin{subfigure}[b]{0.6\textwidth}
+\includegraphics[width=\textwidth]{images/implementation/review_corescs.png}
+\caption{CoreSC content for a sample review paper}
+\end{subfigure}
+\begin{subfigure}[b]{0.6\textwidth}
+\includegraphics[width=\textwidth]{images/implementation/report_corescs.png}
+\caption{CoreSC content for a sample research paper}
+\end{subfigure}
+
 \caption{Contrasting CoreSC content of Review and Research Papers}
@@
 
-Figure \ref{fig:coresc_pies} shows the CoreSC content of a review aper and a
+Figure \ref{fig:coresc_pies} shows the CoreSC content of a review paper and a
 research paper randomly selected from the corpus. The review papers tend to be
@@
 
-Although all of the CoreSC types could be influential in determining a paper's
-type, it was likely that some were more important than others. A further
-investigation was carried out to discover the most effective features for
-categorising the data. Since no classifier model had been trained at this
-point, the data was clustered into three unlabelled groups using the K-means
-clustering algorithm. This algorithm was run with three CoreSC
+\subsubsection{ K-means clustering}
+
+Before working with supervised learning systems, a preliminary experiment was
+carried out to see whether clustering papers using the K-means algorithm could
+successfully identify the paper types, thus removing the need to train and
+maintain a supervised model. This was also an excellent opportunity to explore
+the data and try and detect any inherent patterns within the papers.
+
+K-means clustering uses the Euclidean distance between each data sample to
+decide which cluster it is closest to and should belong to. K is the number of
+clusters that are used and is decided ahead of execution. K-means clustering is
+often run multiple times using a range of K values when the number of clusters
+in the data is unknown. The performance of the clustering algorithm is often
+evaluated using the K-means silhouette which is a measurement of how tightly
+the data is clustered. A low silhouette value ($K \approx 0$) suggests loose
+clustering and therefore little correlation, a high silhouette value ($K
+\approx 1$) corresponds with very tight clustering and good correlation.
+
+All of the papers were manually identified as either a ``Case Study", a
+``Review Paper" or a ``Research Paper." They were then loaded into a script and
+clustered using their CoreSC respective compositions. K-Means silhouettes were
+used as a measure of how effective the clustering process was. This was
+repeated for $ K \in [2..8] $ and the best silhouette measurement and value for
+K retained. The algorithm consistently showed that K=3 was the best K value.
+However, the silhouette value was consistently low. It was suggested that this
+may have been because all CoreSC types were considered equally; the less
+discriminative CoreSCs may have been offsetting the effect of the highly
+discriminative ones.
+
+To remedy this, all papers were again clustered, but using only three CoreSC
+labels at a time: reducing the noise from the less important types. The
+algorithm was run for all combinations of 3 CoreSC labels, again retaining only
+the most successful combination of features and K value based upon the K
+silhouette value. This returned a set of much stronger K silhouette values in
+general. The algorithm also determined that the combination of ``Background",
+``Motivation" and ``Method" CoreSC labels seemed to be the most
+discriminative, providing a silhouette value of 0.63.
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.8\textwidth]{implementation/cluster.png}
+\caption{Paper types rendered using Bac, Met and Mot CoreSCs}
+\label{fig:clusters}
+\end{figure}
+
+Figure \ref{fig:clusters} shows the papers from the corpus rendered in 3
+dimensions using their Background, Method and Motivation CoreSC makeup.
+Although the data does not cluster perfectly by class, these three categories
+do provide fairly clear discrimination between the three types of paper.
+
+Clustering the papers did not seem to provide a reliable way to classify them
+by type and it was decided that better results could be obtained through the
+use of a supervised learning classifier instead. However, the three most
+discriminative CoreSC types were chosen as features for the learner.
+
+\subsubsection{Random Forest Learner}
+
+To classify the papers, a Random Forest Learner was trained using a subset of
+the Partridge corpus using Background, Method and Motivation CoreSC information
+from the papers. The classifier was found to be highly accurate, correctly
+predicting a paper's type in 87.9\% of cases. The classifier's accuracy and
+evaluation are further discussed in Section \ref{sec:evaluation_learners}
+below.
+
+The new classifier was incorporated into the paper preprocessor and triggered
+after SAPIENTA annotation for each new paper. It was also called
+retrospectively for papers in the Farnsworth Partridge instance that were not yet
+classified.
 
@@
 
+Providing notifications to users when a paper has been processed was not part
+of the original design for Partridge. The feature was added to the system after
+being raised as a potential improvement by one of the test users. Previously,
+users to added papers to the Partridge corpus did not know whether the
+operation was a success unless they ran a search and the paper appeared in
+their results. Adding email notifications to Partridge significantly improved
+the user experience for paper uploaders. The uploader is given the option to
+provide their email address when they send the paper to the Partridge server.
+Once the preprocessor has converted, annotated and classified a paper, an email
+is sent to the uploader informing them that the paper has been added to the
+database and containing a direct link to the paper's profile page.
+
+The system also emails users upon failure, allowing them to report the error to
+the GitHub page if required and also providing closure for users who are unsure
+why their paper isn't appearing in Partridge queries.
+
 \section{ Web Backend }
 
+The Partridge web backend was much easier to implement than the preprocessor.
+The web framework Flask was used to do a lot of the hard work such as routing
+requests and encoding data into browser-compatible formats.
+
 \subsection{ Server Views }
+
+Flask provides a model-view-controller style framework in which specific web
+URLS are represented by `view' functions.
 
@@
 compatible and that updates to the code on the development server would break
-the application on the prodution server unless the database structure was also
+the application on the production server unless the database structure was also
 updated.
 
+To prevent this from happening, a Python utility called
+Alembic\cite{alembic2013} was used for keeping the Database structure under
+Version Control. Alembic is executed when Partridge's ORM models are modified
+and can detect differences in database structure between the SQLAlchemy model
+in Partridge's source code and the live database. It generates sets of SQL
+commands that are used to synchronise the database structure with the most
+recent program structure. This allowed the Farnsworth database to be updated
+automatically when a new change to Partridge's data structures was made rather
+than having to be purge and repopulate it.
+
 \subsection{WSGI and Apache Integration}
+
+Flask provides a test server that can be used for developing your web
+application. However, it is written in python and is not designed to be as
+stable or scalable as a full web server application such as Apache. Once
+Partridge's basic web interface was complete and the application ready to be
+deployed, it had to be integrated into Apache to provide stable web server
+support.
+
+By default, Apache only serves static HTML content and image/data files. It makes
+use of plugins to support dynamic web pages, in languages such as PHP and
+Python. A plugin called WSGI is used to allow Apache to serve Python
+applications. WSGI requires that the Python program exposes an
+\emph{application} object which implements a common interface in order to
+communicate with Apache.
+
+After thorough investigation, it was discovered that Flask provides a WSGI
+compatible \emph{application} object. A small wrapper was written that exposes
+the Flask app to WSGI and the server began to work as expected. Unfortunately,
+the WSGI interface didn't allow the preprocessor daemon to be run in the
+background. Therefore, a second wrapper was created that allowed the execution
+of the Paper daemon as a standalone process.
 

### 2013-03-30 doc/final_report/implementation.tex
Put in some stuff about JSON

@@
 Flask provides a model-view-controller style framework in which specific web
-URLS are represented by `view' functions.
+URLS are represented by `view' functions. The behaviour of these views changes
+dependent upon data from the incoming HTTP request. Their return value is
+encoded as an HTTP response and sent back to the browser that made the request.
+
+The implementation of the server views was for the most part straight forward
+with the exception of some of the responses to the interactive web elements in
+the HTML markup. It was determined that the best way to communicate between
+frontend and backend elements interactively was to encode responses as
+JavaScript Object Notation JSON - a common notation used to describe arbitrary
+data structures\cite{jsonRFC}. Despite its name, JSON encoders and decoders are available for
+most common programming languages.  Flask even has an inbuilt method called
+jsonify which can be used to automatically encode arbitrary Python objects as
+JSON and send it back to the browser for parsing by the frontend scripts.
 

### 2013-03-31 doc/final_report/design.tex
Finished introduction to partridge views implementation

@@
 
-\subsection{ Target Platform}
+\subsection{Target Platform}
 
@@
 \subsection{ Data Storage }
+\label{sec:db_layout}
 It is expected that a given Partridge instance may grow in size to contain
@@
 \subsection{ Web Frontend }
+\label{sec:web_frontend}
 

### 2013-03-31 doc/final_report/implementation.tex
Finished introduction to partridge views implementation

@@
 JavaScript Object Notation JSON - a common notation used to describe arbitrary
-data structures\cite{jsonRFC}. Despite its name, JSON encoders and decoders are available for
-most common programming languages.  Flask even has an inbuilt method called
-jsonify which can be used to automatically encode arbitrary Python objects as
-JSON and send it back to the browser for parsing by the frontend scripts.
+data structures\cite{jsonRFC}. Despite its name, JSON encoders and decoders are
+available for most common programming languages, not just JavaScript.  Flask
+even has an inbuilt method called jsonify which can be used to automatically
+encode arbitrary Python objects as JSON and send it back to the browser for
+parsing by the frontend scripts\cite{flask2012}.
+
+Some of the frontend scripts such as the Query Form rely upon the server to
+return dynamically generated HTML markup containing data about the papers being
+processed. In line with its model-view-controller architecture, flask provides
+a templating module that can be used to populate pre-coded HTML templates with
+data from the database on the fly. Templates for each of the views are stored
+within the \emph{templates/} subdirectory within Partridge and are populated
+using data retrieved from the relational database when a call to one of the
+view functions is made\cite{flask2012}.
 
 \subsection{Database Interaction \& SQLAlchemy}
+
+Partridge makes extensive use of a relational database system for storage and
+retrieval of paper data and metadata. It uses an SQL database server and
+initially the schema listed in Section \ref{sec:db_layout}. Rather than using
+raw SQL calls to communicate with the database, It was determined that the use
+of an Object-Relation-Mapper (ORM) library such as SQLAlchemy could
+significantly speed up development time. SQLAlchemy and ORM wrappers are used
+to abstract database entities into language constructs.
+
+SQLAlchemy enables the representation of papers, authors and other entities as
+Python objects. These objects can also be extended and custom methods added to
+them, enabling the creation of specific entity methods such as calculating
+CoreSC makeup of papers and computing first, middle and last names from a
+single input string of an author's full name.
 
@@
 
-\subsection{Query Interface}
+Partridge's web frontend required the least procedural programming and mainly
+consists of HTML markup with some JavaScript. The layouts were based upon the
+interface designs discussed in Section \ref{sec:web_frontend}. However, some
+changes were made to the original designs during implementation to improve
+usability functionality.
+
+As discussed above, the HTML layouts were stored as templates in the
+Partridge system and were evaluated and expanded using data from the SQL
+server at runtime. Flask's database engine supports object oriented templates
+that inherit properties from each other. This allowed the main page layout to
+be designed once and reused for each specific view.
+
+Bootstrap, a powerful design framework was used to help build the frontend
+pages and forms. Bootstrap offers a set of standard CSS and JavaScript
+utilities that assist the developer in designing page layouts and provide
+commonly used boilerplate code and interface elements\cite{bootstrap2013}. This
+allowed the page layouts and forms used in Partridge to be implemented a lot
+quicker than if they had been implemented from scratch. jQuery, a library for
+manipulating HTML page layouts using JavaScript and providing utility functions
+for server communication, was also used to save time in writing the interactive
+aspects of frontend code.
+
+Whilst these libraries did not provide any assistance specific to the domains
+of information retrieval or machine learning, they did help accelerate the
+design of the frontend interfaces and provide cross-browser compatible HTML5
+interfaces. Other javascript libraries providing multiple file upload
+capability and browser history manipulation were incorporated into specific
+user interface modules.
+
+\subsection{Query Interface \& Results View}
 

### 2013-04-01 doc/final_report/implementation.tex
Finished first draft of implementation chapter

@@
 difficult to tackle.
+
+Several libraries were used to accelerate the development and implementation of
+Partridge and avoid `reinventing the wheel.' Whenever code libraries were used,
+the role of the engineer was to be aware of the available solutions and deduce
+which was aposite to the purpose intended.
 
@@
 models since training data sets need to be statistically significant in order
-to provide any meaninful results. Users are given the option, and actively
+to provide any meaningful results. Users are given the option, and actively
 encouraged, to upload papers that they own or publish on another author's
@@
 of information retrieval or machine learning, they did help accelerate the
-design of the frontend interfaces and provide cross-browser compatible HTML5
+implementation of the frontend interfaces and provide cross-browser compatible HTML5
 interfaces. Other javascript libraries providing multiple file upload
@@
 
+After the project had been running for approximately 1 iteration, it was
+decided that the query and results views were confusing and provided a
+disjointed user experience for those trying to query the system. The results
+view was initially designed as a separate page to the query view and
+consequentially, users found it quite confusing when trying to relate the
+results from the system to the query they had provided on the previous page and
+it was inconvenient to have to keep changing the page when manipulating the
+query.
+
+To improve the Partridge user experience, the query and results views were
+combined into a single interactive page that used JavaScript to retrieve
+results from the backend system and simply append them to the current page
+using a jQuery function.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\textwidth]{images/implementation/queryform_actual.png}
+\caption{The updated query form with integrated results}
+\label{fig:queryform_actual}
+\end{figure}
+
+The redesigned query form, as shown in Figure \ref{fig:queryform_actual},
+allows the user to add constraints to the query one at a time using the input
+field at the top of the page. These constraints are then listed on the left
+hand side and can be removed by clicking on the relevant cross icon next to the
+term to be removed. Filters such as paper type and topic are available in the
+left toolbar and be manipulating using the relevant dropdown box. Changing any
+of the filters or constraints automatically triggers the JavaScript routine to
+retrieve new results from the server.
+
+Using JavaScript to update the results and manage the query on a single page
+provides a significantly better user experience. Unfortunately, it does
+interfere with how browser handle a user's history, breaking the Back and
+Forward buttons in all browsers and preventing users from linking to their
+query results and posting them to friends or colleagues.
+
+The jQuery BBQ (jqBBQ) library was used to restore this functionality
+\cite{jqbbq2013}. The library allows the scripted manipulation of the URI
+fragment, a string that forms part of a page's URI but does not change the HTTP
+request made to the server\cite{urifragment2013}. The fragment can be used to
+serialise the the state of the user interface, allowing users to share links to
+search results and restoring browser history functionality. A javascript
+function was set up to fire when the interface was fully loaded and examine the
+URL fragment, converting key, value pairs into search constraints. A
+serialisation function was also set up to trigger whenever search constraints
+and filters were added and removed from the query and update the fragment
+string accordingly.
+
 \subsection{ Paper Upload Interface }
+
+The paper upload interface was initially designed to allow authors of papers to
+submit their work to be analysed by Partridge and display the upload progress
+in the form of a horizontal progress bar on the page. Normally, web browsers
+only allow the selection of one file at a time for upload and makes an HTTP
+request with the file data, without telling the user how long it might take or
+providing any information on the upload progress. To implement multiple file
+uploads and a progress bar, a significant amount of JavaScript code is
+required.
+
+jQuery HTML5 Upload was used to speed up implementing this feature. This
+library provides an interface for uploading files asynchronously within the
+user's web browser and triggering a callback method when progress is made
+during an upload and when a file ha finished uploading. This allowed the
+implementation of a progress bar and text readout of the upload progress
+without forcing the browser to refresh the page.
+
+After reviewing the design of the page, a new checkbox was added to the upload
+form that forces the user to verify that they have permission to upload the
+paper in an attempt to prevent problems with copyright and ownership issues.
+The users are also linked to \url{http://www.sherpa.ac.uk/romeo/}, a service
+that can be used to identify the copyright policy of paper authors and
+journals and whether specific papers can be used by Partridge.
 
@@
 
-The system is implemented as a standard web page wrapped inside a javascript
-bootstrap module that can be added as a bookmark to a user's web browser. When
-the user finds a paper that they wish to add to Partridge on one of the
-compatible journal sites, they click the bookmark, loading an embedded frame in
-their current browser window and automatically uploading the paper that the
-user is looking at to Partridge's server.
+The system is implemented as a standard web page wrapped inside a JavaScript
+module that can be added as a bookmark to a user's web browser. When the user
+finds a paper that they wish to add to Partridge on one of the compatible
+journal sites, they click the bookmark, loading an embedded frame in their
+current browser window and automatically uploading the paper that the user is
+looking at to Partridge's server.
 
 The bookmarklet trivialises the act of adding new papers to Partridge and this
-should help to encourage users to help grow Partridge's paper corpus.
+should help to encourage users to help grow Partridge's paper corpus as quickly
+as possible. It should also remove complications surrouding the rights of authors and
+publishers of papers since it is only compatible with sites that publish open
+access articles and cannot be used to add papers to Partridge that may be
+copyright protected.
+
+\section{Summary}
+
+Partridge's implementation took place over a period of many weeks, with
+incremental improvements, often stemming from user suggestions, being
+incorporated throughout. There were several deviations from the original
+project designs. Nonetheless, most of the designs were appropriate and provided
+an excellent starting point for implementation of the project.
+
+The effective and appropriate use of libraries within Partridge helped in
+speeding up the development of the project using well tested and maintained
+code from other developers. This required a different skillset which could be
+considered equally or more important than just writing new code
+\emph{vis-à-vis} a holistic understanding of the nature of the project and the
+relationships of the core modules. Working with libraries requires
+comprehensive conceptualisation of the task at hand whereas programming
+requires focus on a specific subset of the component's behaviour and attaining
+expected outputs for given inputs to the routine under construction.

### 2013-04-01 doc/final_report/testing.tex
Finished paper preprocessing section in testing and started writing stuff for web backend
Finished first draft of implementation chapter

@@
 %introduction to testing
-Throughout the implementation of the project, testing has remained a very
-important aspect of Partridge's development. A number of testing techniques
+Throughout the implementation of the project, verifying that systems provide
+predictable and reliable outputs for given inputs has remained a very important
+routine, necessary in Partridge's development. A number of testing techniques
 have been used in order to evaluate the individual behaviours of Partridge's
@@
 \section{ Evaluating Learning Algorithms }
+\label{sec:evaluation_learners}
 

### 2013-04-01 doc/final_report/evaluation.tex
Finished first draft of testing chapter and rearranged contents
Finished evaluation section

@@
 
-\subsection{ Achievements }
+Why write in first person in this chapter?
 
-\subsection{ Limitations and Potential Improvements }
+Burrows et al. (2000) suggest that writing in a reflective style enhances the
+author's learning\cite{JEE:JEE657}. Coombs (2001) identified introspection and
+mindfulness as habits of mind to promote reflection. Writing in the first
+person reflects such introspection\cite{coombs2001reflective}.
 
-\subsection{ Further Research }
+\section{ Achievements \& Impact}
+
+Partridge was conceptualised as a tool to assist with scientific research on
+the world wide web by learning the preferences of researchers and returning
+sets of papers that might interest them. Although it does not yet provide an
+automated solution to `information overload' in the form of a suggestion
+engine, Partridge goes a long way towards demonstrating the feasibility of such
+a system and already serves as an elegant search tool for filtering out a great
+deal of irrelevant literature.
+
+\subsection{ Paper Preprocessor}
+
+One of the biggest achievements in the development of Partridge is the flexible
+and resilient paper preprocessing module. This was the most difficult part of
+the system to build and a great deal of time was spent building the various
+converters and classifiers that make up the 1236 lines of code that went into
+the module. Some of the challenges encountered (see below) during the
+implementation of the paper processor served as greatly valuable lessons in
+working with artificial intelligence systems.
+
+During the development of the paper processor, I felt that I learnt the most
+from building the paper type classifier. The implementation of the classifier
+was not difficult in itself. However, determining which features to use for the
+classifier and the clustering analysis were entirely new concepts to me and
+required a lot of investigative work and reading to help me to understand the
+processes and how they should be applied.
+
+Working with the Python implementation of SAPIENTA demonstrated the importance
+of machine learning evaluation methods for testing classifiers rather than
+making assumptions about `sensible looking' output. When the application was
+run on a set of papers acquired for Partridge's corpus, it seemed to give
+sensible CoreSC classifications for the papers. However, upon further analysis
+and calculation of Python SAPIENTA's Classifier Accuracy, it was determined
+that the system was only getting 44\% of CoreSC annotations correct, an
+unacceptably low success rate. If I hadn't have run the evaluation functions on
+SAPIENTA, it would have been easy to assume that it was correctly classifying
+the papers, tainting the input papers and potentially disrupting the
+investigation into CoreSC makeup and paper type.
+
+\subsection{User Interface}
+The Partridge user interface is also a great success, providing a highly usable
+and intuitive representation of the relatively complicated processes that are
+used to classify and organise the papers. The use of HTML and JavaScript
+interactive elements instead of static pages and synchronous calls to the web
+server was certainly a good idea, providing a modern system that keeps the user
+informed at all times. The decision to use the jqBBQ library to add browser
+history support further enhanced the user experience, allowing users of
+Partridge to share links to specific search results over social media channels
+and potentially bookmark significant results.
+
+I was particularly pleased with the Bookmarklet which makes adding papers to
+Partridge significantly easier for non-authors and those who are unsure about
+licensing and copyright restrictions on the papers in the corpus. The
+bookmarklet was quite difficult to implement, requiring parsers for each of the
+supported journal sites. However, I think it offers the most significant
+improvement-to-time-invested ratio of any feature in the project.
+
+The project's impact can also be considered a great achievement, with interest
+from a growing user-base and some of the larger open access journals whose
+papers are interested by the system.
+
+\subsection{Wider Impact}
+
+Since its inception, Partridge's impact has been reflected in the steadily
+increasing number of followers of the project. Towards the beginning of the
+project, many of my close friends and colleagues demonstrated immediate
+interest in the project, volunteering themselves as testers and beta users as
+soon as a usable version of the software became available. I also spoke at the
+BCS Show and Tell event held in Aberystwyth during November, discussing the
+concept behind Partridge and displaying some early interface designs. The
+project attracted a lot of interest from the attendees at the talk and many
+people took my email address and the address of my blog so that they could
+start using the system when it came online.
+
+\begin{figure}[!h]
+\centering
+\includegraphics[width=\textwidth]{images/evaluation/plostweet.png}
+\caption{Tweet from PLOSOne regarding development on Partridge}
+\label{fig:plostweet}
+\end{figure}
+
+The project has also attracted the attention of the wider scientific community
+on the internet, most notably the open access journal PLOSOne, from which many
+of the papers used in Partridge were sourced. During the implementation of
+Partridge, I constantly updated my Twitter account with news about my
+progress. Figure \ref{fig:plostweet} shows one of the positive reactions to
+work I was carrying out on the paper preprocessor.
+
+\subsection{Professional Development}
+
+One of the skills that I have honed through my dissertation project this year
+has been reflecting communally upon my work with my supervisors. During my work
+placement at IBM, I was loosely supervised, however it was never to the close
+and exacting standards of Dr Clare and Dr Liakata, whose guidance has 
+prevented me from taking several wrong turns during the project. Reflecting
+within such a professional community allowed me to develop good professional
+praxis and think more deeply about my programming and Partridge as a whole. It
+provided an induction into a professional community of academic computer
+science and allowed me as a novice to feel comfortable there.
+
+\section{ Limitations and Potential Improvements }
+
+Despite the great achievements and impact of Partridge, a few limitations and
+imperfections have emerged during the course of the project. Many of these
+limitations stem from incorrect estimation of the difficulty and scale
+of the AI and NLP-based tasks within the system and most of them could be
+improved or resolved all together if more time was available to work on the
+project.
+
+\subsection{ Paper Classifiers}
+
+Due to the strict time restrictions, two of the paper preprocessor modules: the
+result and subject classifiers could not be implemented. These were supposed to
+add the ability to filter experimental papers by result: positive or negative
+and filter papers by topic: e.g. Physics, Biology, Maths. After the completion
+of the paper type classifier, the project deadline was only a few weeks away
+and with the dissertation write-up looming, I decided it would be foolish to
+start working on further classifier behaviour.
+
+Given my experience with the paper type classifier, adding the new classifiers
+for result and topic should be fairly simple if I followed the same process:
+determining which features would be the most effective for discriminating
+between the data classes and then training and comparing a few different
+supervised learning algorithms using the Partridge corpus. A number of papers
+that could be reviewed to help with feature selection and training for these
+tasks have been suggested to me for review at a later date.
+
+\subsection{ SAPIENTA }
+
+Whilst SAPIENTA is an excellent piece of research in itself and provides
+fascinating insights and implications into the makeup of scientific literature,
+Dr Liakata concedes that it is purely an experimental system and was not
+intended for large scale analysis of batches of papers in the way that it is
+utilised by Partridge. During the development of the paper type classifier,
+there were several short delays when the SAPIENTA server stopped working and
+had to be restarted. It took several weeks to collect enough data for machine
+learning for this reason.
+
+Unfortunately, SAPIENTA is not scheduled for improvement work until the summer
+and that means that Partridge's paper preprocessor is still not very
+scalable. If further work to Partridge is carried out, I hope to improve the
+accuracy of the Python SAPIENTA implementation to be comparable with the
+current, experimental version of the system and run paper annotations locally
+on the Partridge server.
+
+\subsection{ Scalability }
+
+Aside from the underlying issues with SAPIENTA, some of the other Partridge
+subsystems may suffer from scalability issues when faced with a large volume of
+users.
+
+Partridge currently resides on a single server machine which runs separate
+database server, web server and paper preprocessor tasks. This configuration
+has been effective during Partridge's development and remains effective at
+present. However, if the volume of users increased significantly, a single
+server machine may not offer the processing power or storage capability
+required. If this becomes an issue, the database, web server and paper
+preprocessor systems could all be moved to separate physical machines and
+communicate over a local network.
+
+The paper preprocessor application is also currently single threaded, only
+processing one paper at a time. If more time had been available, the
+preprocessing module would have been modified to use parallel processing when
+processing each paper, allowing uploaded papers to be added to the database more
+quickly.
+
+\subsection{ Recommendation Engine}
+
+During the course of the project, it became clear very quickly that there would
+not be time to implement a recommendation engine as originally hoped. Such a
+system would need to collect data from users and the papers that they looked at
+and correlate it with papers stored in the corpus that the user may be
+interested in viewing. Although there wasn't time to build this feature during
+the project, I certainly think it is more than feasible.
+
+One possible solution would be to use features such as a paper's CoreSC makeup
+to build a user profile and then use a k-Nearest Neighbours algorithm to select
+papers that have similar features to the user's preferences. Given the
+opportunity, I would have liked to have spent a significant amount of time
+investigating possible techniques and implementing a recommendation system
+since this would offer a huge boost in Partridge's utility.
+
+\section{ Further Research }
+
+Partridge already fulfills many of its objectives and has also had a sizeable
+impact on the research community. However in its implementation, a number of
+topics for further research have also been uncovered.
+
+Towards the end of the project, I was given the opportunity to submit an
+overview of Partridge as an academic research paper as part of the proceedings
+for the BCS AI Conference being held in December 2013. This is an excellent
+opportunity to expose Partridge to potential researchers who may be interested
+in examining some of the Natural Language Processing and Artificial
+Intelligence techniques employed in the project.
+
+The relationship between a paper's  CoreSC makeup and its type has a lot of
+potential for further research. During the development of Partridge, this
+relationship was only tested using Research, Review and Case Study papers since
+there were a large number such papers published in open access journals,
+available for analysis. From the analysis in Section
+\ref{sec:evaluaton_learners}, it is clear that a paper's CoreSC makeup can be
+very effective in determining which of these three classes it belongs to. The
+most discriminative features were specifically Background, Method and
+Motivation. However, this relationship was only tested with the three paper
+possible types listed above. Further work could be conducted to discern whether
+the correlation between CoreSC makeup and paper type holds for other classes of
+document and whether the most discriminative CoreSC labels remain the same for
+a larger number of paper types.

### 2013-04-01 doc/final_report/testing.tex
Finished evaluation section

--- 2013-03-26 doc/final_report/testing.tex
@@
 %introduction to testing
-Throughout the implementation of the project, testing has remained a very
-important aspect of Partridge's development. A number of testing techniques
-have been used in order to evaluate the individual behaviours of Partridge's
-key components both separately and the system as a whole. This chapter
-discusses the techniques used to test Partridge, the results from these tests
-and any implications that these results have had upon development of the
-project. Combining all of these testing and evaluation techniques provides an
-in depth view of how useful Partridge is and how it can be improved upon.
+Throughout the implementation of the project, verifying that systems provide
+reliable, expected outputs for given inputs has remained a very important part
+of the overall development process, necessary in Partridge's development.  A
+number of testing techniques have been used in order to evaluate the individual
+behaviours of Partridge's key components both separately and the system as a
+whole. This chapter discusses the techniques used to test Partridge, the
+results from these tests and any implications that these results have had upon
+development of the project. Combining all of these testing and evaluation
+techniques provides an in depth view of how useful Partridge is and how it can
+be improved upon.
 
@@
 
-\subsection{ Back-end \& Infrastructure Testing}
+\subsection{ Backend \& Infrastructure Testing}
 
@@
 issues with the system were identified very early on and resolved due to the
-`open-source-esque' development lifecycle used during the project.  Testing has
-also provided a great deal of understanding about just how useful Partridge is
-as well as highlighting its limitations. It also raises questions as to the
-future development of the project and provides a number of ideas for future
-improvements.
+`open-source-esque' development lifecycle used during the project.  Testing
+Partridge has helped in understanding the system's limitations and raised a
+number of questions about its future development and ideas for additional
+improvements. It has also provided a great deal of insight into how effective
+Partridge is at its intended purposes, as well as its potential impact on
+internet research.

### 2013-04-01 doc/final_report/evaluation.tex
Finished evaluation

@@
 
+\subsection{Professional Development}
+
+One of the skills that I have honed through my dissertation project this year
+has been reflecting communally upon my work with my supervisors. During my work
+placement at IBM, I was loosely supervised, however it was never to the close
+and exacting standards of Dr Clare and Dr Liakata, whose guidance has 
+prevented me from taking several wrong turns during the project. Reflecting
+within such a professional community allowed me to develop good professional
+praxis and think more deeply about my programming and Partridge as a whole. It
+provided an induction into a professional community of academic computer
+science and allowed me as a novice to feel comfortable there.
+
 \subsection{Wider Impact}
@@
 work I was carrying out on the paper preprocessor.
-
-\subsection{Professional Development}
-
-One of the skills that I have honed through my dissertation project this year
-has been reflecting communally upon my work with my supervisors. During my work
-placement at IBM, I was loosely supervised, however it was never to the close
-and exacting standards of Dr Clare and Dr Liakata, whose guidance has 
-prevented me from taking several wrong turns during the project. Reflecting
-within such a professional community allowed me to develop good professional
-praxis and think more deeply about my programming and Partridge as a whole. It
-provided an induction into a professional community of academic computer
-science and allowed me as a novice to feel comfortable there.
 
@@
 a larger number of paper types.
+
+\section{ Summary }
+
+This chapter has discussed the achievements arising from the Partridge project:
+the design and implementation of the paper preprocessor and the integrated
+Artificial Intelligence; lessons learnt from developing Partridge's HTML5
+interface and considerations needed to help users to understand complicated
+applications; professional and personal development through my relationship
+with my supervisors. Wider impacts of Partridge include a growing number of
+users and interest from one of the larger research journals that Partridge
+indexes.
+
+Some of the limitations of Partridge are discussed above. These include the
+additional paper classifiers which were omitted due to time constraints,
+underlying problems with SAPIENTA and scalability in general. Future
+development will deal with the issue of adding a recommendation engine to the
+system and how this could be implemented.
+
+Moreover, the possibility of further research into the relationship between
+CoreSC and paper type is explored and I am hoping that my submission to the BCS
+AI conference inspires others to carry out research in this area.
+
+I have thoroughly enjoyed working on Partridge and feel that this project has
+developed my ability to apply machine learning algorithms to practical
+applications and my professional praxis. I hope to continue to develop
+Partridge into a useful and widely used research tool and am also
+greatly looking forward to submitting my paper to the BCS AI Conference and
+continuing my professional collaboration with Dr Clare and Dr Liakata.

### 2013-04-01 doc/final_report/methodology.tex
Added summary to methodology chapter

@@
 
-\section{ Initial Plan and Project Timeline }
+\subsection{ Initial Plan and Project Timeline }
 
@@
 Appendix \ref{sec:timeline}.
+
+\subsection{Support and Version Control Tools}
+
+Partridge made heavy use of GitHub and the Git version control system. Git,
+developed by Linus Torvalds, is a distributed Version Control System (VCS) that
+offers many of the features of centralised VCSes such as Subversion and CVS.
+However, unlike these centralised products, Git repositories are
+self-contained, requiring no connection to a central server, with each copy of
+the repository containing the complete project history. Copies of the
+repositories are stored on the development machine, the production machine and
+the GitHub server. This makes GIT more reliable than centralised repositories
+since all code is accessible regardless of whether the repository hosted with
+GitHub is online.
+
+GitHub's hosted project management tools and wiki were used to store project
+tasks, notes and metadata during development.
+
+\section{Summary}
+
+Having analysed some of the existing development methodologies and determined
+that most of the common methodologies were not suitable for Partridge. A custom
+methodology was formulated and support tools chosen. Task analysis was then
+performed and a project timeline generated. With a timeline in place, the
+initial design phase for Partridge and its subsystems could begin.

### 2013-04-01 partridge/mltest/clustertest.py
Updated test scripts for ml stuff

@@ -67,7 +67,7 @@ for features in combinations(corescs, 3):
     fig = plt.figure()
     ax = fig.add_subplot(111, projection='3d')
 
-    colours = ['r','g','b']
+    colours = {"Research" : 'r', "Review" : 'g', "Case Study" : 'b'}
     j = 0
 
     clusters = km.clusters
@@ -75,17 +75,13 @@ for features in combinations(corescs, 3):
     for i in range(0, len(paper_table)):
 
         ax.scatter(paper_table[i][0],paper_table[i][1],paper_table[i][2],
-        c=colours[clusters[i]])
-
-        j += 1
+        c=colours[str(paper_table[i]["type"])])
 
     ax.set_xlabel(features[0])
     ax.set_ylabel(features[1])
     ax.set_zlabel(features[2])
     fig.savefig(filename)
     plt.close()
-
-
 
 
 

### 2013-04-01 partridge/mltest/extract_papers.py

@@ -93,12 +93,23 @@ def get_best_k(paper_table):
 
 #----------------------------------------------------------------------------
 
+
+
+#set up data domain
+class_var = Orange.feature.Discrete("type")
+class_var.add_value("Research")
+class_var.add_value("Review")
+class_var.add_value("Case Study")
+
+
 def build_table( papers, features):
+
+
     #set up orange domain
-    domain = Orange.data.Domain([Orange.feature.Continuous(x) for x in features])
+    domain = Orange.data.Domain([Orange.feature.Continuous(x) for x in
+    features], class_var)
 
     paper_table = Orange.data.Table(domain)
-
     for key in ['source','title']:
         newid = Orange.feature.Descriptor.new_meta_id()
         domain.add_meta(newid, Orange.feature.String(key))
@@ -108,10 +119,16 @@ def build_table( papers, features):
         if len(paper.sentences) < 1:
             continue
 
+        if(paper.type == None):
+            continue
+
+
         inst_list = []
         sentdist = paper.sentenceDistribution(True)
         for f in features:
             inst_list.append( sentdist[f] * 100 / len(paper.sentences) )
+
+        inst_list.append(str(paper.type))
             
         inst = Orange.data.Instance(domain, inst_list)
 

### 2013-04-02 doc/final_report/design.tex
Made some changes to design chapter as suggested by Amanda and Maria

@@
 
-Given the project objectives identified above, four primary use cases were
-identified for Partridge as shown in Figure \ref{fig:use_cases}. Users can be
-identified as researchers and people interested in finding and reading
-scientific papers that interested them. This would involve querying the
-database for relevant papers, viewing metrics on the papers that have been used
-to classify them and also downloading the original paper for reading. A subset
-of users were identified as authors who might be interested in adding their own
-papers to the Partridge instance.
+Given the project objectives identified in \ref{sec:objectives}, four primary
+use cases were identified for Partridge as shown in Figure \ref{fig:use_cases}.
+Users of Partridge are likely to be researchers who want to find and read
+scientific papers. This would involve querying the database for relevant
+papers, viewing metrics on the papers that have been used to classify them and
+also downloading the original paper for reading.
+
+Authors are the subset of users who may remain interested in using the query
+functionality of Partridge, but also may wish to upload papers to Partridge and
+add them to the corpus.
 
@@
 One of the main requirements for a web server is that it responds to requests
-relatively quickly, ideally within 10 seconds or less. If they don't, the user
-may get impatient and give up trying to use the system, or in some cases, their
-web browser may timeout and stop trying to load the page. Many of the processes
-involved in extracting meaningful CoreSC information from papers are very slow
-slow. This means that processing papers during web requests is not really
-feasible, since it may take several minutes for a single paper to be annotated
-and classified. Therefore, a third core component was identified: a paper
-preprocessor service that runs on the server and converts, annotates and
-classifies papers as soon as they are uploaded.
+relatively quickly, ideally within 10 seconds or less. If the response is any
+slower than this, the user may get impatient and give up trying to use the
+system, or in some cases, their web browser may timeout and stop trying to load
+the page. Many of the processes involved in extracting meaningful CoreSC
+information from papers are very slow. This means that processing papers
+during web requests is not really feasible, since it may take several minutes
+for a single paper to be annotated and classified. Therefore, a third core
+component was identified: a paper preprocessor service that runs on the server
+and converts, annotates and classifies papers as soon as they are uploaded.
 
@@
 To further increase development speed, a Python framework for developing web
-applications called \emph{Flask\cite{flask2012}} would be used to build the web
-backend.
+applications called \emph{Flask} would be used to build the web backend. Flask
+is a ``...micro webdevelopment framework for Python.\cite{flask2012}" It
+contains a set of utilities and tools for building web applications quickly and
+effectively in Python, taking care of low level behaviours such as TCP socket
+communication and HTTP requests. These capabilities are presented in a
+Model-View-Controller pattern. Flask's capabilities and use within Partridge is
+discussed further in Section \ref{sec:backend}.
 
@@
 write in a cross-browser compatible way. To maximise compatibility and reduce
-development time, it was decided that libraries such as jQuery which are
-designed to carry out HTML manipulation behaviours in a uniform way cross all
-compatible browsers.  As of February 2013, it is estimated that Chrome and
+development time, it was decided jQuery would be used in developing the
+JavaScript frontend behaviours. jQuery is a library of utility functions
+designed for manipulating HTML documents in a uniform way across all compatible
+browsers \cite{jquery2013}. As of February 2013, it is estimated that Chrome and
 Firefox are currently the most popular web browsers, holding 50\% and 29.6\% of
@@
 \center
-\includegraphics[width=0.9\textwidth]{images/design/components_high_level.png}
+\includegraphics[width=0.6\textwidth]{images/design/components_high_level.png}
 \caption{High Level Component Layout for Partridge}
@@
 
-\subsubsection{PDF Conversion}
+\subsubsection{PDF to XML Conversion}
 
@@
 Once the paper has been split, SAPIENTA is used to annotate each sentence with
-a relevant CoreSC allocation. These labels are calculated based upon the
+a relevant CoreSC label. These labels are calculated based upon the
 sentence's location within the paper as well pairs and triplets of words found
@@
 The final stage in the preprocessor pipeline is paper classification. During
-this stage, features are extracted from the papers and used to classify the
+this stage, features wil be extracted from the papers and used to classify the
 paper in three different ways. The paper's type: case study or review paper
-etc. is determined using the presence or absence of different CoreSC labels
-within the paper and their relative proportions. The type of paper is
+etc. will be determined using the presence or absence of different CoreSC labels
+within the paper and their relative proportions. The subject of paper will be
 determined by the presence of domain specific nouns and adjectives within the
@@
 acid. The result of the paper, i.e. whether the paper was conclusive and if the
-results were positive or negative, are detected through the presence or absense
+results were positive or negative, will be detected through the presence or absense
 of words with a strong sentiment polarity as discussed by Wilson et al
@@
 permanent location on the filesystem.  The whole analysis process for a single
-paper is also wrapped within an error handling block that automatically run the
-cleanup routine if something goes wrong. This prevents the system filling up
-with invalid files. This mechanism is shown in Figure
+paper is also wrapped within an error handling block that automatically
+executes the cleanup routine if something goes wrong. This prevents the system
+filling up with invalid files. This mechanism is shown in Figure
 \ref{fig:preprocessor_overview}.
@@
 It is expected that a given Partridge instance may grow in size to contain
-thousands of individual papers that have been annotated and are available to
+tens of thousands of individual papers that have been annotated and are available to
 the web backend for inclusion into a user's search results. Reading in and
@@
 As discussed above, two or more files per paper are always stored within
-partridge so that a user can retrieve them for reading. Therefore files are
+Partridge so that a user can retrieve them for reading. Therefore files are
 kept in their own table along with a record of their type (eg. XML or PDF).
@@
 results, allowing users to download papers, can be considered a `view'. Views
-register themselves with Flask under a specific URL. When flask receives a
+register themselves with Flask under a specific URL. When Flask receives a
 request to any such URL, it automatically routes the request through to the
@@
 unscrupulous users may attempt to use to damage or purge the Partridge
-database. The system must also be capable of interpreting data retrieved from
-the database into HTML to be returned to the user's browser. The server
-mechanism utilises Flask's built in templating mechanism in order to quickly
-transform Python-specific data structures into valid HTML markup and return it
-to the user\cite{flask2012}.
+database. These are handled transparently by the SQLAlchemy library as
+discussed in Section \ref{sec:dbandsqlalchemy}. The system must also be capable
+of interpreting data retrieved from the database into HTML to be returned to
+the user's browser. The server mechanism utilises Flask's built in templating
+mechanism in order to quickly transform Python-specific data structures into
+valid HTML markup and return it to the user\cite{flask2012}.
 
@@
 top right of the form and then selects which section of the paper the term
-should appear within. This could be any of the CoreSC zones within the paper or
+should appear within. This could be any of the CoreSC labels within the paper or
 within the abstract. The user could also specify a specific author's name. Once
@@
 it and determine the paper's relevance to them. There is also a graph showing
-each of the CoreSC types and proportion within the paper. If the user is
+each of the CoreSC types and proportion within the paper (the example chart only
+shows three CoreSC label types for brevity). If the user is
 interested in the paper, they can click the Download link at the top of the
@@
 Partridge has been developed using an iterative methodology and therefore some
-of the designs descussed in this chapter have been modified during the
+of the designs discussed in this chapter have been modified during the
 development of the project. However, these designs did provide an excellent

### 2013-04-02 doc/final_report/implementation.tex
Made some changes to design chapter as suggested by Amanda and Maria
Added jqPlot bit

@@
 \section{ Web Backend }
+\label{sec:backend}
 
@@
 \subsection{Database Interaction \& SQLAlchemy}
+\label{sec:dbandsqlalchemy}
 
@@
 CoreSC makeup of papers and computing first, middle and last names from a
-single input string of an author's full name.
+single input string of an author's full name. SQLAlchemy also takes care of
+data sanitisation and conversion transparently, making sure that users cannot
+input malicious SQL code and storing special characters using relevant text
+encoding.
 
@@
 
+\subsection{ Paper Profile Page }
+
+For the most part, the Paper Profile page was quite simple to implement,
+requiring only minimal Javascript and HTML. However, rendering the CoreSC
+makeup chart for the paper was less trivial. Rather than rendering the chart
+using the server and serving a static image to the user, an interactive
+JavaScript chart was generated using jqPlot. jqPlot is a javascript extension
+of jQuery designed to help render interactive charts and graphs within a web
+browser\cite{jqplot2013}. The CoreSC makeup of the paper is calculated by the
+web backend and encoded as JSON in the profile page markup. The jqPlot code is
+then called and the CoreSC values read from the page structure, producing an
+interactive chart in the user's browser window.
+
+A pie chart was used instead of a bar chart, since it was a more concise and
+expressive way of showing the paper's CoreSC makeup within the space available
+on the page.
+
 \subsection{ Paper Upload Interface }

### 2013-04-02 doc/final_report/appendix_libs.tex
Finished describing the libraries and stuff in appendix

%----------------------------------------------------------------
%
%  Listings of libraries used and where
%
%
%----------------------------------------------------------------

Below is a listing of third party libraries and frameworks used in Partridge, along with a
brief description of their functionality and their usage within the project.
Dependencies of the libraries are not listed, but can be found on the specific
library's home page

\section{Alembic}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{https://bitbucket.org/zzzeek/alembic} \\

\textbf{ Author } & Mike Bayer \\

\textbf{ License } & MIT License \\
\hline

\end{tabular}

\subsection{Description}

Alembic is a database version control system that keeps production RDBMS
servers synchronised with the internal data structure of the application.

\subsection{Usage in Partridge}

Alembic was used to maintain the database at
\url{http://farnsworth.papro.org.uk} and keep its structure synchronised with
the development database as changes were made to Partridge.

\section{Bootstrap}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{https://github.com/twitter/bootstrap} \\

\textbf{ Author } & Mark Otto \& Jacob Thornton \\

\textbf{ License } & Apache Public License \\
\hline

\end{tabular}

\subsection{Description}

Bootstrap is a design framework that uses CSS and Javascript to provide
boilerplate code and functionality so that developers don't have to `reinvent
the wheel'.

\subsection{Usage in Partridge}

Bootstrap was used to accelerate the development of the frontend interface by
providing a basic framework to build the interface on top of.

\section{CRFSuite}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://www.chokkan.org/software/crfsuite/} \\

\textbf{ Author } & Naoaki Okazaki  \\

\textbf{ License } & Modified BSD License \\
\hline

\end{tabular}

\subsection{Description}

CRFSuite is an implementation of Conditional Random Fields, a technique used in
machine learning for labelling sequential features, rather than assuming that
features are conditionally independent as in Naive Bayesian Models.

\subsection{Usage in Partridge}

CRFSuite is used primarily in the Python version of SAPIENTA which I spent a
great deal of time working with and integrating, despite not using it in the
final submission of the project. I had to make some slight modifications to the
library to get it to compile and run as discussed in Section
\ref{sec:sapienta_implementation}.

\section{Flask}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://flask.pocoo.org/} \\

\textbf{ Author } & Armin Ronacher \\

\textbf{ License } & BSD License \\
\hline

\end{tabular}

\subsection{Description}

Flask is a web framework and utility library for the development of Python web
applications. It provides wrappers for low level TCP communication and templating
functionality from within a model-view-controller architecture.

\subsection{Usage in Partridge}
Flask is used extensively in Partridge as a platform for serving the paper
content and interfaces to the user web browser. The templating library is used
to insert data into the user interface at run time and the JSON encoder is used
to provide communication between the JavaScript running in the user's browser
and the web backend.

\section{Flask-SQLAlchemy}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://pythonhosted.org/Flask-SQLAlchemy/} \\

\textbf{ Author } & Armin Ronacher \\

\textbf{ License } & BSD License \\
\hline

\end{tabular}

\subsection{Description}
Flask-SQLAlchemy provides a bridge between Flask-based applications and the
SQLAlchemy library, it is quite lightweight and mainly used to prevent
reimplementation of boilerplate database connection code.

\subsection{Usage in Partridge}

Flask-SQLAlchemy is used in Partridge to establish a connection to the SQL
database used to store the paper data and to provide a convenient way to access
the database from the preprocessor and testing utilities.

\section{jQuery}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://jquery.com} \\

\textbf{ Author } & jQuery Foundation\\

\textbf{ License } & MIT License \\
\hlinea

\end{tabular}

\subsection{Description}

jQuery is a javascript library containing sets of utilities for manipulating
HTML web pages and managing Javascript HTTP requests to web servers. It
assists in helping developers write cross-platform compatible, stable code.

\subsection{Usage in Partridge}

jQuery is used extensively in Partridge's frontend. It is used for manipulating
the user interfaces once they have been loaded and rendered in the web browser
and to facilitate browser-server calls during search queries and file uploads.

\section{jQuery-BBQ}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://benalman.com/projects/jquery-bbq-plugin/} \\

\textbf{ Author } & Ben Alman \\

\textbf{ License } & Dual License: MIT and GPL \\
\hline

\end{tabular}

\subsection{Description}

jQuery-BBQ is a plugin to the jQuery library that facilitates the manipulation
of a web page's URI fragment through the use of JavaScript. This allows pages
that carry out a lot of clientside processing to store the application state in
the fragment and use the Browser History for navigating through changes.

\subsection{Usage in Partridge}

Partridge uses jQuery-BBQ to serialise paper queries into the URI fragment of
the query page and therefore share query results and use their browser history
to undo query constraints.

\section{jQuery-HTML5-Upload}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{https://github.com/mihaild/jquery-html5-upload} \\

\textbf{ Author } & Mikhail Dektyarev \\

\textbf{ License } & Unspecified/Public Domain \\
\hline

\end{tabular}

\subsection{Description}

jQuery HTML5 Upload is a small plugin to the jQuery library that provides a
simple JavaScript interface for asynchronously uploading files using HTML POST
requests and providing progress notifications.

\subsection{Usage in Partridge}

This library is used in the Partridge Paper Uploader view for sending papers to
the server and the progress notifier used to set up a progress bar to inform
the user of how many of the papers have been uploaded.

\section{MatPlotLib}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://matplotlib.org/} \\

\textbf{ Author } & John Hunter \\

\textbf{ License } & Python Software Foundation License \\
\hline

\end{tabular}

\subsection{Description}

MatPlotLib is a library for rendering 2D and 3D graphs from the Python
programming language. It provides a simple programming interface that allows
the generation of a wide number of different types of graph and also provides
functions for exporting the graphs as image files and storing them on the
user's hard disk.

\subsection{Usage in Partridge}

MatPlotLib was used during the implementation and testing of Partridge,
specifically when working on the Machine Learning elements of the system. It
was not used in the live Partridge system, but it was used in some of the test
scripts. Some of the graphics included in this dissertation were generated with
MatPlotLib.

\section{NLTK}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://nltk.org/} \\

\textbf{ Author } & Steven Bird, Edward Loper and Ewan Klein\\

\textbf{ License } & Apache Public License \\
\hline

\end{tabular}

\subsection{Description}

NLTK or the Natural Language Toolkit is a library for Python that provides
implementations of commonly used Natural Language Processing tools and
utilities. NLTK comes with sets of test data and pre-trained models for
convenience.

\subsection{Usage in Partridge}

The NLTK is used in Partridge's preprocessor during the Sentence Splitting
stage. It is not used in any of the other subsystems, but would have been used
to implement the Paper Topic and Paper Result classifiers had there been time.

\section{Orange}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://orange.biolab.si/} \\

\textbf{ Author } & Tomaž Curk et al. \\

\textbf{ License } & GNU General Public License \\
\hline

\end{tabular}

\subsection{Description}

Orange is a data mining library for Python, providing implementations of
commonly used machine learning algorithms. The underlying implementations are
written using native code to increase the speed of the algorithms.

\subsection{Usage in Partridge}

Orange's Random Forest Classifier is used to provide paper type classification
within the preprocessor module. It was also used for clustering the papers
during the investigation into the most effective features for classification.

\section{PDFX}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://pdfx.cs.man.ac.uk/} \\

\textbf{ Author } & Alex Constantin \\

\textbf{ License } & Other \\
\hline

\end{tabular}

\subsection{Description}
PDFX is a web service that converts PDF documents into SciXML compatible
markup. The author provides a REST API which is documented on the home page.
No code is provided, all computations are executed by the server.

\subsection{Usage in Partridge}

PDFX is used by the paper preprocessor to convert uploaded PDF documents into
XML for SAPIENTA to annotate. The PDFs are uploaded to the PDFX server using
HTTP requests.

\section{SAPIENTA}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://www.sapientaproject.com/} \\

\textbf{ Author } & Maria Liakata \\

\textbf{ License } & Other \\
\hline

\end{tabular}

\subsection{Description}
SAPIENTA is a machine learning application that provides CoreSC annotations for
papers formatted in SciXML and PubMed Central compatible markup. Although a
SAPIENTA Python library is available, it is not ready for general use, and the
web service is more reliable for paper annotation.

\subsection{Usage in Partridge}

SAPIENTA is key in paper processing. It is used to annotate the papers stored
in Partridge using CoreSC labels. Like PDFX, no SAPIENTA code is used on the
client side and communication with the remote system is carried out through
HTTP requests.

\section{SQLAlchemy}

\begin{tabular}{ | l | l | }

\hline
\textbf{ Home Page } &
\burl{http://www.sqlalchemy.org/} \\

\textbf{ Author } & Michael Bayer \\

\textbf{ License } & MIT License \\
\hline

\end{tabular}

\subsection{Description}
SQLAlchemy provides a set of functions and utilities for connecting to and
communicating with SQL database systems from the Python programming language.
It also offers an extensive Object Relation Mapper which allows the abstraction
of database entities into Python Data structures for the convenience of
developers.

\subsection{Usage in Partridge}

SQLAlchemy is used by Partridge to communicate with the paper database. A set
of data structures that derrive properties provided by this library allow
Partridge to use native Python objects to refer to entities in the database.
SQLAlchemy also carries out data encoding conversion and input sanitisation
capabilities transparently.

### 2013-04-03 doc/final_report/design.tex
Some spelling mistakes dealt with

@@
 Despite the use of an iterative development methodology, some of the key
-components within Partridge were designed up front in order to accelerate
-implementation and reduce time overheads when adding new components to the
+components within Partridge were designed 'up front' in order to accelerate
+implementation and reduce the time needed to add new components to the
 system. The components that make up Partridge and the ways in which they react
-are described and analysed below. Choices regarding the type of application,
+are described and analysed below; choices regarding the type of application,
 the target audience and the programming environment are also discussed.
@@
 
-It was decided from the outset that Partridge would be a web-based tool.
+From the outset, the aim was that Partridge would be a web-based tool.
 Web-based systems can generally be run on any computer with access to the
@@
 Partridge accessible to non-technical users and those who have aggressive
-software restrictions on their computers, such as GPs and users of public
+software restrictions on their computers, such as GPs and the users of public
 computers in libraries or on academic sites.
@@
 In order to function as a website, Partridge needed to be developed as a server
-application that produced Hyper Text Markup Language (HTML) output that a web
+application that produced Hyper Text Markup Language (HTML) output with which a web
 browser could interpret and display. The browser rendering the forms must then
 communicate with a backend system capable of querying and returning papers to
-the user based on their input. This lead to the decision to split development
+the user based on their input. This lead to the decision to split the development
 of Partridge into two core components: the Web Frontend comprising of user
@@
 system, or in some cases, their web browser may timeout and stop trying to load
-the page. Many of the processes involved in extracting meaningful CoreSC
+the page. Unfortunately, many of the processes involved in extracting meaningful CoreSC
 information from papers are very slow. This means that processing papers
@@
 open source web servers such as Apache or nginx. Common language choices
-include PHP, Python, Perl and Java, all of these languages supported by large
+include PHP, Python, Perl and Java; all of these languages are supported by large
 communities of developers and users who provide with excellent documentation
-and support if required.  For the implementation of Partridge, Python was
-selected as the programming language of choice. This was partially due to the
+and support if required.  Python was
+selected to implement Partidge. This was partially due to the
 author's familiarity with the language and also due to the availability of
@@
 environment. Python is an interpreted cross-platform language, minimising
-deployment problems and supports natively compiled C and C++ extension
+deployment problems and supports natively-compiled C and C++ extension
 libraries allowing intensive processing  and number crunching to be offloaded
@@
 
-The Web Frontend for the system would need to be written using a combination of
+The Web Frontend for the system had to be written using a combination of
 HTML markup and JavaScript. HTML is not a programming language in itself and
@@
 also downloaded from the web server and interpreted by the browser. Although
-this requires the developer to have knowledge of two extra technologies on top
-of Python, it also makes enforcing the design principle of keeping presentation
+this requires the developer to have knowledge of two extra technologies in addition to Python, it also makes enforcing the design principle of keeping presentation
 and logic separate a lot easier.
@@
 write in a cross-browser compatible way. To maximise compatibility and reduce
-development time, it was decided jQuery would be used in developing the
+development time, it was decided that jQuery would be used in developing the
 JavaScript frontend behaviours. jQuery is a library of utility functions
@@
 the market share respectively\cite{browserstats2013}. Internet Explorer is the
-third most popular browser. However, there are several well known compatibility
-issues with Internet Explorer, Microsoft themselves condemning version 6.0 of
-their browser\cite{ie6death}. For this reason, it was decided that Partridge
-would only support Firefox and Chrome. A working interface in modern editions
+third most popular browser. However, there are several well-known compatibility
+issues with Internet Explorer, Microsoft themselves condemning version 6.0\cite{ie6death}. For this reason, it was decided that Partridge
+would initially only support Firefox and Chrome; a working interface in modern editions
 of the Internet Explorer family of browsers would be a bonus.  However, no time
@@
 redundant since the web backend cannot gain any extra information from the
-paper preprocessor while a paper is still being analysed and all finished
+paper preprocessor while a paper is still being analysed. Furthermore, all finished
 papers are added to the database which the web backend has full access to
@@
 determined by the presence of domain specific nouns and adjectives within the
-paper. For example, a biology paper might contain words such as enzyme or amino
-acid. The result of the paper, i.e. whether the paper was conclusive and if the
-results were positive or negative, will be detected through the presence or absense
+paper. For example, a biology paper might contain words such as 'enzyme' or 'amino
+acid.' The result of the paper, i.e. whether the paper was conclusive and if the
+results were positive or negative, will be detected through the presence or absence
 of words with a strong sentiment polarity as discussed by Wilson et al
@@
 \label{sec:db_layout}
-It is expected that a given Partridge instance may grow in size to contain
+It is expected that Partridge may grow in size to contain
 tens of thousands of individual papers that have been annotated and are available to
-the web backend for inclusion into a user's search results. Reading in and
+the web backend for inclusion into a user's search results. Reading and
 parsing each individual XML file stored in the system is not really feasible
@@
 been added to the system. The Paper entity represents a single paper stored in
-Partridge. Information extracted by the classifiers such as the paper's type,
-topic and result are stored as part of the main paper entity. The title and
+Partridge. Information is extracted and classified by indicators such as the paper's type,
+topic and resul. This is are stored as part of the main paper entity. The title and
 topic are also stored for easy retrieval. One of the key requirements of
@@
 facilitated using the intermediary table PaperAuthors. A PaperAuthor record
-contains a boolean field used to indicate whether an author linked to a
+contains a boolean field used to indicate whether the author that is linked to a
 specific paper was the primary author on that paper.
@@
 The Flask web framework uses a model view controller-like architecture. Each
-behaviour of the server: handling paper uploads, displaying paper query
-results, allowing users to download papers, can be considered a `view'. Views
+behaviour of the server, handling paper uploads, displaying paper query
+results and allowing users to download papers, can be considered a `view'. Views
 register themselves with Flask under a specific URL. When Flask receives a
@@
 The search or `Keywords' section of the form shows a set of controls for
-specifying terms that must appear within sections of a document for it to show
+specifying terms that must appear within sections of a document in order to show
 up in the search results. The user enters a search term in the input box on the
@@
 within the abstract. The user could also specify a specific author's name. Once
-they are happy with their keywords and section, they click ``Add" and the
+they are happy with their keywords and section, they click `Add' and the
 keyword/section pair are inserted into the table on the bottom right. If they
 wish to remove a query constraint from this table, they can select it and click
-the ``Delete" button.
+the `Delete' button.
 
-Once the user is happy with their search, they can click the ``Search" button
+Once the user is happy with their search, they can click the `Search' button
 at the extreme top right of the form to carry out the query and see the
@@
 
-Once a user has made their query, the results are displayed for them to peruse
-and find relevant papers to read. Figure \ref{fig:results_mockup} shows a
-mockup of the results view. This simplistic page lists all of the papers found
-during the query in relevence order. The results are paginated so that the user
+After the user has made their query, the results are displayed for them
+to find relevant papers to read. Figure \ref{fig:results_mockup} shows a
+mockup of the results view. This page clearly lists all of the papers found
+during the query in order of relevence. The results are paginated so that the user
 does not have to wait for a large page to render. It is hoped that users will
-run specific queries that do not return a high number of results. There is a
+run such specific queries that they do not return a high number of results. There is a
 prominent link at the top of the page that allows the user to go back to the
@@
 The paper's title and author are displayed prominently in the top left hand
-corner of the page. The full abstract text is shown so that the user can read
-it and determine the paper's relevance to them. There is also a graph showing
+corner of the page. The full text of the abstract is shown so that the user can determine the paper's relevance to them. There is also a graph showing
 each of the CoreSC types and proportion within the paper (the example chart only
@@
 \subsubsection{Paper Upload Form}
-Paper uploading is another highly important user activity within Partridge.
+Paper uploading is another very important user activity within Partridge.
 Without users uploading papers, Partridge has no data to work with. It was
-therefore, very important to make paper uploading as simplistic as possible to
+therefore, very important to make paper uploading as easy as possible to
 the end user. Figure \ref{fig:paper_upload} shows Partridge's main paper upload

### 2013-04-03 doc/final_report/evaluation.tex
Some spelling mistakes dealt with

@@
 provided an induction into a professional community of academic computer
-science and allowed me as a novice to feel comfortable there.
+science and allowed me, as a novice, to feel comfortable there.
 
@@
 there were several short delays when the SAPIENTA server stopped working and
-had to be restarted. It took several weeks to collect enough data for machine
-learning for this reason.
+had to be restarted. For this reason, it took several weeks to collect enough data for machine
+learning.
 
@@
 
-During the course of the project, it became clear very quickly that there would
+During the course of the project, it quickly became clear that there would
 not be time to implement a recommendation engine as originally hoped. Such a
@@
 Partridge already fulfills many of its objectives and has also had a sizeable
-impact on the research community. However in its implementation, a number of
+impact on the research community. However,  during implementation, a number of
 topics for further research have also been uncovered.

### 2013-04-03 doc/final_report/implementation.tex
Finished describing the libraries and stuff in appendix
Some spelling mistakes dealt with

@@
 PDF documents into XML documents. Townsend \emph{et al.} (2009) liken
-converting PDF to XML to ``converting hamburgers into cows," they go on to
+converting PDF to XML to ``converting hamburgers into cows." They go on to
 explain that PDF documents do not contain any semantic data and documents lose
@@
 \subsection{Annotating with SAPIENTA}
+\label{sec:sapienta_implementation}
 
@@
 Central, work could begin on implementing a paper type classifier able to
-discriminate between ``Case Study", ``Research" and ``Review" papers. However,
+discriminate between `Case Study,' `Research' and `Review' papers. However,
 for a machine learning classifier to discriminate between classes of data, it
@@
 between the classes. For example, to discriminate between cats and dogs,
-``number of legs" is a poor feature since both species normally have 4.
+``number of legs" is a poor feature since both species normally have four.
 However, the noise that these animals make may be a good discriminative feature
@@
 
-There are several well established features used for classifying text within
+There are several well-established features used for classifying text within
 the NLP community. However, since Partridge has access to CoreSC annotations
@@
 
-All of the papers were manually identified as either a ``Case Study", a
-``Review Paper" or a ``Research Paper." They were then loaded into a script and
+All of the papers were manually identified as either a `Case Study,' a
+`Review Paper' or a `Research Paper.' They were then loaded into a script and
 clustered using their CoreSC respective compositions. K-Means silhouettes were
@@
 silhouette value. This returned a set of much stronger K silhouette values in
-general. The algorithm also determined that the combination of ``Background",
-``Motivation" and ``Method" CoreSC labels seemed to be the most
+general. The algorithm also determined that the combination of `Background,'
+`Motivation' and `Method' CoreSC labels seemed to be the most
 discriminative, providing a silhouette value of 0.63.

### 2013-04-03 doc/final_report/introduction.tex
Made some changes to design chapter as suggested by Amanda and Maria
Some spelling mistakes dealt with

@@
 information retrieval tool more apparent. The problem is even more vital for
-General Practitioners. Goldacre (2008:97) points out that ``there have been an
+General Practitioners. Goldacre (2008:97) points out that ``...there have been an
 estimated 15 million medical academic articles published so far, and 5000
@@
 
-\section{Background}
+\section{Objectives}
+\label{sec:objectives}
+Partridge's main objective is to provide reading recommendations and
+information retrieval for scientists and researchers. This should reduce the
+amount of extraneous information that users have to read for themselves by
+helping them to quickly find information specific to their interests.
+Partridge will achieve this through the use of several existing techniques in
+Natural Language Processing and utilisation of SAPIENTA as discussed above.
+
+Partridge is designed to help and facilitate researchers and authors of
+scientific papers in the following principal ways:
+
+\begin{itemize}
+\item The system should provide search within specific CoreSC regions of a given
+paper. This would allow users to find the most relevant papers to them. For
+example, a user may search for "mass spectrometer" within the methodology
+section of a paper.
+\item Partridge should allow authors and rightsholders of scientific papers to
+upload their papers to the system for inclusion into the search system. This
+would give Partridge itself more utility and would make involved authors more
+accessible.
+\item The system should provide filtering of papers based upon their
+specific domain (i.e. is the paper primarily concerned with methodology within
+an experiment in chemistry or is it about ethics in psychological studies?) and
+their results, whether the paper yielded positive, negative or inconclusive
+evidence for a hypothesis. 
+\item Depending upon the time constraints of the
+project, it was hoped that Partridge will also offer a user 'profiling' system
+that provides recommendations for researchers based on their reading history.
+This feature should help users find relevant papers more quickly or find
+research that they may have otherwise overlooked.
+\end{itemize}
+
+\section{Background \& Literature Review}
 
@@
 
-\section{ Literature Review}
-
 \subsection{Natural Language Processing}
@@
 trained using a corpus of physical chemistry and biochemistry research papers
-that were pre-processed and annotated using Core Information about Scientific
-Papers (CISP)\cite{LIAKATA10.644}.
+that were manually annotated using the Core Information about Scientific
+Papers (CISP)\cite{LIAKATA10.644} schema.
 
@@
 concepts as a three layered sentence based annotation scheme (CoreSC scheme)
-where annotations are encoded in Extended Markup Language
+where annotations are encoded pin Extended Markup Language
 (XML)\cite{LIAKATA10.644}.
-
-\section{Objectives}
-
-Partridge's main objective is to provide reading recommendations and
-information retrieval for scientists and researchers. This should reduce the
-amount of extraneous information that users have to read for themselves by
-helping them find information specific to their interests more quickly.
-Partridge will achieve this through the use of several existing techniques in
-Natural Language Processing and utilisation of SAPIENTA as discussed above.
-
-Partridge is designed to help and facilitate researchers and authors of
-scientific papers in the following principal ways:
-
-\begin{itemize}
-\item The system should provide search within specific CoreSC regions of a given
-paper. This would allow users to find the most relevant papers to them. For
-example a user may search for "mass spectrometer" within the methodology
-section of a paper.
-\item Partridge should allow authors and rightsholders of scientific papers to
-upload their papers to the system for inclusion into the search system. This
-would give Partridge itself more utility and would make involved authors more
-accessible.
-\item The system should provide filtering of papers based upon their
-specific domain (i.e. is the paper primarily concerned with methodology within
-an experiment in chemistry or is it about ethics in psychological studies?) and
-their result, whether the paper yielded positive, negative or inconclusive
-evidence for a hypothesis. 
-\item Depending upon the time constraints of the
-project, it was hoped that Partridge will also offer a user 'profiling' system
-that provides recommendations for researchers based on their reading history.
-This feature should help users find relevant papers more quickly or find
-research that they may have otherwise overlooked.a
-\end{itemize}

### 2013-04-03 doc/final_report/methodology.tex
Some spelling mistakes dealt with

@@
-Chosing an effective development methodology can play a very large part in the
+Chosing an effective development methodology is vital to the
 success or failure of a software project. A number of existing development
@@
 As an alternative to the heavyweight Waterfall approach, Beck \emph{et al.}
-came up with the principle of the Agile Manifesto, favouring a lightweight,
-responsive development model over the heavyweight slow waterfall
+came up with the principle of the Agile Manifesto, favouring a lightweight and
+responsive development model over the heavyweight, slow waterfall
 system\cite{beck2001agile}. Many of Beck's ideas focus around working in a team

### 2013-04-03 doc/final_report/report.tex
Added a whole load of stuff on testing machine algorithms
Made some crucial changes to the testing chapter and worked in intro and summary
Started writing the implementation chapter
Finished implementation section on clustering and paper type classification
Made some changes to design chapter as suggested by Amanda and Maria
Some spelling mistakes dealt with

@@
 \usepackage{lscape}
-%use natbib bibliography package
-%\usepackage[numbers]{natbib}
-%use harvard bibliography package
-%\usepackage{harvard}	
 %use captions
@@
 \usepackage{url}
+\usepackage{breakurl}
 \usepackage{subcaption}
+\usepackage{rotating}
+\usepackage{pdflscape}
 
@@
 
-I would like to take this opportunity to say thank you to both of my
+I would like to take this opportunity to thank both of my
 supervisors, Amanda Clare and Maria Liakata, for giving up so much of their
@@
 have put up with my gripes and moans throughout the duration of this project
-and without whom, I may have given up hope on my dissertation.
+and, without whom, I couldn't have achieved such an ambitious project.
 
@@
 \chapter{Testing}
+\label{chapter:testing}
 \input{testing}

### 2013-04-03 doc/final_report/testing.tex
Some spelling mistakes dealt with

@@
 reliable, expected outputs for given inputs has remained a very important part
-of the overall development process, necessary in Partridge's development.  A
+of the overall development process necessary to Partridge's development.  A
 number of testing techniques have been used in order to evaluate the individual
-behaviours of Partridge's key components both separately and the system as a
+behaviours of Partridge's key components, both separately and the system as a
 whole. This chapter discusses the techniques used to test Partridge, the
-results from these tests and any implications that these results have had upon
+results of these tests and any implications that these results have for further
 development of the project. Combining all of these testing and evaluation
-techniques provides an in depth view of how useful Partridge is and how it can
-be improved upon.
+techniques provides an in-depth view of how useful Partridge is and how it could
+be improved.
 
@@
 At the beginning of the project, Unit tests for Patridge's server and paper
-preprocessing components were written in order to test that the main bulk of
-the application worked before it was deployed to the production system at
-\url{http://farnsworth.papro.org.uk}. These tests were written and maintained
-throughout the project and occasionally had to be changed as code was
+preprocessing components were written in order to test that the main application worked before it was deployed to the production system at
+\url{http://farnsworth.papro.org.uk}. These tests were maintained
+throughout the project and occasionally had to be changed as the code was
 refactored. As each new feature was added to the system, the whole suite of
@@
 meant that calls to long-running routines and functions that already have tests
-can be validated and a fake return value sent back to the caller, without
+can be validated and a fake return value sent back to the caller without
 having to actually execute the code. This technique also allows the isolation
@@
 of supervised learning systems much more difficult to assess. Russell and
-Norvig(2010) suggest that ``a learning system is good if it produces hypotheses
+Norvig(2010) suggest that ``...a learning system is good if it produces hypotheses
 that do a good job of predicting the classification of unseen
@@
 supervised learning system, some of the example data should be kept back when
-during the training phase and instead, used as `unseen examples' and classified
+during the training phase and instead, used as `...unseen examples' and classified
 by the newly trained system to judge its accuracy
@@
 random sampling.  A 60:40 divide between training and test data is common.
-Witten explains that ``it is better to use more than half the data for
+Witten explains that ``...it is better to use more than half the data for
 training, even at the expense of test data\cite{witten2005data}."
@@
 the trade-off between True Positives(TP) and False Positives(FP) as identified
-by the classifier under evaluation. Witten(2005) explains that ROC is a method
-reappropriated from signal processing analysts who use it to visualise ``...hit
+by the classifier under evaluation. Witten (2005) explains that ROC is a method
+reappropriated from signal processing analysts who use it to visualise the ``...hit
 rate and false alarm rate over noisy communication
@@
 performance of a classifier over several train-test cycles is to be calculated.
-The average AUC for Partridge's Random Tree Paper Type classifier after is
-96.6\% after three fold validation is executed over the whole set of papers.
+The average AUC for Partridge's Random Tree Paper Type classifier is
+96.6\% after three-fold validation is executed over the whole set of papers.
 
-Comparison of this result with the above graph does show discrepancies between
-simple 60:40 proportional validation and 3-fold validation - the average
+A comparison of this result with the above graph does show discrepancies between
+simple 60:40 proportional validation and 3-fold validation; the average
 performance of the latter seems to be slightly more accurate. This may be
@@
 
-Confusion Matrices are a way of showing comprehensively which classes a machine
+Confusion Matrices are a way of comprehensively showing which classes a machine
 learning system struggles to discriminate between the most. Known classes are
@@
 These results show that Partridge's decision tree is very effective at
-classifying the three document types in its database. It is also clear however,
-that whilst the classifier is outstanding at recognising Research papers, it
-sometimes struggles to discriminate between Case Study and review papers. This
+classifying the three document types in its database. It is also clear, however,
+that whilst the classifier is outstanding at recognising research papers, it
+sometimes struggles to discriminate between case study and review papers. This
 may be because case studies can be considered a specific type of review paper
@@
 \ref{fig:fmeasure_table} show good recall, precision and f-measure for all
-three document types within Partridge. These results verify that Case Study is
+three document types within Partridge. These results verify that case study is
 the hardest document type to classify as discussed above.
@@
 
-Raymond(1999) suggests that for developers of open source projects, ``Treating
+Raymond (1999) suggests that for developers of open source projects, ``...treating
 your users as co-developers is your least-hassle route to rapid code
@@
 
-A publicly available instance of Partridge that can be accessed at
-(\url{http://farnsworth.papro.org.uk/}) was made available as soon as iteration
-1 was complete and advertised using several social media streams. This was an
-effort to attract as many users to Partridge as possible in the early stages of
-the project in order to provide user testing. It was made clear to any early
-adopting users that the system was still in development and they were
+A publicly-available version of Partridge that can be accessed at
+(\url{http://farnsworth.papro.org.uk/}). This was made available as soon as iteration
+1 was complete and advertised using several social media stream to attract as many users to Partridge as possible in the early stages of
+the project in order to provide user testing. It was made clear to any early-adopting users that the system was still in development and they were
 encouraged to submit bug reports if they experienced any problems whilst using
@@
 
-There were a few comments on how the uploader system could be improved. Users
+There were a few comments as to how the uploader system could be improved. For example, users
 were confused by the preprocessor and wondered why their paper didn't appear in
@@
 As well as finding out how Partridge performs as a system, it was interesting
-to find out how Partridge blended in to the information retrieval ecosystem around
-it and how effectively it could be used day to day or in combination with any other
+to find out how Partridge blended into the information retrieval ecosystem around
+it and how it could be effectively used day-to-day or in combination with any other
 online tools.
@@
 
-Testing has been highly effective throughout the project and any potential
+Testing throughout the project has meant that any potential
 issues with the system were identified very early on and resolved due to the

### 2013-04-03 doc/final_report/introduction.tex
Finished lit review and therefore dissertation

@@
 To assist in information processing and knowledge acquisition within the domain
-of scientific research, a new web-based tool named Partridge was designed. Its
+of scientific research, a new web-based tool named Partridge has been designed. Its
 creation and implementation are discussed in this document.
 
-\section{Objectives}
+\section{Project Objectives}
 \label{sec:objectives}
@@
 
-Partridge is designed to help and facilitate researchers and authors of
+Partridge has been designed to help and facilitate researchers and authors of
 scientific papers in the following principal ways:
@@
 \begin{itemize}
-\item The system should provide search within specific CoreSC regions of a given
+\item The system provides search within specific CoreSC regions of a given
 paper. This would allow users to find the most relevant papers to them. For
@@
 section of a paper.
-\item Partridge should allow authors and rightsholders of scientific papers to
+\item Partridge allows authors and rightsholders of scientific papers to
 upload their papers to the system for inclusion into the search system. This
@@
 accessible.
-\item The system should provide filtering of papers based upon their
+\item The system provides filtering of papers based upon their
 specific domain (i.e. is the paper primarily concerned with methodology within
@@
 \item Depending upon the time constraints of the
-project, it was hoped that Partridge will also offer a user 'profiling' system
+project, it was hoped that Partridge would also offer a user 'profiling' system
 that provides recommendations for researchers based on their reading history.
-This feature should help users find relevant papers more quickly or find
+This feature would help users find relevant papers more quickly or find
 research that they may have otherwise overlooked.
@@
 
-\subsection{ Related Works }
+\subsection{ Why do we need Partridge? }
 
 There are already a large number of information retrieval and recommendation
-systems for scientific publications. A selection of these systems were
-evaluated to find out which features work well and to identify their
-shortcomings.
+systems for scientific publications.  Many of these systems, such as AGRICOLA
+(\url{http://agricola.nal.usda.gov/}), the Cochrane
+Library(\url{http://www.thecochranelibrary.com/}) and
+EconLit(\url{http://www.aeaweb.org/econlit/index.php}) index only publications
+from predefined journals or topics (for the above examples, Agriculture,
+Biology and Economics respectively). These sites can be very helpful for
+researchers looking for literature covering specific topics. Filtering ever
+smaller collections of academic literature allows for more precision; the
+narrow subject area facilitating specialised search and indexing features that
+help researchers locate relevant publications and articles even more quickly.
+Figure \ref{fig:agricola} shows the extra search and filter controls offered by
+the AGRICOLA repository which allow the user to filter papers by audience and
+specific fields within Agriculture such as ``Animals and Livestock" and ``Food
+and Nutrition".
 
-Several online search systems specifically index scientific papers and other
-publications. One of the most publicised and well known paper search systems is
-Google Scholar (\url{http://scholar.google.com}).  As can be seen in Figure
-\ref{fig:scholar_basic}, This is an adaptation of Google's general search
-engine to specifically index and search scientific papers.  Google offers
-advanced query options specific to Scholar that allow searching by author, year
-and for words that occur only in the document title as shown in figure
-\ref{fig:scholar_advanced}. Whilst this does deal with the problem of
-`information overload' by providing fine control over the information returned
-from searches,  the user is still required to have a very good idea of what
-they are looking for in terms of keywords and/or specific authors. It is
-possible that a user would not know what they are looking for until they've
-seen it. Even if the user has a set of keywords to search for, they can only
-search the title of the paper or the content as a whole. This means that users
-who want to find a particular phrase within a CoreSC part of the paper (e.g.
-only look for this phrase in the `Result' section of the paper) are unable to
-get results at their desired level of detail.
+\begin{figure}[!h]
+\centering
+\includegraphics[width=0.5\textwidth]{images/litreview/agricola.png}
+\caption{The specific search controls and filters offered by AGRICOLA}
+\label{fig:agricola}
+\end{figure}
+
+Unfortunately, these domain specific indexing systems usually only contain a
+small subset of papers, excluding potentially crucial literature because it
+does not quite fit into the subject domain. This problem is often exacerbated
+by the decision to leave out some papers and articles because the system
+administrators do not have permission from the author or publisher to include
+them. The value of these systems to their users is often restricted by the
+small proportion of available literature that they index, forcing researchers
+to use multiple, domain specific, search engines for their queries.
+
+In contrast, there are also a number of interdisciplinary indexing system
+systems such as arXiv( \url{http://arxiv.org/}), Mendeley
+(\url{http://www.mendeley.com/research-papers/}) and JSTOR
+(\url{http://www.jstor.org/}), that try to incorporate wide ranges of papers
+from as many disciplines as possible. The traits of these systems often
+complement those of their domain-specific counterparts; they provide a
+comprehensive collection of literature but insufficient filtering and indexing
+capabilities.
+
+One of the most publicised and well known interdisciplinery scientific
+literature search systems is Google Scholar (\url{http://scholar.google.com}).
+As can be seen in Figure \ref{fig:scholar_basic}, This is an adaptation of
+Google's general search engine to specifically index and search scientific
+papers.  Google offers advanced query options specific to Scholar that allow
+searching by author, year and for words that occur only in the document title
+as shown in figure \ref{fig:scholar_advanced}. Whilst this does deal with the
+problem of `information overload' by providing fine control over the
+information returned from searches,  the user is still required to have a very
+good idea of what they are looking for in terms of keywords and/or specific
+authors. It is possible that a user would not know what they are looking for
+until they've seen it. Even if the user has a set of keywords to search for,
+they can only search the title of the paper or the content as a whole. This
+means that users who want to find a particular phrase within a CoreSC part of
+the paper (e.g.  only look for this phrase in the `Result' section of the
+paper) are unable to get results at their desired level of detail.
 
@@
 
-Social citation and recommendation engines also provide a partial solution to
-the `information overload' problem.  Services like Goodreads
+Search engines such as those discussed above are fairly useful for helping
+people to find relevant literature and information when they have some idea of
+what they are looking for. However, they demand precision in the use of
+keywords and phrases which is unattainable by most researchers. Moreover, users
+can get completely different result sets by entering synonyms. In comparison,
+Recommender Systems may perform with more accuracy and better inclusion when
+a search term cannot be clearly defined.
+
+\subsection{Recommender Systems}
+
+Adomavicius and Tuzhilin(2005) define three main types of recommender systems:
+Collaborative systems that rely upon \emph{user} data to make recommendations,
+Content-based systems that use \emph{content} indexing and feature-extraction
+to make recommendations and Hybrid systems that exploit both of these
+techniques\cite{adomavicius2005toward}.
+
+\subsubsection{Collaborative Recommender Systems}
+
+Collaborative Recommender Services like Goodreads
 (\url{http://www.goodreads.com/}) and CiteUlike
-(\url{http://www.citeulike.org/}) allow you to register your interest in
+(\url{http://www.citeulike.org/}) allow users to register their interest in
 specific authors and subjects. This allows the sites to build up a profile of
-the sorts of materials that you might be interested in and provide lists of
-recommendations as in Figure \ref{fig:social_indexes}.
+the sorts of materials that its users might be interested in and provide lists
+of recommendations as in Figure \ref{fig:social_indexes}.
 
@@
 
-        \caption{Goodreads and citeulike social recommendation systems}
+        \caption{Goodreads and citeulike social Recommender systems}
         \label{fig:social_indexes}
@@
 
-None of these systems make full use of the content within the research papers
-that they index. Those systems with filtering and recommendation capabilities
-rely upon users and their activities to provide discriminatory information
-between papers and facilitate `intelligent' behaviour. It is hoped that by
-making full use of the content within scientific papers, Patridge will offer a
-novel, reliable way of displaying relevant papers to users.
+\subsubsection{ Content-based Recommender Systems}
 
-\subsection{Natural Language Processing}
+Unlike Collaborative Recommender Systems, which have become commonplace on
+today's World Wide Web, there are very few examples of Content-based
+Recommender Systems in common use and most of them use metadata.
 
-Natural Language Processing (NLP)  is a branch of Artificial Intelligence that
-enables the automated extraction of meaningful information from texts written
-in human languages such as French or English. Liddy (2001) defines Natural
-Language Processing as:
+More generally, metadata can be said to be extra data that is used to describe
+a record but is not contained within it. In the case of literature, metadata is
+used to describe attributes of a document such as its title, author and topic.
+Although commonly used in content-based recommender systems, metadata does not
+contain enough information about its associated document to be used to draw any
+meaningful conclusions about whether the paper should recommended. There are
+also many discrepancies in the quality of metadata provided by different
+scientific journals, thus reducing the reliability of any analysis carried out
+on sets of documents from different sources\cite{palepumeta}. A better system
+should take into account the content of the whole document.
+
+One example of this comes from Mooney and Loriene(2000) who describe a
+content-based book recommender system that use Natural Language Processing
+techniques to process full text passages in order to determine similarity
+between books\cite{Mooney:2000:CBR:336597.336662}. With a sample of 20,000
+books of various genres, this system was found to give accurate
+reccomendations. Their work provides an excellent foundation for further
+research in this area.
+
+\subsubsection{ Hybrid Recommender Systems }
+
+Hybrid Recommender Systems are designed to combine the Content-based and
+Collaboration-based models, employing aspects of both techniques. Huang
+\emph{et al.}(2002) describe a graph-based approach to combine content and
+collaborative data from books, customers and transactions taken from an online
+bookseller\cite{Huang:2002:GRS:544220.544231}. Combining both sources of
+information boosted the effectiveness of the recommendation engine and
+\emph{'...the system gained improvement with respect to both precision and
+recall...' (Ibid.)} A scientific literature recommender system could make use
+of a similar hybrid technique in order to provide effective recommendations to
+researchers.
+
+\subsection{Why Does Partridge Need Natural Language Processing?}
+
+Human literature is generally written in human languages for the consumption of
+other humans. Chomsky (1956) defines a hierarchy for the classification of
+formal grammars that describe languages \cite{chomsky1956three}. Although it
+can be debated where exactly on the hierarchy human language fits (
+Reich(1969)\cite{reich1969finiteness} argues that Natural Languages can be
+considered finite state and Matthews(1979)\cite{matthews1979grammatical} argues
+that Natural Languages cannot even be considered recursively enumerable, cited
+in Kornai(1985)\cite{kornai1985}) it is clear that they are not in the same
+category as most forms of machine language. Literature written for humans must
+be interpretted for machines and this is where Natural Language Parsing is
+useful.
+
+Natural Language Processing (NLP)  is a branch of Artificial
+Intelligence that enables the automated extraction of meaningful information
+from texts written in human languages such as French or English. Liddy (2001)
+defines Natural Language Processing as:
 
@@
 classifying emotions within phrases and sentences \cite{Wilson05Polarity} and
-even within suicide notes \cite{citeulike:11077287}.
+even within suicide notes \cite{citeulike:11077287}. Laterly, NLP has been
+used to detect core scientific concepts within scientific literature.
 
-\subsection{CISP, CoreSC and SAPIENTA}
+\subsection{Natural Language Processing in Scientific Papers}
 
@@
 concepts as a three layered sentence based annotation scheme (CoreSC scheme)
-where annotations are encoded pin Extended Markup Language
-(XML)\cite{LIAKATA10.644}.
+where annotations are encoded in Extended Markup Language
+(XML)\cite{LIAKATA10.644}. An intelligent academic information retrieval system
+could utilise this information in order to provide better filtering and search
+capabilities for researchers.
+
+\section{Summary}
+
+After establishing the context and objectives of the Partridge Project, a
+number of existing information retrieval and recommendation tools for
+scientific literature were examined. A set of academic and general purpose
+search engines were critically evaluated; academic search engines found to be
+better for precision and general search engines for having a wider variety of
+indexed materials. The three core types of recommendation engines,
+Content-based, Collaboration-based and Hybrid, were discussed and it was
+concluded that much much could be gained through the use of a Hybrid
+recommendation system in Partridge. With a clear image of Partridge's
+objectives, the next section deals with choosing an effective design
+methodology.

### 2013-04-03 doc/final_report/design.tex
Corrected some tense stuff

@@
 use cases were identified for Partridge as shown in Figure \ref{fig:use_cases}.
-Users of Partridge are likely to be researchers who want to find and read
+Users of Partridge were determined to be researchers who want to find and read
 scientific papers. This would involve querying the database for relevant
@@
 
-Authors are the subset of users who may remain interested in using the query
-functionality of Partridge, but also may wish to upload papers to Partridge and
-add them to the corpus.
+Authors were defined as the subset of users who may remain interested in using
+the query functionality of Partridge, but also may wish to upload papers to
+Partridge and add them to the corpus.
 
@@
 Web-based systems can generally be run on any computer with access to the
-internet and a modern web browser. This also means that there is no need for
+internet and a modern web browser. This also means that there would be no need for
 the end user to install or configure extra software on their computers, making
@@
 application that produced Hyper Text Markup Language (HTML) output with which a web
-browser could interpret and display. The browser rendering the forms must then
+browser could interpret and display. The browser rendering the forms would then
 communicate with a backend system capable of querying and returning papers to
-the user based on their input. This lead to the decision to split the development
+the user based on their input. This led to the decision to split the development
 of Partridge into two core components: the Web Frontend comprising of user
@@
 the page. Unfortunately, many of the processes involved in extracting meaningful CoreSC
-information from papers are very slow. This means that processing papers
-during web requests is not really feasible, since it may take several minutes
+information from papers are very slow. This meant that processing papers
+during web requests was not really feasible, since it may take several minutes
 for a single paper to be annotated and classified. Therefore, a third core
@@
 open source web servers such as Apache or nginx. Common language choices
-include PHP, Python, Perl and Java; all of these languages are supported by large
-communities of developers and users who provide with excellent documentation
-and support if required.  Python was
-selected to implement Partidge. This was partially due to the
-author's familiarity with the language and also due to the availability of
-stable data mining\cite{curk05} and natural language
-processing\cite{bird2009natural} libraries for the Python programming
+include PHP, Python, Perl and Java; all of these languages are supported by
+large communities of developers and users who provide with excellent
+documentation and support if required.  Python was selected to implement
+Partidge. This was partially due to the author's familiarity with the language
+and also due to the availability of stable data mining\cite{curk05} and natural
+language processing\cite{bird2009natural} libraries for the Python programming
 environment. Python is an interpreted cross-platform language, minimising
@@
 
-The Web Frontend for the system had to be written using a combination of
-HTML markup and JavaScript. HTML is not a programming language in itself and
-doesn't contain any logic. It is merely a code representation of the interface
-to be rendered in the browser window which is interpreted once it has been
-downloaded from the web server. In order to carry out actions on the HTML such
-as validating user input and manipulating parts of the display, JavaScript is
-also downloaded from the web server and interpreted by the browser. Although
-this requires the developer to have knowledge of two extra technologies in addition to Python, it also makes enforcing the design principle of keeping presentation
+The Web Frontend for the system had to be written using a combination of HTML
+markup and JavaScript. HTML is not a programming language in itself and doesn't
+contain any logic. It is merely a code representation of the interface to be
+rendered in the browser window which is interpreted once it has been downloaded
+from the web server. In order to carry out actions on the HTML such as
+validating user input and manipulating parts of the display, JavaScript is also
+downloaded from the web server and interpreted by the browser. Although this
+requires the developer to have knowledge of two extra technologies in addition
+to Python, it also makes enforcing the design principle of keeping presentation
 and logic separate a lot easier.
@@
 designed for manipulating HTML documents in a uniform way across all compatible
-browsers \cite{jquery2013}. As of February 2013, it is estimated that Chrome and
-Firefox are currently the most popular web browsers, holding 50\% and 29.6\% of
-the market share respectively\cite{browserstats2013}. Internet Explorer is the
-third most popular browser. However, there are several well-known compatibility
-issues with Internet Explorer, Microsoft themselves condemning version 6.0\cite{ie6death}. For this reason, it was decided that Partridge
-would initially only support Firefox and Chrome; a working interface in modern editions
-of the Internet Explorer family of browsers would be a bonus.  However, no time
-was allocated to ensuring compatibility of Partridge with Internet Explorer.
+browsers \cite{jquery2013}. As of February 2013, it is estimated that Chrome
+and Firefox are currently the most popular web browsers, holding 50\% and
+29.6\% of the market share respectively\cite{browserstats2013}. Internet
+Explorer is the third most popular browser. However, there are several
+well-known compatibility issues with Internet Explorer, Microsoft themselves
+condemning version 6.0\cite{ie6death}. For this reason, it was decided that
+Partridge would initially only support Firefox and Chrome; a working interface
+in modern editions of the Internet Explorer family of browsers would be a
+bonus.  However, no time was allocated to ensuring compatibility of Partridge
+with Internet Explorer.
 
@@
 The final stage in the preprocessor pipeline is paper classification. During
-this stage, features wil be extracted from the papers and used to classify the
+this stage, features will be extracted from the papers and used to classify the
 paper in three different ways. The paper's type: case study or review paper

### 2013-04-03 doc/final_report/methodology.tex
Corrected some tense stuff

@@
 other than moving back up the waterfall to rectify mistakes after
-testing\cite{Royce:1987:MDL:41765.41801}. This model was very focused on
+testing\cite{Royce:1987:MDL:41765.41801}. This model is very focused on
 paperwork and bureaucracy, trying to maintain a paper trail and manage risk
@@
 This is most prominent in the Extreme Programming (XP) method of software
-development. Since Partridge is an individual project, XP was not really
-applicable. However, some concepts like rapid prototyping/spike work and
+development. Since developing Partridge was an individual project, XP was not
+really applicable. However, some concepts like rapid prototyping/spike work and
 iterative release cycles were used as part of the Partridge development
@@
 day or earlier. Each party present at the meeting adds their own observations
-to the notes page. This page is then reviewed at the next meeting.
+to the notes page. This page was then reviewed at the next meeting.
 

### 2013-04-15 doc/final_report/evaluation.tex
I dun added mah fixes for amanda and maria's notes

@@
 
-Why write in first person in this chapter?
+Why write in the first person in this chapter?
 
@@
 Working with the Python implementation of SAPIENTA demonstrated the importance
-of machine learning evaluation methods for testing classifiers rather than
-making assumptions about `sensible looking' output. When the application was
-run on a set of papers acquired for Partridge's corpus, it seemed to give
-sensible CoreSC classifications for the papers. However, upon further analysis
-and calculation of Python SAPIENTA's Classifier Accuracy, it was determined
-that the system was only getting 44\% of CoreSC annotations correct, an
-unacceptably low success rate. If I hadn't have run the evaluation functions on
-SAPIENTA, it would have been easy to assume that it was correctly classifying
-the papers, tainting the input papers and potentially disrupting the
-investigation into CoreSC makeup and paper type.
+of machine learning evaluation methods for testing classifiers, which are
+discussed in depth in Chapter \ref{chapter:testing}, rather than making
+assumptions about `sensible looking' output. Then the application was run on a
+set of papers acquired for Partridge's corpus, it seemed to give sensible
+CoreSC classifications for the papers. However, upon further analysis and
+calculation of Python SAPIENTA's Classifier Accuracy, it was determined that
+the system was only getting 44\% of CoreSC annotations correct, an unacceptably
+low success rate. If I hadn't have run the evaluation functions on SAPIENTA, it
+would have been easy to assume that it was correctly classifying the papers,
+tainting the input papers and potentially disrupting the investigation into
+CoreSC makeup and paper type.
 
 \subsection{User Interface}
+
 The Partridge user interface is also a great success, providing a highly usable
 and intuitive representation of the relatively complicated processes that are
-used to classify and organise the papers. The use of HTML and JavaScript
+used to classify and organise the papers. The interface took a great deal of
+tweaking and user feedback, as discussed in Section \ref{sec:user_testing}, in
+order to make it as user friendly as possible. The use of HTML and JavaScript
 interactive elements instead of static pages and synchronous calls to the web
@@
 there were several short delays when the SAPIENTA server stopped working and
-had to be restarted. For this reason, it took several weeks to collect enough data for machine
-learning.
+had to be restarted. For this reason, it took several weeks to collect enough
+data for machine learning.
 
-Unfortunately, SAPIENTA is not scheduled for improvement work until the summer
-and that means that Partridge's paper preprocessor is still not very
-scalable. If further work to Partridge is carried out, I hope to improve the
-accuracy of the Python SAPIENTA implementation to be comparable with the
-current, experimental version of the system and run paper annotations locally
-on the Partridge server.
+Over the summer, I will be working with Dr Liakata to improve the Python
+implementation of SAPIENTA. We aim to match or even surpass the performance of
+the Perl SAPIENTA implementation and build a new web service using the Python
+backend. It is possible that Partridge will use a local implementation of the
+Python SAPIENTA implementation to process and annotate large volumes of new
+papers as they are added to the corpus.
 
@@
 available for analysis. From the analysis in Section
-\ref{sec:evaluaton_learners}, it is clear that a paper's CoreSC makeup can be
+\ref{sec:evaluation_learners}, it is clear that a paper's CoreSC makeup can be
 very effective in determining which of these three classes it belongs to. The

### 2013-04-15 doc/final_report/implementation.tex
I dun added mah fixes for amanda and maria's notes

@@
 
-Implementing Partridge from a set of initial designs proved to be a
-challenging but rewarding process. There were a great number of technical
-challenges involved in building the system, a large proportion of the
-implementation time was spent working on the paper preprocessor module.
-However, some aspects of the web interface and backend were also quite
-difficult to tackle.
+Implementing Partridge from a set of initial designs proved to be a challenging
+but rewarding process. Initially, a set of research papers to be used as for
+Partridge were sourced from a number of open access journals and the Paper
+Preprocessor system constructed. The backend infrastructure for the project was
+then constructed and the web interface set up. After some initial suggestions
+from early users, a web bookmarklet was developed to allow papers to be easily
+imported from online journals such as PlOS ONE.
 
-Several libraries were used to accelerate the development and implementation of
-Partridge and avoid `reinventing the wheel.' Whenever code libraries were used,
-the role of the engineer was to be aware of the available solutions and deduce
-which was aposite to the purpose intended.
-
-\section{Paper Preprocessor}
-
-Partridge's Paper Preprocessor module was the most difficult part of the
-project to implement. From acquiring papers for use in the project to teaching
-a machine learning system to recognise different types of scientific
-publication, a number of technical challenges were encountered.
-
-\subsection{ Sourcing and Acquiring Scientific Papers}
+\section{ Sourcing and Acquiring Scientific Papers}
 
@@
 behalf to the Partridge instance. However, to speed up this process, a number
-of papers were acquired from various open access sources.
+of papers were acquired from a variety of sources.
 
 The most convenient and accessible source was the ART corpus that SAPIENTA was
-trained with\cite{citeulike:11077287}. This corpus was already stored using the
+trained with\cite{LIAKATA10.644}. This corpus was already stored using the
 CoreSC schema and had been pre-annotated. This meant that Partridge would not
@@
 corpus were all of a similar type and covered similar subject areas within the
-domain of Biochemistry. There were also approximately 260 papers in the
-collection. These papers were used to help establish a conversion process from
-PDF to annotated XML. However, they only formed part of the final corpus.
-Including a large number of papers from other sources provided a more
-comprehensive collection of data for Partridge to learn from.
+domain of Biochemistry. There were 265 papers in the collection. These papers
+were used to help establish a conversion process from PDF to annotated XML.
+However, they only formed part of the final corpus.  Including a large number
+of papers from other sources provided a more comprehensive collection of data
+for Partridge to learn from. A much larger number of papers had to be acquired
+for training and testing of the machine learning systems in the paper
+preprocessor.
 
-The `mega-journals' PLOSOne \url{http://www.plosone.org/} and arXiv
+Open Access (OA) journals are research journals that provide their papers free
+to read online, often making revenue by charging authors to publish their
+articles \cite{solomon2012study}. Many OA journals provide free read access to
+their papers, but do not permit the user of articles for data mining purposes.
+However, there are a number of large online journals that provide papers under
+Creative Commons licenses, allowing data mining, provided that attribution of
+the paper's author is provided in any derivative works. OA is a growing trend
+and it is hoped that there will soon be enough permissively licensed, OA
+literature generally available to allow Partridge to become a wide reaching and
+useful research tool.
+
+The `mega-journals' PLoSOne \url{http://www.plosone.org/} and arXiv
 \url{http://www.arxiv.org/} were suggested as sources for more open access
 articles that could be added to Partridge. Both of these sites were found to
-contain large volumes of open access papers. Most of the articles stored on the
-arXiv site were in PDF format which, as discussed below, are difficult to
-convert and annotate. However, PLOSOne use the SciXML markup language for
-papers published through their journal, which made converting and annotating
-them a lot simpler for Patridge. PLOSOne also publish all of their papers under
-the Creative Commons Share-Alike-By-Attribution license\cite{ccbyattr}. This
-meant that as long as the author information was left intact, all of the papers
-could be used for data mining purposes.
+contain large volumes of OA literature under a permissive license that allowed
+data mining. Most of the articles stored on the arXiv site were in PDF format
+which, as discussed below, are difficult to convert and annotate. However,
+PLoSOne use the Pubmed Central markup schema, which is compatible with
+SAPIENTA, for papers published through their journal, which made converting and
+annotating them for inclusion into Partridge's corpus.  PLoSOne also publish
+all of their papers under the Creative Commons Share-Alike-By-Attribution
+license\cite{ccbyattr}. As mentioned above, this meant that as long as the
+author information was left intact, all of the papers could be used for data
+mining purposes.
 
-A third mega-journal used for downloading papers was the PubMed Centrala (PMC)
+A third mega-journal used for downloading papers was the PubMed Central (PMC)
 repository \url{http://www.ncbi.nlm.nih.gov/pmc/}. Not all of
 the papers available for viewing at the PMC website are open access. However,
-they do offer a listing for the subset of open access papers available on their
+they do offer a listing for the subset of OA papers available on their
 website. The PubMed Central format is also very similar to the SciXML format
@@
 
+\section{Paper Preprocessor}
+
+With a number of papers available to use to form an initial corpus for the
+system, work on the Paper Preprocessor could begin. Partridge's Paper
+Preprocessor module was the most difficult part of the project to implement.
+From acquiring papers for use in the project to teaching a machine learning
+system to recognise different types of scientific publication, a number of
+technical challenges were encountered.
+
 \subsection{Format Conversion} Most scientific papers available on the internet
 are formatted as PDF documents. However, Partridge uses and stores documents as
-XML markup and uses the CoreSC schema by Soldatova and
-Liakata\cite{liakata2008guidelines} for annotation. Therefore some spike work
-was carried out to determine the feasibility of converting papers published as
-PDF documents into XML documents. Townsend \emph{et al.} (2009) liken
-converting PDF to XML to ``converting hamburgers into cows." They go on to
-explain that PDF documents do not contain any semantic data and documents lose
-much of their explicit structure when they are formatted in this way
-\cite{Townsend2009}.  Therefore, to convert PDF documents into an NLP-friendly
-format, some heuristics must be used to detect the document's
+XML markup and uses the CoreSC
+schema\cite{LIAKATA10.644}\cite{citeulike:10444769} for annotation.  Therefore
+some spike work was carried out to determine the feasibility of converting
+papers published as PDF documents into XML documents. Townsend \emph{et al.}
+(2009) liken converting PDF to XML to ``converting hamburgers into cows." They
+go on to explain that PDF documents do not contain any semantic data and
+documents lose much of their explicit structure when they are formatted in this
+way \cite{Townsend2009}.  Therefore, to convert PDF documents into an
+NLP-friendly format, some heuristics must be used to detect the document's
 structure\cite{pdfminer}.
@@
 The next stage was to split the text into sentences in preparation for
-processing with SAPIENTA. With the assistance of the NLTK library, a sentence
+processing with SAPIENTA, the classifier for CoreSC zones as discussed in
+Section \ref{sec:nlpsapienta}. With the assistance of the NLTK library, a sentence
 splitting subroutine was implemented. This used a machine learning algorithm
@@
 provide CoreSC annotations, scoring 44\% accuracy on average. After discussion
-with its author, it became apparent that some of the features provided in the
+with its authors, it became apparent that some of the features provided in the
 server-side version of SAPIENTA had not been implemented in the Python code
-yet. Therefore, it was necessary to switch bak to remote annotation.
+yet. It is intended that I will be employed to fix the Python SAPIENTA
+implementation during the summer. However, until it is repaired, it was
+necessary to switch back to remote annotation.
 
@@
 Central, work could begin on implementing a paper type classifier able to
-discriminate between `Case Study,' `Research' and `Review' papers. However,
-for a machine learning classifier to discriminate between classes of data, it
+discriminate between `Case Study,' `Research' and `Review' papers. This would
+allow researchers to filter papers into types, providing them with more search
+precision and hopefully better results from using Partride.
+
+For a machine learning classifier to discriminate between classes of data, it
 is necessary to choose a set of features that differ as much as possible
@@
 for each paper, an investigation was carried out into how useful CoreSC data
-can be as a feature for paper type discrimination. Every sentence in a given
-annotated paper has an associated CoreSC label. It is therefore trivial to
-calculate the proportion of a paper made up of sentences with a specified
-CoreSC type. Several papers were manually inspected and the proportions of each
-CoreSC represented within were calculated. A pattern quickly emerged between
-the types of paper and the proportions of each CoreSC within them.
+can be as a feature for paper type discrimination. As discussed in Section
+\ref{sec:nlpsapienta}, CoreSC information can be used to help users find
+phrases within very specific contexts in the paper, vastly improving the
+precision and accuracy of Partridge's search facility. Every sentence in a given
+annotated paper has an associated CoreSC label.
+
+It is therefore trivial to calculate the proportion of a paper made up of
+sentences with a specified CoreSC type. Several papers were manually inspected
+and the proportions of each CoreSC represented within were calculated. A
+pattern quickly emerged between the types of paper and the proportions of each
+CoreSC within them.
 
@@
 Before working with supervised learning systems, a preliminary experiment was
-carried out to see whether clustering papers using the K-means algorithm could
-successfully identify the paper types, thus removing the need to train and
-maintain a supervised model. This was also an excellent opportunity to explore
-the data and try and detect any inherent patterns within the papers.
+carried out to see whether clustering papers using CoreSC tags as features for
+the K-means algorithm could successfully identify the paper types, thus
+removing the need to train and maintain a supervised model. This was also an
+excellent opportunity to explore the data and try and detect any inherent
+patterns within the papers.
 
@@
 often run multiple times using a range of K values when the number of clusters
-in the data is unknown. The performance of the clustering algorithm is often
+in the data is unknown.
+
+The performance of the clustering algorithm is often
 evaluated using the K-means silhouette which is a measurement of how tightly
-the data is clustered. A low silhouette value ($K \approx 0$) suggests loose
-clustering and therefore little correlation, a high silhouette value ($K
-\approx 1$) corresponds with very tight clustering and good correlation.
+the data is clustered\cite{Rousseeuw198753}. An $s(i)$ value is calculated for
+each datum $i$ in the dataset. This is defined as:
+
+\begin{displaymath}
+s(i) = \frac{ b(i) - a(i) }{ max\{a(i), b(i)\} }
+\end{displaymath}
+
+For each $s(i)$, $a(i)$ denotes the dissimilarity of the data item to its
+neighbours in the cluster it belongs to. It is defined using a distance
+measure, in this case euclidean. Similarly, $b(i)$ denotes the lowest average dissimilarity of $i$ to
+any cluster (i.e. neighbouring clusters too). This constrains $s(i)$ such that
+$ -1 < s(i) < 1$. The average $s(i)$ for a cluster provides the cluster's
+silhouette value and an indication of how appropriately data has been
+clustered\cite{Rousseeuw198753}.
+
+A low silhouette value ($K \approx
+0$) suggests loose clustering and therefore little correlation, a high
+silhouette value ($K \approx 1$) corresponds with very tight clustering and
+good correlation.
 
@@
 `Review Paper' or a `Research Paper.' They were then loaded into a script and
-clustered using their CoreSC respective compositions. K-Means silhouettes were
+clustered using their CoreSC respective compositions.
+
+K-Means clustering relies upon the knowledge of how many clusters the data
+should fit into before the algorithm starts. However silhouettes can be used to
+evaluate a number of different $K$ values and determine which number of
+clusters best fits the data. Since there are three classes, silhouettes were
 used as a measure of how effective the clustering process was. This was
@@
 \includegraphics[width=0.8\textwidth]{implementation/cluster.png}
-\caption{Paper types rendered using Bac, Met and Mot CoreSCs}
+\caption{Paper types rendered using Bac, Met and Mot CoreSCs; Research papers
+are red, Review papers green and Case Studies blue.}
 \label{fig:clusters}
@@
 
-Clustering the papers did not seem to provide a reliable way to classify them
-by type and it was decided that better results could be obtained through the
+Due to its unsupervised behaviour, Clustering can produce very unpredictable
+results. Beyond specifying how many clusters to generate and the features to
+use in discriminating between data items, the developer has no control over
+behaviour of the k-means algorithm. In this case, there is no way to tell what
+the three categories that have been generated correspond to. It was considered
+that the clusters may correspond to the three main paper sources used: PloSONE,
+Pubmed Central and the ART Corpus. However, the clusters did not match the
+paper sources precisely either as can be seen in Figure
+\ref{fig:cluster_sources}
+
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.8\textwidth]{implementation/cluster_sources.png}
+\caption{Paper sources rendered using Bac, Met and Mot CoreSCs; PlosONE papers
+are red, ART papers green and PubMed Central papers blue}
+\label{fig:cluster_sources}
+\end{figure}
+
+Since clustering the papers did not seem to provide a reliable way to classify them
+by type, it was decided that better results could be obtained through the
 use of a supervised learning classifier instead. However, the three most

### 2013-04-15 doc/final_report/introduction.tex
I dun added mah fixes for amanda and maria's notes

@@
 
-Since the advent of the 'Digital Age' and the ability of computers to copy and
+Since the advent of the `Digital Age' and the ability of computers to copy and
 reproduce information for a negligible cost, the amount of information
@@
 Partridge will achieve this through the use of several existing techniques in
-Natural Language Processing and utilisation of SAPIENTA as discussed above.
+Natural Language Processing.
 
@@
 \begin{itemize}
-\item The system provides search within specific CoreSC regions of a given
+\item The system provides search within specific sentence-based zones of a given
 paper. This would allow users to find the most relevant papers to them. For
-example, a user may search for "mass spectrometer" within the methodology
+example, a user may search for ``mass spectrometer" within the methodology
 section of a paper.
@@
 upload their papers to the system for inclusion into the search system. This
-would give Partridge itself more utility and would make involved authors more
-accessible.
-\item The system provides filtering of papers based upon their
-specific domain (i.e. is the paper primarily concerned with methodology within
+would give Partridge itself more utility and would make the works of involved authors more
+accessible to researchers.
+\item The system provides filtering of papers based upon their type (i.e Review
+Papers, Research Papers and Case Studies). It also was hoped that Partridge would
+also provide filtering by subject domain (i.e. is the paper primarily concerned with methodology within
 an experiment in chemistry or is it about ethics in psychological studies?) and
@@
 evidence for a hypothesis. 
+\item A `paper profile' page is generated for each paper included in Partridge
+which provides graphical representation of some of the analysis carried out on
+the paper and helps the user to begin to judge the paper's content.
 \item Depending upon the time constraints of the
-project, it was hoped that Partridge would also offer a user 'profiling' system
+project, it was hoped that Partridge would also offer a user `profiling' system
 that provides recommendations for researchers based on their reading history.
@@
 Library(\url{http://www.thecochranelibrary.com/}) and
-EconLit(\url{http://www.aeaweb.org/econlit/index.php}) index only publications
+Textpresso (\url{http://www.textpresso.org/}) index only publications
 from predefined journals or topics (for the above examples, Agriculture,
-Biology and Economics respectively). These sites can be very helpful for
+Biology and Bioinformatics respectively). These sites can be very helpful for
 researchers looking for literature covering specific topics. Filtering ever
@@
 
-In contrast, there are also a number of interdisciplinary indexing system
-systems such as arXiv( \url{http://arxiv.org/}), Mendeley
-(\url{http://www.mendeley.com/research-papers/}) and JSTOR
-(\url{http://www.jstor.org/}), that try to incorporate wide ranges of papers
-from as many disciplines as possible. The traits of these systems often
-complement those of their domain-specific counterparts; they provide a
-comprehensive collection of literature but insufficient filtering and indexing
-capabilities.
+In contrast, there are also a number of interdisciplinary indexing systems and
+online journals such as arXiv( \url{http://arxiv.org/}),
+PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}),
+that try to incorporate wide ranges of papers from as many disciplines as
+possible. The traits of these systems often complement those of their
+domain-specific counterparts; they provide a comprehensive collection of
+literature but insufficient filtering and indexing capabilities.
 
@@
 they can only search the title of the paper or the content as a whole. This
-means that users who want to find a particular phrase within a CoreSC part of
-the paper (e.g.  only look for this phrase in the `Result' section of the
-paper) are unable to get results at their desired level of detail.
+means that users who want to find a particular phrase within a specific
+subsection of the paper (e.g.  only look for this phrase in the `Result'
+section of the paper) are unable to get results at their desired level of
+detail.
 
@@
 what they are looking for. However, they demand precision in the use of
-keywords and phrases which is unattainable by most researchers. Moreover, users
-can get completely different result sets by entering synonyms. In comparison,
-Recommender Systems may perform with more accuracy and better inclusion when
-a search term cannot be clearly defined.
+keywords and phrases, often leaving researchers looking for literature on highly
+specific topics frustrated. Moreover, users can get completely different result
+sets by entering synonyms. In comparison, Recommender Systems may perform with
+more accuracy and better inclusion when a search term cannot be clearly
+defined.
 
@@
 
-Collaborative Recommender Services like Goodreads
-(\url{http://www.goodreads.com/}) and CiteUlike
+Collaborative Recommender Services like Mendeley
+(\url{http://www.mendeley.com/}), ResearchGate
+(\url{http://www.researchgate.net/})  and CiteUlike
 (\url{http://www.citeulike.org/}) allow users to register their interest in
@@
 the sorts of materials that its users might be interested in and provide lists
-of recommendations as in Figure \ref{fig:social_indexes}.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/goodreads_index.png}
-                \caption{Goodreads user profile page}
-                \label{fig:goodreads_index}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/citeulike_index.png}
-                \caption{a CiteULike user profile page}
-                \label{fig:citeulike_index}
-        \end{subfigure}
-
-        \caption{Goodreads and citeulike social Recommender systems}
-        \label{fig:social_indexes}
-\end{figure}
+of recommendations.
 
@@
 requiring specific keywords or search terms. They do this by learning the
-user's profile and taking into account the preferences of their 'friends' and
+user's profile and taking into account the preferences of their `friends' and
 their browsing history. However, the above-named systems do not take into
-account the content of the paper or book. They only deal with metadata as can
-be seen in Figure \ref{fig:social_searches}. This means that important
+account the content of the paper or book. They only deal with the relationships
+between users and their reading history. This means that important
 discriminatory information that could be contained within the actual document
 content is overlooked completely.
-
-\begin{figure}[!hbt]
-        \centering
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/goodreads_search.png}
-                \caption{Goodreads advanced search page}
-                \label{fig:goodreads_search}
-        \end{subfigure}%
-        \begin{subfigure}[b]{0.50\textwidth}
-                \centering
-                \includegraphics[width=\textwidth]{images/citeulike_search.png}
-                \caption{CiteULike advanced search options}
-                \label{fig:citeulike_search}
-        \end{subfigure}
-
-        \caption{Goodreads and citeulike search only deal with metadata.}
-        \label{fig:social_searches}
-\end{figure}
 
@@
 information boosted the effectiveness of the recommendation engine and
-\emph{'...the system gained improvement with respect to both precision and
-recall...' (Ibid.)} A scientific literature recommender system could make use
+the system gained improvement with respect to both precision and
+recall \emph{(Ibid.).} A scientific literature recommender system could make use
 of a similar hybrid technique in order to provide effective recommendations to
@@
 that Natural Languages cannot even be considered recursively enumerable, cited
-in Kornai(1985)\cite{kornai1985}) it is clear that they are not in the same
+in Kornai(1985)\cite{kornai1985natural}) it is clear that they are not in the same
 category as most forms of machine language. Literature written for humans must
@@
 \subsection{Natural Language Processing in Scientific Papers}
+\label{sec:nlpsapienta}
 
@@
 trained using a corpus of physical chemistry and biochemistry research papers
-that were manually annotated using the Core Information about Scientific
-Papers (CISP)\cite{LIAKATA10.644} schema.
+that were manually annotated using the Core Scientific Concepts
+(CoreSC)\cite{LIAKATA10.644} scheme.
 
-CISP, Soldatova and Liakata (2007), is a way to formally represent core
-scientific concepts (CoreSC), e.g. background, hypothesis, method etc., that
-should be present in the articles in a logical
-ontology\cite{soldatova2007ontology}. Subsequent work implements this set of
-concepts as a three layered sentence based annotation scheme (CoreSC scheme)
-where annotations are encoded in Extended Markup Language
-(XML)\cite{LIAKATA10.644}. An intelligent academic information retrieval system
-could utilise this information in order to provide better filtering and search
-capabilities for researchers.
+CoreSC Liakata \emph{et al.} (2010), derived from earlier work in which Core
+Information about Scientific Papers (CISP) is formalised as a way of improving
+better metadata for papers\cite{soldatova2007ontology}, is a way to formally
+represent core scientific concepts (CoreSC), e.g. background, hypothesis,
+method etc., that should be present in scientific articles in a logical
+ontology\cite{LIAKATA10.644}. It is implemented as a three layered sentence
+based annotation scheme  where annotations are encoded in Extended Markup
+Language (XML). CoreSC labels can be allocated to all sentences in a
+scientific paper in order to identify which scientific concept each sentence
+encapsulates. For example, a sentence with the CoreSC label ``Hypothesis"
+conveys some expectation of an experiment or action. An example ``Hypothesis"
+identified in a Bioinformatics paper used for testing is:
+
+\begin{quotation}
+We assume that, as in the HACA process, condensation is initiated by radical
+formation, and then consider reactions of phenyl, naphthyl and anthracenyl with
+another PAH to yield for example fluoranthene or
+perylene\cite{unterreiner2004reaction}.
+\end{quotation}
+
+Alternatively, a ``Background'' CoreSC sentence may refer to prior work or
+merely declare a point of interest to the reader. An example from the same
+paper is:
+
+\begin{quotation}
+The central issue is here the formation of polycyclic aromatic hydrocarbons
+(PAHs), which are the main constituents of soot; the PAHs are also health
+hazards since they are carcinogenic\cite{unterreiner2004reaction}.
+\end{quotation}
+
+An intelligent academic information retrieval system could utilise this
+information in order to provide better filtering and search capabilities for
+researchers. The ability to search for phrases and keywords by CoreSC would
+facilitate context-aware keyword search, that allows researchers to only accept
+papers where a term appears in sentences with a specific CoreSC label. This
+could be used to greatly improve both the precision with which researchers are
+able to perform searches for scientific literature and the accuracy of those
+searches in terms of relevance to the reader.
 

### 2013-04-15 doc/final_report/methodology.tex
I dun added mah fixes for amanda and maria's notes

@@
 Having analysed some of the existing development methodologies and determined
-that most of the common methodologies were not suitable for Partridge. A custom
+that most of the common methodologies were not suitable for Partridge, a custom
 methodology was formulated and support tools chosen. Task analysis was then

### 2013-04-15 doc/final_report/report.tex
Added some images and final changes
I dun added mah fixes for amanda and maria's notes

@@
 
-A preprocessing system system that exploits existing tools such as SAPIENTA and
-PDFX was used to analyse a large sample of research papers, labelling the
-presence of core scientific concepts (CoreSCs) within each paper and extracting
-metadata. Decision trees were also trained to classify papers into categories
-such as `Research Paper', `Review Paper' and `Case Study' based upon the
-relative proportions of core scientific concepts in the papers.
+A preprocessing system that exploits existing Natural Language Processing tools
+was used to analyse a large sample of research papers, labelling the presence
+of conceptual zones within each paper and extracting metadata.  Decision trees
+were also trained to classify papers into well established type categories
+based upon the relative proportions of the types of conceptual zones
+present within the papers.
 
-A web interface was built to facilitate user search of papers based upon the
-contents of specific CoreSCs. Filtering of papers using their type as
-determined by the preprocessor was also built in and a page allowing authors and
-rightsholders to submit their own papers for analysis was created to allow
-the scientific community to extend the utility of the system.
+A web interface was built to facilitate fine grain search, making use of the
+zone information captured during preprocessing. Filtering of papers using their
+type as determined by the preprocessor was also built in. Individual papers
+returned during searches are presented in their own profile page that provides
+charts and extra metadata to help researchers to understand the paper's
+content. A page allowing authors and rightsholders to submit their own papers
+for analysis was also created to allow the scientific community to extend the
+impact and utility of the system.
+
+The machine learning systems used within the project have been evaluated and
+found to be accurate to 87.9\% when classifying a paper's type. The possibility
+of extending the machine learning capabilities of the system to categorise
+papers by subject domain and outcome of experimental results is discussed as
+well as the potential for further improvements to the user interface.
+
+A working version of the software has been made generally available at
+\url{http://farnsworth.papro.org.uk} and can be explored and used by the
+general public. It is hoped that over the coming months, the system will grow
+to become a far reaching, widely used tool for academic research.
 
@@
 
-\chapter{Evaluation}
+\chapter{Critical Evaluation}
 \input{evaluation}

### 2013-04-15 doc/final_report/testing.tex
I dun added mah fixes for amanda and maria's notes

@@
 Receiver Operating Characteristics (ROC) Charts are used to visually represent
-the trade-off between True Positives(TP) and False Positives(FP) as identified
+the trade-off between True Positives(TP); items that are correctly identified
+as a given class and False Positives(FP); items that are identified as a given
+class but are actually of aother class as identified
 by the classifier under evaluation. Witten (2005) explains that ROC is a method
@@
 These results show that Partridge's decision tree is very effective at
-classifying the three document types in its database. It is also clear, however,
-that whilst the classifier is outstanding at recognising research papers, it
-sometimes struggles to discriminate between case study and review papers. This
-may be because case studies can be considered a specific type of review paper
-and the two classes share more similar CoreSC features than they do with
-research papers.
+classifying the three document types in its database. It is also clear,
+however, that whilst the classifier is outstanding at recognising research
+papers, it sometimes struggles to discriminate between case study and review
+papers. This may be because case studies share more similar CoreSC features
+with review papers than they do with research papers.
 
@@
 \section{ User Testing } 
-
+\label{sec:user_testing}
 Raymond (1999) suggests that for developers of open source projects, ``...treating
@@
 A publicly-available version of Partridge that can be accessed at
-(\url{http://farnsworth.papro.org.uk/}). This was made available as soon as iteration
-1 was complete and advertised using several social media stream to attract as many users to Partridge as possible in the early stages of
-the project in order to provide user testing. It was made clear to any early-adopting users that the system was still in development and they were
+(\url{http://farnsworth.papro.org.uk/}). This was made available as soon as
+iteration 1 was complete and advertised using several social media stream to
+attract as many users to Partridge as possible in the early stages of the
+project in order to provide user testing. It was made clear to any
+early-adopting users that the system was still in development and they were
 encouraged to submit bug reports if they experienced any problems whilst using

### 2013-04-15 partridge/mltest/clustertest.py

@@ -21,7 +21,7 @@ from matplotlib import pyplot as plt
 
 from itertools import combinations
 
-from extract_papers import get_best_k,build_table
+from extract_papers import get_best_k,build_table, find_paper_ids
 
 #----------------------------------------------------------------------------
 
@@ -41,13 +41,44 @@ best_features = None
 
 pone_ids = []
 art_ids = []
+pubmed_ids = []
 
+print "finding paper sources..."
 
+art_dir = "/home/james/dissertation/papers/art"
+papers_dir = "/home/james/dissertation/data/processed"
+
+for root,dirs,files in os.walk(papers_dir):
+    for file in files:
+        name,ext = os.path.splitext(file)
+
+        if ext == ".xml":
+            pfile = PaperFile.query.filter(
+                    PaperFile.path.like("%%%s%%" % name)).first()
+
+            if(pfile != None):
+
+                if name.startswith("journal.p"):
+                    pone_ids.append(pfile.paper_id)
+                elif name.startswith("pmc"):
+                    pubmed_ids.append(pfile.paper_id)
+                elif os.path.exists( os.path.join(art_dir, name.split("_")[0] +
+                ".xml")):
+                    art_ids.append(pfile.paper_id)
+
+art_ids = set(art_ids)
+pubmed_ids = set(pubmed_ids)
+pone_ids = set(pone_ids)
+
+print "Found %d art papers, %d PMC papers and %d PloSOne papers" % (
+len(art_ids), len(pubmed_ids), len(pone_ids))
+
+corescs = ["Bac","Met","Mot"]
 for features in combinations(corescs, 3):
    
 
     print "Testing with features %s" % str(features)
-    paper_table = build_table(papers, features)
+    paper_table = build_table(papers, features, pone_ids, art_ids, pubmed_ids)
 
     k,score = get_best_k(paper_table)
 
@@ -67,7 +98,7 @@ for features in combinations(corescs, 3):
     fig = plt.figure()
     ax = fig.add_subplot(111, projection='3d')
 
-    colours = {"Research" : 'r', "Review" : 'g', "Case Study" : 'b'}
+    colours = {"pone" : 'r', "art" : 'g', "pubmed" : 'b', "other" : 'y'}
     j = 0
 
     clusters = km.clusters
@@ -75,7 +106,7 @@ for features in combinations(corescs, 3):
     for i in range(0, len(paper_table)):
 
[…]

### 2013-04-15 partridge/mltest/extract_papers.py

@@ -101,8 +101,13 @@ class_var.add_value("Research")
 class_var.add_value("Review")
 class_var.add_value("Case Study")
 
+src_var = Orange.feature.Discrete("source")
+src_var.add_value("pone")
+src_var.add_value("art")
+src_var.add_value("pubmed")
+src_var.add_value("other")
 
-def build_table( papers, features):
+def build_table( papers, features, pone_ids, art_ids, pubmed_ids):
 
 
     #set up orange domain
@@ -129,15 +134,21 @@ def build_table( papers, features):
             inst_list.append( sentdist[f] * 100 / len(paper.sentences) )
 
         inst_list.append(str(paper.type))
+
+
             
         inst = Orange.data.Instance(domain, inst_list)
 
         inst['title'] = str(paper.title.encode('ascii', 'ignore'))
-
-        #if( paper.id in pone_ids):
-        #    inst['source'] = "pone"
-        #elif( paper.id in art_ids):
-        #    inst['source'] = "art"
+        
+        if( paper.id in pone_ids):
+            inst['source'] = "pone"
+        elif( paper.id in art_ids):
+            inst['source'] = "art"
+        elif (paper.id in pubmed_ids):
+            inst['source'] = "pubmed"
+        else:
+            inst['source'] = "other"
 
         paper_table.append(inst)
 

### 2013-04-17 doc/final_report/design.tex
Added some punctuation corrections

@@
 Despite the use of an iterative development methodology, some of the key
-components within Partridge were designed 'up front' in order to accelerate
+components within Partridge were designed `up front' in order to accelerate
 implementation and reduce the time needed to add new components to the
@@
 determined by the presence of domain specific nouns and adjectives within the
-paper. For example, a biology paper might contain words such as 'enzyme' or 'amino
+paper. For example, a biology paper might contain words such as `enzyme' or `amino
 acid.' The result of the paper, i.e. whether the paper was conclusive and if the

### 2013-04-17 doc/final_report/report.tex
Added some punctuation corrections

@@
 I would like to take this opportunity to thank both of my
-supervisors, Amanda Clare and Maria Liakata, for giving up so much of their
+supervisors, Dr Amanda Clare and Dr Maria Liakata, for giving up so much of their
 time to support me in designing and developing this project.

### 2013-04-18 doc/final_report/report.tex
Finished title page added wordcount etc

@@
 Thanks to the users who tested Partridge once it was made generally available
-and for their feedback in the form of bug reports and suggestions.
+and for their feedback in the form of bug reports and suggestions. Especially
+my close friends Alexander Brown and Douglas Eggleton who provided a great deal
+of feedback throughout the project. I would also like to thank Matt Pugh for
+helping me decide on the name of the project.
 
@@
 and, without whom, I couldn't have achieved such an ambitious project.
+
+\begin{center}
+\line(1,0){250}
+\end{center}
+
+The image on the front cover is an illustration of a Partridge, donated to the
+public domain by Pearson Scott Foresman in 2007. A list of their donations can
+be found at
+\url{http://commons.wikimedia.org/wiki/Commons:Pearson_Scott_Foresman}
 

### 2013-04-18 setup.py
added some dependencies to setup.py and detailed installation instructions

@@ -12,7 +12,8 @@ setup(
             'nltk>=2.0.4',
             'progressbar>=2.3',
             'pyinotify>=0.9.4',
-            'alembic>=0.4.2'],
+            'alembic>=0.4.2',
+            'Orange>=2.6'],
 
     #program entrypoints
     entry_points ={

### 2013-04-23 partridge/tools/paperstore.py
Started building remote data processing intrastructure

@@ -28,6 +28,8 @@ class PaperParser:
     def parseFileObject(self, f):
         self.doc = xml.dom.minidom.parse(f)
 
+    def parseString(self, s):
+        self.doc = xml.dom.minidom.parseString(s)
 
     def parsePaper(self, filename):
         """Parse a paper but don't store it"""
@@ -47,9 +49,13 @@ class PaperParser:
 
         #add authors
         paper.authors.extend(self.extractAuthors())
-        
-        #get sentence information
-        paper.sentences.extend( self.extractSentences() )
+
+        sentences = self.extractSentences()
+
+        for text,coresc in sentences:
+            sent = Sentence(text=text,coresc=coresc)
+            db.session.add(sent)
+            paper.sentences.append(sent)
 
         #store the updated database info
         db.session.add(paper)
@@ -66,13 +72,14 @@ class PaperParser:
             s = annoEl.parentNode
             annoType = annoEl.getAttribute("type")
 
-            #store sentence information
-            sent = Sentence(text=self.extractText(s),
-                coresc=annoType)
+            yield (self.extractText(s), annoType)
 
-            db.session.add(sent)
+    def extractRawSentences(self):
+        """Extract sentence data without coresc information"""
+        
+        for s in self.doc.getElementsByTagName("s"):
+            yield self.extractText(s)
 
-            yield sent
 
     def extractAbstract(self):
         """Extract the paper abstract from xml"""

### 2013-04-23 partridge/tools/split.py

@@ -18,8 +18,6 @@ blacklist = Set(['journal-id', 'journal-meta','article-id','article-categories'
 'copyright-statement', 'copyright-year','counts','s','subj-group','author-notes'
 'title','ref-list','ack','meta'])
 
-logging.basicConfig(level=logging.DEBUG)
-
 SPLITTER_PATH = str(os.path.join(config['MODELS_DIR'], "splitter.dat"))
 
 class SentenceSplitter:

### 2013-04-23 partridge/util/client.py

@@ -1,0 +1,34 @@
+from partridge.util.subjects import parse_paper
+
+from multiprocessing import Pool
+import cPickle
+
+from multiprocessing.managers import BaseManager
+
+class QueueManager(BaseManager):
+    pass
+
+if __name__ == "__main__":
+
+    QueueManager.register("qsize")
+    QueueManager.register("get_work")
+    qm = QueueManager(address=("",1234), authkey="icecream")
+    qm.connect()
+
+
+    queue = qm.qsize()
+
+    batch_size = 12
+
+    p = Pool()
+
+    print qm.qsize()._getvalue()
+
+    while qm.qsize() > 0:
+        print "Trying to get %d papers" % batch_size
+
+        batch = cPickle.loads(qm.get_work(batch_size)._getvalue())
+        
+        print len(batch)
+
+        p.map(parse_paper, batch)

### 2013-04-23 partridge/util/manager.py

@@ -1,0 +1,79 @@
+"""System for distributing NLTK work to remote clients
+"""
+
+import nltk
+import os
+import logging
+import cPickle
+import zlib
+
+from multiprocessing import Queue
+from multiprocessing.managers import BaseManager
+
+from partridge.util.subjects import labels
+
+from partridge.tools.split import SentenceSplitter
+
+class QueueManager(BaseManager):
+    pass
+
+paper_root = "/home/james/dissertation/papers"
+
+def get_uptox_items( x, queue):
+    
+    work = []
+    i=0
+
+    while( (i < x ) & (not queue.empty()) ):
+        filename = queue.get()
+        dirname = os.path.basename(os.path.dirname(filename))
+        label = labels[dirname]
+        
+        with open(filename,'rb') as f:
+            data = zlib.compress(f.read())
+
+        i += 1
+
+        work.append( ( filename, label, data) )
+
+    return cPickle.dumps(work)
+
+
+if __name__ == "__main__":
+    
+    queue = Queue()
+    QueueManager.register("qsize", lambda:queue.qsize())
+    QueueManager.register("get_work", lambda x: get_uptox_items(x, queue))
+    qm = QueueManager(address=("", 1234), authkey="icecream")
+
+
+    print "Finding all papers..."
+
+    for root,dirs,files in os.walk(paper_root):
+
+        for file in files:
+            if file.endswith("_split.xml"):
+                print "Found a paper %s" % file
+
+                queue.put(os.path.join(root,file))
+
+            elif file.endswith(".xml"):
+                print "Found an unsplit paper"
+
+                fname,ext = os.path.splitext(file)
+
+                splitfile = os.path.join(root, fname + "_split" + ext)
+
+                if os.path.exists(splitfile):
+                    print "Split file exists for this paper"
+                else:
+                    s = SentenceSplitter()
+                    s.split(os.path.join(root,file), splitfile)
+                    queue.put(splitfile)
+
+    print queue.qsize()
+
+    print "Starting server..."
+
+    s = qm.get_server()
+    s.serve_forever()

### 2013-04-23 partridge/util/subjects.py

@@ -1,0 +1,76 @@
+import nltk
+import os
+import logging
+import cPickle
+import zlib
+
+from multiprocessing import Pool
+
+from partridge.models import db
+from partridge.models.doc import Paper, PaperFile, Sentence, C_ABRV
+from partridge.config import config
+
+from partridge.tools.paperstore import PaperParser
+from partridge.tools.split import SentenceSplitter
+
+from flask import Flask
+
+from collections import Counter
+
+app = Flask(__name__)
+app.config.update(config)
+
+db.app = app
+db.init_app(app)
+
+corescs = C_ABRV.keys()
+
+paper_root = "/home/james/dissertation/papers"
+
+labels = {
+"plos_maths" : "Mathematics", 
+"plos_compsci" : "Information Technology",
+"plos_physics" : "Physics"
+}
+
+
+
+
+
+
+
+
+def process_file( file ):
+    """Process a paper file in the queue"""
+
+    if file.endswith("_split.xml"):
+        print "Found a paper %s" % file
+        parse_paper( file )
+
+    elif file.endswith(".xml"):
+        print "Found an unsplit paper"
+
+        fname,ext = os.path.splitext(file)
+
+        splitfile = fname + "_split" + ext
+
+        if os.path.exists(splitfile):
+            print "Split file exists for this paper"
+        else:
+            s = SentenceSplitter()
+            s.split(file, splitfile)
+
+            parse_paper( splitfile)
+
+
+if __name__ == "__main__":
+
+    papers = []
+
+    p = Pool()
+
+    for root,dirs,files in os.walk(paper_root):
+        p.map( process_file, [os.path.join(root,file) for file in files])
+
+logging.basicConfig(level=logging.INFO)
+

### 2013-04-23 partridge/util/client.py
Updated remote worker to now extract interesting POS words

@@ -2,6 +2,7 @@ from partridge.util.subjects import parse_paper
 
 from multiprocessing import Pool
 import cPickle
+import zlib
 
 from multiprocessing.managers import BaseManager
 
@@ -12,6 +13,8 @@ if __name__ == "__main__":
 
     QueueManager.register("qsize")
     QueueManager.register("get_work")
+    QueueManager.register("return_result")
+
     qm = QueueManager(address=("",1234), authkey="icecream")
     qm.connect()
 
@@ -29,6 +32,14 @@ if __name__ == "__main__":
 
         batch = cPickle.loads(qm.get_work(batch_size)._getvalue())
         
-        print len(batch)
+        results = p.map(parse_paper, batch)
 
-        p.map(parse_paper, batch)
+        print "Returning results of batch to server"
+
+        zippedlist = zlib.compress(cPickle.dumps(results))
+
+        qm.return_result(zippedlist)
+
+
+
+

### 2013-04-23 partridge/util/manager.py

@@ -34,16 +34,31 @@ def get_uptox_items( x, queue):
 
         i += 1
 
-        work.append( ( filename, label, data) )
+        work.append( ( os.path.basename(filename), label, data) )
 
     return cPickle.dumps(work)
+
+resultdir = "/home/james/dissertation/results"
+
+def done_papers( zippedlist ):
+        results = cPickle.loads(zlib.decompress(zippedlist))
+
+        for result in results:
+            print "Storing results for %s" % result[0]
+            with open(os.path.join(resultdir, result[0]), 'wb') as f:
+                cPickle.dump(result, f)
+                
 
 
 if __name__ == "__main__":
     
     queue = Queue()
+    done = Queue()
+
+
     QueueManager.register("qsize", lambda:queue.qsize())
     QueueManager.register("get_work", lambda x: get_uptox_items(x, queue))
+    QueueManager.register("return_result", lambda: done_papers)
     qm = QueueManager(address=("", 1234), authkey="icecream")
 
 
@@ -55,7 +70,10 @@ if __name__ == "__main__":
             if file.endswith("_split.xml"):
                 print "Found a paper %s" % file
 
-                queue.put(os.path.join(root,file))
+                if( os.path.exists( os.path.join(resultdir, file))):
+                    print "Already have a result for %s. Skipping..." % file
+                else:
+                    queue.put(os.path.join(root,file))
 
             elif file.endswith(".xml"):
                 print "Found an unsplit paper"

### 2013-04-23 partridge/util/subjects.py

@@ -33,11 +33,59 @@ labels = {
 "plos_physics" : "Physics"
 }
 
+interesting_tags = ['NNP', 'NN', 'JJ']
+
+def parse_paper( (filename, label, data) ):
+    
+    print "Parsing %s" % filename
+
+    paperstring = zlib.decompress(data)
+
+    p = PaperParser()
+    p.parseString(paperstring)
+
+    features = extract_features(p)
+
+    return (filename, label, features)
 
 
 
+def extract_features( paper_parser ):
+    """Use the paper parser object to extract features"""
+    wordfreq = {}
+    
+    print "Extracting sentences from paper..." 
+
+    for sentence in paper_parser.extractRawSentences():
+        tokens = nltk.word_tokenize(sentence)
+        tagged = nltk.pos_tag(tokens)
+
+        for word,tag in tagged:
+            
+            if (tag in interesting_tags) & (len(word) > 1):
+                if word not in wordfreq:
+                    wordfreq[word] = 1
+                else:
+                    wordfreq[word] += 1
+
+    return wordfreq
 
 
+def parse_paper_file( filename ):
+
+    print "Parsing %s..." % filename
+
+    dirname = os.path.basename(os.path.dirname(filename))
+    label = labels[dirname]
+
+    p = PaperParser()
+    p.parsePaper(filename)
+
+    features = extract_features(p)
+
+    return (filename, label, features)
+    
+                
 
 
 def process_file( file ):
@@ -45,7 +93,7 @@ def process_file( file ):
 
     if file.endswith("_split.xml"):
         print "Found a paper %s" % file
-        parse_paper( file )
+        parse_paper_file( file )
 
     elif file.endswith(".xml"):
         print "Found an unsplit paper"
@@ -60,7 +108,7 @@ def process_file( file ):
             s = SentenceSplitter()
             s.split(file, splitfile)
 
-            parse_paper( splitfile)
+            parse_paper_file( splitfile)
 
 
 if __name__ == "__main__":

### 2013-04-23 partridge/util/client.py
fixed client stopping condition

@@ -27,7 +27,7 @@ if __name__ == "__main__":
 
     print qm.qsize()._getvalue()
 
-    while qm.qsize() > 0:
+    while qm.qsize()._getvalue() > 0:
         print "Trying to get %d papers" % batch_size
 
         batch = cPickle.loads(qm.get_work(batch_size)._getvalue())

### 2013-04-23 partridge/util/manager.py

@@ -58,7 +58,7 @@ if __name__ == "__main__":
 
     QueueManager.register("qsize", lambda:queue.qsize())
     QueueManager.register("get_work", lambda x: get_uptox_items(x, queue))
-    QueueManager.register("return_result", lambda: done_papers)
+    QueueManager.register("return_result", done_papers)
     qm = QueueManager(address=("", 1234), authkey="icecream")
 
 

### 2013-04-23 partridge/util/manager.py
Sort of got classifier to train

@@ -10,7 +10,7 @@ import zlib
 from multiprocessing import Queue
 from multiprocessing.managers import BaseManager
 
-from partridge.util.subjects import labels
+from partridge.util.subjects import labels, resultdir
 
 from partridge.tools.split import SentenceSplitter
 
@@ -38,7 +38,6 @@ def get_uptox_items( x, queue):
 
     return cPickle.dumps(work)
 
-resultdir = "/home/james/dissertation/results"
 
 def done_papers( zippedlist ):
         results = cPickle.loads(zlib.decompress(zippedlist))

### 2013-04-23 partridge/util/subjects.py

@@ -26,6 +26,7 @@ db.init_app(app)
 corescs = C_ABRV.keys()
 
 paper_root = "/home/james/dissertation/papers"
+resultdir = "/home/james/dissertation/results"
 
 labels = {
 "plos_maths" : "Mathematics", 
@@ -47,6 +48,22 @@ def parse_paper( (filename, label, data) ):
     features = extract_features(p)
 
     return (filename, label, features)
+
+
+def collect_test_samples():
+
+    results = []
+    
+    for root, dirs, files in os.walk(paper_root):
+        
+        for file in files:
+
+            if file.endswith("_split.xml"):
+                #see if there is a results file for this file
+                if not os.path.exists( os.path.join(resultdir, file)):
+                    results.append( os.path.join(root,file) )
+
+    return results
 
 
 

### 2013-04-23 partridge/util/train_nbc.py

@@ -1,0 +1,113 @@
+"""Train a Naive Bayes Filter using the results from the feature extraction"""
+
+from __future__ import division
+
+import nltk
+import os
+import cPickle
+
+
+from nltk.probability import ELEProbDist, FreqDist
+
+from nltk import NaiveBayesClassifier
+
+from collections import defaultdict
+
+
+from partridge.tools.paperstore import PaperParser
+from partridge.util.manager import resultdir
+from partridge.util.subjects import labels, collect_test_samples
+
+
+samplecount = 0
+
+def get_label_probdist(labelled_features):
+    label_fd = FreqDist()
+    for item,counts in labelled_features.items():
+        for label in labels.values():
+            if counts[label] > 0:
+                label_fd.inc(label)
+
+    label_probdist = ELEProbDist(label_fd)
+    return label_probdist
+
+
+def get_feature_probdist(labelled_features):
+    feature_freqdist = defaultdict(FreqDist)
+    feature_values = defaultdict(set)
+    num_samples = samplecount / 2
+    for token, counts in labelled_features.items():
+        for label in labels.values():
+            feature_freqdist[label, token].inc(True, count=counts[label])
+            feature_freqdist[label, token].inc(None, num_samples - counts[label])
+            feature_values[token].add(None)
+            feature_values[token].add(True)
+    for item in feature_freqdist.items():
+        print item[0],item[1]
+    feature_probdist = {}
+    for ((label, fname), freqdist) in feature_freqdist.items():
+        probdist = ELEProbDist(freqdist, bins=len(feature_values[fname]))
+        feature_probdist[label,fname] = probdist
+    return feature_probdist
+
+
+
+if __name__ == "__main__":
+
+
+    label_count = {labels[x]:0 for x in labels }
+
+    labelled_features = {}
+
+    #collect test data for analysis of the classifier
+    test_samples = collect_test_samples()
+
+    print "Found %d test samples" % len(test_samples)
+    
+    for root, dirs, files in os.walk(resultdir):
+    
+        for file in files:
+            print "Loading file %s " % file
+
+
+            #increment sample count
+            samplecount += 1
+
+            with open(os.path.join(root,file),'rb') as f:
+                fname, label, features = cPickle.load(f)
+
+            for word in features:
+                
+                if word not in labelled_features:
+                    labelled_features[word] = label_count
+                
+                labelled_features[word][label] += 1
+
[…]

### 2013-04-23 partridge/util/client.py
Added zlib compression to all ipc comms

@@ -30,7 +30,7 @@ if __name__ == "__main__":
     while qm.qsize()._getvalue() > 0:
         print "Trying to get %d papers" % batch_size
 
-        batch = cPickle.loads(qm.get_work(batch_size)._getvalue())
+        batch = cPickle.loads(zlib.decompress(qm.get_work(batch_size)._getvalue()))
         
         results = p.map(parse_paper, batch)
 

### 2013-04-23 partridge/util/manager.py

@@ -30,13 +30,13 @@ def get_uptox_items( x, queue):
         label = labels[dirname]
         
         with open(filename,'rb') as f:
-            data = zlib.compress(f.read())
+            data = f.read()
 
         i += 1
 
         work.append( ( os.path.basename(filename), label, data) )
 
-    return cPickle.dumps(work)
+    return zlib.compress(cPickle.dumps(work))
 
 
 def done_papers( zippedlist ):

### 2013-04-23 partridge/util/subjects.py

@@ -40,10 +40,8 @@ def parse_paper( (filename, label, data) ):
     
     print "Parsing %s" % filename
 
-    paperstring = zlib.decompress(data)
-
     p = PaperParser()
-    p.parseString(paperstring)
+    p.parseString(data)
 
     features = extract_features(p)
 
@@ -80,6 +78,7 @@ def extract_features( paper_parser ):
         for word,tag in tagged:
             
             if (tag in interesting_tags) & (len(word) > 1):
+                
                 if word not in wordfreq:
                     wordfreq[word] = 1
                 else:

### 2013-04-23 partridge/util/train_nbc.py

@@ -35,15 +35,14 @@ def get_label_probdist(labelled_features):
 def get_feature_probdist(labelled_features):
     feature_freqdist = defaultdict(FreqDist)
     feature_values = defaultdict(set)
-    num_samples = samplecount / 2
+    num_samples = samplecount
     for token, counts in labelled_features.items():
         for label in labels.values():
             feature_freqdist[label, token].inc(True, count=counts[label])
             feature_freqdist[label, token].inc(None, num_samples - counts[label])
             feature_values[token].add(None)
             feature_values[token].add(True)
-    for item in feature_freqdist.items():
-        print item[0],item[1]
+
     feature_probdist = {}
     for ((label, fname), freqdist) in feature_freqdist.items():
         probdist = ELEProbDist(freqdist, bins=len(feature_values[fname]))
@@ -79,9 +78,9 @@ if __name__ == "__main__":
             for word in features:
                 
                 if word not in labelled_features:
-                    labelled_features[word] = label_count
+                    labelled_features[word.lower()] = label_count
                 
-                labelled_features[word][label] += 1
+                labelled_features[word.lower()][label] += features[word]
 
             print "Currently at %d distinct tokens and %d papers" % (
                 len(labelled_features), samplecount)

### 2013-04-23 partridge/util/subjects.py
Now only interested in POS tagging of all documents

@@ -43,9 +43,22 @@ def parse_paper( (filename, label, data) ):
     p = PaperParser()
     p.parseString(data)
 
-    features = extract_features(p)
+    sentences = []
 
-    return (filename, label, features)
+    #return pos tagged sentences
+    for sentence in p.extractRawSentences():
+        tokens = nltk.word_tokenize(sentence)
+        tagged = nltk.pos_tag(tokens)
+
+        sentences.append(tagged)
+
+    print "Found %d sentences in %s" %(len(sentences), filename)
+
+    return (filename,sentences)
+
+
+    #features = extract_features(p)
+    #return (filename, label, features)
 
 
 def collect_test_samples():

### 2013-04-23 partridge/util/subjects.py
safety now sorted

@@ -15,7 +15,10 @@ from partridge.tools.split import SentenceSplitter
 
 from flask import Flask
 
-from collections import Counter
+try:
+    from collections import Counter
+except:
+    from partridge.utils.counter import Counter
 
 app = Flask(__name__)
 app.config.update(config)

### 2013-04-23 partridge/util/subjects.py
fixed counter import

@@ -18,7 +18,7 @@ from flask import Flask
 try:
     from collections import Counter
 except:
-    from partridge.utils.counter import Counter
+    from partridge.util.counter import Counter
 
 app = Flask(__name__)
 app.config.update(config)

### 2013-04-24 partridge/util/subjects.py
improved feature extraction

@@ -34,10 +34,10 @@ resultdir = "/home/james/dissertation/results"
 labels = {
 "plos_maths" : "Mathematics", 
 "plos_compsci" : "Information Technology",
-"plos_physics" : "Physics"
+"plos_physics" : "Physics",
+"plos_biochem" :" Biochemistry"
 }
 
-interesting_tags = ['NNP', 'NN', 'JJ']
 
 def parse_paper( (filename, label, data) ):
     

### 2013-04-24 partridge/util/client.py
Updated client address for laptop as master server

@@ -15,7 +15,7 @@ if __name__ == "__main__":
     QueueManager.register("get_work")
     QueueManager.register("return_result")
 
-    qm = QueueManager(address=("",1234), authkey="icecream")
+    qm = QueueManager(address=("ravey.zapto.org",1234), authkey="icecream")
     qm.connect()
 
 

### 2013-04-24 partridge/util/client.py
updated the client application

@@ -15,7 +15,7 @@ if __name__ == "__main__":
     QueueManager.register("get_work")
     QueueManager.register("return_result")
 
-    qm = QueueManager(address=("ravey.zapto.org",1234), authkey="icecream")
+    qm = QueueManager(address=("localhost",1234), authkey="icecream")
     qm.connect()
 
 

### 2013-04-24 partridge/util/manager.py

@@ -17,7 +17,7 @@ from partridge.tools.split import SentenceSplitter
 class QueueManager(BaseManager):
     pass
 
-paper_root = "/home/james/dissertation/papers"
+paper_root = "/home/james/partridge/papers"
 
 def get_uptox_items( x, queue):
     

### 2013-04-24 partridge/util/subjects.py

@@ -28,13 +28,17 @@ db.init_app(app)
 
 corescs = C_ABRV.keys()
 
-paper_root = "/home/james/dissertation/papers"
-resultdir = "/home/james/dissertation/results"
+paper_root = "/home/james/partridge/papers"
+resultdir = "/home/james/partridge/results"
 
 labels = {
 "plos_maths" : "Mathematics", 
 "plos_compsci" : "Information Technology",
-"plos_physics" : "Physics"
+"plos_physics" : "Physics",
+"plos_dna" : "DNA",
+"plos_zoology" : "Zoology",
+"plos_genetics" : "Genetics",
+"plos_sociology" : "Sociology",
 }
 
 interesting_tags = ['NNP', 'NN', 'JJ']

### 2013-04-28 partridge/util/subjects.py
Using tf;idf to classify subjects

@@ -35,7 +35,7 @@ labels = {
 "plos_maths" : "Mathematics", 
 "plos_compsci" : "Information Technology",
 "plos_physics" : "Physics",
-"plos_biochem" :" Biochemistry"
+"plos_biochem" :" Biochemistry",
 "plos_dna" : "DNA",
 "plos_zoology" : "Zoology",
 "plos_genetics" : "Genetics",

### 2013-04-28 doc/bcspaper/article.tex
Created bcs paper directory

%%%%%%%%%%%%%%%%%%%% author.tex %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% sample root file for your "contribution" to a contributed volume
%
% Use this file as a template for your own input.
%
%%%%%%%%%%%%%%%% Springer %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[graybox]{svmult}
%
%% choose options for [] as required from the list
%% in the Reference Guide
%
\usepackage{mathptmx}       % selects Times Roman as basic font
\usepackage{helvet}         % selects Helvetica as sans-serif font
\usepackage{courier}        % selects Courier as typewriter font
\usepackage{type1cm}        % activate if the above 3 fonts are
                             % not available on your system
%
\usepackage{makeidx}         % allows index generation
\usepackage{graphicx}        % standard LaTeX graphics tool
%                             % when including figure files
\usepackage{multicol}        % used for the two-column index
\usepackage[bottom]{footmisc}% places footnotes at page bottom
%
%% see the list of further useful packages
%% in the Reference Guide
%
\makeindex             % used for the subject index
%                       % please use the style svind.ist with
%                       % your makeindex program
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
\begin{document}

\title{Contribution Title}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Name of First Author and Name of Second Author}
% Use \authorrunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
\and Name of Second Author \at Name, Address of Institute \email{name@email.address}}
%
% Use the package "url.sty" to avoid
% problems with special characters
% used in your e-mail or web address
%
\maketitle

\abstract*{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter. As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.
Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

\abstract{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content. The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access. This allows unregistered users to read the abstract as a teaser for the complete chapter. As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.\newline\indent
Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf. source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript. Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}

\section{Section Heading}
\label{sec:1}
Use the template \emph{chapter.tex} together with the Springer document class SVMono (monograph-type books) or SVMult (edited books) to style the various elements of your chapter content in the Springer layout.

Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations. And please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

\section{Section Heading}
\label{sec:2}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

Use the standard \verb|equation| environment to typeset your equations, e.g.
%
\begin{equation}
a \times b = c\;,
\end{equation}
%
however, for multiline equations we recommend to use the \verb|eqnarray|
environment\footnote{In physics texts please activate the class option
\texttt{vecphys} to depict your vectors in \textbf{\itshape
boldface-italic} type - as is customary for a wide range of physical
subjects}.
\begin{eqnarray}
a \times b = c \nonumber\\
\vec{a} \cdot \vec{b}=\vec{c}
\label{eq:01}
\end{eqnarray}

\subsection{Subsection Heading}
\label{subsec:2}
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references\index{cross-references} and citations\index{citations} as has already been described in Sect.~\ref{sec:2}.

\begin{quotation}
Please do not use quotation marks when quoting texts! Simply use the \verb|quotation| environment -- it will automatically render Springer's preferred layout.
\end{quotation}

\subsubsection{Subsubsection Heading}
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{subsec:2}, see also Fig.~\ref{fig:1}\footnote{If you copy text passages, figures, or tables from other works, you must obtain \textit{permission} from the copyright holder (usually the original publisher). Please enclose the signed permission with the manucript. The sources\index{permission to print} must be acknowledged either in the captions, as footnotes or in a separate section of the book.}

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

% For figures use
%
\begin{figure}[b]
\sidecaption
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the graphicx style use
\includegraphics[scale=.65]{figure}
%
% If no graphics program available, insert a blank space i.e. use
%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
%
\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page. If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
\label{fig:1}       % Give a unique label
\end{figure}

\paragraph{Paragraph Heading} %
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

For typesetting numbered lists we recommend to use the \verb|enumerate| environment -- it will automatically render Springer's preferred layout.

\begin{enumerate}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\begin{enumerate}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{enumerate}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{enumerate}

\subparagraph{Subparagraph Heading} In order to avoid simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}, see also Fig.~\ref{fig:2}.

For unnumbered list we recommend to use the \verb|itemize| environment -- it will automatically render Springer's preferred layout.

\begin{itemize}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development, cf. Table~\ref{tab:1}.}
\begin{itemize}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{itemize}
\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
\end{itemize}

\begin{figure}[t]
\sidecaption[t]
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the option graphics use
\includegraphics[scale=.65]{figure}
%
% If no graphics program available, insert a blank space i.e. use
%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
%
%\caption{Please write your figure caption here}
\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page. If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
\label{fig:2}       % Give a unique label
\end{figure}

\runinhead{Run-in Heading Boldface Version} Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

\subruninhead{Run-in Heading Italic Version} Use the \LaTeX\ automatism for all your cross-refer\-ences and citations as has already been described in Sect.~\ref{sec:2}\index{paragraph}.
% Use the \index{} command to code your index words
%
% For tables use
%
\begin{table}
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
%
% Follow this input for your own table layout
%
\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
\hline\noalign{\smallskip}
Classes & Subclass & Length & Action Mechanism  \\
\noalign{\smallskip}\svhline\noalign{\smallskip}
Translation & mRNA$^a$  & 22 (19--25) & Translation repression, mRNA cleavage\\
Translation & mRNA cleavage & 21 & mRNA cleavage\\
Translation & mRNA  & 21--22 & mRNA cleavage\\
Translation & mRNA  & 24--26 & Histone and DNA Modification\\
\noalign{\smallskip}\hline\noalign{\smallskip}
\end{tabular}
$^a$ Table foot note (with superscript)
\end{table}
%
\section{Section Heading}
\label{sec:3}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

If you want to list definitions or the like we recommend to use the Springer-enhanced \verb|description| environment -- it will automatically render Springer's preferred layout.

\begin{description}[Type 1]
\item[Type 1]{That addresses central themes pertainng to migration, health, and disease. In Sect.~\ref{sec:1}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
\item[Type 2]{That addresses central themes pertainng to migration, health, and disease. In Sect.~\ref{subsec:2}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
\end{description}

\subsection{Subsection Heading} %
In order to avoid simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Use the \LaTeX\ automatism for all your cross-references and citations citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

\begin{svgraybox}
If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option \verb|graybox| and the newly defined environment \verb|svgraybox|. This will produce a 15 percent screened box 'behind' your text.

If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option and environment \verb|svgraybox|. This will produce a 15 percent screened box 'behind' your text.
\end{svgraybox}

\subsubsection{Subsubsection Heading}
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.

\begin{theorem}
Theorem text goes here.
\end{theorem}
%
% or
%
\begin{definition}
Definition text goes here.
\end{definition}

\begin{proof}
%\smartqed
Proof text goes here.
\qed
\end{proof}

\paragraph{Paragraph Heading} %
Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text. Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.

Note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
%
% For built-in environments use
%
\begin{theorem}
Theorem text goes here.
\end{theorem}
%
\begin{definition}
Definition text goes here.
\end{definition}
%
\begin{proof}
\smartqed
Proof text goes here.
\qed
\end{proof}
%
\begin{acknowledgement}
If you want to include acknowledgments of assistance and the like at the end of an individual chapter please use the \verb|acknowledgement| environment -- it will automatically render Springer's preferred layout.
\end{acknowledgement}
%
\section*{Appendix}
\addcontentsline{toc}{section}{Appendix}
%
%
When placed at the end of a chapter or contribution (as opposed to at the end of the book), the numbering of tables, figures, and equations in the appendix section continues on from that in the main text. Hence please \textit{do not} use the \verb|appendix| command when writing an appendix at the end of your chapter or contribution. If there is only one the appendix is designated ``Appendix'', or ``Appendix 1'', or ``Appendix 2'', etc. if there is more than one.

\begin{equation}
a \times b = c
\end{equation}

\input{referenc}
\end{document}

### 2013-04-28 doc/bcspaper/article.tex
Started putting things in article text

@@
 % your contribution title if the original one is too long
-\author{Name of First Author and Name of Second Author}
+\author{Amanda Clare and Maria Liakata and James Ravenscroft}
 % Use \authorrunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
+\institute{James Ravenscroft \at Aberystwyth University, Department of Computer Science, Llandinam Building, Aberystwyth University, Aberystwyth, Ceredigion, SY23 3DB  \email{jrr9@aber.ac.uk}
 \and Name of Second Author \at Name, Address of Institute \email{name@email.address}}

### 2013-05-20 doc/bcspaper/article.tex
Started updating names in paper doc
Added a bib file, and an abstract. Commented out the example stuff.

--- 2013-04-28 doc/bcspaper/article.tex
@@
 
-\title{Contribution Title}
+\title{Partridge: An effective system for the automatic classification of the types of academic papers}
+\titlerunning{Partridge: classifying academic papers}
 % Use \titlerunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\author{Name of First Author and Name of Second Author}
+\author{James Ravenscroft and Maria Liakata and Amanda Clare}
 % Use \authorrunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\institute{Name of First Author \at Name, Address of Institute, \email{name@email.address}
-\and Name of Second Author \at Name, Address of Institute \email{name@email.address}}
+\institute{James Ravenscroft \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
+\and Maria Liakata \at Name, Address of Institute \email{name@email.address}
+\and Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK \email{afc@aber.ac.uk}}
 %
@@
 
-\abstract*{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content.
+\abstract{Partridge is a system that enables intelligent search for academic papers.
+Here we describe how Partridge implements the automatic classification of the type of a publication.
+For each paper, Partridge automatically extracts the full paper content from PDF files, determines sentence boundaries, automatically labels the sentences with core scientific concepts, and then uses a random forest model to classify the paper type.
+We show that the type of a paper can be reliably predicted by a model which analyses the distribution of core scientific concepts within the sentences of the paper.
+We discuss the appropriateness of many of the existing paper types used by major journals, and their corresponding distributions.
+Partridge is online and available for use, includes a browser-friendly bookmarklet for new paper submission, and demonstrates a range of possibilities for more intelligent search in the scientific literature.}
+
+%\abstract*{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content.
 The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access.
@@
 As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.
-Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf.
+%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf.
 source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript.
@@
 
-\abstract{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content.
+%\abstract{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content.
 The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access.
@@
 As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.\newline\indent
-Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf.
+%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf.
 source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript.
@@
 
-\section{Section Heading}
+\section{Introduction}
 \label{sec:1}
-Use the template \emph{chapter.tex} together with the Springer document class SVMono (monograph-type books) or SVMult (edited books) to style the various elements of your chapter content in the Springer layout.
+Introduce paper search, CoreSC and SAPIENTA \cite{Liakata2012}, Partridge as a platform, and random forests as a technology
 
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
+%Use the template \emph{chapter.tex} together with the Springer document class SVMono (monograph-type books) or SVMult (edited books) to style the various elements of your chapter content in the Springer layout.
+
+%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
 Further on please use the \LaTeX\ automatism for all your cross-references and citations.
@@
 
-\section{Section Heading}
+\section{Methods}
 \label{sec:2}
+
+Discuss in more detail how Partridge processes papers, how types were chosen, how papers were acquired and how the machine learning is conducted (features, algorithm, libraries, validation methods).
+
 % Always give a unique label
@@
 % to alter or adjust the section heading in the running head
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references and citations.
 
-Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
+%Use the standard \verb|equation| environment to typeset your equations, e.g.
+%
+%\begin{equation}
+%a \times b = c\;,
+%\end{equation}
+%
+%however, for multiline equations we recommend to use the \verb|eqnarray|
+%environment\footnote{In physics texts please activate the class option
+%\texttt{vecphys} to depict your vectors in \textbf{\itshape
+%boldface-italic} type - as is customary for a wide range of physical
+%subjects}.
+%\begin{eqnarray}
+%a \times b = c \nonumber\\
+%\vec{a} \cdot \vec{b}=\vec{c}
+%\label{eq:01}
+%\end{eqnarray}
 
-Use the standard \verb|equation| environment to typeset your equations, e.g.
-%
-\begin{equation}
-a \times b = c\;,
-\end{equation}
-%
-however, for multiline equations we recommend to use the \verb|eqnarray|
-environment\footnote{In physics texts please activate the class option
-\texttt{vecphys} to depict your vectors in \textbf{\itshape
-boldface-italic} type - as is customary for a wide range of physical
-subjects}.
-\begin{eqnarray}
-a \times b = c \nonumber\\
-\vec{a} \cdot \vec{b}=\vec{c}
-\label{eq:01}
-\end{eqnarray}
-
-\subsection{Subsection Heading}
-\label{subsec:2}
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
+%\subsection{Subsection Heading}
+%\label{subsec:2}
+%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
 Further on please use the \LaTeX\ automatism for all your cross-references\index{cross-references} and citations\index{citations} as has already been described in Sect.~\ref{sec:2}.
 
-\begin{quotation}
-Please do not use quotation marks when quoting texts! Simply use the \verb|quotation| environment -- it will automatically render Springer's preferred layout.
-\end{quotation}
+%\begin{quotation}
+%Please do not use quotation marks when quoting texts! Simply use the \verb|quotation| environment -- it will automatically render Springer's preferred layout.
+%\end{quotation}
 
-\subsubsection{Subsubsection Heading}
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
+%\subsubsection{Subsubsection Heading}
+%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
 Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{subsec:2}, see also Fig.~\ref{fig:1}\footnote{If you copy text passages, figures, or tables from other works, you must obtain \textit{permission} from the copyright holder (usually the original publisher).
@@
 
-Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
+%For typesetting numbered lists we recommend to use the \verb|enumerate| environment -- it will automatically render Springer's preferred layout.
 
-% For figures use
-%
-\begin{figure}[b]
-\sidecaption
-% Use the relevant command for your figure-insertion program
-% to insert the figure file.
-% For example, with the graphicx style use
-\includegraphics[scale=.65]{figure}
-%
-% If no graphics program available, insert a blank space i.e. use
-%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
-%
-\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page.
-If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
-\label{fig:1}       % Give a unique label
-\end{figure}
+%\begin{enumerate}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
+%\begin{enumerate}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
+%\end{enumerate}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
+%\end{enumerate}
 
-\paragraph{Paragraph Heading} %
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
+%For unnumbered list we recommend to use the \verb|itemize| environment -- it will automatically render Springer's preferred layout.
 
-Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
+%\begin{itemize}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development, cf. Table~\ref{tab:1}.}
+%\begin{itemize}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
+%\end{itemize}
+%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
+%\end{itemize}
 
-For typesetting numbered lists we recommend to use the \verb|enumerate| environment -- it will automatically render Springer's preferred layout.
-
-\begin{enumerate}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-\begin{enumerate}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-\end{enumerate}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-\end{enumerate}
-
-\subparagraph{Subparagraph Heading} In order to avoid simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}, see also Fig.~\ref{fig:2}.
-
-For unnumbered list we recommend to use the \verb|itemize| environment -- it will automatically render Springer's preferred layout.
-
-\begin{itemize}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development, cf. Table~\ref{tab:1}.}
-\begin{itemize}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-\end{itemize}
-\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-\end{itemize}
-
-\begin{figure}[t]
-\sidecaption[t]
+%\begin{figure}[t]
+%\sidecaption[t]
 % Use the relevant command for your figure-insertion program
@@
 % For example, with the option graphics use
-\includegraphics[scale=.65]{figure}
+%\includegraphics[scale=.65]{figure}
 %
@@
 %\caption{Please write your figure caption here}
-\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page.
+%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page.
 If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
-\label{fig:2}       % Give a unique label
-\end{figure}
+%\label{fig:2}       % Give a unique label
+%\end{figure}
 
-\runinhead{Run-in Heading Boldface Version} Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
+%\runinhead{Run-in Heading Boldface Version} Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
 
-\subruninhead{Run-in Heading Italic Version} Use the \LaTeX\ automatism for all your cross-refer\-ences and citations as has already been described in Sect.~\ref{sec:2}\index{paragraph}.
+%\subruninhead{Run-in Heading Italic Version} Use the \LaTeX\ automatism for all your cross-refer\-ences and citations as has already been described in Sect.~\ref{sec:2}\index{paragraph}.
+
 % Use the \index{} command to code your index words
@@
 %
-\begin{table}
-\caption{Please write your table caption here}
-\label{tab:1}       % Give a unique label
+%\begin{table}
+%\caption{Please write your table caption here}
+%\label{tab:1}       % Give a unique label
 %
@@
 %
-\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
-\hline\noalign{\smallskip}
-Classes & Subclass & Length & Action Mechanism  \\
-\noalign{\smallskip}\svhline\noalign{\smallskip}
-Translation & mRNA$^a$  & 22 (19--25) & Translation repression, mRNA cleavage\\
-Translation & mRNA cleavage & 21 & mRNA cleavage\\
-Translation & mRNA  & 21--22 & mRNA cleavage\\
-Translation & mRNA  & 24--26 & Histone and DNA Modification\\
-\noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
-$^a$ Table foot note (with superscript)
-\end{table}
+%\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
+%\hline\noalign{\smallskip}
+%Classes & Subclass & Length & Action Mechanism  \\
+%\noalign{\smallskip}\svhline\noalign{\smallskip}
+%Translation & mRNA$^a$  & 22 (19--25) & Translation repression, mRNA cleavage\\
+%Translation & mRNA cleavage & 21 & mRNA cleavage\\
+%Translation & mRNA  & 21--22 & mRNA cleavage\\
+%Translation & mRNA  & 24--26 & Histone and DNA Modification\\
+%\noalign{\smallskip}\hline\noalign{\smallskip}
+%\end{tabular}
+%$^a$ Table foot note (with superscript)
+%\end{table}
 %
-\section{Section Heading}
+
+\section{Results}
 \label{sec:3}
-% Always give a unique label
-% and use \ref{<label>} for cross-references
-% and \cite{<label>} for bibliographic references
-% use \sectionmark{}
-% to alter or adjust the section heading in the running head
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
 
-Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
+Present the random forest results. Maybe also the clustering results. Include a few pie charts showing example distributions for typical papers from a few types.
 
-If you want to list definitions or the like we recommend to use the Springer-enhanced \verb|description| environment -- it will automatically render Springer's preferred layout.
+%\begin{description}[Type 1]
+%\item[Type 1]{That addresses central themes pertainng to migration, health, and disease.
+In Sect.~\ref{sec:1}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
+%\item[Type 2]{That addresses central themes pertainng to migration, health, and disease.
+In Sect.~\ref{subsec:2}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
+%\end{description}
 
-\begin{description}[Type 1]
-\item[Type 1]{That addresses central themes pertainng to migration, health, and disease.
-In Sect.~\ref{sec:1}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
-\item[Type 2]{That addresses central themes pertainng to migration, health, and disease.
-In Sect.~\ref{subsec:2}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
-\end{description}
-
-\subsection{Subsection Heading} %
-In order to avoid simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Use the \LaTeX\ automatism for all your cross-references and citations citations as has already been described in Sect.~\ref{sec:2}.
-
-Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
-
-\begin{svgraybox}
-If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option \verb|graybox| and the newly defined environment \verb|svgraybox|.
+%\begin{svgraybox}
+%If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option \verb|graybox| and the newly defined environment \verb|svgraybox|.
 This will produce a 15 percent screened box 'behind' your text.
 
-If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option and environment \verb|svgraybox|.
+%If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option and environment \verb|svgraybox|.
 This will produce a 15 percent screened box 'behind' your text.
-\end{svgraybox}
+%\end{svgraybox}
 
-\subsubsection{Subsubsection Heading}
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
-
-Please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
-
-\begin{theorem}
-Theorem text goes here.
-\end{theorem}
+%\begin{theorem}
+%Theorem text goes here.
+%\end{theorem}
 %
@@
 %
-\begin{definition}
-Definition text goes here.
-\end{definition}
+%\begin{definition}
+%Definition text goes here.
+%\end{definition}
 
-\begin{proof}
+%\begin{proof}
 %\smartqed
-Proof text goes here.
-\qed
-\end{proof}
+%Proof text goes here.
+%\qed
+%\end{proof}
 
-\paragraph{Paragraph Heading} %
-Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
+%\paragraph{Paragraph Heading} %
+%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
 Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
 
-Note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
+%Note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
 %
@@
 %
-\begin{theorem}
-Theorem text goes here.
-\end{theorem}
+%\begin{theorem}
+%Theorem text goes here.
+%\end{theorem}
 %
-\begin{definition}
-Definition text goes here.
-\end{definition}
+%\begin{definition}
+%Definition text goes here.
+%\end{definition}
 %
-\begin{proof}
-\smartqed
-Proof text goes here.
-\qed
-\end{proof}
+%\begin{proof}
+%\smartqed
+%Proof text goes here.
+%\qed
+%\end{proof}
 %
+
+\section{Discussion and Conclusion}
+\label{sec:4}
+
+Discuss why it's possible to predict type from CoreSC, which classes are confused and why, which types are well defined by CoreSC.
+
+Discuss the potential for intelligent paper search opportunities in general and the future for Partridge.
+
 \begin{acknowledgement}
-If you want to include acknowledgments of assistance and the like at the end of an individual chapter please use the \verb|acknowledgement| environment -- it will automatically render Springer's preferred layout.
+Thanks to the Leverhulme for Maria's funding....
 \end{acknowledgement}
 %
-\section*{Appendix}
-\addcontentsline{toc}{section}{Appendix}
-%
-%
-When placed at the end of a chapter or contribution (as opposed to at the end of the book), the numbering of tables, figures, and equations in the appendix section continues on from that in the main text.
+%\section*{Appendix}
+%\addcontentsline{toc}{section}{Appendix}
+%%
+%%
+%When placed at the end of a chapter or contribution (as opposed to at the end of the book), the numbering of tables, figures, and equations in the appendix section continues on from that in the main text.
 Hence please \textit{do not} use the \verb|appendix| command when writing an appendix at the end of your chapter or contribution.
@@
 
-\begin{equation}
-a \times b = c
-\end{equation}
+%\begin{equation}
+%a \times b = c
+%\end{equation}
 
-\input{referenc}
+\bibliographystyle{plain}
+\bibliography{partridge}
+
+%\input{referenc}
 \end{document}

### 2013-05-20 doc/bcspaper/article.tex
First draft of introduction

@@
 
-%% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\documentclass[graybox]{svmult}
+% RECOMMENDED %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\documentclass{svmult}
 %
@@
 %
-\makeindex             % used for the subject index
+%\makeindex             % used for the subject index
 %                       % please use the style svind.ist with
@@
 
-\title{Partridge: An effective system for the automatic classification of the types of academic papers}
+\title*{Partridge: An effective system for the automatic classification of the types of academic papers}
 \titlerunning{Partridge: classifying academic papers}
@@
 % your contribution title if the original one is too long
-\author{James Ravenscroft and Maria Liakata and Amanda Clare}
+\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
 % Use \authorrunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\institute{James Ravenscroft \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
-\and Maria Liakata \at Name, Address of Institute \email{name@email.address}
-\and Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK \email{afc@aber.ac.uk}}
+\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
+\and Maria Liakata \at Name, Address of Institute \email{name@email.address}}
+
 %
@@
 \label{sec:1}
-Introduce paper search, CoreSC and SAPIENTA \cite{Liakata2012}, Partridge as a platform, and random forests as a technology
+Since the advent of the `Digital Age' and the ability of computers to copy and reproduce information for a negligible cost, the amount of information available to researchers has been increasing drastically.
+B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million papers were published in the year 2006 alone\cite{bjork2009}.
+As available information increases, relevant material becomes progressively more difficult to find manually and the need for an automated information retrieval tool more apparent.
+There are already a large number of information retrieval and recommendation systems for scientific publications.
+Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso (\url{http://www.textpresso.org/}) index only publications from predefined journals or topics (for the above examples, Agriculture, Biology and Bioinformatics respectively).
+Unfortunately, these domain specific indexing systems usually only contain a small subset of papers, excluding potentially crucial literature because it does not quite fit into the subject domain. 
+%This problem is often exacerbated by the decision to leave out some papers and articles because the system administrators do not have permission from the author or publisher to include them. 
+The value of these systems to their users is often restricted by the small proportion of available literature that they index, forcing researchers to use multiple, domain specific, search engines for their queries.
+In contrast, there are also a number of interdisciplinary indexing systems and online journals such as arXiv( \url{http://arxiv.org/}), PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}), that try to incorporate wide ranges of papers from as many disciplines as possible.
+The traits of these systems often complement those of their domain-specific counterparts; they provide a comprehensive collection of literature but insufficient filtering and indexing capabilities.
+One of the most publicised and well known interdisciplinery scientific literature search systems is Google Scholar (\url{http://scholar.google.com}).
+Google offers advanced query options specific to Scholar that allow searching by author, year and for words that occur only in the document title.
+
+However, the document title is just one part of the important structure to be found within a scientific document.
+Liakata \emph{et al.} (2012) describe a system for automatically processing and classifying sentences in a research paper according to the core scientific concept (CoreSC) that they describe\cite{Liakata2012}.
+There are 13 CoreSCs, including {\em hypothesis}, {\it background}, {\em result}, {\em method} and {\em conclusion}.
+CoreSC labels can be allocated to all sentences in a scientific paper in order to identify which scientific concept each sentence encapsulates.
+SAPIENTA (\url{http://www.sapientaproject.com}) is a machine learning application which can automatically annotate all sentences in a scientific paper with their CoreSC labels.
+It was trained using a corpus of physical chemistry and biochemistry research papers whose sentences were manually annotated using the CoreSC\cite{LIAKATA10.644} scheme.
+An intelligent academic information retrieval system can use this information in order to provide better filtering and search capabilities for researchers. 
+The ability to search for phrases and keywords by CoreSC will facilitate context-aware keyword search, that allows researchers to only accept papers where a term appears in sentences with a specific CoreSC label.
+This can be used to greatly improve both the precision with which researchers are able to perform searches for scientific literature and the accuracy of those searches in terms of relevance to the reader.
+
+The type of a paper ({\em review}, {\em case study}, {\em research}, {\em perspective}, etc) is another useful feature through which a user can narrow down the results of a search. 
+The type of a paper can then be used to augment queries.
+For example, a user may search for a {\em review} paper containing the keywords ``PCR microfluidics'', or a {\em research} paper with a {\em hypothesis} containing the keywords ``cerevisiae'' and ``glucose''.
+Such paper types are not yet standardised by journals.
+We expect the structure of a paper to reflect its paper type. 
+For example, review papers would be expected to contain a large amount of background material.
+In this article, we describe the application of machine learning (using random forests) to create predictive models of a paper's type, using the distribution of CoreSC labels found in the full text of the paper.
+
+This model of paper type is currently in use in our Partridge system, which has been created as an intelligent full-text search platform for scientific papers. 
+Partridge can make use of automatically derived CoreSC sentence labels and automatically derived paper types, to allow deeper information queries.  
+We discuss the reliability of this model of paper types and the insights that have been gained for the authorship of papers.
 
@@
 
-Discuss in more detail how Partridge processes papers, how types were chosen, how papers were acquired and how the machine learning is conducted (features, algorithm, libraries, validation methods).
+Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)
+
+how types were chosen,
+
+how papers were acquired
+
+how the machine learning is conducted (features, algorithm, libraries, validation methods).
 

### 2013-05-21 doc/bcspaper/article.tex
Minor fiddles to notes in other sections
First draft of methods section. Added a little outline to results

@@
 We discuss the appropriateness of many of the existing paper types used by major journals, and their corresponding distributions.
-Partridge is online and available for use, includes a browser-friendly bookmarklet for new paper submission, and demonstrates a range of possibilities for more intelligent search in the scientific literature.}
+Partridge is online and available for use, includes a browser-friendly bookmarklet for new paper submission, and demonstrates a range of possibilities for more intelligent search in the scientific literature.
+The Partidge instance can be used at \url{http://farnsworth.papro.org.uk}, and further information about the project can be found at \url{http://papro.org.uk}}
 
@@
 
-Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)
+%Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)
 
-how types were chosen,
+The first process in the processing pipeline is conversion of the papers to a format that can be analysed by SAPIENTA.
+Currently, SAPIENTA supports the SciXML and PubMed Central DTDs. 
+Papers in PDF format must be converted to XML in order to be processed. 
+For this, we use PDFX \cite{PDFX}, a free service hosted by the University of Manchester (\url{http://pdfx.cs.man.ac.uk/}). 
+PDFX also provides output that already has some metadata, such as title, author, and abstract, associated with it.
+SAPIENTA allocates each sentence within a paper a separate CoreSC label. 
+However, the sentence boundaries must be detected before the document is passed into SAPIENTA for annotation. 
+The sentence splitter uses a regular expression to split the sentences within the document and then adds the necessary \verb|<s>| tags to the markup to indicate the location of each sentence.
+Once the paper has been split, SAPIENTA is used to annotate each sentence with a relevant CoreSC label. 
+These labels are calculated based upon the sentence's location within the paper as well pairs and triplets of words found consecutively within the sentence.
 
-how papers were acquired
+%how types were chosen,
 
-how the machine learning is conducted (features, algorithm, libraries, validation methods).
+Open Access (OA) journals are research journals that provide their papers free to read online, often making revenue by charging authors to publish their articles \cite{solomon2012study}. 
+Many OA journals provide free read access to their papers, but do not permit the user of articles for data mining purposes.
+The PLoS journals\footnote{PLoS: \url{http://www.plos.org/}} contains large volumes of OA literature under a permissive license that allows data mining. 
+PLoS use the Pubmed Central markup schema, which is compatible with SAPIENTA, for papers published through their journal.
+The PLoS journals advanced search offers approximately 50 types of paper through which to restrict the search.
+Many of these paper type categories contain too few papers to be useful.
+Others are too specific (e.g.``Message from PLoS'').
+We chose to look at XX paper types (Essay, Correspondence, Synopsis, Perspective, Viewpoint, Opinion, Review, Research).
+These paper types represent a range of types, some of which we expect to overlap or have an unclear distinction.
 
-% Always give a unique label
-% and use \ref{<label>} for cross-references
-% and \cite{<label>} for bibliographic references
-% use \sectionmark{}
-% to alter or adjust the section heading in the running head
+%how papers were acquired 
+The papers were downloaded from PLoS using XXX (bookmarklet? plosget.py using the PLoS restful search API? choosing first N available? or by keyword?)
+The number of papers downloaded per paper type category was as follows: 200 Essay, 99 Correspondence, 174 Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 312 Review, 200 Research.
+These formed a corpus of 1352 papers.
+
+Figure \ref{fig:coresc_pies} shows the CoreSC content of a review paper and a research paper randomly selected from the corpus. 
+The review papers tend to be made up almost entirely from Background CoreSC sentences. 
+However, research papers are much more evenly spread, made up of several different types of CoreSC. 
+This investigation suggested that there is almost certainly a discriminative relationship between CoreSC categories and a paper's type.
+
+\begin{figure}[t]
+\sidecaption[t]
+% Use the relevant command for your figure-insertion program
+% to insert the figure file.
+% For example, with the option graphics use
+%\includegraphics[scale=.65]{figure}
+%
+% If no graphics program available, insert a blank space i.e. use
+%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
+%
+\caption{coresc pies}
+%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page.
+If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
+\label{fig:coresc_pies} 
+\end{figure}
+
+%how the machine learning is conducted (random forest using orange, features, validation methods).
+
+Machine learning to build a classifer of paper type was conducted using random forest learning \cite{Breiman2001}. 
+A random forest learning algorithm was chosen because this is a fast, accurate and widely accepted learning technology, and because the underlying decision trees can be used to describe and inspect some of the reasoning behind the predictions made by the final paper type classifiers.
+The feature set consisted of the percentage composition of the CoreSC labels given to the sentences in each paper (the percentage of {\em Background} sentences, the percentage of {\em Hypothesis} sentences, etc.).
+Thus there are XX features corresponding to the XX CoreSC labels.
+The random forest learning was conducted using the Orange data mining library for Python \cite{Curk2005}.
+The parameters for the random forest learner were XXX.  
+We used 10-fold cross validation to estimate the precision, recall and F-measure.
+
+\section{Results and Discussion}
+\label{sec:3}
+
+\begin{table}
+\caption{Per-class recall, precision and f-measure averaged over 10-fold cross validation}
+\label{tab:1}       % Give a unique label
+\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
+\hline\noalign{\smallskip}
+Classes & Recall & Precision & F-measure  \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+Case Study & 0.000 & 0.000 & 0.000 \\
+Correspondence & 0.000 & 0.000 & 0.000 \\
+Essay & 0.000 & 0.000 & 0.000 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Confusion matrix summed over 10-fold cross validation. Rows represent true classes, columns represent predicted classes.}
+\label{tab:2}       % Give a unique label
+\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
+\hline\noalign{\smallskip}
+ & Case study & Essay & Correspondence  \\
+\noalign{\smallskip}\svhline\noalign{\smallskip}
+Case Study & 1.000 & 0.000 & 0.000 \\
+Essay & 0.000 & 1.000 & 0.000 \\
+Correspondence & 0.000 & 0.000 & 1.000 \\
+\noalign{\smallskip}\hline\noalign{\smallskip}
+\end{tabular}
+\end{table}
+
+Discuss which classes are predicted well and which are poorly recognised.
+
+Discuss why it's possible to predict type from CoreSC (which CoreSC define a class).
+
+Discuss which classes are confused and why.
+
+\section{Conclusion}
+\label{sec:4}
+
+Summary of findings.
+
+Discuss the potential for intelligent paper search opportunities in general and the future for Partridge.
+
+\begin{acknowledgement}
+Thanks to the Leverhulme for Maria's funding....
+\end{acknowledgement}
+
+\bibliographystyle{plain}
+\bibliography{partridge}
+
+%\input{referenc}
+\end{document}
 
@@
 
-\section{Results}
-\label{sec:3}
-
-Present the random forest results. Maybe also the clustering results. Include a few pie charts showing example distributions for typical papers from a few types.
-
 %\begin{description}[Type 1]
@@
 
-\section{Discussion and Conclusion}
-\label{sec:4}
-
-Discuss why it's possible to predict type from CoreSC, which classes are confused and why, which types are well defined by CoreSC.
-
-Discuss the potential for intelligent paper search opportunities in general and the future for Partridge.
-
-\begin{acknowledgement}
-Thanks to the Leverhulme for Maria's funding....
-\end{acknowledgement}
 %
@@
 %\end{equation}
-
-\bibliographystyle{plain}
-\bibliography{partridge}
-
-%\input{referenc}
-\end{document}

### 2013-05-22 partridge/mltest/paper_forest.py
updated paper tree and forest with micro averaging

@@ -15,6 +15,93 @@ from matplotlib import pyplot as plt
 from partridge.models import db
 from partridge.models.doc import Paper, PaperFile, Sentence, C_ABRV
 
+
+
+app = Flask(__name__)
+app.config.update(config)
+
+db.app = app
+db.init_app(app)
+
+TYPE_DIRS = {
+    "Review"     : "/home/james/dissertation/papers_for_type/review",
+    "Research"   : "/home/james/dissertation/papers_for_type/research",
+    "Case Study" : "/home/james/dissertation/papers_for_type/case", 
+    #"Subjective" : "/home/james/dissertation/papers_for_type/subjective",
+    "Essay"      : "/home/james/dissertation/papers_for_type/essay",
+    "Opinion"    : "/home/james/dissertation/papers_for_type/opinion",
+    "Perspective": "/home/james/dissertation/papers_for_type/perspective",
+    "Viewpoint"  : "/home/james/dissertation/papers_for_type/viewpoints",
+    "Synopsis"   : "/home/james/dissertation/papers_for_type/synopsis",
+    "Correspondence" : "/home/james/dissertation/papers_for_type/correspondence"
+}
+
+
+#set up data domain
+class_var = Orange.feature.Discrete("type")
+
+for type in TYPE_DIRS:
+    class_var.add_value(type)
+
+FEATURES = C_ABRV.keys()
+
+domain = Orange.data.Domain(
+        [Orange.feature.Continuous(x) for x in FEATURES], class_var)
+
+def build_papers_table():
+    """Given TYPE_DIRS, create an Orange Table using paper data from db"""
+
+    types = {}
+    for paper_type in TYPE_DIRS:
+        types[paper_type] = set(find_paper_ids(TYPE_DIRS[paper_type]))
+        
+        print "Found %d %s papers" % (len(types[paper_type]), paper_type)
+        
+
+    all_ids = set()
+
+    for type in types:
+        all_ids |= types[type]
+
+    print "Found %d papers in total" % len(all_ids)
+    
+    paper_table = Orange.data.Table(domain)
+    print "Loading Data..."
+
+    offset = 0
+    limit = 50
+    
+    q = Paper.query.filter(Paper.id.in_(all_ids))
+
+    while q.offset(offset).limit(limit).count() > 0:
+
+        print "Downloading batch of %d papers..." % limit
+
+        for paper in q.offset(offset).limit(limit).all():
+            if len(paper.sentences) < 1:
+                continue
+
[…]

### 2013-05-22 partridge/mltest/paper_tree.py

@@ -1,3 +1,63 @@
 """ Like paper forest but trains single Dtree so we can see decisions
 
 """
+
+import os
+import Orange
+import orngTree
+
+from partridge.mltest.paper_forest import FEATURES, TYPE_DIRS,\
+build_papers_table, printResults, buildConfusion, printConfusion, printMeasures
+
+def buildTotalConfusions(confusions, keys):
+    
+    confusion = {y : { x:0 for x in keys } for y in keys}
+
+
+    for c in confusions:
+        for c1,c2 in [(c1,c2) for c1 in keys for c2 in keys]:
+            confusion[c1][c2] += c[c1][c2]
+
+    return confusion
+            
+        
+
+def main():
+    """Main script"""
+
+    paper_table = build_papers_table()
+    tree = orngTree.TreeLearner(minSubset=5,sameMajorityPruning=True)
+
+    learners = [tree]
+
+    FOLDS = 10
+
+    results = Orange.evaluation.testing.cross_validation(learners, paper_table,
+    folds=FOLDS,storeClassifiers=1)
+
+    confusions = []
+
+    print "Learner  CA     Brier  AUC"
+    for i in range(len(learners)):
+        print "%-8s %5.3f  %5.3f  %5.3f" % (learners[i].name, \
+        Orange.evaluation.scoring.CA(results)[i], 
+        Orange.evaluation.scoring.Brier_score(results)[i],
+        Orange.evaluation.scoring.AUC(results)[i])
+    
+        for k in range(0,FOLDS):
+            indices = [paper_table[x] for x in range(0,len(paper_table)) 
+                if results.results[x].iteration_number == k]
+            
+            confusions.append(buildConfusion(indices,
+            results.classifiers[k][i], TYPE_DIRS.keys()))
+
+        confusion = buildTotalConfusions(confusions, TYPE_DIRS.keys())
+
+        printConfusion(confusion, TYPE_DIRS.keys())
+        printMeasures(confusion)
+        
+
+        orngTree.printTxt(results.classifiers[k][i], leafFields=['major', 'contingency'])
+
+if __name__ == "__main__":
+    main()

### 2013-05-22 doc/bcspaper/article.tex
Added coresc pie charts for review and research papers

@@
 \usepackage[bottom]{footmisc}% places footnotes at page bottom
+\usepackage{subcaption}
+\captionsetup{compatibility=false}
 %
@@
 
-\abstract{Partridge is a system that enables intelligent search for academic papers.
-Here we describe how Partridge implements the automatic classification of the type of a publication.
-For each paper, Partridge automatically extracts the full paper content from PDF files, determines sentence boundaries, automatically labels the sentences with core scientific concepts, and then uses a random forest model to classify the paper type.
-We show that the type of a paper can be reliably predicted by a model which analyses the distribution of core scientific concepts within the sentences of the paper.
-We discuss the appropriateness of many of the existing paper types used by major journals, and their corresponding distributions.
-Partridge is online and available for use, includes a browser-friendly bookmarklet for new paper submission, and demonstrates a range of possibilities for more intelligent search in the scientific literature.
-The Partidge instance can be used at \url{http://farnsworth.papro.org.uk}, and further information about the project can be found at \url{http://papro.org.uk}}
+\abstract{Partridge is a system that enables intelligent search for academic
+papers. Here we describe how Partridge implements the automatic classification
+of the type of a publication. For each paper, Partridge automatically extracts
+the full paper content from PDF files, determines sentence boundaries,
+automatically labels the sentences with core scientific concepts, and then uses
+a random forest model to classify the paper type. We show that the type of a
+paper can be reliably predicted by a model which analyses the distribution of
+core scientific concepts within the sentences of the paper. We discuss the
+appropriateness of many of the existing paper types used by major journals, and
+their corresponding distributions. Partridge is online and available for use,
+includes a browser-friendly bookmarklet for new paper submission, and
+demonstrates a range of possibilities for more intelligent search in the
+scientific literature. The Partidge instance can be used at
+\url{http://farnsworth.papro.org.uk}, and further information about the project
+can be found at \url{http://papro.org.uk}}
 
-%\abstract*{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content.
-The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access.
-This allows unregistered users to read the abstract as a teaser for the complete chapter.
-As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.
-%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf.
-source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript.
-Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}
+\section{Introduction} \label{sec:1} Since the advent of the `Digital Age' and
+the ability of computers to copy and reproduce information for a negligible
+cost, the amount of information available to researchers has been increasing
+drastically.  B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million
+papers were published in the year 2006 alone\cite{bjork2009}.  As available
+information increases, relevant material becomes progressively more difficult
+to find manually and the need for an automated information retrieval tool more
+apparent.  There are already a large number of information retrieval and
+recommendation systems for scientific publications.  Many of these systems,
+such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane
+Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
+(\url{http://www.textpresso.org/}) index only publications from predefined
+journals or topics (for the above examples, Agriculture, Biology and
+Bioinformatics respectively).  Unfortunately, these domain specific indexing
+systems usually only contain a small subset of papers, excluding potentially
+crucial literature because it does not quite fit into the subject domain. 
+%This problem is often exacerbated by the decision to leave out some papers and
+%articles because the system administrators do not have permission from the
+%author or publisher to include them. 
+The value of these systems to their users is often restricted by the small
+proportion of available literature that they index, forcing researchers to use
+multiple, domain specific, search engines for their queries.  In contrast,
+there are also a number of interdisciplinary indexing systems and online
+journals such as arXiv( \url{http://arxiv.org/}),
+PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}),
+that try to incorporate wide ranges of papers from as many disciplines as
+possible. The traits of these systems often complement those of their
+domain-specific counterparts; they provide a comprehensive collection of
+literature but insufficient filtering and indexing capabilities.  One of the
+most publicised and well known interdisciplinery scientific literature search
+systems is Google Scholar (\url{http://scholar.google.com}). Google offers
+advanced query options specific to Scholar that allow searching by author, year
+and for words that occur only in the document title.
 
-%\abstract{Each chapter should be preceded by an abstract (10--15 lines long) that summarizes the content.
-The abstract will appear \textit{online} at \url{www.SpringerLink.com} and be available with unrestricted access.
-This allows unregistered users to read the abstract as a teaser for the complete chapter.
-As a general rule the abstracts will not appear in the printed version of your book unless it is the style of your particular book or that of the series to which your book belongs.\newline\indent
-%Please use the 'starred' version of the new Springer \texttt{abstract} command for typesetting the text of the online abstracts (cf.
-source file of this chapter template \texttt{abstract}) and include them with the source files of your manuscript.
-Use the plain \texttt{abstract} command if the abstract is also to appear in the printed version of the book.}
+However, the document title is just one part of the important structure to be
+found within a scientific document.  Liakata \emph{et al.} (2012) describe a
+system for automatically processing and classifying sentences in a research
+paper according to the core scientific concept (CoreSC) that they
+describe\cite{Liakata2012}.  There are 13 CoreSCs, including {\em hypothesis},
+{\it background}, {\em result}, {\em method} and {\em conclusion}.  CoreSC
+labels can be allocated to all sentences in a scientific paper in order to
+identify which scientific concept each sentence encapsulates.  SAPIENTA
+(\url{http://www.sapientaproject.com}) is a machine learning application which
+can automatically annotate all sentences in a scientific paper with their
+CoreSC labels. It was trained using a corpus of physical chemistry and
+biochemistry research papers whose sentences were manually annotated using the
+CoreSC\cite{LIAKATA10.644} scheme.  An intelligent academic information
+retrieval system can use this information in order to provide better filtering
+and search capabilities for researchers.  The ability to search for phrases and
+keywords by CoreSC will facilitate context-aware keyword search, that allows
+researchers to only accept papers where a term appears in sentences with a
+specific CoreSC label.  This can be used to greatly improve both the precision
+with which researchers are able to perform searches for scientific literature
+and the accuracy of those searches in terms of relevance to the reader.
 
-\section{Introduction}
-\label{sec:1}
-Since the advent of the `Digital Age' and the ability of computers to copy and reproduce information for a negligible cost, the amount of information available to researchers has been increasing drastically.
-B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million papers were published in the year 2006 alone\cite{bjork2009}.
-As available information increases, relevant material becomes progressively more difficult to find manually and the need for an automated information retrieval tool more apparent.
-There are already a large number of information retrieval and recommendation systems for scientific publications.
-Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso (\url{http://www.textpresso.org/}) index only publications from predefined journals or topics (for the above examples, Agriculture, Biology and Bioinformatics respectively).
-Unfortunately, these domain specific indexing systems usually only contain a small subset of papers, excluding potentially crucial literature because it does not quite fit into the subject domain. 
-%This problem is often exacerbated by the decision to leave out some papers and articles because the system administrators do not have permission from the author or publisher to include them. 
-The value of these systems to their users is often restricted by the small proportion of available literature that they index, forcing researchers to use multiple, domain specific, search engines for their queries.
-In contrast, there are also a number of interdisciplinary indexing systems and online journals such as arXiv( \url{http://arxiv.org/}), PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}), that try to incorporate wide ranges of papers from as many disciplines as possible.
-The traits of these systems often complement those of their domain-specific counterparts; they provide a comprehensive collection of literature but insufficient filtering and indexing capabilities.
-One of the most publicised and well known interdisciplinery scientific literature search systems is Google Scholar (\url{http://scholar.google.com}).
-Google offers advanced query options specific to Scholar that allow searching by author, year and for words that occur only in the document title.
+The type of a paper ({\em review}, {\em case study}, {\em research}, {\em
+perspective}, etc) is another useful feature through which a user can narrow
+down the results of a search.  The type of a paper can then be used to augment
+queries.  For example, a user may search for a {\em review} paper containing
+the keywords ``PCR microfluidics'', or a {\em research} paper with a {\em
+hypothesis} containing the keywords ``cerevisiae'' and ``glucose''.   Such
+paper types are not yet standardised by journals.  We expect the structure of a
+paper to reflect its paper type.  For example, review papers would be expected
+to contain a large amount of background material.  In this article, we describe
+the application of machine learning (using random forests) to create predictive
+models of a paper's type, using the distribution of CoreSC labels found in the
+full text of the paper.
 
-However, the document title is just one part of the important structure to be found within a scientific document.
-Liakata \emph{et al.} (2012) describe a system for automatically processing and classifying sentences in a research paper according to the core scientific concept (CoreSC) that they describe\cite{Liakata2012}.
-There are 13 CoreSCs, including {\em hypothesis}, {\it background}, {\em result}, {\em method} and {\em conclusion}.
-CoreSC labels can be allocated to all sentences in a scientific paper in order to identify which scientific concept each sentence encapsulates.
-SAPIENTA (\url{http://www.sapientaproject.com}) is a machine learning application which can automatically annotate all sentences in a scientific paper with their CoreSC labels.
-It was trained using a corpus of physical chemistry and biochemistry research papers whose sentences were manually annotated using the CoreSC\cite{LIAKATA10.644} scheme.
-An intelligent academic information retrieval system can use this information in order to provide better filtering and search capabilities for researchers. 
-The ability to search for phrases and keywords by CoreSC will facilitate context-aware keyword search, that allows researchers to only accept papers where a term appears in sentences with a specific CoreSC label.
-This can be used to greatly improve both the precision with which researchers are able to perform searches for scientific literature and the accuracy of those searches in terms of relevance to the reader.
-
-The type of a paper ({\em review}, {\em case study}, {\em research}, {\em perspective}, etc) is another useful feature through which a user can narrow down the results of a search. 
-The type of a paper can then be used to augment queries.
-For example, a user may search for a {\em review} paper containing the keywords ``PCR microfluidics'', or a {\em research} paper with a {\em hypothesis} containing the keywords ``cerevisiae'' and ``glucose''.
-Such paper types are not yet standardised by journals.
-We expect the structure of a paper to reflect its paper type. 
-For example, review papers would be expected to contain a large amount of background material.
-In this article, we describe the application of machine learning (using random forests) to create predictive models of a paper's type, using the distribution of CoreSC labels found in the full text of the paper.
-
-This model of paper type is currently in use in our Partridge system, which has been created as an intelligent full-text search platform for scientific papers. 
-Partridge can make use of automatically derived CoreSC sentence labels and automatically derived paper types, to allow deeper information queries.  
-We discuss the reliability of this model of paper types and the insights that have been gained for the authorship of papers.
+This model of paper type is currently in use in our Partridge system, which has
+been created as an intelligent full-text search platform for scientific papers.
+Partridge can make use of automatically derived CoreSC sentence labels and
+automatically derived paper types, to allow deeper information queries.  We
+discuss the reliability of this model of paper types and the insights that have
+been gained for the authorship of papers.
 
@@
 
-The first process in the processing pipeline is conversion of the papers to a format that can be analysed by SAPIENTA.
-Currently, SAPIENTA supports the SciXML and PubMed Central DTDs. 
-Papers in PDF format must be converted to XML in order to be processed. 
-For this, we use PDFX \cite{PDFX}, a free service hosted by the University of Manchester (\url{http://pdfx.cs.man.ac.uk/}). 
-PDFX also provides output that already has some metadata, such as title, author, and abstract, associated with it.
-SAPIENTA allocates each sentence within a paper a separate CoreSC label. 
-However, the sentence boundaries must be detected before the document is passed into SAPIENTA for annotation. 
-The sentence splitter uses a regular expression to split the sentences within the document and then adds the necessary \verb|<s>| tags to the markup to indicate the location of each sentence.
-Once the paper has been split, SAPIENTA is used to annotate each sentence with a relevant CoreSC label. 
-These labels are calculated based upon the sentence's location within the paper as well pairs and triplets of words found consecutively within the sentence.
+The first process in the processing pipeline is conversion of the papers to a
+format that can be analysed by SAPIENTA.  Currently, SAPIENTA supports the
+SciXML and PubMed Central DTDs.  Papers in PDF format must be converted to XML
+in order to be processed.  For this, we use PDFX \cite{PDFX}, a free service
+hosted by the University of Manchester (\url{http://pdfx.cs.man.ac.uk/}).  PDFX
+also provides output that already has some metadata, such as title, author, and
+abstract, associated with it.  SAPIENTA allocates each sentence within a paper
+a separate CoreSC label.  However, the sentence boundaries must be detected
+before the document is passed into SAPIENTA for annotation.  The sentence
+splitter uses a regular expression to split the sentences within the document
+and then adds the necessary \verb|<s>| tags to the markup to indicate the
+location of each sentence.  Once the paper has been split, SAPIENTA is used to
+annotate each sentence with a relevant CoreSC label.  These labels are
+calculated based upon the sentence's location within the paper as well pairs
+and triplets of words found consecutively within the sentence.
 
@@
 
-Open Access (OA) journals are research journals that provide their papers free to read online, often making revenue by charging authors to publish their articles \cite{solomon2012study}. 
-Many OA journals provide free read access to their papers, but do not permit the user of articles for data mining purposes.
-The PLoS journals\footnote{PLoS: \url{http://www.plos.org/}} contains large volumes of OA literature under a permissive license that allows data mining. 
-PLoS use the Pubmed Central markup schema, which is compatible with SAPIENTA, for papers published through their journal.
-The PLoS journals advanced search offers approximately 50 types of paper through which to restrict the search.
-Many of these paper type categories contain too few papers to be useful.
-Others are too specific (e.g.``Message from PLoS'').
-We chose to look at XX paper types (Essay, Correspondence, Synopsis, Perspective, Viewpoint, Opinion, Review, Research).
-These paper types represent a range of types, some of which we expect to overlap or have an unclear distinction.
+Open Access (OA) journals are research journals that provide their papers free
+to read online, often making revenue by charging authors to publish their
+articles \cite{solomon2012study}.  Many OA journals provide free read access to
+their papers, but do not permit the user of articles for data mining purposes.
+The PLoS journals\footnote{PLoS: \url{http://www.plos.org/}} contains large
+volumes of OA literature under a permissive license that allows data mining.
+PLoS use the Pubmed Central markup schema, which is compatible with SAPIENTA,
+for papers published through their journal.  The PLoS journals advanced search
+offers approximately 50 types of paper through which to restrict the search.
+Many of these paper type categories contain too few papers to be useful. Others
+are too specific (e.g.``Message from PLoS''). We chose to look at XX paper
+types (Essay, Correspondence, Synopsis, Perspective, Viewpoint, Opinion,
+Review, Research). These paper types represent a range of types, some of which
+we expect to overlap or have an unclear distinction.
 
 %how papers were acquired 
-The papers were downloaded from PLoS using XXX (bookmarklet? plosget.py using the PLoS restful search API? choosing first N available? or by keyword?)
-The number of papers downloaded per paper type category was as follows: 200 Essay, 99 Correspondence, 174 Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 312 Review, 200 Research.
-These formed a corpus of 1352 papers.
+The papers were downloaded from PLoS using {\em plosget.py}, a short python
+script that uses the PLoS restful search API. The number of papers downloaded
+per paper type category was as follows: 200 Essay, 99 Correspondence, 174
+Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 107, Case Study, 312
+Review, 200 Research.  These formed a corpus of 1459 papers.
 
-Figure \ref{fig:coresc_pies} shows the CoreSC content of a review paper and a research paper randomly selected from the corpus. 
-The review papers tend to be made up almost entirely from Background CoreSC sentences. 
-However, research papers are much more evenly spread, made up of several different types of CoreSC. 
-This investigation suggested that there is almost certainly a discriminative relationship between CoreSC categories and a paper's type.
+Figure \ref{fig:coresc_pies} shows the CoreSC content of a review paper and a
+research paper randomly selected from the corpus.  The review papers tend to be
+made up almost entirely from Background CoreSC sentences.  However, research
+papers are much more evenly spread, made up of several different types of
+CoreSC.  This investigation suggested that there is almost certainly a
+discriminative relationship between CoreSC categories and a paper's type.
 
@@
 %
+\centering
+%\begin{subfigure}[b]{0.6\textwidth}
+\includegraphics[width=\textwidth]{figures/review_corescs.png}
+%\caption{CoreSC content for a sample review paper}
+%\end{subfigure}
+%\begin{subfigure}[b]{0.6\textwidth}
+\includegraphics[width=\textwidth]{figures/report_corescs.png}
+%\caption{CoreSC content for a sample research paper}
+%\end{subfigure}
 \caption{coresc pies}
@@
 
-Machine learning to build a classifer of paper type was conducted using random forest learning \cite{Breiman2001}. 
-A random forest learning algorithm was chosen because this is a fast, accurate and widely accepted learning technology, and because the underlying decision trees can be used to describe and inspect some of the reasoning behind the predictions made by the final paper type classifiers.
-The feature set consisted of the percentage composition of the CoreSC labels given to the sentences in each paper (the percentage of {\em Background} sentences, the percentage of {\em Hypothesis} sentences, etc.).
-Thus there are XX features corresponding to the XX CoreSC labels.
-The random forest learning was conducted using the Orange data mining library for Python \cite{Curk2005}.
-The parameters for the random forest learner were XXX.  
-We used 10-fold cross validation to estimate the precision, recall and F-measure.
+Machine learning to build a classifer of paper type was conducted using random
+forest learning \cite{Breiman2001}.  A random forest learning algorithm was
+chosen because this is a fast, accurate and widely accepted learning
+technology, and because the underlying decision trees can be used to describe
+and inspect some of the reasoning behind the predictions made by the final
+paper type classifiers.  The feature set consisted of the percentage
+composition of the CoreSC labels given to the sentences in each paper (the
+percentage of {\em Background} sentences, the percentage of {\em Hypothesis}
+sentences, etc.).  Thus there are XX features corresponding to the XX CoreSC
+labels.  The random forest learning was conducted using the Orange data mining
+library for Python \cite{Curk2005}.  The parameters for the random forest
+learner were XXX.  We used 10-fold cross validation to estimate the precision,
+recall and F-measure.
 

### 2013-05-23 doc/bcspaper/article.tex
Maria intro edits

@@
 \usepackage{subcaption}
+\usepackage{soul}
 \captionsetup{compatibility=false}
@@
 
-\abstract{Partridge is a system that enables intelligent search for academic
-papers. Here we describe how Partridge implements the automatic classification
-of the type of a publication. For each paper, Partridge automatically extracts
-the full paper content from PDF files, determines sentence boundaries,
-automatically labels the sentences with core scientific concepts, and then uses
-a random forest model to classify the paper type. We show that the type of a
-paper can be reliably predicted by a model which analyses the distribution of
-core scientific concepts within the sentences of the paper. We discuss the
-appropriateness of many of the existing paper types used by major journals, and
-their corresponding distributions. Partridge is online and available for use,
-includes a browser-friendly bookmarklet for new paper submission, and
-demonstrates a range of possibilities for more intelligent search in the
-scientific literature. The Partidge instance can be used at
-\url{http://farnsworth.papro.org.uk}, and further information about the project
-can be found at \url{http://papro.org.uk}}
+\abstract{Partridge is a system that enables intelligent search for
+  academic papers by allowing users to query particular terms within
+  sentences designating a particular core scientific concept (e.g. Hypotheses, Results, etc). 
+  The system also automatically classifies papers according to
+  article types (e.g. Review, Case Study). Here we focus on the latter
+  aspect of the system. For each paper, Partridge automatically
+  extracts the full paper content from PDF files, converts it to XML,
+  determines sentence boundaries, automatically labels the sentences
+  with core scientific concepts, and then uses a random forest model to
+  classify the paper type. We show that the type of a paper can be
+  reliably predicted by a model which analyses the distribution of
+  core scientific concepts within the sentences of the paper. We
+  discuss the appropriateness of many of the existing paper types used
+  by major journals, and their corresponding distributions. Partridge
+  is online and available for use, includes a browser-friendly
+  bookmarklet for new paper submission, and demonstrates a range of
+  possibilities for more intelligent search in the scientific
+  literature. The Partidge instance can be used at
+  \url{http://farnsworth.papro.org.uk}, and further information about
+  the project can be found at \url{http://papro.org.uk}}
 
@@
 cost, the amount of information available to researchers has been increasing
-drastically.  B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million
-papers were published in the year 2006 alone\cite{bjork2009}.  As available
+drastically. \st{ B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million
+papers were published in the year 2006 alone\cite{bjork2009}}. As available
 information increases, relevant material becomes progressively more difficult
@@
 paper according to the core scientific concept (CoreSC) that they
-describe\cite{Liakata2012}.  There are 13 CoreSCs, including {\em hypothesis},
-{\it background}, {\em result}, {\em method} and {\em conclusion}.  CoreSC
+describe\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis}, {\em Goal},
+{\it Background}, {\em Method}, {\em Result} and {\em Conclusion}.  CoreSC
 labels can be allocated to all sentences in a scientific paper in order to
 identify which scientific concept each sentence encapsulates.  SAPIENTA
-(\url{http://www.sapientaproject.com}) is a machine learning application which
+(\url{http://www.sapientaproject.com}) is a publicly available machine learning application which
 can automatically annotate all sentences in a scientific paper with their
@@
 retrieval system can use this information in order to provide better filtering
-and search capabilities for researchers.  The ability to search for phrases and
-keywords by CoreSC will facilitate context-aware keyword search, that allows
-researchers to only accept papers where a term appears in sentences with a
-specific CoreSC label.  This can be used to greatly improve both the precision
+and search capabilities for researchers.  Partridge {\st the ability to search for phrases and
+keywords by CoreSC will facilitate} implements such context-aware keyword search, by allowing
+researchers to search for papers where a term appears in sentences with a
+specific CoreSC label (e.g only in {\em Method} senetences). This can be used to greatly improve both the precision
 with which researchers are able to perform searches for scientific literature
@@
 been created as an intelligent full-text search platform for scientific papers.
-Partridge can make use of automatically derived CoreSC sentence labels and
+Partridge makes use of automatically derived CoreSC sentence labels and
 automatically derived paper types, to allow deeper information queries.  We

### 2013-05-23 doc/bcspaper/article.tex
Results and conclusions

--- 2013-05-22 doc/bcspaper/article.tex
@@
 \usepackage[bottom]{footmisc}% places footnotes at page bottom
-\usepackage{subcaption}
-\captionsetup{compatibility=false}
+
+%\usepackage{subcaption}
+%\captionsetup{compatibility=false}
+
 %
@@
 %\end{subfigure}
-\caption{coresc pies}
+\caption{The CoreSC content of a review paper and a research paper randomly selected from the corpus}
 %\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page.
@@
 library for Python \cite{Curk2005}.  The parameters for the random forest
-learner were XXX.  We used 10-fold cross validation to estimate the precision,
+learner were as the defaults, except with min\_subsets=5 and same\_majority\_pruning=true.  We used 10-fold cross validation to estimate the precision,
 recall and F-measure.
@@
 
+We report the results of the random forest learning as recall, precision and F-measure for each paper type, averaged over a 10-fold cross validation in Table \ref{tab:recallPrecision}.
+Paper types {\em Research}, {\em Review} and {\em Correspondence} are the most accurate classes, and {\em Viewpoint} is the most difficult paper type to predict.
+
 \begin{table}
-\caption{Per-class recall, precision and f-measure averaged over 10-fold cross validation}
-\label{tab:1}       % Give a unique label
+\caption{Per-class recall, precision and F-measure averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
+\label{tab:recallPrecision}       % Give a unique label
 \begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
@@
 \noalign{\smallskip}\svhline\noalign{\smallskip}
-Case Study & 0.000 & 0.000 & 0.000 \\
-Correspondence & 0.000 & 0.000 & 0.000 \\
-Essay & 0.000 & 0.000 & 0.000 \\
+Case Study   &     0.243    &    0.245     &   0.244 \\
+Correspondence  &      0.545    &    0.505    &    0.524 \\ 
+Essay     &   0.450     &   0.462    &    0.456 \\
+Opinion   &     0.247    &    0.235  &      0.241 \\   
+Perspective &       0.255  &      0.304  &       0.277 \\
+Research     &   0.700    &    0.619    &    0.657 \\
+Review      &  0.631     &   0.625     &   0.628 \\
+Viewpoint   &     0.149     &   0.157  &      0.153 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 
+A confusion matrix for the paper types in given in Table \ref{tab:confusion}.
+Research papers are usually predicted to belong to the Research class, and are sometimes confused with Case Study.
+However, Case Study papers are often predicted to be Research or Review.
+There are fewer Case Study papers for the learning algorithm to train on, and many research papers, so we would expect this outcome.
+We might also expect that Research and Case Study would share similar paper structures.
+We initially expected the classes Essay, Opinion, Perspective and Viewpoint to be confused, as the four labels all indicate a paper containing an author's personal thoughts on an issue, rather than traditional experiment-driven science.
+Opinion is confused with Perspective and Viewpoint.
+Perspective is confused with almost all classes, except Research.
+Viewpoint is a small class and mostly confused with Opinion and Perspective.
+From this it would seem that there is a clear grouping of paper types which are very similar, and could better be labelled as a single type: \{Opinion, Perspective, Viewpoint\}.
+However, Essay appears to be different.
+
+Essay is confused with Perspective and Review.
+Review is confused with Case Study and Essay, and a few others.
+They share overlapping aspects, but are not entirely synonymous.
+A review should cover a wide range of background material (which we might also expect to find in an Essay), and might make recommendations based on the material presented (which we might also expect to find in a Case Study).
+
 \begin{table}
-\caption{Confusion matrix summed over 10-fold cross validation. Rows represent true classes, columns represent predicted classes.}
-\label{tab:2}       % Give a unique label
-\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
+\caption{Confusion matrix summed over 10-fold cross validation, reporting the results on the held-out validation segment. Rows represent true classes, columns represent predicted classes.}
+\label{tab:confusion}       % Give a unique label
+\begin{tabular}{lllllllll}
 \hline\noalign{\smallskip}
- & Case study & Essay & Correspondence  \\
+      &  Case Study   &     Corresp.      &   Essay  & Opinion &     Perspective    &     Research    &     Review  & Viewpoint \\
 \noalign{\smallskip}\svhline\noalign{\smallskip}
-Case Study & 1.000 & 0.000 & 0.000 \\
-Essay & 0.000 & 1.000 & 0.000 \\
-Correspondence & 0.000 & 0.000 & 1.000 \\
+Case Study    &    26   &     2     &   11    &    2  &      5 & 26       & 25 &       10 \\
+Correspondence  &      4  &      54   &     3    &    9     &   15 & 8   &     4 &       2 \\
+Essay      &  8     &   5    &   90    &    2 &       39      &  5 & 46    &    5 \\
+Opinion    &    4   &     7 &       2   &     23      &  27     &   10   &  3  &      17 \\
+Perspective &       11  &      16    &    49       & 30      &  51 & 6      &  26    &   11 \\
+Research      &  19    &    6 &       2 &       8    &    5      &  140  &   12    &    8\\
+Review       & 27     &   8     &   35    &    5      &  13    &    21   &  197 &       6\\
+Viewpoint    &    7  &      9   &     3     &   19     &   13 & 10     &   2  &      11 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
@@
 
-Discuss which classes are predicted well and which are poorly recognised.
+%Discuss why it's possible to predict type from CoreSC (which CoreSC define a class).
 
-Discuss why it's possible to predict type from CoreSC (which CoreSC define a class).
+We inspected the detail of a single decision tree, grown on the entire dataset, to give further insight into which CoreSC class decisions were responsible for the paper type predictions.
+This was a very large tree, with a depth of 37 nodes in places.
+The first decision was regarding the number of Background sentences in the article.
+A low Background percentage, of less than 0.694 indicates a Correspondence paper.
+28 out of the 31 papers that were classified by this decision as Correpondence were correctly labelled.
 
-Discuss which classes are confused and why.
+The next decision, for higher amounts of Background, was based on the percentage of Experiment sentences in the paper.
+For a very low percentage of Experiment sentences ($<$ 0.061), the papers then branched into a long side chain of detailed classification decisions, to separate mostly the Opinion, Viewpoint and Perspective papers from other Correspondence papers, and a few examples of the remaining categories.
+For a higher percentage of Experiment sentences, Research papers were classified as those that had Observations $>$ 5.6\%, or Conclusions  $<=$ 1.4\%, whereas Case Studies had fewer Observations and more Conclusions.
+
+The largest node classifiying Essay did so via a route after the low Experiment decision that asked for a Background $>$ 48\%, but then low values for Goal, Hypothesis, Result, Observation, Model, Conclusion and Object.
+These decisions seem reasonable and agreed with our expectations of the content of an Essay.
 
@@
 
-Summary of findings.
+To summarise, we have demonstrated that paper type can largely be predicted from the distribution of the CoreSC sentence labels in the full text of a paper.
+The CoreSC labels themselves are automatically annotated.
+We have described some of the particular CoreSC features that determine a paper type, and discussed which of the paper types are not easily separable in this way.
+Analysis of an example tree shows the decision making process to be complex, but agrees with our general understanding of paper types.
+The Partridge online system now allows refinement of paper search using CoreSC and paper type, both of which can be intelligently determined using machine learning methods.
 
-Discuss the potential for intelligent paper search opportunities in general and the future for Partridge.
+%Discuss the potential for intelligent paper search opportunities in general and the future for Partridge.
+
+The potential for automatic extraction of useful features from scientific papers to assist researchers in their knowledge queries is now an exciting area for research.
+Open Access journals that permit full text mining lead the way in allowing this research to expand and flourish.
+In future work we aim to develop and implement a range of further useful properties that will uncover more of the information that is hidden within the text of articles, and to use Partridge as a working engine to demonstrate their usefulness in practice.
 

### 2013-05-23 doc/bcspaper/article.tex

@@
 %\captionsetup{compatibility=false}
+%\usepackage{soul}
 

### 2013-05-23 doc/bcspaper/article.tex
sorry, adding the subcaption and soul packages back in
Maria methods edits

@@
 
-%\usepackage{subcaption}
-%\captionsetup{compatibility=false}
-%\usepackage{soul}
+\usepackage{subcaption}
+\usepackage{soul}
+\captionsetup{compatibility=false}
 
@@
 \label{sec:2}
-
-%Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)
-
-The first process in the processing pipeline is conversion of the papers to a
-format that can be analysed by SAPIENTA.  Currently, SAPIENTA supports the
-SciXML and PubMed Central DTDs.  Papers in PDF format must be converted to XML
-in order to be processed.  For this, we use PDFX \cite{PDFX}, a free service
-hosted by the University of Manchester (\url{http://pdfx.cs.man.ac.uk/}).  PDFX
-also provides output that already has some metadata, such as title, author, and
-abstract, associated with it.  SAPIENTA allocates each sentence within a paper
-a separate CoreSC label.  However, the sentence boundaries must be detected
-before the document is passed into SAPIENTA for annotation.  The sentence
-splitter uses a regular expression to split the sentences within the document
-and then adds the necessary \verb|<s>| tags to the markup to indicate the
-location of each sentence.  Once the paper has been split, SAPIENTA is used to
-annotate each sentence with a relevant CoreSC label.  These labels are
-calculated based upon the sentence's location within the paper as well pairs
-and triplets of words found consecutively within the sentence.
-
 %how types were chosen,
 
-Open Access (OA) journals are research journals that provide their papers free
+\subsection*{Collection of scientific articles}
+Partridge allows users to upload any paper which is free of copyright restrictions.
+For the purpose of this study we needed a large set of papers that we could label with CoreSC
+to investigate how this information assists classification into paper type.
+Open Access (OA) journals \st{are research journals that provide their papers free
 to read online, often making revenue by charging authors to publish their
-articles \cite{solomon2012study}.  Many OA journals provide free read access to
+articles \cite{solomon2012study}.  Many OA journals} provide free read access to
 their papers, but do not permit the user of articles for data mining purposes.
-The PLoS journals\footnote{PLoS: \url{http://www.plos.org/}} contains large
+The PLoS journals\footnote{PLoS: \url{http://www.plos.org/}} contain large
 volumes of OA literature under a permissive license that allows data mining.
-PLoS use the Pubmed Central markup schema, which is compatible with SAPIENTA,
+They also use the Pubmed Central markup schema, which is compatible with SAPIENTA,
 for papers published through their journal.  The PLoS journals advanced search
 offers approximately 50 types of paper through which to restrict the search.
-Many of these paper type categories contain too few papers to be useful. Others
-are too specific (e.g.``Message from PLoS''). We chose to look at XX paper
-types (Essay, Correspondence, Synopsis, Perspective, Viewpoint, Opinion,
-Review, Research). These paper types represent a range of types, some of which
+Many of these paper type categories contain too few papers to be useful, others
+are too specific (e.g.``Message from PLoS'') or appear rather adhoc. 
+Indeed it is not clear how these paper types have been identified. % in conclusions add how this can give recommendations for Plos and other journals
+We chose to look at a range of types, some of which
 we expect to overlap or have an unclear distinction.
-
+These are namely: Essay, Correspondence, Case Study, Synopsis, Perspective, Viewpoint, Opinion,
+Review, Research). 
 %how papers were acquired 
@@
 per paper type category was as follows: 200 Essay, 99 Correspondence, 174
-Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 107, Case Study, 312
+Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 107 Case Study, 312
 Review, 200 Research.  These formed a corpus of 1459 papers.
@@
 discriminative relationship between CoreSC categories and a paper's type.
+
+\subsection*{Paper Processing and classification}
+%Discuss in more detail how Partridge processes papers (PDFX, sentence splitting) 
+In order to obtain automatic labeling of sentences in a paper with
+CoreSC concepts we first needed to convert the papers to a format that
+the the CoreSC classifier, SAPIENTA can analyse.  Currently, SAPIENTA
+supports the SciXML and PubMed Central DTDs.  Papers in PDF format are
+first converted to XML using PDFX \cite{PDFX}, a free service hosted
+by the University of Manchester (\url{http://pdfx.cs.man.ac.uk/}).
+PDFX also provides output that already has some metadata, such as
+title, author, and abstract, associated with it.  SAPIENTA allocates
+each sentence within a paper a separate CoreSC label.  However, the
+sentence boundaries must be detected before the document is passed
+into SAPIENTA for annotation.  The sentence splitter uses a regular
+expression to split the sentences within the document and then adds
+the necessary \verb|<s>| tags to the markup to indicate the location
+of each sentence.  Once the paper has been split, SAPIENTA is used to
+annotate each sentence with a relevant CoreSC label.  These labels are
+assigned using a conditional random fields model based upon a number
+of features such as the sentence's location within the paper and pairs
+and triplets of words found consecutively within the sentence
+\cite{Liakata2012}.  The SAPIENTA system has been trained on a corpus
+of 265 chemistry and biochemistry papers and we have done no domain
+adaptation for the papers in PLoS.
 
@@
 paper type classifiers.  The feature set consisted of the percentage
-composition of the CoreSC labels given to the sentences in each paper (the
+composition of the CoreSC labels given to the sentences in each paper i.e. (the
 percentage of {\em Background} sentences, the percentage of {\em Hypothesis}
-sentences, etc.).  Thus there are XX features corresponding to the XX CoreSC
+sentences, etc.).  Thus there are 11 features corresponding to the 11 CoreSC
 labels.  The random forest learning was conducted using the Orange data mining
 library for Python \cite{Curk2005}.  The parameters for the random forest
-learner were as the defaults, except with min\_subsets=5 and same\_majority\_pruning=true.  We used 10-fold cross validation to estimate the precision,
+learner were as the defaults, except with min\_subsets=5 and same\_majority\_pruning=true.  
+We used 10-fold cross validation to estimate the precision,
 recall and F-measure.

### 2013-05-23 doc/bcspaper/article.tex
Removed some of the strikethrough bits since they were breaking pdflatex for me and we were going to omit them anyway (easy to get them back using VCS)

@@
 cost, the amount of information available to researchers has been increasing
-drastically. \st{ B-C Bj\"{o}rk (2009) estimates that approximately 1.4 Million
-papers were published in the year 2006 alone\cite{bjork2009}}. As available
-information increases, relevant material becomes progressively more difficult
-to find manually and the need for an automated information retrieval tool more
-apparent.  There are already a large number of information retrieval and
-recommendation systems for scientific publications.  Many of these systems,
-such as AGRICOLA (\url{http://agricola.nal.usda.gov/}), the Cochrane
-Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
+drastically. As available information increases, relevant material becomes
+progressively more difficult to find manually and the need for an automated
+information retrieval tool more apparent.  There are already a large number of
+information retrieval and recommendation systems for scientific publications.
+Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}),
+the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
 (\url{http://www.textpresso.org/}) index only publications from predefined
@@
 crucial literature because it does not quite fit into the subject domain.
-%This problem is often exacerbated by the decision to leave out some papers and
-%articles because the system administrators do not have permission from the
-%author or publisher to include them. 
+
 The value of these systems to their users is often restricted by the small
@@
 paper according to the core scientific concept (CoreSC) that they
-describe\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis}, {\em Goal},
-{\it Background}, {\em Method}, {\em Result} and {\em Conclusion}.  CoreSC
-labels can be allocated to all sentences in a scientific paper in order to
-identify which scientific concept each sentence encapsulates.  SAPIENTA
-(\url{http://www.sapientaproject.com}) is a publicly available machine learning application which
-can automatically annotate all sentences in a scientific paper with their
-CoreSC labels. It was trained using a corpus of physical chemistry and
-biochemistry research papers whose sentences were manually annotated using the
-CoreSC\cite{LIAKATA10.644} scheme.  An intelligent academic information
-retrieval system can use this information in order to provide better filtering
-and search capabilities for researchers.  Partridge {\st the ability to search for phrases and
-keywords by CoreSC will facilitate} implements such context-aware keyword search, by allowing
-researchers to search for papers where a term appears in sentences with a
-specific CoreSC label (e.g only in {\em Method} senetences). This can be used to greatly improve both the precision
-with which researchers are able to perform searches for scientific literature
-and the accuracy of those searches in terms of relevance to the reader.
+describe\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis},
+{\em Goal}, {\it Background}, {\em Method}, {\em Result} and {\em Conclusion}.
+CoreSC labels can be allocated to all sentences in a scientific paper in order
+to identify which scientific concept each sentence encapsulates.  SAPIENTA
+(\url{http://www.sapientaproject.com}) is a publicly available machine learning
+application which can automatically annotate all sentences in a scientific
+paper with their CoreSC labels. It was trained using a corpus of physical
+chemistry and biochemistry research papers whose sentences were manually
+annotated using the CoreSC\cite{LIAKATA10.644} scheme.  An intelligent academic
+information retrieval system can use this information in order to provide
+better filtering and search capabilities for researchers.  Partridge {\st the
+ability to search for phrases and keywords by CoreSC will facilitate}
+implements such context-aware keyword search, by allowing researchers to search
+for papers where a term appears in sentences with a specific CoreSC label (e.g
+only in {\em Method} senetences). This can be used to greatly improve both the
+precision with which researchers are able to perform searches for scientific
+literature and the accuracy of those searches in terms of relevance to the
+reader.
 
@@
 
-%Use the template \emph{chapter.tex} together with the Springer document class SVMono (monograph-type books) or SVMult (edited books) to style the various elements of your chapter content in the Springer layout.
-
-%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references and citations.
-And please note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
-
 \section{Methods}
@@
 
-\subsection*{Collection of scientific articles}
-Partridge allows users to upload any paper which is free of copyright restrictions.
-For the purpose of this study we needed a large set of papers that we could label with CoreSC
-to investigate how this information assists classification into paper type.
-Open Access (OA) journals \st{are research journals that provide their papers free
-to read online, often making revenue by charging authors to publish their
-articles \cite{solomon2012study}.  Many OA journals} provide free read access to
-their papers, but do not permit the user of articles for data mining purposes.
-The PLoS journals\footnote{PLoS: \url{http://www.plos.org/}} contain large
-volumes of OA literature under a permissive license that allows data mining.
-They also use the Pubmed Central markup schema, which is compatible with SAPIENTA,
-for papers published through their journal.  The PLoS journals advanced search
-offers approximately 50 types of paper through which to restrict the search.
-Many of these paper type categories contain too few papers to be useful, others
-are too specific (e.g.``Message from PLoS'') or appear rather adhoc. 
-Indeed it is not clear how these paper types have been identified. % in conclusions add how this can give recommendations for Plos and other journals
-We chose to look at a range of types, some of which
-we expect to overlap or have an unclear distinction.
-These are namely: Essay, Correspondence, Case Study, Synopsis, Perspective, Viewpoint, Opinion,
-Review, Research). 
-%how papers were acquired 
+\subsection*{Collection of scientific articles} Partridge allows users to
+upload any paper which is free of copyright restrictions.  For the purpose of
+this study we needed a large set of papers that we could label with CoreSC to
+investigate how this information assists classification into paper type.  Open
+Access (OA) journals provide free read access to their papers, but many do not
+permit the user of articles for data mining purposes.  The PLoS
+journals\footnote{PLoS: \url{http://www.plos.org/}} contain large volumes of OA
+literature under a permissive license that allows data mining.  They also use
+the Pubmed Central markup schema, which is compatible with SAPIENTA, for papers
+published through their journal.  The PLoS journals advanced search offers
+approximately 50 types of paper through which to restrict the search.  Many of
+these paper type categories contain too few papers to be useful, others are too
+specific (e.g.``Message from PLoS'') or appear rather adhoc.  Indeed it is not
+clear how these paper types have been identified. % in conclusions add how this
+can give recommendations for Plos and other journals We chose to look at a
+range of types, some of which we expect to overlap or have an unclear
+distinction.  These are namely: Essay, Correspondence, Case Study, Synopsis,
+Perspective, Viewpoint, Opinion, Review, Research).
+
 The papers were downloaded from PLoS using {\em plosget.py}, a short python

### 2013-05-24 doc/bcspaper/article.tex
Resized figure 1 to make more room and make Latex position it more suitably

@@
 
-However, the document title is just one part of the important structure to be
-found within a scientific document.  Liakata \emph{et al.} (2012) describe a
-system for automatically processing and classifying sentences in a research
-paper according to the core scientific concept (CoreSC) that they
+However, the document title is just one of the crucial parts of a scientific
+paper's structure.  Liakata \emph{et al.} (2012) describe a system for
+automatically processing and classifying sentences in a research paper
+according to the core scientific concept (CoreSC) that they
 describe\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis},
@@
 specific (e.g.``Message from PLoS'') or appear rather adhoc.  Indeed it is not
-clear how these paper types have been identified. % in conclusions add how this
-can give recommendations for Plos and other journals We chose to look at a
-range of types, some of which we expect to overlap or have an unclear
-distinction.  These are namely: Essay, Correspondence, Case Study, Synopsis,
-Perspective, Viewpoint, Opinion, Review, Research).
+clear how these paper types have been identified. We chose to look at a range
+of types, some of which we expect to overlap or have an unclear distinction.
+These are namely: Essay, Correspondence, Case Study, Synopsis, Perspective,
+Viewpoint, Opinion, Review, Research.
 
+% in conclusions add how this can give recommendations for Plos and other journals 
 The papers were downloaded from PLoS using {\em plosget.py}, a short python
-script that uses the PLoS restful search API. The number of papers downloaded
+script that uses the PLoS RESTful search API. The number of papers downloaded
 per paper type category was as follows: 200 Essay, 99 Correspondence, 174
@@
 supports the SciXML and PubMed Central DTDs.  Papers in PDF format are
-first converted to XML using PDFX \cite{PDFX}, a free service hosted
+first converted to XML using PDFX %\cite{PDFX} - no paper known yet
+, a free service hosted
 by the University of Manchester (\url{http://pdfx.cs.man.ac.uk/}).
@@
 \begin{figure}[t]
-\sidecaption[t]
-% Use the relevant command for your figure-insertion program
-% to insert the figure file.
-% For example, with the option graphics use
-%\includegraphics[scale=.65]{figure}
-%
-% If no graphics program available, insert a blank space i.e. use
-%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
-%
+
 \centering
-%\begin{subfigure}[b]{0.6\textwidth}
-\includegraphics[width=\textwidth]{figures/review_corescs.png}
-%\caption{CoreSC content for a sample review paper}
-%\end{subfigure}
-%\begin{subfigure}[b]{0.6\textwidth}
-\includegraphics[width=\textwidth]{figures/report_corescs.png}
-%\caption{CoreSC content for a sample research paper}
-%\end{subfigure}
+
+\includegraphics[width=0.75\textwidth]{figures/review_corescs.png}
+
+\includegraphics[width=0.75\textwidth]{figures/report_corescs.png}
+
 \caption{The CoreSC content of a review paper and a research paper randomly selected from the corpus}
-%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page.
-If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
+
 \label{fig:coresc_pies} 

### 2013-05-24 doc/bcspaper/article.tex
Added reference to Maria's CoreSC paper to the bibliography. Made some general cuts and rephrasings in introduction

@@
 annotated using the CoreSC\cite{LIAKATA10.644} scheme.  An intelligent academic
-information retrieval system can use this information in order to provide
-better filtering and search capabilities for researchers.  Partridge {\st the
-ability to search for phrases and keywords by CoreSC will facilitate}
-implements such context-aware keyword search, by allowing researchers to search
-for papers where a term appears in sentences with a specific CoreSC label (e.g
-only in {\em Method} senetences). This can be used to greatly improve both the
-precision with which researchers are able to perform searches for scientific
-literature and the accuracy of those searches in terms of relevance to the
-reader.
+information retrieval system can use this data to provide better filtering and
+search capabilities for researchers.  Partridge implements such context-aware
+keyword search, by allowing researchers to search for papers where a term
+appears in sentences with a specific CoreSC label (e.g only in {\em Method}
+senetences). This can be used to greatly improve both the precision with which
+researchers are able to perform searches for scientific literature and the
+accuracy of those searches in terms of relevance to the reader.
 

### 2013-05-24 doc/bcspaper/article.tex
Got rid of some of the commented out example code - can restore using VCS if we need it back
latest Maria edits
Changed a couple of sentences in article and tried to cut down the words a bit more

@@
 
-Machine learning to build a classifer of paper type was conducted using random
-forest learning \cite{Breiman2001}.  A random forest learning algorithm was
-chosen because this is a fast, accurate and widely accepted learning
-technology, and because the underlying decision trees can be used to describe
-and inspect some of the reasoning behind the predictions made by the final
-paper type classifiers.  The feature set consisted of the percentage
-composition of the CoreSC labels given to the sentences in each paper i.e. (the
-percentage of {\em Background} sentences, the percentage of {\em Hypothesis}
-sentences, etc.).  Thus there are 11 features corresponding to the 11 CoreSC
-labels.  The random forest learning was conducted using the Orange data mining
-library for Python \cite{Curk2005}.  The parameters for the random forest
-learner were as the defaults, except with min\_subsets=5 and same\_majority\_pruning=true.  
-We used 10-fold cross validation to estimate the precision,
-recall and F-measure.
+Random forest learning\cite{Breiman2001} was chosen for the construction of the
+paper type classifier. This is because random forests are a fast, accurate and
+widely accepted learning technology, and the underlying decision trees can be
+inspected to understand some of the reasoning behind the predictions made by
+the final paper type classifiers. The feature set consisted of the percentage
+composition of each of the 11 respective CoreSC labels assigned to the
+sentences in each paper i.e. (the percentage of {\em Background} sentences, the
+percentage of {\em Hypothesis} sentences, etc.). The random forest learning was
+conducted using the Orange data mining library for Python \cite{Curk2005}.  The
+parameters for the random forest learner were as the defaults, except with
+min\_subsets=5 and same\_majority\_pruning=true.  We used 10-fold cross
+validation to estimate the precision, recall and F-measure.
 
@@
 
-We report the results of the random forest learning as recall, precision and F-measure for each paper type, averaged over a 10-fold cross validation in Table \ref{tab:recallPrecision}.
-Paper types {\em Research}, {\em Review} and {\em Correspondence} are the most accurate classes, and {\em Viewpoint} is the most difficult paper type to predict.
+The results of the random forest learning as recall, precision and F-measure
+for each paper type, averaged over a 10-fold cross validation are shown in Table
+\ref{tab:recallPrecision}. Paper types {\em Research}, {\em Review} and {\em
+Correspondence} are the most accurate classes, and {\em Viewpoint} is the most
+difficult paper type to predict.
 
@@
 A confusion matrix for the paper types in given in Table \ref{tab:confusion}.
-Research papers are usually predicted to belong to the Research class, and are sometimes confused with Case Study.
-However, Case Study papers are often predicted to be Research or Review.
-There are fewer Case Study papers for the learning algorithm to train on, and many research papers, so we would expect this outcome.
-We might also expect that Research and Case Study would share similar paper structures.
-We initially expected the classes Essay, Opinion, Perspective and Viewpoint to be confused, as the four labels all indicate a paper containing an author's personal thoughts on an issue, rather than traditional experiment-driven science.
-Opinion is confused with Perspective and Viewpoint.
-Perspective is confused with almost all classes, except Research.
+Research papers are classified correctly most frequently, but are sometimes
+confused with Case Study. However, Case Study papers are often predicted to be
+Research or Review. There are fewer Case Study papers for the learning
+algorithm to train on, and many research papers, so we would expect this
+outcome. We might also expect that Research and Case Study would share similar
+paper structures.  We initially expected the classes Essay, Opinion,
+Perspective and Viewpoint to be confused, as the four labels all indicate a
+paper containing an author's personal thoughts on an issue, rather than
+traditional experiment-driven science. Opinion is confused with Perspective and
+Viewpoint. Perspective is confused with almost all classes, except Research.
 Viewpoint is a small class and mostly confused with Opinion and Perspective.
-From this it would seem that there is a clear grouping of paper types which are very similar, and could better be labelled as a single type: \{Opinion, Perspective, Viewpoint\}.
-However, Essay appears to be different.
+From this it would seem that there is a clear grouping of paper types which are
+very similar, and could better be labelled as a single type: \{Opinion,
+Perspective, Viewpoint\}. However, Essay appears to be different.
 
@@
 \end{document}
-
-%Use the standard \verb|equation| environment to typeset your equations, e.g.
-%
-%\begin{equation}
-%a \times b = c\;,
-%\end{equation}
-%
-%however, for multiline equations we recommend to use the \verb|eqnarray|
-%environment\footnote{In physics texts please activate the class option
-%\texttt{vecphys} to depict your vectors in \textbf{\itshape
-%boldface-italic} type - as is customary for a wide range of physical
-%subjects}.
-%\begin{eqnarray}
-%a \times b = c \nonumber\\
-%\vec{a} \cdot \vec{b}=\vec{c}
-%\label{eq:01}
-%\end{eqnarray}
-
-%\subsection{Subsection Heading}
-%\label{subsec:2}
-%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references\index{cross-references} and citations\index{citations} as has already been described in Sect.~\ref{sec:2}.
-
-%\begin{quotation}
-%Please do not use quotation marks when quoting texts! Simply use the \verb|quotation| environment -- it will automatically render Springer's preferred layout.
-%\end{quotation}
-
-%\subsubsection{Subsubsection Heading}
-%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{subsec:2}, see also Fig.~\ref{fig:1}\footnote{If you copy text passages, figures, or tables from other works, you must obtain \textit{permission} from the copyright holder (usually the original publisher).
-Please enclose the signed permission with the manucript.
-The sources\index{permission to print} must be acknowledged either in the captions, as footnotes or in a separate section of the book.}
-
-%For typesetting numbered lists we recommend to use the \verb|enumerate| environment -- it will automatically render Springer's preferred layout.
-
-%\begin{enumerate}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-%\begin{enumerate}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-%\end{enumerate}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-%\end{enumerate}
-
-%For unnumbered list we recommend to use the \verb|itemize| environment -- it will automatically render Springer's preferred layout.
-
-%\begin{itemize}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development, cf. Table~\ref{tab:1}.}
-%\begin{itemize}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-%\end{itemize}
-%\item{Livelihood and survival mobility are oftentimes coutcomes of uneven socioeconomic development.}
-%\end{itemize}
-
-%\begin{figure}[t]
-%\sidecaption[t]
-% Use the relevant command for your figure-insertion program
-% to insert the figure file.
-% For example, with the option graphics use
-%\includegraphics[scale=.65]{figure}
-%
-% If no graphics program available, insert a blank space i.e. use
-%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
-%
-%\caption{Please write your figure caption here}
-%\caption{If the width of the figure is less than 7.8 cm use the \texttt{sidecapion} command to flush the caption on the left side of the page.
-If the figure is positioned at the top of the page, align the sidecaption with the top of the figure -- to achieve this you simply need to use the optional argument \texttt{[t]} with the \texttt{sidecaption} command}
-%\label{fig:2}       % Give a unique label
-%\end{figure}
-
-%\runinhead{Run-in Heading Boldface Version} Use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
-
-%\subruninhead{Run-in Heading Italic Version} Use the \LaTeX\ automatism for all your cross-refer\-ences and citations as has already been described in Sect.~\ref{sec:2}\index{paragraph}.
-
-% Use the \index{} command to code your index words
-%
-% For tables use
-%
-%\begin{table}
-%\caption{Please write your table caption here}
-%\label{tab:1}       % Give a unique label
-%
-% Follow this input for your own table layout
-%
-%\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
-%\hline\noalign{\smallskip}
-%Classes & Subclass & Length & Action Mechanism  \\
-%\noalign{\smallskip}\svhline\noalign{\smallskip}
-%Translation & mRNA$^a$  & 22 (19--25) & Translation repression, mRNA cleavage\\
-%Translation & mRNA cleavage & 21 & mRNA cleavage\\
-%Translation & mRNA  & 21--22 & mRNA cleavage\\
-%Translation & mRNA  & 24--26 & Histone and DNA Modification\\
-%\noalign{\smallskip}\hline\noalign{\smallskip}
-%\end{tabular}
-%$^a$ Table foot note (with superscript)
-%\end{table}
-%
-
-%\begin{description}[Type 1]
-%\item[Type 1]{That addresses central themes pertainng to migration, health, and disease.
-In Sect.~\ref{sec:1}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
-%\item[Type 2]{That addresses central themes pertainng to migration, health, and disease.
-In Sect.~\ref{subsec:2}, Wilson discusses the role of human migration in infectious disease distributions and patterns.}
-%\end{description}
-
-%\begin{svgraybox}
-%If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option \verb|graybox| and the newly defined environment \verb|svgraybox|.
-This will produce a 15 percent screened box 'behind' your text.
-
-%If you want to emphasize complete paragraphs of texts we recommend to use the newly defined Springer class option and environment \verb|svgraybox|.
-This will produce a 15 percent screened box 'behind' your text.
-%\end{svgraybox}
-
-%\begin{theorem}
-%Theorem text goes here.
-%\end{theorem}
-%
-% or
-%
-%\begin{definition}
-%Definition text goes here.
-%\end{definition}
-
-%\begin{proof}
-%\smartqed
-%Proof text goes here.
-%\qed
-%\end{proof}
-
-%\paragraph{Paragraph Heading} %
-%Instead of simply listing headings of different levels we recommend to let every heading be followed by at least a short passage of text.
-Further on please use the \LaTeX\ automatism for all your cross-references and citations as has already been described in Sect.~\ref{sec:2}.
-
-%Note that the first line of text that follows a heading is not indented, whereas the first lines of all subsequent paragraphs are.
-%
-% For built-in environments use
-%
-%\begin{theorem}
-%Theorem text goes here.
-%\end{theorem}
-%
-%\begin{definition}
-%Definition text goes here.
-%\end{definition}
-%
-%\begin{proof}
-%\smartqed
-%Proof text goes here.
-%\qed
-%\end{proof}
-%
-
-%
-%\section*{Appendix}
-%\addcontentsline{toc}{section}{Appendix}
-%%
-%%
-%When placed at the end of a chapter or contribution (as opposed to at the end of the book), the numbering of tables, figures, and equations in the appendix section continues on from that in the main text.
-Hence please \textit{do not} use the \verb|appendix| command when writing an appendix at the end of your chapter or contribution.
-If there is only one the appendix is designated ``Appendix'', or ``Appendix 1'', or ``Appendix 2'', etc.
-if there is more than one.
-
-%\begin{equation}
-%a \times b = c
-%\end{equation}

### 2013-05-24 doc/bcspaper/article.tex
Maria latest edits

@@
 \usepackage{subcaption}
-\usepackage{soul}
+
 \captionsetup{compatibility=false}
@@
 \abstract{Partridge is a system that enables intelligent search for
-  academic papers by allowing users to query particular terms within
-  sentences designating a particular core scientific concept (e.g. Hypotheses, Results, etc). 
+  academic papers by allowing users to query terms within
+  sentences designating a particular core scientific concept (e.g. Hypothesis, Result, etc). 
   The system also automatically classifies papers according to
@@
 been created as an intelligent full-text search platform for scientific papers.
-Partridge makes use of automatically derived CoreSC sentence labels and
+Partridge (which currently holds XXX papers and is constantly expanding) 
+makes use of automatically derived CoreSC sentence labels and
 automatically derived paper types, to allow deeper information queries.  We
@@
 first converted to XML using PDFX %\cite{PDFX} - no paper known yet
-, a free service hosted
-by the University of Manchester (\url{http://pdfx.cs.man.ac.uk/}).
-PDFX also provides output that already has some metadata, such as
-title, author, and abstract, associated with it.  SAPIENTA allocates
-each sentence within a paper a separate CoreSC label.  However, the
-sentence boundaries must be detected before the document is passed
-into SAPIENTA for annotation.  The sentence splitter uses a regular
-expression to split the sentences within the document and then adds
-the necessary \verb|<s>| tags to the markup to indicate the location
-of each sentence.  Once the paper has been split, SAPIENTA is used to
-annotate each sentence with a relevant CoreSC label.  These labels are
-assigned using a conditional random fields model based upon a number
-of features such as the sentence's location within the paper and pairs
-and triplets of words found consecutively within the sentence
-\cite{Liakata2012}.  The SAPIENTA system has been trained on a corpus
-of 265 chemistry and biochemistry papers and we have done no domain
-adaptation for the papers in PLoS.
+, a free service hosted by the University of Manchester
+(\url{http://pdfx.cs.man.ac.uk/}). Once the paper has been split into
+sentences, SAPIENTA is used to annotate each sentence with a relevant
+CoreSC label. These labels are assigned using a conditional random
+fields model based upon a number of features such as the sentence's
+location within the paper and pairs and triplets of words found
+consecutively within the sentence \cite{Liakata2012}.  The SAPIENTA
+system has been trained on a corpus of 265 chemistry and biochemistry
+papers and we have done no domain adaptation for the papers in PLoS.
 
@@
 
-Random forest learning\cite{Breiman2001} was chosen for the construction of the
-paper type classifier. This is because random forests are a fast, accurate and
-widely accepted learning technology, and the underlying decision trees can be
-inspected to understand some of the reasoning behind the predictions made by
-the final paper type classifiers. The feature set consisted of the percentage
-composition of each of the 11 respective CoreSC labels assigned to the
-sentences in each paper i.e. (the percentage of {\em Background} sentences, the
-percentage of {\em Hypothesis} sentences, etc.). The random forest learning was
-conducted using the Orange data mining library for Python \cite{Curk2005}.  The
-parameters for the random forest learner were as the defaults, except with
-min\_subsets=5 and same\_majority\_pruning=true.  We used 10-fold cross
-validation to estimate the precision, recall and F-measure.
+Machine learning to build a classifer of paper type was conducted using random
+forest learning \cite{Breiman2001}.  A random forest learning algorithm was
+chosen because this is a fast, accurate and widely accepted learning
+technology, and because the underlying decision trees can be used to describe
+and inspect some of the reasoning behind the predictions made by the final
+paper type classifiers.  The feature set consisted of the percentage
+composition of the CoreSC labels given to the sentences in each paper i.e. (the
+percentage of {\em Background} sentences, the percentage of {\em Hypothesis}
+sentences, etc.).  Thus there are 11 features corresponding to the 11 CoreSC
+labels.  The random forest learning was conducted using the Orange data mining
+library for Python \cite{Curk2005}.  The parameters for the random forest
+learner were as the defaults, except with min\_subsets=5 and same\_majority\_pruning=true.  
+We used 10-fold cross validation to estimate the precision,
+recall and F-measure.
 
@@
 
-The results of the random forest learning as recall, precision and F-measure
-for each paper type, averaged over a 10-fold cross validation are shown in Table
-\ref{tab:recallPrecision}. Paper types {\em Research}, {\em Review} and {\em
-Correspondence} are the most accurate classes, and {\em Viewpoint} is the most
-difficult paper type to predict.
+We report the results of the random forest learning as recall, precision and F-measure for each paper type, averaged over a 10-fold cross validation in Table \ref{tab:recallPrecision}.
+Paper types {\em Research}, {\em Review} and {\em Correspondence} are the most accurate classes, and {\em Viewpoint} is the most difficult paper type to predict.
 
@@
 A confusion matrix for the paper types in given in Table \ref{tab:confusion}.
-Research papers are classified correctly most frequently, but are sometimes
-confused with Case Study. However, Case Study papers are often predicted to be
-Research or Review. There are fewer Case Study papers for the learning
-algorithm to train on, and many research papers, so we would expect this
-outcome. We might also expect that Research and Case Study would share similar
-paper structures.  We initially expected the classes Essay, Opinion,
-Perspective and Viewpoint to be confused, as the four labels all indicate a
-paper containing an author's personal thoughts on an issue, rather than
-traditional experiment-driven science. Opinion is confused with Perspective and
-Viewpoint. Perspective is confused with almost all classes, except Research.
+Research papers are usually predicted to belong to the Research class, and are sometimes confused with Case Study.
+However, Case Study papers are often predicted to be Research or Review.
+There are fewer Case Study papers for the learning algorithm to train on, and many research papers, so we would expect this outcome.
+We might also expect that Research and Case Study would share similar paper structures.
+We initially expected the classes Essay, Opinion, Perspective and Viewpoint to be confused, as the four labels all indicate a paper containing an author's personal thoughts on an issue, rather than traditional experiment-driven science.
+Opinion is confused with Perspective and Viewpoint.
+Perspective is confused with almost all classes, except Research.
 Viewpoint is a small class and mostly confused with Opinion and Perspective.
-From this it would seem that there is a clear grouping of paper types which are
-very similar, and could better be labelled as a single type: \{Opinion,
-Perspective, Viewpoint\}. However, Essay appears to be different.
+From this it would seem that there is a clear grouping of paper types which are very similar, and could better be labelled as a single type: \{Opinion, Perspective, Viewpoint\}.
+However, Essay appears to be different.
 

### 2013-05-24 doc/bcspaper/article.tex
Maria edits all sections

--- 2013-05-24 doc/bcspaper/article.tex
@@
 
-\usepackage{subcaption}
+%\usepackage{subcaption}
 
-\captionsetup{compatibility=false}
+%\captionsetup{compatibility=false}
 
@@
 \institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
-\and Maria Liakata \at Name, Address of Institute \email{name@email.address}}
+\and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}
 
@@
 of types, some of which we expect to overlap or have an unclear distinction.
-These are namely: Essay, Correspondence, Case Study, Synopsis, Perspective,
+These are namely: Essay, Correspondence, Case Study, Perspective,
 Viewpoint, Opinion, Review, Research.
@@
 % in conclusions add how this can give recommendations for Plos and other journals 
-The papers were downloaded from PLoS using {\em plosget.py}, a short python
-script that uses the PLoS RESTful search API. The number of papers downloaded
-per paper type category was as follows: 200 Essay, 99 Correspondence, 174
-Synopsis, 200 Perspective, 74 Viewpoint, 93 Opinion, 107 Case Study, 312
-Review, 200 Research.  These formed a corpus of 1459 papers.
+The papers were downloaded from PLoS using {\em plosget.py}, a short
+python script that uses the PLoS RESTful search API. The number of
+papers downloaded per paper type category was as follows: 200 Essay,
+99 Correspondence, 107 Case Study, 200 Perspective, 74 Viewpoint, 93
+Opinion, 312 Review, 200 Research.  These formed a corpus of 1285 %1459-174 after removing synopsis. Should double check the numbers add up
+papers.
 
@@
 \begin{table}
-\caption{Per-class recall, precision and F-measure averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
+\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
 \label{tab:recallPrecision}       % Give a unique label
@@
 Case Study   &     0.243    &    0.245     &   0.244 \\
-Correspondence  &      0.545    &    0.505    &    0.524 \\ 
+Correspondence  &     {\bf  0.545}    &    {\bf 0.505}    &    {\bf 0.524} \\ 
 Essay     &   0.450     &   0.462    &    0.456 \\
@@
 Perspective &       0.255  &      0.304  &       0.277 \\
-Research     &   0.700    &    0.619    &    0.657 \\
-Review      &  0.631     &   0.625     &   0.628 \\
+Research     &   {\bf 0.700}    &    {\bf 0.619}    &    {\bf 0.657} \\
+Review      &  {\bf 0.631}     &   {\bf 0.625}     &   {\bf 0.628} \\
 Viewpoint   &     0.149     &   0.157  &      0.153 \\
@@
 
-A confusion matrix for the paper types in given in Table \ref{tab:confusion}.
-Research papers are usually predicted to belong to the Research class, and are sometimes confused with Case Study.
-However, Case Study papers are often predicted to be Research or Review.
-There are fewer Case Study papers for the learning algorithm to train on, and many research papers, so we would expect this outcome.
-We might also expect that Research and Case Study would share similar paper structures.
-We initially expected the classes Essay, Opinion, Perspective and Viewpoint to be confused, as the four labels all indicate a paper containing an author's personal thoughts on an issue, rather than traditional experiment-driven science.
-Opinion is confused with Perspective and Viewpoint.
-Perspective is confused with almost all classes, except Research.
-Viewpoint is a small class and mostly confused with Opinion and Perspective.
-From this it would seem that there is a clear grouping of paper types which are very similar, and could better be labelled as a single type: \{Opinion, Perspective, Viewpoint\}.
-However, Essay appears to be different.
+A confusion matrix for the paper types in given in Table
+\ref{tab:confusion}. Research papers are usually predicted to belong
+to the Research class, and are sometimes confused with Case
+Study. However, Case Study papers are often predicted to be Research
+or Review. The ratio between Case study, Research and Review papers is
+~1:2:3 so the outcome is not entirely surprising in terms of the data
+size effect. We expected Research and Case Study to share similar
+paper structures but perhaps the fact that Case Study is equally
+confused with Research and Review suggests two distinct types of Case
+Study.  We expected the classes Essay, Opinion, Perspective and
+Viewpoint to be confused, as the four labels all indicate a paper
+containing an author's personal thoughts on an issue, rather than
+experiment-driven science. Opinion is confused with Perspective and
+Viewpoint. Perspective is confused with almost all classes, except
+Research. Viewpoint is a small class and mostly confused with Opinion
+and Perspective. From this it would seem that the paper types
+\{Opinion, Perspective, Viewpoint\} are very similar and should be
+grouped together into one category. Indeed when we trained the model
+on a super class consisting of the previous three categories,
+performance was improved overall with the following f-measures:
+OpinionSuper: 59, Research: 67.6, Review: 63.7, Essay: 44.9,
+Correspondence: 46 abd Case Study 24.8.
 
-Essay is confused with Perspective and Review.
-Review is confused with Case Study and Essay, and a few others.
-They share overlapping aspects, but are not entirely synonymous.
-A review should cover a wide range of background material (which we might also expect to find in an Essay), and might make recommendations based on the material presented (which we might also expect to find in a Case Study).
+Essay appears to be distinct enought to justify a class of its own.
+Essay is confused with Perspective and Review. Review is the second
+best category but is at times confused with Case Study and Essay. A
+possible explanation is that Review should cover a wide range of
+background material (which we may also expect to find in an Essay),
+and could make recommendations based on the material presented (which
+we might also expect to find in a Case Study).
 
@@
 
-The next decision, for higher amounts of Background, was based on the percentage of Experiment sentences in the paper.
-For a very low percentage of Experiment sentences ($<$ 0.061), the papers then branched into a long side chain of detailed classification decisions, to separate mostly the Opinion, Viewpoint and Perspective papers from other Correspondence papers, and a few examples of the remaining categories.
-For a higher percentage of Experiment sentences, Research papers were classified as those that had Observations $>$ 5.6\%, or Conclusions  $<=$ 1.4\%, whereas Case Studies had fewer Observations and more Conclusions.
+The next decision, for higher amounts of Background, was based on the
+percentage of Experiment sentences in the paper. For a very low
+percentage of Experiment sentences ($<$ 0.061), the papers then
+branched into a long side chain of detailed classification decisions,
+to separate mostly the Opinion, Viewpoint and Perspective papers from
+other Correspondence papers, and a few examples of the remaining
+categories. For a higher percentage of Experiment sentences, Research
+papers were classified as those that had Observations $>$ 5.6\%, or
+Conclusions $<=$ 1.4\%, whereas Case Studies had fewer Observations
+and more Conclusions.
 
-The largest node classifiying Essay did so via a route after the low Experiment decision that asked for a Background $>$ 48\%, but then low values for Goal, Hypothesis, Result, Observation, Model, Conclusion and Object.
-These decisions seem reasonable and agreed with our expectations of the content of an Essay.
+The largest node classifiying Essay did so via a route after the low
+Experiment decision that asked for a Background $>$ 48\%, but then low
+values for Goal, Hypothesis, Result, Observation, Model, Conclusion
+and Object. These decisions seem reasonable and agreed with our
+expectations of the content of an Essay.
 
@@
 
-To summarise, we have demonstrated that paper type can largely be predicted from the distribution of the CoreSC sentence labels in the full text of a paper.
-The CoreSC labels themselves are automatically annotated.
-We have described some of the particular CoreSC features that determine a paper type, and discussed which of the paper types are not easily separable in this way.
-Analysis of an example tree shows the decision making process to be complex, but agrees with our general understanding of paper types.
-The Partridge online system now allows refinement of paper search using CoreSC and paper type, both of which can be intelligently determined using machine learning methods.
+To summarise, we have demonstrated that paper type can largely be
+predicted from the distribution of the automatically obtained CoreSC
+sentence labels in the full text of a paper. We have described some of
+the particular CoreSC features that determine a paper type
+(e.g. Corresponsence characterised by very little Background, Opinions
+characterised by low percentage of Experiment) and discussed which of
+the paper types are not easily separable in this way. We recommended
+for example merging the Opinion, Viewpoint and Perspective articles
+into a single category, which increased overall
+classification performance. It is also potentially useful to distinguish between two types of Case study.
+Analysis of an example tree shows the decision making
+process to be complex, but agrees with our general understanding of
+paper types. The Partridge online system now allows refinement of
+paper search using CoreSC and paper type, both of which can be
+intelligently determined using machine learning methods.
 
@@
 
-The potential for automatic extraction of useful features from scientific papers to assist researchers in their knowledge queries is now an exciting area for research.
-Open Access journals that permit full text mining lead the way in allowing this research to expand and flourish.
-In future work we aim to develop and implement a range of further useful properties that will uncover more of the information that is hidden within the text of articles, and to use Partridge as a working engine to demonstrate their usefulness in practice.
+The potential for automatic extraction of useful features from
+scientific papers to assist researchers in their knowledge queries is
+now an exciting area for research. Open Access journals that permit
+full text mining lead the way in allowing this research to expand and
+flourish. In future work we aim to develop and implement a range of
+further useful properties that will uncover more of the information
+that is hidden within the text of articles, and to use Partridge as a
+working engine to demonstrate their usefulness in practice.
 
 \begin{acknowledgement}
-Thanks to the Leverhulme for Maria's funding....
+Dr Liakata is in receipt of a Leverhulme trust Early Career Fellowship.
 \end{acknowledgement}

### 2013-05-24 doc/bcspaper/article.tex
Maria edits all sections-change to authors address

@@
 % your contribution title if the original one is too long
-\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
+\author{James Ravenscroft\,$^{1}$\footnote{to whom correspondence should be addressed}, Maria Liakata\,$^{2,3}$ and Amanda Clare$^{1}$}
+\address{$^{1}$Department of Computer Science, Aberystwyth University,
+$^{2}$Department of Computer Science, University of Warwick,
+$^{2}$Text mining group, EMBL-EBI Cambridge}
+%\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
 % Use \authorrunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
-\and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}
+%\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
+%\and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}
 
@@
 \begin{acknowledgement}
-Dr Liakata is in receipt of a Leverhulme trust Early Career Fellowship.
+We thank the Leverhulme trust for the support to Dr Liakata's Early Career Fellowship and also EMBL-EBI, Cambridge UK for the facilities offered to Dr Liakata.
 \end{acknowledgement}

### 2013-05-24 doc/bcspaper/article.tex

@@
 
-Essay appears to be distinct enought to justify a class of its own.
-Essay is confused with Perspective and Review. Review is the second
-best category but is at times confused with Case Study and Essay. A
-possible explanation is that Review should cover a wide range of
-background material (which we may also expect to find in an Essay),
-and could make recommendations based on the material presented (which
-we might also expect to find in a Case Study).
-
 \begin{table}
@@
 
-We inspected the detail of a single decision tree, grown on the entire dataset, to give further insight into which CoreSC class decisions were responsible for the paper type predictions.
-This was a very large tree, with a depth of 37 nodes in places.
-The first decision was regarding the number of Background sentences in the article.
-A low Background percentage, of less than 0.694 indicates a Correspondence paper.
-28 out of the 31 papers that were classified by this decision as Correpondence were correctly labelled.
+We inspected the detail of a single decision tree, grown on the entire dataset,
+to give further insight into which CoreSC class decisions were responsible for
+the paper type predictions. This was a very large tree, with a depth of 37
+nodes in places.  The first decision was regarding the number of Background
+sentences in the article. A low Background percentage, of less than 0.694
+indicates a Correspondence paper. 28 out of the 31 papers that were classified
+by this decision as Correpondence were correctly labelled.
 
@@
 
-\begin{acknowledgement}
-We thank the Leverhulme trust for the support to Dr Liakata's Early Career Fellowship and also EMBL-EBI, Cambridge UK for the facilities offered to Dr Liakata.
-\end{acknowledgement}
+\begin{acknowledgement} We thank the Leverhulme trust for the support to Dr
+Liakata's Early Career Fellowship and also EMBL-EBI, Cambridge UK for the
+facilities offered to Dr Liakata.  \end{acknowledgement}
 

### 2013-05-24 doc/bcspaper/article.tex
Got rid of more space by condensing figures and tables. Still need to get rid of about 3 lines

@@
 
-%\usepackage{subcaption}
+\usepackage{wrapfig}
+\usepackage{subfig}
 
@@
 % your contribution title if the original one is too long
-\author{James Ravenscroft\,$^{1}$\footnote{to whom correspondence should be addressed}, Maria Liakata\,$^{2,3}$ and Amanda Clare$^{1}$}
-\address{$^{1}$Department of Computer Science, Aberystwyth University,
-$^{2}$Department of Computer Science, University of Warwick,
-$^{2}$Text mining group, EMBL-EBI Cambridge}
-%\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
+%\author{James Ravenscroft\,$^{1}$\footnote{to whom correspondence should be addressed}, Maria Liakata\,$^{2,3}$ and Amanda Clare$^{1}$}
+%\address{$^{1}$Department of Computer Science, Aberystwyth University,
+%$^{2}$Department of Computer Science, University of Warwick,
+%$^{2}$Text mining group, EMBL-EBI Cambridge}
+\author{James Ravenscroft \and Maria Liakata \and Amanda Clare}
 % Use \authorrunning{Short Title} for an abbreviated version of
 % your contribution title if the original one is too long
-%\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
-%\and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}
+\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
+\and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}
 
@@
 
-\abstract{Partridge is a system that enables intelligent search for
+\abstract*{Partridge is a system that enables intelligent search for
   academic papers by allowing users to query terms within
@@
 domain-specific counterparts; they provide a comprehensive collection of
-literature but insufficient filtering and indexing capabilities.  One of the
-most publicised and well known interdisciplinery scientific literature search
-systems is Google Scholar (\url{http://scholar.google.com}). Google offers
-advanced query options specific to Scholar that allow searching by author, year
-and for words that occur only in the document title.
+literature but insufficient filtering and indexing capabilities.
 
@@
 appears in sentences with a specific CoreSC label (e.g only in {\em Method}
-senetences). This can be used to greatly improve both the precision with which
+sentences). This can be used to greatly improve both the precision with which
 researchers are able to perform searches for scientific literature and the
@@
 been created as an intelligent full-text search platform for scientific papers.
-Partridge (which currently holds XXX papers and is constantly expanding) 
+Partridge (which currently holds 1288 papers and is constantly expanding) 
 makes use of automatically derived CoreSC sentence labels and
@@
 
-\includegraphics[width=0.75\textwidth]{figures/review_corescs.png}
-
-\includegraphics[width=0.75\textwidth]{figures/report_corescs.png}
-
+\subfloat[]{
+\includegraphics[width=0.48\textwidth]{figures/review_corescs.png}
+}
+\subfloat[]{
+\includegraphics[width=0.48\textwidth]{figures/report_corescs.png}
+}
 \caption{The CoreSC content of a review paper and a research paper randomly selected from the corpus}
 
+\vspace{-20pt}
 \label{fig:coresc_pies} 
@@
 
-\begin{table}
-\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
-\label{tab:recallPrecision}       % Give a unique label
-\begin{tabular}{p{2cm}p{2.4cm}p{2cm}p{4.9cm}}
+\begin{wraptable}{l}{0.65\textwidth}
+\vspace{-20pt}
+
+\begin{tabular}{p{2.4cm}p{1.5cm}p{1.5cm}p{1.5cm}}
 \hline\noalign{\smallskip}
@@
 \noalign{\smallskip}\svhline\noalign{\smallskip}
-Case Study   &     0.243    &    0.245     &   0.244 \\
-Correspondence  &     {\bf  0.545}    &    {\bf 0.505}    &    {\bf 0.524} \\ 
-Essay     &   0.450     &   0.462    &    0.456 \\
-Opinion   &     0.247    &    0.235  &      0.241 \\   
-Perspective &       0.255  &      0.304  &       0.277 \\
-Research     &   {\bf 0.700}    &    {\bf 0.619}    &    {\bf 0.657} \\
-Review      &  {\bf 0.631}     &   {\bf 0.625}     &   {\bf 0.628} \\
-Viewpoint   &     0.149     &   0.157  &      0.153 \\
+Case Study      &   24.3\verb|%|    &    24.5\verb|%|     &   24.4\verb|%| \\
+Correspondence  &   {\bf  54.5\verb|%|}    &    {\bf 50.5\verb|%|}    &    {\bf 52.4\verb|%|} \\ 
+Essay           &   45.0\verb|%|     &   46.2\verb|%|    &    45.6\verb|%| \\
+Opinion         &   24.7\verb|%|    &    23.5\verb|%|  &      24.1\verb|%| \\   
+Perspective     &   25.5\verb|%|  &      30.4\verb|%|  &       27.7\verb|%| \\
+Research        &   {\bf 70.0\verb|%|}    &    {\bf 61.9\verb|%|}    &    {\bf 65.7\verb|%|} \\
+Review          &  {\bf 63.1\verb|%|}     &   {\bf 62.5\verb|%|}     &   {\bf 62.8\verb|%|} \\
+Viewpoint       &     14.9\verb|%|     &   15.7\verb|%|  &      15.3\verb|%| \\
 \noalign{\smallskip}\hline\noalign{\smallskip}
 \end{tabular}
-\end{table}
+\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
+\label{tab:recallPrecision}       % Give a unique label
+\vspace{-30pt}
+\end{wraptable}
 

### 2013-05-24 doc/bcspaper/article.tex
Very close to fitting everything onto 6 pages

@@
 
-\abstract*{Partridge is a system that enables intelligent search for
+\abstract{Partridge is a system that enables intelligent search for
   academic papers by allowing users to query terms within
@@
 
-\section{Introduction} \label{sec:1} Since the advent of the `Digital Age' and
-the ability of computers to copy and reproduce information for a negligible
-cost, the amount of information available to researchers has been increasing
-drastically. As available information increases, relevant material becomes
+\vspace{-15pt}
+\section{Introduction} \label{sec:1}
+
+Since the advent of the `Digital Age', the amount of information available to
+researchers has been increasing drastically and relevant material is becoming
 progressively more difficult to find manually and the need for an automated
@@
 
+\vspace{-15pt}
 \section{Methods}
@@
 
-\subfloat[]{
-\includegraphics[width=0.48\textwidth]{figures/review_corescs.png}
+\subfloat{
+\includegraphics[width=0.45\textwidth]{figures/review_corescs.png}
 }
-\subfloat[]{
-\includegraphics[width=0.48\textwidth]{figures/report_corescs.png}
+\subfloat{
+\includegraphics[width=0.45\textwidth]{figures/report_corescs.png}
 }
@@
 
+\vspace{-15pt}
 \section{Results and Discussion}
@@
 
-The results of the random forest learning as recall, precision and F-measure
-for each paper type, averaged over a 10-fold cross validation are shown in Table
-\ref{tab:recallPrecision}. Paper types {\em Research}, {\em Review} and {\em
-Correspondence} are the most accurate classes, and {\em Viewpoint} is the most
-difficult paper type to predict.
-
-\begin{wraptable}{l}{0.65\textwidth}
-\vspace{-20pt}
+\begin{table}
 
@@
 \caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
+
+\vspace{-20pt}
 \label{tab:recallPrecision}       % Give a unique label
-\vspace{-30pt}
-\end{wraptable}
+\end{table}
+
+The results of the random forest learning as recall, precision and F-measure
+for each paper type, averaged over a 10-fold cross validation are shown in Table
+\ref{tab:recallPrecision}. Paper types {\em Research}, {\em Review} and {\em
+Correspondence} are the most accurate classes, and {\em Viewpoint} is the most
+difficult paper type to predict.
 
@@
 \begin{table}
+
+\vspace{-10pt}
+
 \caption{Confusion matrix summed over 10-fold cross validation, reporting the results on the held-out validation segment. Rows represent true classes, columns represent predicted classes.}
-\label{tab:confusion}       % Give a unique label
+\label{tab:confusion}       % Give a unique label]
+
 \begin{tabular}{lllllllll}
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}
+\end{tabular}]
+\vspace{-15pt}
 \end{table}
@@
 
+\vspace{-15pt}
 \section{Conclusion}
@@
 
+\vspace{-15pt}
 \bibliographystyle{plain}

### 2013-05-24 doc/bcspaper/article.tex
tried to fix table layout
spelling and shortening of bib entries

@@
   possibilities for more intelligent search in the scientific
-  literature. The Partidge instance can be used at
-  \url{http://farnsworth.papro.org.uk}, and further information about
+  literature. The Partridge instance and further information about
   the project can be found at \url{http://papro.org.uk}}
@@
 there are also a number of interdisciplinary indexing systems and online
-journals such as arXiv( \url{http://arxiv.org/}),
-PloSOne(\url{http://plosone.org/}), and JSTOR (\url{http://www.jstor.org/}),
+journals such as arXiv and 
+PloSOne
 that try to incorporate wide ranges of papers from as many disciplines as
@@
 chemistry and biochemistry research papers whose sentences were manually
-annotated using the CoreSC\cite{LIAKATA10.644} scheme.  An intelligent academic
+annotated using the CoreSC\cite{LIAKATA10.644} scheme.  An intelligent 
 information retrieval system can use this data to provide better filtering and
@@
 
-The type of a paper ({\em review}, {\em case study}, {\em research}, {\em
-perspective}, etc) is another useful feature through which a user can narrow
+The type of a paper ({\em Review}, {\em Case Study}, {\em Research}, {\em
+Perspective}, etc) is another useful feature through which a user can narrow
 down the results of a search.  The type of a paper can then be used to augment
-queries.  For example, a user may search for a {\em review} paper containing
-the keywords ``PCR microfluidics'', or a {\em research} paper with a {\em
-hypothesis} containing the keywords ``cerevisiae'' and ``glucose''.   Such
+queries.  For example, a user may search for a {\em Review} paper containing
+the keywords ``PCR microfluidics'', or a {\em Research} paper with a {\em
+Hypothesis} containing the keywords ``cerevisiae'' and ``glucose''.   Such
 paper types are not yet standardised by journals.  We expect the structure of a
@@
 literature under a permissive license that allows data mining.  They also use
-the Pubmed Central markup schema, which is compatible with SAPIENTA, for papers
+the PubMed Central markup schema, which is compatible with SAPIENTA, for papers
 published through their journal. The PLoS journals advanced search offers
@@
 these paper type categories contain too few papers to be useful, others are too
-specific (e.g.``Message from PLoS'') or appear rather adhoc. Indeed it is not
+specific (e.g. {\it Message from PLoS}) or appear rather {\it ad hoc}. Indeed it is not
 clear how these paper types have been identified. We chose to look at a range
@@
 
+\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
+
 \begin{tabular}{p{2.4cm}p{1.5cm}p{1.5cm}p{1.5cm}}
@@
 \end{tabular}
-\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
 
@@
 Study. However, Case Study papers are often predicted to be Research
-or Review. The ratio between Case study, Research and Review papers is
+or Review. The ratio between Case Study, Research and Review papers is
 ~1:2:3 so the outcome is not entirely surprising in terms of the data
@@
 on a super class consisting of the previous three categories,
-performance was improved overall with the following f-measures:
-OpinionSuper: 59, Research: 67.6, Review: 63.7, Essay: 44.9,
-Correspondence: 46 abd Case Study 24.8.
+performance was improved overall with the following F-measures:
+{\bf OpinionSuper: 59, Research: 67.6, Review: 63.7, Essay: 44.9,
+Correspondence: 46 and Case Study 24.8}.
 
@@
 \noalign{\smallskip}\hline\noalign{\smallskip}
-\end{tabular}]
+\end{tabular}
 \vspace{-15pt}
@@
 indicates a Correspondence paper. 28 out of the 31 papers that were classified
-by this decision as Correpondence were correctly labelled.
+by this decision as Correspondence were correctly labelled.
 
@@
 
-The largest node classifiying Essay did so via a route after the low
+The largest node classifying Essay did so via a route after the low
 Experiment decision that asked for a Background $>$ 48\%, but then low
@@
 the particular CoreSC features that determine a paper type
-(e.g. Corresponsence characterised by very little Background, Opinions
+(e.g. Correspondence characterised by very little Background, Opinions
 characterised by low percentage of Experiment) and discussed which of

### 2013-05-24 doc/bcspaper/article.tex
Added subfig caption=false to bring down to 6 pages
Fixed percentages in table 1

@@
 \usepackage{wrapfig}
-\usepackage{subfig}
+\usepackage[caption=false]{subfig}
 
@@
 }
-\caption{The CoreSC content of a review paper and a research paper randomly selected from the corpus}
+\caption{The CoreSC content of a review paper (left) and a research paper (right) randomly selected from the corpus}
 
@@
 
-\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment}
+\caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment. Top paper types in bold.}
 
-\begin{tabular}{p{2.4cm}p{1.5cm}p{1.5cm}p{1.5cm}}
+\begin{tabular}{p{2.4cm}p{2.0cm}p{2.0cm}p{2.5cm}}
 \hline\noalign{\smallskip}
-Classes & Recall & Precision & F-measure  \\
+Classes & Recall(\verb|%|) & Precision(\verb|%|)& F-measure(\verb|%|) \\
 \noalign{\smallskip}\svhline\noalign{\smallskip}
-Case Study      &   24.3\verb|%|    &    24.5\verb|%|     &   24.4\verb|%| \\
-Correspondence  &   {\bf  54.5\verb|%|}    &    {\bf 50.5\verb|%|}    &    {\bf 52.4\verb|%|} \\ 
-Essay           &   45.0\verb|%|     &   46.2\verb|%|    &    45.6\verb|%| \\
-Opinion         &   24.7\verb|%|    &    23.5\verb|%|  &      24.1\verb|%| \\   
-Perspective     &   25.5\verb|%|  &      30.4\verb|%|  &       27.7\verb|%| \\
-Research        &   {\bf 70.0\verb|%|}    &    {\bf 61.9\verb|%|}    &    {\bf 65.7\verb|%|} \\
-Review          &  {\bf 63.1\verb|%|}     &   {\bf 62.5\verb|%|}     &   {\bf 62.8\verb|%|} \\
-Viewpoint       &     14.9\verb|%|     &   15.7\verb|%|  &      15.3\verb|%| \\
+Case Study      &   24.3    &    24.5     &   24.4 \\
+Correspondence  &   {\bf  54.5}    &    {\bf 50.5}    &    {\bf 52.4} \\ 
+Essay           &   45.0     &   46.2    &    45.6 \\
+Opinion         &   24.7    &    23.5  &      24.1 \\   
+Perspective     &   25.5  &      30.4  &       27.7 \\
+Research        &   {\bf 70.0}    &    {\bf 61.9}    &    {\bf 65.7} \\
+Review          &  {\bf 63.1}     &   {\bf 62.5}     &   {\bf 62.8} \\
+Viewpoint       &     14.9     &   15.7  &      15.3 \\
 \noalign{\smallskip}\hline\noalign{\smallskip}

### 2013-05-25 doc/bcspaper/article.tex
Expanded PloS rather than reporting url twice
Updated James' email address to ravenscroft@papro.org.uk

@@
 % your contribution title if the original one is too long
-\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{jrr9@aber.ac.uk}
+\institute{James Ravenscroft, Amanda Clare \at Department of Computer Science, Aberystwyth University, Aberystwyth, SY23 3DB, UK  \email{ravenscroft@papro.org.uk}, \email{afc@aber.ac.uk}
 \and Maria Liakata \at Department of Computer Science, University of Warwick \email{M.Liakata@warwick.ac.uk}}
@@
 Access (OA) journals provide free read access to their papers, but many do not
-permit the user of articles for data mining purposes. The PLoS
-journals\footnote{PLoS: \url{http://www.plos.org/}} contain large volumes of OA
-literature under a permissive license that allows data mining.  They also use
-the PubMed Central markup schema, which is compatible with SAPIENTA, for papers
-published through their journal. The PLoS journals advanced search offers
-approximately 50 types of paper through which to restrict the search.  Many of
-these paper type categories contain too few papers to be useful, others are too
-specific (e.g. {\it Message from PLoS}) or appear rather {\it ad hoc}. Indeed it is not
-clear how these paper types have been identified. We chose to look at a range
-of types, some of which we expect to overlap or have an unclear distinction.
-These are namely: Essay, Correspondence, Case Study, Perspective,
-Viewpoint, Opinion, Review, Research.
+permit the user of articles for data mining purposes. The Public Library of
+Science (PLoS) journals contain large volumes of OA literature under a
+permissive license that allows data mining.  They also use the PubMed Central
+markup schema, which is compatible with SAPIENTA, for papers published through
+their journal. The PLoS journals advanced search offers approximately 50 types
+of paper through which to restrict the search.  Many of these paper type
+categories contain too few papers to be useful, others are too specific (e.g.
+{\it Message from PLoS}) or appear rather {\it ad hoc}. Indeed it is not clear
+how these paper types have been identified. We chose to look at a range of
+types, some of which we expect to overlap or have an unclear distinction.
+These are namely: Essay, Correspondence, Case Study, Perspective, Viewpoint,
+Opinion, Review, Research.
 

### 2013-05-26 doc/bcspaper/article.tex
made some changes as requested by Amanda

@@
   The system also automatically classifies papers according to
-  article types (e.g. Review, Case Study). Here we focus on the latter
+  article types (e.g. Review, Case Study). Here, we focus on the latter
   aspect of the system. For each paper, Partridge automatically
@@
 there are also a number of interdisciplinary indexing systems and online
-journals such as arXiv and 
-PloSOne
-that try to incorporate wide ranges of papers from as many disciplines as
-possible. The traits of these systems often complement those of their
-domain-specific counterparts; they provide a comprehensive collection of
-literature but insufficient filtering and indexing capabilities.
+journals such as arXiv and PloSOne that try to incorporate wide ranges of
+papers from as many disciplines as possible. The traits of these systems often
+complement those of their domain-specific counterparts; they provide a
+comprehensive collection of literature but insufficient filtering and indexing
+capabilities, usually based on title and abstract.
 
@@
 
-\subfloat{
-\includegraphics[width=0.45\textwidth]{figures/review_corescs.png}
-}
-\subfloat{
-\includegraphics[width=0.45\textwidth]{figures/report_corescs.png}
-}
-\caption{The CoreSC content of a review paper (left) and a research paper (right) randomly selected from the corpus}
+%\subfloat{
+\includegraphics[width=0.75\textwidth]{figures/corescs.png}
+%}
+%\subfloat{
+%\includegraphics[width=0.45\textwidth]{figures/report_corescs.png}
+%}
+\caption{The CoreSC content of a research paper (left) and a review paper (right) randomly selected from the corpus}
 

### 2013-05-26 partridge/mltest/paper_forest.py
Made charts uniform colours

@@ -29,10 +29,11 @@ TYPE_DIRS = {
     "Case Study" : "/home/james/dissertation/papers_for_type/case", 
     #"Subjective" : "/home/james/dissertation/papers_for_type/subjective",
     "Essay"      : "/home/james/dissertation/papers_for_type/essay",
-    "Opinion"    : "/home/james/dissertation/papers_for_type/opinion",
-    "Perspective": "/home/james/dissertation/papers_for_type/perspective",
-    "Viewpoint"  : "/home/james/dissertation/papers_for_type/viewpoints",
-    "Synopsis"   : "/home/james/dissertation/papers_for_type/synopsis",
+    "OpinionSuper": "/home/james/dissertation/papers_for_type/view_per_op",
+    #"Opinion"    : "/home/james/dissertation/papers_for_type/opinion",
+    #"Perspective": "/home/james/dissertation/papers_for_type/perspective",
+    #"Viewpoint"  : "/home/james/dissertation/papers_for_type/viewpoints",
+    #"Synopsis"   : "/home/james/dissertation/papers_for_type/synopsis",
     "Correspondence" : "/home/james/dissertation/papers_for_type/correspondence"
 }
 
@@ -136,7 +137,7 @@ def printMeasures( confusion ):
     print "Class\t\tRecall\t\tPrecision\t\tF-measure"
     print "-----------------------------------------------"
 
-    for c in confusion:
+    for c in sorted(confusion):
         recall  = confusion[c][c] / sum(confusion[c].values())
 
 

### 2013-05-26 partridge/mltest/paper_tree.py

@@ -57,7 +57,8 @@ def main():
         printMeasures(confusion)
         
 
-        orngTree.printTxt(results.classifiers[k][i], leafFields=['major', 'contingency'])
+        orngTree.printTxt(results.classifiers[k][i], leafStr="%V (%M / %N)",
+        nodeStr="(%M / %N)", leafFields=['major', 'contingency'])
 
 if __name__ == "__main__":
     main()

### 2013-05-26 partridge/models/doc.py

@@ -44,7 +44,7 @@ class Paper( db.Model ):
   def sentenceDistribution(self, returnCounter=False):
     totalSentences = len(self.sentences)
 
-    count = Counter()
+    count = Counter({x:0 for x in C_ABRV})
 
     for sent in self.sentences:
         count[sent.coresc] += 1
@@ -54,11 +54,10 @@ class Paper( db.Model ):
 
     percentages = []
 
-    for label, num in count.items():
+    for label, num in sorted(count.items(), key=lambda x: x[0]):
         percentages.append( (C_ABRV[label], num * 100 / totalSentences) )
     
     return percentages
-        
 
 #-----------------------------------------------------------------------------
 

### 2013-05-26 doc/bcspaper/article.tex
Fixed Maria's comments

@@
 Since the advent of the `Digital Age', the amount of information available to
-researchers has been increasing drastically and relevant material is becoming
+researchers has been increasing drastically, relevant material is becoming
 progressively more difficult to find manually and the need for an automated
@@
 of paper through which to restrict the search.  Many of these paper type
-categories contain too few papers to be useful, others are too specific (e.g.
-{\it Message from PLoS}) or appear rather {\it ad hoc}. Indeed it is not clear
-how these paper types have been identified. We chose to look at a range of
-types, some of which we expect to overlap or have an unclear distinction.
-These are namely: Essay, Correspondence, Case Study, Perspective, Viewpoint,
-Opinion, Review, Research.
+categories contain too few papers to be useful, others are too ad hoc (e.g.
+{\it Message from PLoS}). Indeed it is not clear how these paper types have
+been identified. We chose to look at a range of types, some of which we expect
+to overlap or have an unclear distinction.  These are namely: Essay,
+Correspondence, Case Study, Perspective, Viewpoint, Opinion, Review, Research.
 

### 2013-06-27 doc/bcspaper/article.tex
Updated reference to Alex C's pdfx paper

@@
 , a free service hosted by the University of Manchester
-(\url{http://pdfx.cs.man.ac.uk/}). Once the paper has been split into
+(\cite{Constantin2013}). Once the paper has been split into
 sentences, SAPIENTA is used to annotate each sentence with a relevant

### 2013-07-15 doc/bcspaper/article.tex
Started changing things to appease reviewers

@@
 information retrieval and recommendation systems for scientific publications.
-Many of these systems, such as AGRICOLA (\url{http://agricola.nal.usda.gov/}),
-the Cochrane Library(\url{http://www.thecochranelibrary.com/}) and Textpresso
-(\url{http://www.textpresso.org/}) index only publications from predefined
+Many of these systems, such as AGRICOLA \footnote{\url{http://agricola.nal.usda.gov/}},
+the Cochrane Library\footnote{\url{http://www.thecochranelibrary.com/}} and Textpresso
+\footnote{\url{http://www.textpresso.org/}} index only publications from predefined
 journals or topics (for the above examples, Agriculture, Biology and
@@
 there are also a number of interdisciplinary indexing systems and online
-journals such as arXiv and PloSOne that try to incorporate wide ranges of
+journals such as arXiv \footnote{\url{http://arxiv.org}} and PloSOne
+\footnote{\url{http://plosone.org}} that try to incorporate wide ranges of
 papers from as many disciplines as possible. The traits of these systems often
@@
 to identify which scientific concept each sentence encapsulates.  SAPIENTA
-(\url{http://www.sapientaproject.com}) is a publicly available machine learning
+\footnote{\url{http://www.sapientaproject.com}} is a publicly available machine learning
 application which can automatically annotate all sentences in a scientific
@@
 
-% in conclusions add how this can give recommendations for Plos and other journals 
-The papers were downloaded from PLoS using {\em plosget.py}, a short
-python script that uses the PLoS RESTful search API. The number of
-papers downloaded per paper type category was as follows: 200 Essay,
-99 Correspondence, 107 Case Study, 200 Perspective, 74 Viewpoint, 93
-Opinion, 312 Review, 200 Research.  These formed a corpus of 1285 %1459-174 after removing synopsis. Should double check the numbers add up
-papers.
+% in conclusions add how this can give recommendations for Plos and other
+% journals 
+A script called {\em plosget.py} was written, in order to download the
+papers via the PloS RESTful search API \footnote{\url{http://api.plos.org/solr/faq/}}. The number of papers downloaded per
+paper type category was as follows: 200 Essay, 99 Correspondence, 107 Case
+Study, 200 Perspective, 74 Viewpoint, 93 Opinion, 312 Review, 200 Research.
+These formed a corpus of 1285 %1459-174 after removing synopsis. Should double
+check the numbers add up papers.
 
@@
 
-A confusion matrix for the paper types in given in Table
+A confusion matrix for the paper types is given in Table
 \ref{tab:confusion}. Research papers are usually predicted to belong
@@
 \vspace{-15pt}
-\section{Conclusion}
+\section{Summary and Conclusions}
 \label{sec:4}
 
-To summarise, we have demonstrated that paper type can largely be
-predicted from the distribution of the automatically obtained CoreSC
-sentence labels in the full text of a paper. We have described some of
-the particular CoreSC features that determine a paper type
-(e.g. Correspondence characterised by very little Background, Opinions
-characterised by low percentage of Experiment) and discussed which of
-the paper types are not easily separable in this way. We recommended
-for example merging the Opinion, Viewpoint and Perspective articles
-into a single category, which increased overall
-classification performance. It is also potentially useful to distinguish between two types of Case study.
-Analysis of an example tree shows the decision making
-process to be complex, but agrees with our general understanding of
-paper types. The Partridge online system now allows refinement of
-paper search using CoreSC and paper type, both of which can be
-intelligently determined using machine learning methods.
+To summarise, we have demonstrated that paper type can largely be predicted
+from the distribution of the automatically obtained CoreSC sentence labels in
+the full text of a paper. We have described some of the particular CoreSC
+features that determine a paper type (e.g. Correspondence characterised by very
+little Background, Opinions characterised by low percentage of Experiment) and
+discussed which of the paper types are not easily separable in this way. We
+recommended for example merging the Opinion, Viewpoint and Perspective articles
+into a single category, which increased overall classification performance. It
+is also potentially useful to distinguish between two types of Case study.
+Analysis of an example tree shows the decision making process to be complex,
+but agrees with our general understanding of paper types. The Partridge system
+allows refinement of paper search using CoreSC and paper type, both of which
+can be intelligently determined using machine learning methods.
 

### 2013-07-16 doc/bcspaper/article.tex
Fixed 6 pages issue with vspaces, horrible but it worked

@@
 \section{Introduction} \label{sec:1}
-
+\vspace{-11pt}
 Since the advent of the `Digital Age', the amount of information available to
@@
 information retrieval and recommendation systems for scientific publications.
-Many of these systems, such as AGRICOLA \footnote{\url{http://agricola.nal.usda.gov/}},
+Many of these systems, such as AGRICOLA\footnote{\url{http://agricola.nal.usda.gov/}},
 the Cochrane Library\footnote{\url{http://www.thecochranelibrary.com/}} and Textpresso
@@
 
-\subsection*{Collection of scientific articles} Partridge allows users to
-upload any paper which is free of copyright restrictions.  For the purpose of
-this study we needed a large set of papers that we could label with CoreSC to
-investigate how this information assists classification into paper type.  Open
-Access (OA) journals provide free read access to their papers, but many do not
-permit the user of articles for data mining purposes. The Public Library of
-Science (PLoS) journals contain large volumes of OA literature under a
-permissive license that allows data mining.  They also use the PubMed Central
-markup schema, which is compatible with SAPIENTA, for papers published through
-their journal. The PLoS journals advanced search offers approximately 50 types
-of paper through which to restrict the search.  Many of these paper type
-categories contain too few papers to be useful, others are too ad hoc (e.g.
-{\it Message from PLoS}). Indeed it is not clear how these paper types have
-been identified. We chose to look at a range of types, some of which we expect
-to overlap or have an unclear distinction.  These are namely: Essay,
-Correspondence, Case Study, Perspective, Viewpoint, Opinion, Review, Research.
+\subsection*{Collection of scientific articles} 
+\vspace{-15pt}
+Partridge allows users to upload any paper which is free of copyright
+restrictions.  For the purpose of this study we needed a large set of papers
+that we could label with CoreSC to investigate how this information assists
+classification into paper type.  Open Access (OA) journals provide free read
+access to their papers, but many do not permit the user of articles for data
+mining purposes. The Public Library of Science (PLoS) journals contain large
+volumes of OA literature under a permissive license that allows data mining.
+They also use the PubMed Central markup schema, which is compatible with
+SAPIENTA, for papers published through their journal. The PLoS journals
+advanced search offers approximately 50 types of paper through which to
+restrict the search.  Many of these paper type categories contain too few
+papers to be useful, others are too ad hoc (e.g.  {\it Message from PLoS}).
+Indeed it is not clear how these paper types have been identified. We chose to
+look at a range of types, some of which we expect to overlap or have an unclear
+distinction.  These are namely: Essay, Correspondence, Case Study, Perspective,
+Viewpoint, Opinion, Review, Research.
 
@@
 
+\begin{figure}[t]
+\centering
+\includegraphics[width=0.75\textwidth]{figures/corescs.png}
+\caption{The CoreSC content of a research paper (left) and a review paper (right) randomly selected from the corpus}
+\vspace{-20pt}
+\label{fig:coresc_pies} 
+\end{figure}
+
 \subsection*{Paper Processing and classification}
 %Discuss in more detail how Partridge processes papers (PDFX, sentence splitting) 
+\vspace{-15pt}
+
 In order to obtain automatic labeling of sentences in a paper with
@@
 papers and we have done no domain adaptation for the papers in PLoS.
-
-\begin{figure}[t]
-
-\centering
-
-%\subfloat{
-\includegraphics[width=0.75\textwidth]{figures/corescs.png}
-%}
-%\subfloat{
-%\includegraphics[width=0.45\textwidth]{figures/report_corescs.png}
-%}
-\caption{The CoreSC content of a research paper (left) and a review paper (right) randomly selected from the corpus}
-
-\vspace{-20pt}
-\label{fig:coresc_pies} 
-\end{figure}
 
@@
 \label{sec:3}
+\vspace{-15pt}
 
@@
 
+\vspace{-10pt}
 \caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment. Top paper types in bold.}
@@
 the paper type predictions. This was a very large tree, with a depth of 37
-nodes in places.  The first decision was regarding the number of Background
-sentences in the article. A low Background percentage, of less than 0.694
-indicates a Correspondence paper. 28 out of the 31 papers that were classified
-by this decision as Correspondence were correctly labelled.
+nodes in places.  The first decision was based upon the number of Background
+sentences in the article. Low Background percentages, of less than 0.694
+indicates a Correspondence paper. 28 out of the 31 Correspondence papers were
+correctly labelled by this decision  classified by this decision as
+Correspondence were correctly labelled.
 
@@
 \label{sec:4}
-
+\vspace{-15pt}
 To summarise, we have demonstrated that paper type can largely be predicted
@@
 Analysis of an example tree shows the decision making process to be complex,
-but agrees with our general understanding of paper types. The Partridge system
-allows refinement of paper search using CoreSC and paper type, both of which
+but agrees with our general understanding of paper types. Partridge allows refinement of paper search using CoreSC and paper type, both of which
 can be intelligently determined using machine learning methods.
@@
 
+\vspace{-10pt}
 \begin{acknowledgement} We thank the Leverhulme trust for the support to Dr
@@
 facilities offered to Dr Liakata.  \end{acknowledgement}
+\vspace{-2pt}
 
-\vspace{-15pt}
+\vspace{-30pt}
 \bibliographystyle{plain}

### 2013-07-17 doc/bcspaper/article.tex
Made some more minor changes to the article formatting

@@
 \vspace{-11pt}
+
 Since the advent of the `Digital Age', the amount of information available to
@@
 information retrieval and recommendation systems for scientific publications.
-Many of these systems, such as AGRICOLA\footnote{\url{http://agricola.nal.usda.gov/}},
-the Cochrane Library\footnote{\url{http://www.thecochranelibrary.com/}} and Textpresso
-\footnote{\url{http://www.textpresso.org/}} index only publications from predefined
-journals or topics (for the above examples, Agriculture, Biology and
-Bioinformatics respectively).  Unfortunately, these domain specific indexing
-systems usually only contain a small subset of papers, excluding potentially
-crucial literature because it does not quite fit into the subject domain.
+Many of these systems, such as
+AGRICOLA\footnote{\url{http://agricola.nal.usda.gov/}}, the Cochrane
+Library\footnote{\url{http://www.thecochranelibrary.com/}} and
+Textpresso\footnote{\url{http://www.textpresso.org/}} index only publications
+from predefined journals or topics (for the above examples, Agriculture,
+Biology and Bioinformatics respectively).  Unfortunately, these domain specific
+indexing systems usually only contain a small subset of papers, excluding
+potentially crucial literature because it does not quite fit into the subject
+domain.
 
@@
 there are also a number of interdisciplinary indexing systems and online
-journals such as arXiv \footnote{\url{http://arxiv.org}} and PloSOne
-\footnote{\url{http://plosone.org}} that try to incorporate wide ranges of
-papers from as many disciplines as possible. The traits of these systems often
-complement those of their domain-specific counterparts; they provide a
+journals such as arXiv\footnote{\url{http://arxiv.org}} and
+PloSOne\footnote{\url{http://plosone.org}} that try to incorporate wide ranges
+of papers from as many disciplines as possible. The traits of these systems
+often complement those of their domain-specific counterparts; they provide a
 comprehensive collection of literature but insufficient filtering and indexing
@@
 automatically processing and classifying sentences in a research paper
-according to the core scientific concept (CoreSC) that they
-describe\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis},
-{\em Goal}, {\it Background}, {\em Method}, {\em Result} and {\em Conclusion}.
+according to the core scientific concept (CoreSC) that they describe
+\cite{Liakata2012}.  There are 11 CoreSCs, including {\em Hypothesis}, {\em
+Goal}, {\it Background}, {\em Method}, {\em Result} and {\em Conclusion}.
 CoreSC labels can be allocated to all sentences in a scientific paper in order
-to identify which scientific concept each sentence encapsulates.  SAPIENTA
-\footnote{\url{http://www.sapientaproject.com}} is a publicly available machine learning
-application which can automatically annotate all sentences in a scientific
-paper with their CoreSC labels. It was trained using a corpus of physical
-chemistry and biochemistry research papers whose sentences were manually
-annotated using the CoreSC\cite{LIAKATA10.644} scheme.  An intelligent 
-information retrieval system can use this data to provide better filtering and
-search capabilities for researchers.  Partridge implements such context-aware
-keyword search, by allowing researchers to search for papers where a term
-appears in sentences with a specific CoreSC label (e.g only in {\em Method}
-sentences). This can be used to greatly improve both the precision with which
-researchers are able to perform searches for scientific literature and the
-accuracy of those searches in terms of relevance to the reader.
+to identify which scientific concept each sentence encapsulates.
+SAPIENTA\footnote{\url{http://www.sapientaproject.com}} is a publicly available
+machine learning application which can automatically annotate all sentences in
+a scientific paper with their CoreSC labels. It was trained using a corpus of
+physical chemistry and biochemistry research papers whose sentences were
+manually annotated using the CoreSC \cite{LIAKATA10.644} scheme.  An
+intelligent information retrieval system can use this data to provide better
+filtering and search capabilities for researchers.  Partridge implements such
+context-aware keyword search, by allowing researchers to search for papers
+where a term appears in sentences with a specific CoreSC label (e.g only in
+{\em Method} sentences). This can be used to greatly improve both the precision
+with which researchers are able to perform searches for scientific literature
+and the accuracy of those searches in terms of relevance to the reader.
 
@@
 A script called {\em plosget.py} was written, in order to download the
-papers via the PloS RESTful search API \footnote{\url{http://api.plos.org/solr/faq/}}. The number of papers downloaded per
+papers via the PloS RESTful search API\footnote{\url{http://api.plos.org/solr/faq/}}. The number of papers downloaded per
 paper type category was as follows: 200 Essay, 99 Correspondence, 107 Case
@@
 
-In order to obtain automatic labeling of sentences in a paper with
-CoreSC concepts we first needed to convert the papers to a format that
-the the CoreSC classifier, SAPIENTA can analyse.  Currently, SAPIENTA
-supports the SciXML and PubMed Central DTDs.  Papers in PDF format are
-first converted to XML using PDFX %\cite{PDFX} - no paper known yet
-, a free service hosted by the University of Manchester
-(\cite{Constantin2013}). Once the paper has been split into
-sentences, SAPIENTA is used to annotate each sentence with a relevant
-CoreSC label. These labels are assigned using a conditional random
-fields model based upon a number of features such as the sentence's
-location within the paper and pairs and triplets of words found
-consecutively within the sentence \cite{Liakata2012}.  The SAPIENTA
-system has been trained on a corpus of 265 chemistry and biochemistry
-papers and we have done no domain adaptation for the papers in PLoS.
+In order to obtain automatic labeling of sentences in a paper with CoreSC
+concepts we first needed to convert the papers to a format that the the CoreSC
+classifier, SAPIENTA can analyse.  Currently, SAPIENTA supports the SciXML and
+PubMed Central DTDs.  Papers in PDF format are first converted to XML using
+PDFX , a free service hosted by the University of Manchester
+\cite{Constantin2013}. Once the paper has been split into sentences, SAPIENTA
+is used to annotate each sentence with a relevant CoreSC label. These labels
+are assigned using a conditional random fields model based upon a number of
+features such as the sentence's location within the paper and pairs and
+triplets of words found consecutively within the sentence \cite{Liakata2012}.
+The SAPIENTA system has been trained on a corpus of 265 chemistry and
+biochemistry papers and we have done no domain adaptation for the papers in
+PLoS.
 
@@
 
-Random forest learning\cite{Breiman2001} was chosen for the construction of the
+Random forest learning \cite{Breiman2001} was chosen for the construction of the
 paper type classifier. This is because random forests are a fast, accurate and

### 2013-07-22 doc/bcspaper/article.tex
Removed ugly formatting from paper

@@
 
-\vspace{-15pt}
 \section{Introduction} \label{sec:1}
-\vspace{-11pt}
 
@@
 
-\vspace{-15pt}
 \section{Methods}
@@
 \subsection*{Collection of scientific articles} 
-\vspace{-15pt}
 Partridge allows users to upload any paper which is free of copyright
@@
 \caption{The CoreSC content of a research paper (left) and a review paper (right) randomly selected from the corpus}
-\vspace{-20pt}
 \label{fig:coresc_pies} 
@@
 %Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)
-\vspace{-15pt}
 
@@
 
-\vspace{-15pt}
 \section{Results and Discussion}
 \label{sec:3}
-\vspace{-15pt}
 
@@
 
-\vspace{-10pt}
 \caption{Per-class recall, precision and F-measure micro-averaged over 10-fold cross validation, reporting the results on the held-out validation segment. Top paper types in bold.}
@@
 
-\vspace{-20pt}
 \label{tab:recallPrecision}       % Give a unique label
@@
 
-\vspace{-10pt}
-
 \caption{Confusion matrix summed over 10-fold cross validation, reporting the results on the held-out validation segment. Rows represent true classes, columns represent predicted classes.}
@@
 \end{tabular}
-\vspace{-15pt}
 \end{table}
@@
 
-\vspace{-15pt}
 \section{Summary and Conclusions}
 \label{sec:4}
-\vspace{-15pt}
 To summarise, we have demonstrated that paper type can largely be predicted
@@
 
-\vspace{-10pt}
 \begin{acknowledgement} We thank the Leverhulme trust for the support to Dr
@@
 facilities offered to Dr Liakata.  \end{acknowledgement}
-\vspace{-2pt}
 
-\vspace{-30pt}
 \bibliographystyle{plain}

### 2013-07-24 doc/bcspaper/article.tex
Updated bib style in line with BCS:SGAI guidelines

@@
 % journals 
-A script called {\em plosget.py} was written, in order to download the
+A script called {\em plosget.py}\footnote{\url{https://github.com/ravenscroftj/partridge}} was written, in order to download the
 papers via the PloS RESTful search API\footnote{\url{http://api.plos.org/solr/faq/}}. The number of papers downloaded per
@@
 
-\bibliographystyle{plain}
+\bibliographystyle{acm}
 \bibliography{partridge}

### 2013-08-10 doc/bcspaper/article.tex
Fixed reference to orange and capitalised Leverhulme

@@
 
-\begin{acknowledgement} We thank the Leverhulme trust for the support to Dr
+\begin{acknowledgement} We thank the Leverhulme Trust for the support to Dr
 Liakata's Early Career Fellowship and also EMBL-EBI, Cambridge UK for the

### 2013-08-18 doc/bcspaper/article.tex
made some changes in accordance with maria's suggestions

@@
 
-\subsection*{Paper Processing and classification}
+\subsection*{Paper Processing and Classification}
 %Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)
@@
 PDFX , a free service hosted by the University of Manchester
-\cite{Constantin2013}. Once the paper has been split into sentences, SAPIENTA
-is used to annotate each sentence with a relevant CoreSC label. These labels
-are assigned using a conditional random fields model based upon a number of
-features such as the sentence's location within the paper and pairs and
-triplets of words found consecutively within the sentence \cite{Liakata2012}.
-The SAPIENTA system has been trained on a corpus of 265 chemistry and
-biochemistry papers and we have done no domain adaptation for the papers in
-PLoS.
+\cite{Constantin2013}. Once the paper has been split into sentences with
+Liakata's SSplit tool \cite{liakata2009semantic}, SAPIENTA is used to annotate
+each sentence with a relevant CoreSC label. These labels are assigned using a
+conditional random fields model based upon a number of features such as the
+sentence's location within the paper and pairs and triplets of words found
+consecutively within the sentence \cite{Liakata2012}.  The SAPIENTA system has
+been trained on a corpus of 265 chemistry and biochemistry papers and we have
+done no domain adaptation for the papers in PLoS.
 
@@
 We inspected the detail of a single decision tree, grown on the entire dataset,
-to give further insight into which CoreSC class decisions were responsible for
+to gain further insight into which CoreSC class decisions were responsible for
 the paper type predictions. This was a very large tree, with a depth of 37
@@
 indicates a Correspondence paper. 28 out of the 31 Correspondence papers were
-correctly labelled by this decision  classified by this decision as
-Correspondence were correctly labelled.
+correctly classified by this decision.
 

### 2013-08-25 doc/bcspaper/article.tex
Made some changes as requested by SGAI paper administrator

@@
 \title*{Partridge: An effective system for the automatic classification of the types of academic papers}
-\titlerunning{Partridge: classifying academic papers}
+\titlerunning{Partridge: A system for classification of academic papers}
 % Use \titlerunning{Short Title} for an abbreviated version of
@@
 
-\subsection*{Collection of scientific articles} 
+\subsection{Collection of scientific articles} 
 Partridge allows users to upload any paper which is free of copyright
@@
 \centering
-\includegraphics[width=0.75\textwidth]{figures/corescs.png}
-\caption{The CoreSC content of a research paper (left) and a review paper (right) randomly selected from the corpus}
+\includegraphics[width=\textwidth]{figures/corescs.png}
+\caption{The CoreSC content of a research paper (top) and a review paper (bottom) randomly selected from the corpus}
 \label{fig:coresc_pies} 
@@
 
-\subsection*{Paper Processing and Classification}
+\subsection{Paper Processing and Classification}
 %Discuss in more detail how Partridge processes papers (PDFX, sentence splitting)
@@
 on a super class consisting of the previous three categories,
-performance was improved overall with the following F-measures:
+performance was improved overall with the following F-measures:\\
 {\bf OpinionSuper: 59, Research: 67.6, Review: 63.7, Essay: 44.9,
@@
 
-\bibliographystyle{acm}
+\bibliographystyle{spphys}
 \bibliography{partridge}

### 2013-08-29 doc/bcspaper/article.tex
Made further required changes for bcs sgai submission

@@
 \includegraphics[width=\textwidth]{figures/corescs.png}
-\caption{The CoreSC content of a research paper (top) and a review paper (bottom) randomly selected from the corpus}
+\caption{The CoreSC makeup of a research paper and a review paper randomly selected from the corpus}
 \label{fig:coresc_pies} 
@@
 on a super class consisting of the previous three categories,
-performance was improved overall with the following F-measures:\\
-{\bf OpinionSuper: 59, Research: 67.6, Review: 63.7, Essay: 44.9,
-Correspondence: 46 and Case Study 24.8}.
+performance was improved overall with the following F-measures:
+OpinionSuper: 59, Research: 67.6, Review: 63.7, Essay: 44.9,
+Correspondence: 46 and Case Study 24.8.
 

### 2013-08-29 partridge/tools/annotate.py
Replaced partridge's sapienta utilities with references to SAPIENTA python packages

@@ -1,247 +1,0 @@
-'''
-
-Take a known, split paper and annotate it using Sapienta remotely
-
-'''
-import sys
-import os
-import pycurl
-import codecs
-import subprocess
-import tempfile
-import logging
-from urllib import urlencode
-
-#from sapienta.docparser import SciXML
-#from sapienta.crf import Tagger
-
-from partridge.config import config
-
-from progressbar import ProgressBar
-from xml.dom import minidom
-
-from partridge.config import config
-
-from curlutil import CURLUploader
-
-from collections import Counter
-
-SAPIENTA_URL="http://www.ebi.ac.uk/Rebholz-srv/sapienta/CoreSCWeb/submitRPC"
-
-MODEL_PATH = str(os.path.join(config['MODELS_DIR'], "a.model"))
-
-class SapientaException(Exception):
-    pass
-
-
-class BaseAnnotator(object):
-    """Basic annotator with some boilerplate stuff in it"""
-
-    def _annotateXML(self, labels):
-        """Read in the xml document and add labels to it
-        """
-
-        c = Counter()
-
-        for s in self.doc.getElementsByTagName("s"):
-            if s.parentNode.localName == "article-title": continue 
-
-            label = labels.pop(0)
-
-            c[label] += 1
-
-            annoEl = self.doc.createElement("CoreSc1")
-            annoEl.setAttribute("type", label)
-            annoEl.setAttribute("conceptID", label + str(c[label]))
-            annoEl.setAttribute("novelty", "None")
-            annoEl.setAttribute("advantage","None")
-
-            s.insertBefore(annoEl, s.firstChild)
-
-
-    def __upgradeXML(self):
-        """When passed in an old annotation format doc, upgrade the format
-        
-        This method takes an XML document and replaces old fashioned 
-        annotationART style elements with the new CoreSC style.
-        """
-
-        for annoEl in self.doc.getElementsByTagName("annotationART"):
-            sentEl = annoEl.parentNode
-
-            #remove annotation element from tree
-            sentEl.removeChild(annoEl)
-
-            #create the CoreSC element
-            coreEl = self.doc.createElement("CoreSc1")
-
-
-            for key in ['type', 'advantage', 'conceptID', 'novelty']:
-                coreEl.setAttribute(key, annoEl.getAttribute(key))
-
-            for child in annoEl.childNodes:
-                sentEl.appendChild(child.cloneNode(True))
-                child.unlink()
-
-            sentEl.insertBefore( coreEl, sentEl.firstChild)
[…]

### 2013-08-29 partridge/tools/converter.py

@@ -1,59 +1,0 @@
-'''
-Library for converting PDF to minimal sapienta xml
-
-'''
-
-import os
-import pycurl
-import codecs
-
-from xml.dom import minidom
-from nltk.tokenize import word_tokenize, sent_tokenize
-
-from curlutil import CURLUploader
-
-PDFX_URL = "http://pdfx.cs.man.ac.uk"
-
-class PDFXConverter(CURLUploader):
-
-    nextSID = 1
-
-    #-------------------------------------------------------------------------
-    def convert(self, filename, outfile):
-
-       c = pycurl.Curl()
-
-       pdfsize = os.path.getsize(filename)
-
-       header = ["Content-Type: application/pdf", 
-            "Content-length: " + str(pdfsize)] 
-       
-       f = open(filename, 'rb')
-       c.setopt(pycurl.URL, PDFX_URL)
-       c.setopt(pycurl.HTTPHEADER, header)
-       c.setopt(pycurl.FOLLOWLOCATION, True)
-       c.setopt(pycurl.POST, 1)
-       c.setopt(pycurl.INFILE, f)
-       c.setopt(pycurl.INFILESIZE, pdfsize)
-       
-       print "Uploading %s..." % filename
-
-       self.perform(c, pdfsize)
-
-       f.close()
-
-       print "Saving XML from %s..." %filename
-       
-       self.indoc = minidom.parseString(self.result)
-
-
-
-       print "Writing result to %s" % outfile
-       #write resulting xml file
-       with codecs.open(outfile,'w', encoding='utf-8') as f:
-            self.indoc.writexml(f)
-                        
-     
-
-    
- 

### 2013-08-29 partridge/tools/sapienta/crf.py

@@ -1,168 +1,0 @@
-from __future__ import division
-'''
-Created on 7 Mar 2012
-
-@author: grabmuel
-'''
-
-import crfsuite
-import sys
-from candc import SoapClient
-import unicodedata
-from docparser import SciXML
-import os
-import logging
-import pdb
-
-logging.basicConfig()
-logger = logging.getLogger('crf')
-logger.setLevel(logging.INFO)
-
-class AttributeGenerator:
-    
-    @staticmethod
-    def createUnicodeAttribute(uni):
-        ascii = unicodedata.normalize('NFKD', uni).encode('ascii', 'ignore')
-        return crfsuite.Attribute(ascii)
-    
-    @staticmethod
-    def yieldCandcAttributes(candcFeatures):
-        for label, ngrams in {'unigram':candcFeatures.unigrams, 'bigram':candcFeatures.bigrams, 'trigram':candcFeatures.trigrams}.items():
-            for ngram in ngrams:
-                if isinstance(ngram, tuple):
-                    ngram = '|'.join(ngram)
-                field = '%s=%s' % (label, ngram)
-                yield AttributeGenerator.createUnicodeAttribute(field)
-                
-        for verb in candcFeatures.verbs:
-            field = 'verb=' + verb
-            yield AttributeGenerator.createUnicodeAttribute(field)
-            
-        for verbClass in candcFeatures.verbClasses:
-            field = 'verbclass=' + verbClass
-            yield AttributeGenerator.createUnicodeAttribute(field)
-            
-        for verbPos in candcFeatures.verbsPos:
-            field = 'verbPos=' + verbPos
-            yield AttributeGenerator.createUnicodeAttribute(field)
-        
-        if candcFeatures.passive:
-            field = u'passive=yes' 
-        else:
-            field = u'passive=no'
-        yield AttributeGenerator.createUnicodeAttribute(field)
-            
-        for triple in candcFeatures.relationTriples:
-            field = 'triple=' + '|'.join(triple)
-            yield AttributeGenerator.createUnicodeAttribute(field)
-            
-        for relation, targets in candcFeatures.relationMap.items():
-            for target in targets:
-                field = '%s=%s' % (unicode(relation), target)
-                yield AttributeGenerator.createUnicodeAttribute(field)
-                
-    @staticmethod
-    def yieldPositionAttributes(sentence):
-        for variable, value in vars(sentence).items():
-            if variable not in ('corescLabel', 'content'):
[…]

### 2013-08-29 partridge/tools/sapienta/docencoding.py

@@ -1,31 +1,0 @@
-'''
-Created on 26 Mar 2012
-
-@author: grabmuel
-'''
-import os
-from os.path import join, split
-
-
-sourceDirs = [
-              '/nfs/research2/textmining/sapienta/Project/Development/Sapient2/corpora/TierA',
-              '/nfs/research2/textmining/sapienta/Project/Development/Sapient2/corpora/TierB'
-              ]
-targetRoot = '/nfs/research2/textmining/grabmuel/coresc_corpus'
-
-for sourceDir in sourceDirs:
-    targetDir = join(targetRoot, split(sourceDir)[1])
-    try:
-        os.makedirs(targetDir)
-    except OSError:
-        pass # directory already exists
-    
-    files = [f for f in os.listdir(sourceDir) if f.endswith('.xml') and not f.startswith('.')]
-    for f in files:
-        targetFile = open(join(targetDir, f), 'w')
-        for line in open(join(sourceDir, f)):
-            if line == '<?xml version="1.0"?>\n':
-                targetFile.write('<?xml version="1.0" encoding="ISO-8859-1"?>\n')
-            else:
-                targetFile.write(line) 
-        targetFile.close()

### 2013-08-29 partridge/tools/sapienta/docparser.py

@@ -1,389 +1,0 @@
-from __future__ import division
-'''
-Created on 12 Mar 2012
-
-@author: grabmuel
-'''
-
-import xml.parsers.expat
-import unittest
-import math
-
-class Document:
-    def __init__(self):
-        self.headers = []
-        self.numSentencesTotal = 0
-        self.hightesWordCount = 0
-        
-    def setHighestWordCount(self, sentence):
-        numWords = len(sentence.content.split(' '))
-        if numWords > self.hightesWordCount:
-            self.hightesWordCount = numWords
-        
-    def addHeader(self, header):
-        self.headers.append(header)
-        
-    def getAbsoluteSentenceLocation(self, sentCountDoc):
-        '''
-        Calculate the 'Absolute Location' feature of a sentence.
-        
-        TODO: READ TEUFEL 2000
-        '''
-        norm = sentCountDoc / (self.numSentencesTotal + 0.1)
-        charNum = int(math.floor(norm * 10)) + 65
-        letter = chr(charNum)
-        return letter
-    
-    def getHeaderId(self, headerIndex):
-        '''
-        Calculate the 'SectionId' feature of a section.
-        Simply return the header/section number, starting from 1, maximum value is 10.
-        '''
-        paragraphNumber = headerIndex + 1
-        if paragraphNumber > 10:
-            return 10
-        else:
-            return paragraphNumber
-        
-    def getSentenceLength(self, sentence):
-        '''
-        Caclualte the 'Length' feature of a sentence.
-        TODO: get proper specification
-        For now split into 10 equal partitions (A-J), scaled to using the longest 
-        sentence in the document.
-        '''
-        numWords = len(sentence.content.split(' ')) #move to function
-        norm = numWords / (self.hightesWordCount + 0.1)
-        charNum = int(math.floor(norm * 10)) + 65
-        letter = chr(charNum)
-        return letter
-    
-    def getCorescLabels(self):
-        for header in self.headers:
-            for para in header.paragraphs:
-                for sent in para.sentences:
-                    yield sent.corescLabel
-            
-    def yieldSentences(self):
-        for header in self.headers:
-            for para in header.paragraphs:
-                for sentence in para.sentences:
-                    self.numSentencesTotal += 1
-                    self.setHighestWordCount(sentence)
-                    header.numSentencesInHeader += 1
-                    
-        sentCountDoc = 0
-        for headerIndex, header in enumerate(self.headers):
-            sentCountHeader = 0
-            headerId = self.getHeaderId(headerIndex)
[…]

### 2013-08-29 partridge/tools/sapienta/evaluation.py

@@ -1,206 +1,0 @@
-from __future__ import division
-from candc import SoapClient
-from crf import Tagger, AttributeGenerator, Trainer
-from docparser import SciXML
-import cPickle
-import crfsuite
-import logging
-import os
-import pdb
-import csv
-'''
-Created on 18 Apr 2012
-
-@author: grabmuel
-'''
-
-logging.basicConfig()
-logger = logging.getLogger('evaluation')
-logger.setLevel(logging.INFO)
-
-class Evaluation:
-    
-    def __init__(self):
-        self.tagger = Tagger('/nfs/research2/textmining/grabmuel/aho/coresc/crfsuite/a.model')
-        self.dirs = [ '/nfs/research2/textmining/grabmuel/coresc_corpus/combined' ]        
-
-    def evaluateFile(self, path):
-        logger.info('generating features for %s', path)
-        parser = SciXML()
-        doc = parser.parse(path)
-        trueLabels = list(doc.getCorescLabels())
-        #pdb.set_trace()
-        
-        predictedLabels, probabilities = self.tagger.getSentenceLabelsWithProbabilities(doc)
-        self.calcPrecRecall(trueLabels, predictedLabels, probabilities)
-        
-    def pickleSentences(self):
-        candcClient = SoapClient()
-        
-        for directory in self.dirs:
-            outputPath = os.path.join(directory, 'pickled_M')
-            files = [f for f in os.listdir(directory) if f.endswith('.xml') and not f.startswith('.')]
-            #files = ['b412883d_mode2.Kamran.xml']
-            for f in files:
-                logger.info("pickling %s", f)
-                parser = SciXML() # this is where I want to put PMC parser if I use that instead
-                doc = parser.parse(os.path.join(directory, f))
-                
-                processedSentences = []
-                for sentence in doc.yieldSentences():
-                    candcFeatures = candcClient.getFeatures(sentence.content)
-                    sentence.candcFeatures = candcFeatures
-                    processedSentences.append(sentence)
-                with open(os.path.join(outputPath, f), 'wb') as pickleFile:
-                    cPickle.dump(processedSentences, pickleFile, -1)
-                    
-    def partitionFiles(self, numBlocks):
-        folds = [[] for i in range(numBlocks)] 
-        for directory in self.dirs:
-            directory = os.path.join(directory, 'pickled')
-            files = os.listdir(directory)
-            for i, f in enumerate(files):
-                path = os.path.join(directory, f)
-                folds[i % numBlocks].append(path)
-        return folds
-
[…]

### 2013-08-29 partridge/tools/sapienta/testreliability.py

@@ -1,66 +1,0 @@
-from crf import runTagger
-import os
-import sys
-
-from xml.dom import minidom
-
-PAPER_PATH = "/home/james/tmp/corpus/combined"
-
-total = 0
-correct = 0
-wrong = 0
-
-for root, dirs, files in os.walk(PAPER_PATH):
-    
-
-    for file in files:
-    
-        sentConcepts = {}
-
-        path = os.path.join(root, file)
-
-        print "Processing file %s " % path
-
-        with open(path,'rb') as f:
-            doc = minidom.parse(f)
-
-        for sEl in doc.getElementsByTagName("s"):
-            sid = sEl.getAttribute("sid") 
-
-            #now get the coresc
-            l = sEl.getElementsByTagName("annotationART")
-
-            if(len(l) < 1):
-                l = sEl.getElementsByTagName("CoreSc1")
-
-            if(len(l) > 0):
-                concept = l[0].getAttribute("type")
-
-                sentConcepts[ sid ] = concept
-
-        print "Found %d sentences" % len(sentConcepts)
-        print "Running tagger"
-
-        #now lets do the tagging and get back each sentence
-        labels = runTagger(path)
-
-        for id, type in labels:
-            
-            if sentConcepts.has_key(id):
-
-                print id
-                
-                if sentConcepts[id] == type:
-                    correct += 1
-                else:
-                    wrong += 1
-
-                total += 1
-
-        corrpercent = (correct * 100) / total
-        wrongpercent = (wrong * 100) / total
-
-        print "Total sentences analysed %d" % total
-        print "total correct %d (%d%%)" % (correct, corrpercent)
-        print "total wrong %d (%d%%)" % (wrong, wrongpercent)
-

### 2013-08-29 partridge/tools/split.py

@@ -1,188 +1,0 @@
-'''
-Module for splitting sentences on articles that need splitting
-'''
-import codecs
-import logging
-import cPickle
-import os
-import sys
-import locale
-
-from nltk.tokenize.punkt import PunktSentenceTokenizer
-
-from xml.dom import minidom
-from sets import Set
-
-from text_sentence import Tokenizer
-
-from partridge.config import config
-
-sys.stdout = codecs.getwriter('utf8')(sys.stdout)
-
-blacklist = set(['journal-id', 'journal-meta','article-id','article-categories'
-'contrib','contrib-group', 'aff','pub-date','volume','issue','elocation-id',
-'history','author-notes', 'copyright-statement', 'funding-group',
-'copyright-year','counts','s', 'subj-group','author-notes', 'alt-title',
-'title','ref-list','ack','meta','permissions', 'custom-meta-group',
-'responseDate','request','header', 'xref', 'object-id'])
-
-class SentenceSplitter:
-    '''XML Aware sentence splitter for Partridge
-    '''
-
-    def __init__(self):
-        self.nextSID = 1
-        self.tokenizer = Tokenizer()
-        self.inSentence = False
-
-    def split(self, filename, outfile):
-
-        #read the document
-        with open(filename, 'rb') as f:
-            self.indoc = minidom.parse(f)
-
-
-        logging.debug("Parsed input file %s " % filename)
-
-        # check for existence of multiple s elements, possibly skip
-        # actually splitting things
-        if(len(self.indoc.getElementsByTagName("s")) > 0):
-            logging.debug("Skipped splitting document... already split!")
-        else:
-            #make sure there is an abstract or else create one
-            
-            if ( (len(self.indoc.getElementsByTagName("abstract")) < 1 ) &
-            (len(self.indoc.getElementsByTagName("ABSTRACT")) < 1) ):
-                #add abstract to paper
-                self.addDummyAbstract()
-
-
-            #do the annotating
-            self.splitElement(self.indoc)
-            
-            #allocate the sentence IDs
-            self.allocateSIDs()
-
-        with codecs.open(outfile,'w', encoding='utf-8') as f:
-            self.indoc.writexml(f)
-
-    def addDummyAbstract(self):
-        """If no abstract is found, insert one"""
-
-        dummytext = "No abstract available for this paper"
-
-        logging.info("Adding dummy abstract...")
-
-        if(len(self.indoc.getElementsByTagName("TITLE")) > 0):
[…]

### 2013-08-30 partridge/tools/papertype.py
Implemented more advanced paper type classifier from BCS SGAI paper research

@@ -110,29 +110,34 @@ if __name__ == "__main__":
 
     if(options.all):
         print "ignoring ID arguments and retrieving all papers"
-        papers = Paper.query.all()
+        q = Paper.query
     else:
         print "Retrieving papers with IDs in %s" % args
-        papers = Paper.query.filter(Paper.id.in_(args)).all()
+        q= Paper.query.filter(Paper.id.in_(args))
 
-    for p in papers:
+    offset = 0
+    limit = 50
 
-        if( p.type != None ):
-            print "Skipping paper %s" % p.title
-            continue
+
+    while q.offset(offset).limit(limit).count() > 0:
+
+        print "Downloading batch of %d papers..." % limit
+
+        for p in q.offset(offset).limit(limit).all():
+            
+            print p.title
+            for author in p.authors:
+                print "\t\t" + author.surname
+
+            cls = str(c.classify_paper(p))
+            
+            print "Predicted Class:" + cls
+
+            print "Saving paper type in database"
+            p.type = cls
+            db.session.merge(p)
         
-        print p.title
-        for author in p.authors:
-            print "\t\t" + author.surname
+        #commit the database session at the end of the run
+        db.session.commit()
 
-        cls = str(c.classify_paper(p))
-        
-        print "Predicted Class:" + cls
-
-        print "Saving paper type in database"
-        p.type = cls
-        db.session.merge(p)
-    
-    #commit the database session at the end of the run
-    db.session.commit()
-
+        offset += limit

### 2013-08-30 partridge/views/query.py

@@ -5,8 +5,7 @@ from flask import render_template,request,jsonify
 from partridge.views import frontend
 
 from partridge.models import db
-from partridge.models.doc import Paper,Sentence,Author, C_ABRV, PAPER_TYPES
-
+from partridge.models.doc import Paper,Sentence,Author, C_ABRV
 from sqlalchemy import func, or_, and_
 
 PAGE_LIMIT = 10
@@ -20,9 +19,10 @@ def query():
 
     papercount = Paper.query.count()
 
+    PAPER_TYPES = [str(x[0]) for x in db.session.query(Paper.type).distinct().all()]
+
     #do paper counts for all paper types
     paper_types = {x:Paper.query.filter(Paper.type == x).count() for x in PAPER_TYPES}
-
 
     if(searchterms != ''):
 
@@ -42,8 +42,6 @@ def query():
         paper_q = pq.get_query()
 
         papers = paper_q.limit(PAGE_LIMIT).offset(offset).all()
-
-        print len(paper_q.all())
 
         return jsonify(html=render_template("query_result.html",
             papers=papers), total=paper_q.count(), count=len(papers))
